---
title: "Untitled"
author: "Spyros"
date: "19/9/2018"
output: html_document
---


Import Workspace 
Workspace contains a big Seurat object with all cells
In the future, remove this part. Make one data import script that dowloads from gDrive 
```{r}
#rm(list=ls())
# load("/myVolume/Analysis_remote/R_objects/04_main_seurat_subset_181102.RData")
load("/myVolume/sclung_adeno/rawdata/04_main_seurat_subset_190128.RData")
ls()
```

Table of immune/non-immune cells 
```{r}
table(tiss_subset@meta.data$immune_annotation)
```

Subset Seurat object to cells annotated as immune 
```{r}
# Get cell names 
cells.use <- row.names(tiss_subset@meta.data)[which(tiss_subset@meta.data$immune_annotation=="immune")]
# Subset Seurat object 
tiss_subset_immune <- SubsetData(tiss_subset, cells.use = cells.use)
# How many immune cells ? 
length(cells.use)
```

Import TCR metadata and merge with immune cell Seurat object 
# Not Updated to the latest TCR output 
```{r}
require(dplyr)
tcr_output <- read.csv("/myVolume/sclung_adeno/TCR_analysis/filtered_TCRAB_summary/cell_data.csv")
# Change cell_name to cell_ID 
colnames(tcr_output)[grep("cell_name", colnames(tcr_output))] <- "cell_id"
# Join metadata with TCR metadata 
meta_new <- left_join(x = tiss_subset_immune@meta.data, y = tcr_output, by = "cell_id")
row.names(meta_new) <- row.names(tiss_subset_immune@meta.data)
# Add updated metadata (containing TCR info) to the Seurat obect 
tiss_subset_immune@meta.data <- meta_new
```

Save immune cell workspace 
```{r}
save(tiss_subset_immune, file = "/myVolume/sclung_adeno/R_objects/04_main_seurat_subset_190128_IMMUNE.RData")
```

Find variable genes
```{r}
tiss_subset_immune <- FindVariableGenes(object = tiss_subset_immune, do.plot = TRUE, x.high.cutoff = Inf, y.cutoff = 1, num.bin = 20, 
                                          binning.method = "equal_width", do.recalc = T, x.low.cutoff=1)
# Selction vector 
sel.vec <- row.names(tiss_subset_immune@data) %in% tiss_subset_immune@var.genes
table(sel.vec)
# Create color vector 
col.vec <- rep("black", nrow(tiss_subset_immune@data))
col.vec[sel.vec] <- "red"
# Plot 
# par(mfcol=c(2,1))
# plot(tiss_subset_immune@hvg.info$gene.mean, tiss_subset_immune@hvg.info$gene.dispersion.scaled, 
#      pch=19, col=alpha(col.vec,0.2),cex=0.5)
# plot(tiss_subset_immune@hvg.info$gene.mean[sel.vec], tiss_subset_immune@hvg.info$gene.dispersion.scaled[sel.vec], 
#      pch=19, col=alpha("red", 0.2),cex=0.5)
```

Perform PCA
```{r}
tiss_subset_immune <- RunPCA(object = tiss_subset_immune, do.print = FALSE)
tiss_subset_immune <- ProjectPCA(object = tiss_subset_immune, do.print = FALSE)
```

Visualize top genes across principal components
```{r}
PCHeatmap(object = tiss_subset_immune, pc.use = 1:15, cells.use = 100, do.balanced = TRUE, label.columns = FALSE, num.genes = 10)
```

Perform correlation of PCs and metadata fields
```{r}
require(corrplot)
pca.obj <- tiss_subset_immune@dr$pca
pc.coords <- pca.obj@cell.embeddings
df1 <- tiss_subset_immune@meta.data[,c("nGene","nReads","percent.ribo")]
df2 <- pc.coords[,c(1:10)]
cordf12 <- cor(df1,df2)
# Make a correlation plot
corrplot(cordf12, method = "number", main="Correlation of PCs and metadata")
```

Also visaulize PC variance
```{r}
#comp.dev <-pca.obj@sdev
PCElbowPlot(object = tiss_subset_immune)
```
Plot a few of the principal components 
```{r}
require(GGally)
require(reshape)
temp <- tiss_subset_immune@dr$pca@cell.embeddings
temp <- as.data.frame(temp)
names <- colnames(temp)
temp <- cbind(temp, tiss_subset_immune@meta.data$general_annotation)
colnames(temp) <- c(names, "general.annotation")
pca.scatter = ggpairs(data=temp,
             columns=1:10, 
             upper = list(continuous = "points"),
             lower = list(combo = "na"),
             mapping=ggplot2::aes(colour = general.annotation), legend = 2) + theme(legend.position = "bottom")
ggsave(plot = pca.scatter, filename = "/myVolume/sclung_adeno/immune_cell_analysis/plot_out/I01/Immune_cells_PCA_scatterplots_largefile.pdf",width = 15, height = 12)
```


```{r}
tiss_subset_immune <- JackStraw(tiss_subset_immune, num.replicate = 100, num.cores = 15, do.par = T)
JackStrawPlot(object = tiss_subset_immune, PCs = 1:20)
```

Choose the number of principal components to use.
```{r}
n.pcs = 20
```

Set resolution and perform clustering
```{r}
res.used <- 0.3
tiss_subset_immune <- FindClusters(object = tiss_subset_immune, reduction.type = "pca", dims.use = 1:n.pcs, 
    resolution = res.used, print.output = 0, save.SNN = TRUE, k.param = 10)
```

Perform  tSNE
```{r}
tiss_subset_immune <- RunTSNE(object = tiss_subset_immune, dims.use = 1:n.pcs, seed.use = 10, perplexity=30)
```

Visualize TSNE colored by cluster
```{r}
# note that you can set do.label=T to help label individual clusters
TSNEPlot(object = tiss_subset_immune, do.label = T)
```

Visualize TSNE metadata field
```{r}
# note that you can set do.label=T to help label individual clusters
TSNEPlot(object = tiss_subset_immune, do.label = F, group.by = "driver_gene")
```

Visualize TSNE metadata field
```{r}
# note that you can set do.label=T to help label individual clusters
TSNEPlot(object = tiss_subset_immune, do.label = F, group.by = "patient_id")
```

Find markers for each cluster
```{r}
tiss.markers.immune <- FindAllMarkers(object = tiss_subset_immune, only.pos = TRUE, min.pct = 0.25, thresh.use = 0.25, 
                                      do.print=T)
```


Write differential gene table
```{r}
write.table(tiss.markers.immune, file="/myVolume/sclung_adeno/immune_cell_analysis/data_out/Immune_cells_DE_genes_among_Seurat_clusters.csv")
#tiss.markers.immune <- read.csv("/myVolume/sclung_adeno/immune_cell_analysis/data_out/181102_Differentially_expressed_genes_all_immune_cells.csv", header=T, sep=" ")
```

Save image 
```{r}
#load("/myVolume/Analysis_remote/R_objects/04_tiss_subset_181022_IMMUNE.RData")
# save(tiss_subset_immune, file = "/myVolume/sclung_adeno/R_objects/04_main_seurat_subset_190128.RData")
```

Display the top markers you computed above.
```{r}
require(tidyverse)
tiss.markers.immune %>% group_by(cluster) %>% top_n(5, avg_logFC)
```

Short list of genes (top5) per cluster
```{r}
markers.small  <- tiss.markers.immune %>% group_by(cluster) %>% top_n(5, avg_logFC)
genes_to_check <- unique(markers.small$gene)
```

Create plot pdf bundle
```{r}
pdf("/myVolume/sclung_adeno/immune_cell_analysis/plot_out/I01/Immune_cells_first_annotation_plots.pdf",10,10)
# Plot TSNEs with different annotations 
TSNEPlot(object = tiss_subset_immune, do.label = T)
TSNEPlot(object = tiss_subset_immune, do.label = F, group.by = "driver_gene")
TSNEPlot(object = tiss_subset_immune, do.label = F, group.by = "patient_id")
# Create Dotplot 
DotPlot(tiss_subset_immune, genes_to_check, x.lab.rot = T)
DoHeatmap(tiss_subset_immune,genes.use =  genes_to_check, cex.col = 0.1, cex.row = 5)
# Barplot of patients per cluster 
tab1 <- cbind(as.data.frame(tiss_subset_immune@meta.data$patient_id),as.data.frame(tiss_subset_immune@meta.data$res.0.3))
colnames(tab1) <- c("Patient", "Immune.cluster")
ggplot(tab1) +
  aes(x = Immune.cluster, fill = factor(Patient)) +
  geom_bar(position = "fill")
dev.off()
# 
```

Plot individualy
Dotplot of top N DE expressed genes 
```{r}
Ngenes <- 5
markers.small  <- tiss.markers.immune %>% group_by(cluster) %>% top_n(Ngenes, avg_logFC)
genes_to_check <- unique(markers.small$gene)
# Create Dotplot 
DotPlot(tiss_subset_immune, genes_to_check, x.lab.rot = T)
```

Plot individualy
Heatmap of top N DE expressed genes 
```{r}
Ngenes <- 5
markers.small  <- tiss.markers.immune %>% group_by(cluster) %>% top_n(Ngenes, avg_logFC)
genes_to_check <- unique(markers.small$gene)
# Create Heatmap
DoHeatmap(tiss_subset_immune,genes.use =  genes_to_check, cex.col = 0.1, cex.row = 5, use.scaled = F, remove.key = T)
```

Plot individualy
Patients per cluster
```{r}
# Barplot of patients per cluster 
tab1 <- cbind(as.data.frame(tiss_subset_immune@meta.data$patient_id),as.data.frame(tiss_subset_immune@meta.data$res.0.3))
colnames(tab1) <- c("Patient", "Immune.cluster")
ggplot(tab1) +
  aes(x = Immune.cluster, fill = factor(Patient)) +
  geom_bar(position = "fill")
```

Calculate and plot average expression of broad cell type specific gene sets 
```{r}
library(ggridges)
library(ggplot2)
# # # 
cell.genes <- read.table("/myVolume/sclung_adeno/immune_cell_analysis/gene_lists/broad_cell_markers_immune.csv", header=T)
cell.types  <- as.character(unique(cell.genes$cell))
tsne.coor <- slot(tiss_subset_immune@dr$tsne, "cell.embeddings")
## 
ggplot.list <- list()
ggplot.list.2 <- list()
# 
rm(temp)
for(i in 1:length(unique(cell.types))){
genes <- as.character(cell.genes$gene[which(cell.genes$cell==cell.types[i])])
gene.exp <- colMeans(as.matrix(tiss_subset_immune@data[genes,]))[row.names(tsne.coor)]
clusters <- tiss_subset_immune@meta.data$res.0.3
# Make ggplot friendly 
temp <- as.data.frame(cbind(tsne.coor, as.data.frame(gene.exp), as.data.frame(clusters)))
# Plot with ggplot 
ggplot.list[[i]] <- ggplot(temp, aes(tSNE_1, tSNE_2)) + 
      geom_point(aes(colour = gene.exp)) + 
      scale_colour_gradient(low = "grey95", high = "red") + 
      labs(title = cell.types[i], subtitle = paste(genes, collapse = ", "))
# Boxplot per cluster 
ggplot.list.2[[i]] <- ggplot(temp, aes(x = clusters, y = gene.exp)) + 
                      geom_boxplot() + 
                      ggtitle(cell.types[i]) + ylab("Average gene expression (log)")
}
# Plot all 
library(gridExtra)
n <- length(ggplot.list)
nCol <- floor(sqrt(n))
# Exzpression on tSNE
pdf("/myVolume/sclung_adeno/immune_cell_analysis/plot_out/I01/Immune_cells_TSNE_with_average_expression_of_cell_markers.pdf",15,15)
do.call("grid.arrange", c(ggplot.list, ncol=nCol))
dev.off()
# Expression per cluster boxplots 
pdf("/myVolume/sclung_adeno/immune_cell_analysis/plot_out/I01/Immune_cells_per_cluster_with_average_expression_of_cell_markers.pdf",15,15)
do.call("grid.arrange", c(ggplot.list.2, ncol=nCol))
dev.off()
```


Annotate cells
```{r}
tiss.markers.immune %>% group_by(cluster) %>% top_n(5, avg_logFC)
# stash current cluster IDs
tiss_subset_immune <- StashIdent(object = tiss_subset_immune, save.name = "immune.subcluster.ids")
# enumerate current cluster IDs and the labels for them
cluster.ids <- c(0:16)
# Annotate each of the clusters 
# free_annotation <- c("0","1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "17", "18")
free_annotation <- c("Myeloid","T-cells", "T-cells", "Myeloid", "B-cells-PB", 
                     "Neutrophils", "T-cells", "B-cells-M", "Myeloid", "Dendritic", 
                     "Mast", "NK-cells", "pDCs", "T-cells", 
                     "Dendritic", "Myeloid", "Myeloid")
# Map free annotation to cluster numbers and store as immune_subtype_annotation
tiss_subset_immune@meta.data[,'immune_subtype_annotation'] <- plyr::mapvalues(x = tiss_subset_immune@meta.data$immune.subcluster.ids, from = cluster.ids, to = free_annotation)
# Plot 
pdf("/myVolume/sclung_adeno/immune_cell_analysis/plot_out/I01/Immune_cells_free_annotation_on_TSNE.pdf",10,10)
TSNEPlot(object = tiss_subset_immune, do.label = TRUE, pt.size = 0.5, group.by='immune_subtype_annotation', label.size = 6)
TSNEPlot(object = tiss_subset_immune, do.label = F, pt.size = 0.5, group.by='immune_subtype_annotation', label.size = 6)
dev.off()
```
# Barplot of all immune cell counts 
```{r}
table.temp <- as.data.frame(table(tiss_subset_immune@meta.data$immune_subtype_annotation))
p <-  ggplot(data=table.temp, aes(x=Var1, y=Freq)) +
      geom_bar(stat="identity") + coord_flip()
ggsave("/myVolume/sclung_adeno/immune_cell_analysis/plot_out/I01/Immune_cell_counts.pdf", width = 10, height = 7)
```

Write annotations of immune cells to tiss_subset (which is the master object containing all cells)
```{r}
# Add column epithelial_annotation_lvl_1 to tiss_subset
tiss_subset@meta.data[,"immune_subtype_annotation"] <- NA
# Add annotations 
for(i in 1:nrow(tiss_subset_immune@meta.data)){
  cell <- row.names(tiss_subset_immune@meta.data)[i]
  a <- which(row.names(tiss_subset@meta.data)==cell)
  tiss_subset@meta.data[a,"immune_subtype_annotation"] <- tiss_subset_immune@meta.data$immune_subtype_annotation[i]
}
```

Save immune cell workspace as well as updated main workspace 
```{r}
save(tiss_subset_immune, file = "/myVolume/sclung_adeno/R_objects/04_tiss_subset_190128_IMMUNE.RData")
save(tiss_subset, file = "/myVolume/sclung_adeno/R_objects/04_main_seurat_subset_190128_immune_annotated.RData")
```
