---
title: "CPBD wrap up and plotting"
output: html_document
---

Load immune workspace
```{r}
rm(list=ls())
dir <- "/myVolume/scell_lung_adenocarcinoma/"
load(file=paste(dir,"Data_input/Immuune_Seurat_object.RData", sep=""))
```

Subset Lung cells 
```{r}
cells <- row.names(tiss_immune@meta.data)[which(tiss_immune@meta.data$biopsy_site == "Lung")]
length(cells)
tiss_immune_lung <- SubsetData(object = tiss_immune, cells.use = cells)
```

Table of all immune cells
```{r}
ann_all <- as.character(tiss_immune_lung@meta.data$immune_subtype_annotation)
table(ann_all)
```

Combine in one table with response to treatment 
```{r}
meta.temp <- cbind(as.data.frame(tiss_immune_lung@meta.data$analysis), as.data.frame(ann_all))
# Rename columns 
colnames(meta.temp) <- c("analysis", "annotation")
# Add row names 
row.names(meta.temp) <- row.names(tiss_immune_lung@meta.data)
```

# Collapse cell types 
```{r}
meta.temp$annotation <- as.character(meta.temp$annotation)
meta.temp[grep("B-cells", meta.temp$annotation),"annotation"] <- "B-cells"
meta.temp[grep("pDCs", meta.temp$annotation),"annotation"] <- "Dendritic"
meta.temp$annotation <- as.character(meta.temp$annotation)
table(meta.temp$annotation)
```

Plot table of cell types across treatment response groups 
```{r}
require(gplots)
tab1 <- table(meta.temp$analysis, meta.temp$annotation)
balloonplot(tab1, main ="Response vs Annotation", xlab ="", ylab="",
            label = T, show.margins = F)
```

Convert gene names to ensembl gene ids
```{r}
library('biomaRt')
library('Biobase')
# Convert to Ensembl
mart <- useDataset("hsapiens_gene_ensembl", useMart("ensembl"))
# Subset data 
data.pro <- as.matrix(tiss_immune_lung@data[,row.names(meta.temp)])
# Subset gene names 
genes <- as.character(row.names(data.pro))
G_list <- getBM(filters= "hgnc_symbol", attributes= c("ensembl_gene_id",
"entrezgene", "hgnc_symbol"),values=genes,mart= mart)
# Filter unique
G_list <- G_list[isUnique(G_list$hgnc_symbol),]
data.pro <- data.pro[G_list$hgnc_symbol,]
row.names(data.pro) <- G_list$ensembl_gene_id
```
  
Export metadata and normalized data for each group 
```{r}
string <- "/myVolume/scell_lung_adenocarcinoma/interaction_analysis/data/in/"
groups <- unique(meta.temp$analysis)
for(i in 1:length(groups)){
  cells <- row.names(meta.temp)[which(meta.temp$analysis==groups[i])]
  data.exp <- data.pro[,cells]
  # Keep only unique genes 
  data.exp <- data.exp[row.names(data.exp)[which(isUnique(row.names(data.exp))==T)],]
  meta.exp <- meta.temp[cells,]
  # Fix metadata format (IF not containing multiple fields)
  cell_type <- meta.exp$annotation
  unique(cell_type)
  # Combine 
  df.m <- cbind(as.data.frame(row.names(meta.exp)), as.data.frame(cell_type))
  colnames(df.m) <- c("Cell", "cell_type")
  write.table(x = df.m, file = paste(string,groups[i],"_CPDB_meta_collapsed.txt", sep=""), sep = "\t", 
              quote = FALSE, row.names = F)
  # write.table(x = df[1:50,], file = paste(string,groups[i],"_CPDB_meta_collapsed_SHORT.txt", sep=""), sep = "\t",
  #             quote = FALSE, row.names = F)
  # Process counts and convert to Ensembl IDs
  df.c <- as.data.frame(cbind(as.data.frame(row.names(data.exp)), as.data.frame(data.exp)))
  colnames(df.c) <- c("Gene", colnames(data.exp))
  write.table(x = df.c, file = paste(string,groups[i],"_CPDB_counts_collapsed.txt", sep=""), 
              sep = "\t", row.names = F, quote = FALSE)
  # write.table(x = df[,1:51], file = paste(string,groups[i],"_CPDB_counts_collapsed_SHORT.txt", sep=""),
  #             sep = "\t", row.names = F, quote = FALSE)
}
```

Process data through the CPDB pipeline.
That part is done as part of a python package 
```{r}
# For example
### Activate venv 
# source cpdb-venv/bin/activate
# Run script in scripts/main_CPDB_script.sh
```

Parse CPDB outputs 
```{r}
dir <- "/myVolume/scell_lung_adenocarcinoma/"
# Create list to store results 
list_counts_symmetric <- list()
# Imoprt separate significant_means output files 
# NAIVE
baseline.sig.means <- read.table(paste(dir,"interaction_analysis/data/out/NAIVE/significant_means.txt", sep=""), sep = "\t", header=T)
# Replace "_" at ending so it doesnt end up in wrong subsetting 
colnames(baseline.sig.means) <- gsub("_IFNG",".IFNG",colnames(baseline.sig.means))
colnames(baseline.sig.means) <- gsub("_PD1",".PD1",colnames(baseline.sig.means))
# PD
pd.sig.means <- read.table(paste(dir,"interaction_analysis/data/out/grouped_PD/significant_means.txt", sep=""), sep = "\t", header=T)
# Replace "_" at ending so it doesnt end up in wrong subsetting 
colnames(pd.sig.means) <- gsub("_IFNG",".IFNG",colnames(pd.sig.means))
colnames(pd.sig.means) <- gsub("_PD1",".PD1",colnames(pd.sig.means))
# PR
pr.sig.means <- read.table(paste(dir,"interaction_analysis/data/out/grouped_PR/significant_means.txt", sep=""), sep = "\t", header=T)
# Replace "_" at ending so it doesnt end up in wrong subsetting 
colnames(pr.sig.means) <- gsub("_IFNG",".IFNG",colnames(pr.sig.means))
colnames(pr.sig.means) <- gsub("_PD1",".PD1",colnames(pr.sig.means))
# Combine to list 
list.sig.means <- list(baseline.sig.means,pr.sig.means,pd.sig.means)
names(list.sig.means) <- c("naive.sig.means", "pr.sig.means", "pd.sig.means")
```

```{r}
# Loop over all sig.mean files 
# REmove any collagen interactions 
list_counts_symmetric <- list()
rm(temp)
for(k in 1:length(list.sig.means)){
  temp <- list.sig.means[[k]]
  message(paste("Number of interacting pairs for ",names(list.sig.means)[k],"is:" ,nrow(temp)))
  # Find and remove collagen interactions 
  a <- grep("COL", as.character(temp$interacting_pair))
  temp <- temp[-a,]
  # REmove those from the original list as well 
  list.sig.means[[k]] <- temp
  message(paste("Number of interacting pairs for ",names(list.sig.means)[k],"without collagen is:" ,nrow(temp)))
  # Count number of significant interactions for each group and convert to n*n table 
  a <- grep("rank", colnames(temp))+1
  b <- ncol(temp)
  sig.means_sub  <- temp[,c(a:b)]  
  rm(temp)
  # Convert NA to 0 
  sig.means_sub[is.na(sig.means_sub)] <- 0
# Count number of non-zero interactions in every column 
sig.means_sub_counts <- apply(sig.means_sub, MARGIN = 2, function(x) length(which(x != 0)))
rm(sig.means_sub)
# Convert to a symmetrical table 
types <- unique(unlist(strsplit(names(sig.means_sub_counts), "_")))
message(paste("Number of cell types for",names(list.sig.means)[k],"is:", length(types))) 
# Create symmetrical table 
table.temp <- matrix(nrow=length(types), ncol=length(types))
row.names(table.temp) <- types
colnames(table.temp) <- types
# Loop over 
for(i in 1:length(sig.means_sub_counts)){
  a <- strsplit(names(sig.means_sub_counts[i]), "_")[[1]][1]
  b <- strsplit(names(sig.means_sub_counts[i]), "_")[[1]][2]
  table.temp[a,b] <- sig.means_sub_counts[i]}
# 
list_counts_symmetric[[k]] <- table.temp
rm(sig.means_sub_counts)
}
names(list_counts_symmetric) <- c("naive", "pr", "pd")
```


Plot a histogram of the number of total interactions per group 
```{r}
melted.temp <- melt(list_counts_symmetric)
p <-  ggplot(melted.temp, aes(x=value, fill=L1, color=L1)) +
      geom_histogram(position="identity", binwidth = 1) +
      facet_grid(L1 ~ .) 
ggsave(plot = p, filename = paste(dir,"plot_out/IM05/Total_number_of_interactions_per_category.pdf", sep=""),width = 10,height = 10)
```

Plot as heatmaps 
```{r}
library(ggplot2)
library(viridis)
# Create list to store plots 
list_ggplots <- list()
# Set range for all graphs 
rng = range(list_counts_symmetric)
# Plot 
for(i in 1:length(list_counts_symmetric)){
melted.temp <- melt(list_counts_symmetric[[i]])
# # Convert 0s to 1s and log 
# melted.temp[melted.temp$value==0,"value"] <- 1
# melted.temp$value <- log10(melted.temp$value)
# Plot heatmap   
list_ggplots[[i]] <-  ggplot(data = melted.temp, aes(x=X1, y=X2, fill=value)) + 
                      geom_tile() + 
                      theme(axis.text.x = element_text(angle=90,hjust=0.95,vjust=0.2), axis.text.y = element_text(angle=0)) +
                      #labs(x = "Giver", y = "Receiver") + 
                      labs(x = "", y = "") + 
                     #scale_fill_viridis_c(option = "plasma", direction = 1,) +
                      theme(strip.placement = "outside") + 
                      ggtitle(names(list_counts_symmetric)[i]) +
                      scale_fill_gradientn(
                      colors = viridis_pal()(9),
                      # breaks=seq(0,200,10), #breaks in the scale bar
                      limits=c(rng[1], rng[2]))
  
}
list_ggplots[[i]]
```

Plot subtracted heatmaps to compare 
```{r}
# Libraries 
library(ggplot2)
# Set range for all graphs 
rng = range(-70,70)
# Make pair list 
pairs <- combn(c(1,2,3), m = 2)
pairs <- rbind(pairs, c(1,2,3)) # Last row is for list index 
list_ggplot_pairs <- list()
# Calculate for each pair
for(i in 1:ncol(pairs)){
    melted.temp.minus <- melt(list_counts_symmetric[[pairs[1,i]]]-list_counts_symmetric[[pairs[2,i]]])
    # Plot 
    list_ggplot_pairs[[pairs[3,i]]] <- ggplot(data = melted.temp.minus, aes(x=X1, y=X2, fill=value)) + 
                      geom_tile() + 
                      theme(axis.text.x = element_text(angle=90,hjust=0.95,vjust=0.2), 
                            axis.text.y = element_text(angle=0)) +
                      #labs(x = "Giver", y = "Receiver") +
                      labs(x = "", y = "") + 
                      scale_fill_gradient2(midpoint = 0, low="blue", mid="white",high="red", space ="RGB",
                                           limits=c(floor(rng[1]), ceiling(rng[2]))) + 
                      ggtitle(paste(names(list_counts_symmetric)[[pairs[1,i]]], names(list_counts_symmetric)[[pairs[2,i]]], sep="-"))  
    # Name list entry 
    names(list_ggplot_pairs)[[pairs[3,i]]] <- paste(names(list_counts_symmetric)[[pairs[1,i]]],names(list_counts_symmetric)[[pairs[2,i]]], sep="-")
  }
```
Plot correlations between conditions (instead of subtracting)
```{r}
library(broom)
library(ggridges)
library(ggplot2)
library(ggrepel)
# Make pair list 
pairs <- combn(c(1,2,3), m = 2)
pairs <- rbind(pairs, c(1,2,3)) # Last row is for list index 
list_ggplot_cor <- list()
list_ggplot_res <- list()
list_lm <- list()
# Calculate for each pair
for(i in 1:ncol(pairs)){
    df.temp <- cbind(as.data.frame(melt(list_counts_symmetric[[pairs[1,i]]])[,"value"]),
                  as.data.frame(melt(list_counts_symmetric[[pairs[2,i]]])[,"value"]))
    # Replace NAs with zeros 
    df.temp[is.na(df.temp)] <- 0
    name.1 <- names(list_counts_symmetric)[[pairs[1,i]]]
    name.2 <- names(list_counts_symmetric)[[pairs[2,i]]]
    colnames(df.temp) <- c("x", "y")
    row.names(df.temp) <- paste(melt(list_counts_symmetric[[pairs[1,i]]])[,"X1"],
      melt(list_counts_symmetric[[pairs[1,i]]])[,"X2"], sep="//")
    ###################################
    # REgression analysis 
    mod <- lm(df.temp$x~df.temp$y)
    # Plot residuals 
    df <- augment(mod)
    df$names <- row.names(df.temp)
    # Sort on residuals 
    df <- df[order(df$.resid, decreasing = F),]
        # Change name factor order 
    df$names <- factor(df$names, levels = df$names[order(df$.resid, decreasing = F)])
    # Select the top and bottom 3 residuals 
    # df.less <- rbind(head(df, 3), tail(df, 3))
    # Create color 
    # df.less$color <- df.less$.resid
    # df.less$color[df.less$color > 0] <- c("darkolivegreen3")
    # df.less$color[as.numeric(df.less$color) < 0] <- c("firebrick")
    ###################################
    # Calculate distances from the diagonal (https://brilliant.org/wiki/dot-product-distance-between-point-and-a-line/)
    df.temp$dist <- NA
    for(k in 1:nrow(df.temp)){
        df.temp$dist[k] <- abs(df.temp[k,1]-df.temp[k,2])/sqrt(2)
    }
    # Order on distance 
    df.temp <- df.temp[order(df.temp$dist),]
    df.less <- tail(df.temp, 10)
    df.less$names <- row.names(df.less)
    ################################### 
    # Plot correlations 
    # Keep only top labels for residuals 
    df.temp$names <- row.names(df.temp)
    df.temp$names[!df.temp$names %in% row.names(df.less) ] <- ""
    list_ggplot_cor[[i]] <-   ggplot(df.temp, aes(x=x, y=y,label=names )) +
                              xlim(0,200) + ylim(0,200) +
                              geom_point(shape=1) +    
                              geom_label_repel(nudge_y = 0.3,direction = "y",hjust= 1,segment.size = 0.1,
                                        label.size = 0.05, ylim = c(0,200),xlim=c(120,200), label.padding = 0.1, vjust=20)  +
                              geom_abline(slope = 1, intercept = 0, col="red") +
                              labs(x = name.1, y = name.2) +
                              annotate("text", x=20, y=150, label= paste("cor=",round(cor(df.temp$x,df.temp$y),3),sep=""))  
                              #+ geom_smooth(method='lm',formula=y~x)  
  
                              geom_label_repel(nudge_y = 0.3,direction = "y",hjust= 10,segment.size = 0.5,
                                        label.size = 0.05, ylim = c(20,200),xlim=c(50,200), label.padding = 0.1)
    
    
#     # #  Plot the top
#     list_ggplot_res[[i]] <-   ggplot(data=df.less, aes(x=names, y=dist)) +
#                               geom_bar(stat="identity") +
#                               theme(axis.text.y = element_text(size = 10), legend.position="bottom") +
#                               geom_hline(yintercept = 0) + coord_flip() +
#                               labs(x = "", y = "Interaction Delta") +
#                               # scale_fill_manual(values = c("firebrick" = "firebrick", "darkolivegreen3" = "darkolivegreen3"),
#                               #                   labels=c(name.1,name.2), name="Higher in")
# # Store parsed linear regression results to plot all in one big histogram 
# df$group <- paste(name.1, name.2, sep="/")
# list_lm[[i]] <- df
}
```



Plot all heatmaps 
```{r}
require(ggpubr)
# All plots except correlations 
list_all <- c(list_ggplots, list_ggplot_pairs) #, list_ggplot_res
opqr <- ggarrange(plotlist = list_all,nrow = 3, ncol=3, labels = "AUTO") 
# Save 
ggsave(filename = paste(dir,"plot_out/IM05/CPDB_heatmaps_treatment_status.pdf", sep=""), plot = opqr, width = 17, height = 17)
# Correlations 
opqrs <- ggarrange(plotlist = list_ggplot_cor,nrow = 2, ncol=2, labels = "AUTO") 
ggsave(filename = paste(dir,"plot_out/IM05/CPDB_heatmaps_treatment_status_correlations.pdf", sep=""), plot = opqrs, width = 17, height = 17)
```


Lets play with networks 
Construct and plot networks 
```{r}
list.igraph <- list()
require(igraph)
names(list_counts_symmetric) <- c("naive", "grouped_pr", "grouped_pd")
for(i in 1:length(list_counts_symmetric)){
net2 <- graph_from_adjacency_matrix(list_counts_symmetric[[i]], weighted = T)
type <- names(list_counts_symmetric)[i]
# Change node size based on cell numbers 
# Lets recover the cell numbers per category and cell type 
cell.numbers <- as.data.frame.array(t(table(meta.temp))) # Thats the meta.temp made in line 33 from object ann_all)
row.names(cell.numbers) <- gsub("-",".",row.names(cell.numbers)) # Change names for compatibility 
row.names(cell.numbers) <- gsub("/",".",row.names(cell.numbers)) # Change names for compatibility 
row.names(cell.numbers) <- gsub("_",".",row.names(cell.numbers)) # Change names for compatibility 
# Sort 
cell.numbers <- cell.numbers[V(net2)$name,]
# Set node siae 
V(net2)$size <- log2(cell.numbers[,type])
# Set edge width based on weight:
E(net2)$width <- E(net2)$weight/2
#change arrow size  edge color and edge width :
E(net2)$arrow.size <- .05
E(net2)$edge.color <- "gray80"
E(net2)$width <- E(net2)$weight/mean(E(net2)$weight)
plot(net2, vertex.frame.color="white")
# Remove edges that correspond to less than 10 interactions 
cut.off <- mean(list_counts_symmetric[[i]]) 
net.sp <- delete_edges(net2, E(net2)[weight<20])
# Change layout 
l <- layout_nicely(net.sp)
filename <- paste(dir,"plot_out/IM05/Interaction_network_",type,".pdf",sep="")
pdf(filename,10,10)
plot(net.sp, vertex.frame.color="white", edge.curved=.1, layout=l, main=type)
dev.off()
list.igraph[[i]] <-net.sp
}
names(list.igraph) <- c("naive", "grouped_pr", "grouped_pd")
```


Plot Myeloid interactions (Myeloid--ligand) to all other cell types as boxplots across conditions 
```{r}
# New dataframe with neoplastic interaction counts 
a <-  cbind(as.data.frame(list_counts_symmetric$naive["MF.Monocytes",]), 
      row.names(as.data.frame(list_counts_symmetric$naive["MF.Monocytes",])), 
      rep("Naive", length(list_counts_symmetric$naive["MF.Monocytes",])))
colnames(a) <- c("counts", "cell", "group")
b <-  cbind(as.data.frame(list_counts_symmetric$grouped_pr["MF.Monocytes",]), 
      row.names(as.data.frame(list_counts_symmetric$grouped_pr["MF.Monocytes",])), 
      rep("PR", length(list_counts_symmetric$grouped_pr["MF.Monocytes",])))
colnames(b) <- c("counts", "cell", "group")
c <-  cbind(as.data.frame(list_counts_symmetric$grouped_pd["MF.Monocytes",]), 
      row.names(as.data.frame(list_counts_symmetric$grouped_pd["MF.Monocytes",])), 
      rep("PD", length(list_counts_symmetric$grouped_pd["MF.Monocytes",])))
colnames(c) <- c("counts", "cell", "group")
mat.neo <-  rbind(a,b,c)
rm(a,b,c)
# Plot 
p <-  ggplot(data=mat.neo, aes(x=cell, y=counts, group=group)) +
      geom_line(aes(color=group))+
      geom_point(aes(shape=group))+ 
      theme(axis.text.x = element_text(angle=90,hjust=0.95,vjust=0.05, size=10), axis.text.y = element_text(angle=0)) +
      #labs(x = "Giver", y = "Receiver") + 
      labs(x = "", y = "") + 
      theme(strip.placement = "outside") + 
      ggtitle("Number of possible MF.monocytes interactions")

ggsave(filename = paste(dir,"plot_out/IM05/Number_of_MF_interactions_across_groups.pdf", sep=""), plot = p, width = 10, height = 7)
p
```






For each cell type plot Myeloid-cell type interacting pairs as 
venn diagrams between naive, PD and PR samples 
```{r}
list.interacting.pairs <- list()
# Get all other cell types 
types <- colnames(list.sig.means[[1]])[grep("MF.Monocytes_", colnames(list.sig.means[[1]]))]
types <- do.call(rbind, strsplit(types, "_"))[,2]

for(i in 1:length(list.sig.means)){
  temp <- list.sig.means[[i]]
  # Subset only neoplastic cell interactions 
  # in which the neoplastic cells are the ones expressing the ligand
  temp <- cbind(temp$interacting_pair, temp$id_cp_interaction,temp[,grep("MF.Monocytes_", colnames(temp))])
  # Create temporary list to hold each cell type 
  list.temp <- list()
    for(k in 1:length(types)){
      # Subset only positive interactions for the given not neoplastic cell type 
      genes <- as.character(temp[which(is.na(temp[,grep(types[k], colnames(temp))])==F),"temp$interacting_pair"])
      # Store genes in list 
      list.temp[[k]] <- genes 
    }
  names(list.temp) <- types 
  # Place back in big list (which is a list of lists )
  list.interacting.pairs[[i]] <- list.temp
}
names(list.interacting.pairs) <- names(list.sig.means)
```

Plot agreement between cell types across each condition 
```{r}
require(UpSetR)
# Crate a list for the given cell type 
list.venn <- list()
for(i in 1:length(list.interacting.pairs[[1]])){
message(paste("Processing:", names(list.interacting.pairs[[1]])[i], sep=""))
# Concatenate lists for the given cell type 
list.temp <-  list(list.interacting.pairs$naive.sig.means[[i]], 
              list.interacting.pairs$pr.sig.means[[i]],
              list.interacting.pairs$pd.sig.means[[i]])
# Name list with cell type because venn is a stupi function 
names(list.temp) <- c("Naive", "PR", "PD")
# Get all unique genes 
all.pairs <- unique(unlist(list.temp))
# Create a table of entries for which treatment group each pair is found in 
mat.temp <- matrix(nrow=length(all.pairs), ncol=3, 0)
colnames(mat.temp) <- c("Naive", "PR", "PD")
row.names(mat.temp) <- all.pairs
  # Loop over all pairs and fill in matrixd 
for(k in 1:nrow(mat.temp)){
    mat.temp[k,colnames(mat.temp) %in% names(list.temp)[grep(row.names(mat.temp)[k], list.temp)]]  <- 1      
}
# Store mat.temp 
list.venn[[i]] <- mat.temp
# Plot mat temp as upsetR plot 
pdf(paste(dir,"plot_out/IM05/Upset_plot_Myeloid_",names(list.interacting.pairs[[1]])[i],".pdf", sep=""))
upset(as.data.frame(mat.temp))
dev.off()
# Plot mat temp as heatmap
# Order for heatmap 
order <- row.names(mat.temp)[order(rowSums(mat.temp), decreasing = T)]
order <- order[!is.na(order)]
# Melt matrix 
df <- melt(mat.temp[order,])
# convert to ordered factor
df$X1 <- factor(df$X1, levels = order)
# Plot heatmap
p <-                  ggplot(data = df, aes(x=X1, y=X2, fill=as.factor(value))) + 
                      geom_tile() + 
                      scale_fill_manual(values=c("white", "gray50")) + 
                      theme(axis.text.x = element_text(angle=90,hjust=0.95,vjust=0.2, size=5), axis.text.y = element_text(angle=0)) +
                      #labs(x = "Giver", y = "Receiver") + 
                      labs(x = "", y = "") + 
                     #scale_fill_viridis_c(option = "plasma", direction = 1,) +
                      theme(strip.placement = "outside") + 
                      ggtitle(names(list.interacting.pairs[[1]])[i])
# Save 
ggsave(filename = paste(dir,"plot_out/IM05/Heatmap_plot_Myeloid_",names(list.interacting.pairs[[1]])[i],".pdf", sep=""), plot = p, width = 10, height = 10)
p
}
names(list.venn) <- names(list.interacting.pairs[[1]])
```



```{r}
t.cells <- row.names(tiss_immune_lung@meta.data)[which(tiss_immune_lung@meta.data$immune_subtype_annotation=="T-cells")]
t.cell.tiss <- SubsetData(tiss_immune_lung, cells.use = t.cells)
mf.cells <- row.names(tiss_immune_lung@meta.data)[which(tiss_immune_lung@meta.data$immune_subtype_annotation=="MF-Monocytes")]
mf.cell.tiss <- SubsetData(tiss_immune_lung, cells.use = mf.cells)
```

```{r}
t.cell.tiss <- SetIdent(t.cell.tiss, ident.use = t.cell.tiss@meta.data$analysis)
VlnPlot(t.cell.tiss, "TNFRSF10B")
```

```{r}
mf.cell.tiss <- SetIdent(mf.cell.tiss, ident.use = t.cell.tiss@meta.data$analysis)
VlnPlot(mf.cell.tiss, "TNFSF10")
```














<!-- Start looking at the actual interactions between conditions  -->

<!-- For each cell type plot Neoplastic-cell type interacting pairs as  -->
<!-- venn diagrams between naive, PD and PR samples  -->
<!-- ```{r} -->
<!-- list.interacting.pairs <- list() -->
<!-- # Get all other cell types  -->
<!-- types <- colnames(list.sig.means[[1]])[grep("Neoplastic_", colnames(list.sig.means[[1]]))] -->
<!-- types <- do.call(rbind, strsplit(types, "_"))[,2] -->

<!-- for(i in 1:length(list.sig.means)){ -->
<!--   temp <- list.sig.means[[i]] -->
<!--   # Subset only neoplastic cell interactions  -->
<!--   # in which the neoplastic cells are the ones expressing the ligand -->
<!--   temp <- cbind(temp$interacting_pair, temp$id_cp_interaction,temp[,grep("Neoplastic_", colnames(temp))]) -->
<!--   # Create temporary list to hold each cell type  -->
<!--   list.temp <- list() -->
<!--     for(k in 1:length(types)){ -->
<!--       # Subset only positive interactions for the given not neoplastic cell type  -->
<!--       genes <- as.character(temp[which(is.na(temp[,grep(types[k], colnames(temp))])==F),"temp$interacting_pair"]) -->
<!--       # Store genes in list  -->
<!--       list.temp[[k]] <- genes  -->
<!--     } -->
<!--   names(list.temp) <- types  -->
<!--   # Place back in big list (which is a list of lists ) -->
<!--   list.interacting.pairs[[i]] <- list.temp -->
<!-- } -->
<!-- names(list.interacting.pairs) <- names(list.sig.means) -->
<!-- ``` -->

<!-- Plot agreement between cell types across each condition  -->
<!-- ```{r} -->
<!-- # Crate a list for the given cell type  -->
<!-- list.venn <- list() -->
<!-- for(i in 1:length(list.interacting.pairs[[1]])){ -->
<!-- message(paste("Processing:", names(list.interacting.pairs[[1]])[i], sep="")) -->
<!-- # Concatenate lists for the given cell type  -->
<!-- list.temp <-  list(list.interacting.pairs$naive.sig.means[[i]],  -->
<!--               list.interacting.pairs$pr.sig.means[[i]], -->
<!--               list.interacting.pairs$pd.sig.means[[i]]) -->
<!-- # Name list with cell type because venn is a stupi function  -->
<!-- names(list.temp) <- c("Naive", "PR", "PD") -->
<!-- # Get all unique genes  -->
<!-- all.pairs <- unique(unlist(list.temp)) -->
<!-- # Create a table of entries for which treatment group each pair is found in  -->
<!-- mat.temp <- matrix(nrow=length(all.pairs), ncol=3, 0) -->
<!-- colnames(mat.temp) <- c("Naive", "PR", "PD") -->
<!-- row.names(mat.temp) <- all.pairs -->
<!--   # Loop over all pairs and fill in matrixd  -->
<!-- for(k in 1:nrow(mat.temp)){ -->
<!--     mat.temp[k,colnames(mat.temp) %in% names(list.temp)[grep(row.names(mat.temp)[k], list.temp)]]  <- 1       -->
<!-- } -->
<!-- # Store mat.temp  -->
<!-- list.venn[[i]] <- mat.temp -->
<!-- # Plot mat temp as upsetR plot  -->
<!-- pdf(paste("/myVolume/sclung_adeno/interaction_analysis/plot_out/collapsed_annotation/upset_plots/Upset_plot_", names(list.interacting.pairs[[1]])[i], ".pdf", sep="")) -->
<!-- upset(as.data.frame(mat.temp)) -->
<!-- dev.off() -->
<!-- # Plot mat temp as heatmap -->
<!-- # Order for heatmap  -->
<!-- order <- row.names(mat.temp)[order(rowSums(mat.temp), decreasing = T)] -->
<!-- order <- order[!is.na(order)] -->
<!-- # Melt matrix  -->
<!-- df <- melt(mat.temp[order,]) -->
<!-- # convert to ordered factor -->
<!-- df$X1 <- factor(df$X1, levels = order) -->
<!-- # Plot heatmap -->
<!-- p <-                  ggplot(data = df, aes(x=X1, y=X2, fill=as.factor(value))) +  -->
<!--                       geom_tile() +  -->
<!--                       scale_fill_manual(values=c("white", "gray50")) +  -->
<!--                       theme(axis.text.x = element_text(angle=90,hjust=0.95,vjust=0.2, size=5), axis.text.y = element_text(angle=0)) + -->
<!--                       #labs(x = "Giver", y = "Receiver") +  -->
<!--                       labs(x = "", y = "") +  -->
<!--                      #scale_fill_viridis_c(option = "plasma", direction = 1,) + -->
<!--                       theme(strip.placement = "outside") +  -->
<!--                       ggtitle(names(list.interacting.pairs[[1]])[i]) -->
<!-- # Save  -->
<!-- ggsave(filename = paste("/myVolume/sclung_adeno/interaction_analysis/plot_out/collapsed_annotation/gene_heatmaps/Heatmap_", names(list.interacting.pairs[[1]])[i], ".pdf", sep=""), plot = p, width = 10, height = 10) -->
<!-- p -->
<!-- } -->
<!-- names(list.venn) <- names(list.interacting.pairs[[1]]) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- pdf("/myVolume/sclung_adeno/interaction_analysis/plot_out/GPR35.pdf", 10,10) -->
<!-- VlnPlot(tiss_subset, features.plot = "GPR35", group.by = "Final_immune_annotation", x.lab.rot = T) -->
<!-- dev.off() -->
<!-- colnames(tiss_subset@meta.data) -->
<!-- ``` -->


<!-- Plot neoplastic interactions (neoplastic--ligand) to all other cell types as boxplots across conditions  -->
<!-- ```{r} -->
<!-- # New dataframe with neoplastic interaction counts  -->
<!-- a <-  cbind(as.data.frame(list_counts_symmetric$naive["Neoplastic",]),  -->
<!--       row.names(as.data.frame(list_counts_symmetric$naive["Neoplastic",])),  -->
<!--       rep("Naive", length(list_counts_symmetric$naive["Neoplastic",]))) -->
<!-- colnames(a) <- c("counts", "cell", "group") -->
<!-- b <-  cbind(as.data.frame(list_counts_symmetric$grouped_pr["Neoplastic",]),  -->
<!--       row.names(as.data.frame(list_counts_symmetric$grouped_pr["Neoplastic",])),  -->
<!--       rep("PR", length(list_counts_symmetric$grouped_pr["Neoplastic",]))) -->
<!-- colnames(b) <- c("counts", "cell", "group") -->
<!-- c <-  cbind(as.data.frame(list_counts_symmetric$grouped_pd["Neoplastic",]),  -->
<!--       row.names(as.data.frame(list_counts_symmetric$grouped_pd["Neoplastic",])),  -->
<!--       rep("PD", length(list_counts_symmetric$grouped_pd["Neoplastic",]))) -->
<!-- colnames(c) <- c("counts", "cell", "group") -->
<!-- mat.neo <-  rbind(a,b,c) -->
<!-- rm(a,b,c) -->
<!-- # Plot  -->
<!-- p <-  ggplot(data=mat.neo, aes(x=cell, y=counts, group=group)) + -->
<!--       geom_line(aes(color=group))+ -->
<!--       geom_point(aes(shape=group))+  -->
<!--       theme(axis.text.x = element_text(angle=90,hjust=0.95,vjust=0.05, size=10), axis.text.y = element_text(angle=0)) + -->
<!--       #labs(x = "Giver", y = "Receiver") +  -->
<!--       labs(x = "", y = "") +  -->
<!--       theme(strip.placement = "outside") +  -->
<!--       ggtitle("Number of possible neoplastic cell interactions") -->
<!-- ggsave(filename = "/myVolume/sclung_adeno/interaction_analysis/plot_out/collapsed_annotation/Number_of_neoplastic_interactions_across_groups.pdf", plot = p, width = 10, height = 7) -->
<!-- p -->
<!-- ``` -->

<!-- For each cell type plot Dendritic-cell type interacting pairs as  -->
<!-- venn diagrams between naive, PD and PR samples  -->
<!-- ```{r} -->
<!-- list.interacting.pairs <- list() -->
<!-- # Get all other cell types  -->
<!-- types <- colnames(list.sig.means[[1]])[grep("Dendritic_", colnames(list.sig.means[[1]]))] -->
<!-- types <- do.call(rbind, strsplit(types, "_"))[,2] -->

<!-- for(i in 1:length(list.sig.means)){ -->
<!--   temp <- list.sig.means[[i]] -->
<!--   # Subset only neoplastic cell interactions  -->
<!--   # in which the neoplastic cells are the ones expressing the ligand -->
<!--   temp <- cbind(temp$interacting_pair, temp$id_cp_interaction,temp[,grep("Dendritic_", colnames(temp))]) -->
<!--   # Create temporary list to hold each cell type  -->
<!--   list.temp <- list() -->
<!--     for(k in 1:length(types)){ -->
<!--       # Subset only positive interactions for the given not neoplastic cell type  -->
<!--       genes <- as.character(temp[which(is.na(temp[,grep(types[k], colnames(temp))])==F),"temp$interacting_pair"]) -->
<!--       # Store genes in list  -->
<!--       list.temp[[k]] <- genes  -->
<!--     } -->
<!--   names(list.temp) <- types  -->
<!--   # Place back in big list (which is a list of lists ) -->
<!--   list.interacting.pairs[[i]] <- list.temp -->
<!-- } -->
<!-- names(list.interacting.pairs) <- names(list.sig.means) -->
<!-- ``` -->

<!-- Plot agreement between cell types across each condition  -->
<!-- ```{r} -->
<!-- # Crate a list for the given cell type  -->
<!-- list.venn <- list() -->
<!-- for(i in 1:length(list.interacting.pairs[[1]])){ -->
<!-- message(paste("Processing:", names(list.interacting.pairs[[1]])[i], sep="")) -->
<!-- # Concatenate lists for the given cell type  -->
<!-- list.temp <-  list(list.interacting.pairs$naive.sig.means[[i]],  -->
<!--               list.interacting.pairs$pr.sig.means[[i]], -->
<!--               list.interacting.pairs$pd.sig.means[[i]]) -->
<!-- # Name list with cell type because venn is a stupi function  -->
<!-- names(list.temp) <- c("Naive", "PR", "PD") -->
<!-- # Get all unique genes  -->
<!-- all.pairs <- unique(unlist(list.temp)) -->
<!-- # Create a table of entries for which treatment group each pair is found in  -->
<!-- mat.temp <- matrix(nrow=length(all.pairs), ncol=3, 0) -->
<!-- colnames(mat.temp) <- c("Naive", "PR", "PD") -->
<!-- row.names(mat.temp) <- all.pairs -->
<!--   # Loop over all pairs and fill in matrixd  -->
<!-- for(k in 1:nrow(mat.temp)){ -->
<!--     mat.temp[k,colnames(mat.temp) %in% names(list.temp)[grep(row.names(mat.temp)[k], list.temp)]]  <- 1       -->
<!-- } -->
<!-- # Store mat.temp  -->
<!-- list.venn[[i]] <- mat.temp -->
<!-- # Plot mat temp as upsetR plot  -->
<!-- pdf(paste("/myVolume/sclung_adeno/interaction_analysis/plot_out/collapsed_annotation/upset_plots/Upset_plot_Dendritic_", names(list.interacting.pairs[[1]])[i], ".pdf", sep="")) -->
<!-- upset(as.data.frame(mat.temp)) -->
<!-- dev.off() -->
<!-- # Plot mat temp as heatmap -->
<!-- # Order for heatmap  -->
<!-- order <- row.names(mat.temp)[order(rowSums(mat.temp), decreasing = T)] -->
<!-- order <- order[!is.na(order)] -->
<!-- # Melt matrix  -->
<!-- df <- melt(mat.temp[order,]) -->
<!-- # convert to ordered factor -->
<!-- df$X1 <- factor(df$X1, levels = order) -->
<!-- # Plot heatmap -->
<!-- p <-                  ggplot(data = df, aes(x=X1, y=X2, fill=as.factor(value))) +  -->
<!--                       geom_tile() +  -->
<!--                       scale_fill_manual(values=c("white", "gray50")) +  -->
<!--                       theme(axis.text.x = element_text(angle=90,hjust=0.95,vjust=0.2, size=5), axis.text.y = element_text(angle=0)) + -->
<!--                       #labs(x = "Giver", y = "Receiver") +  -->
<!--                       labs(x = "", y = "") +  -->
<!--                      #scale_fill_viridis_c(option = "plasma", direction = 1,) + -->
<!--                       theme(strip.placement = "outside") +  -->
<!--                       ggtitle(names(list.interacting.pairs[[1]])[i]) -->
<!-- # Save  -->
<!-- ggsave(filename = paste("/myVolume/sclung_adeno/interaction_analysis/plot_out/collapsed_annotation/gene_heatmaps/Heatmap_Dendritic_", names(list.interacting.pairs[[1]])[i], ".pdf", sep=""), plot = p, width = 10, height = 10) -->
<!-- p -->
<!-- } -->
<!-- names(list.venn) <- names(list.interacting.pairs[[1]]) -->
<!-- ``` -->

<!-- Plot Dendritic interactions (Dendritic--ligand) to all other cell types as boxplots across conditions  -->
<!-- ```{r} -->
<!-- # New dataframe with neoplastic interaction counts  -->
<!-- a <-  cbind(as.data.frame(list_counts_symmetric$naive["Dendritic",]),  -->
<!--       row.names(as.data.frame(list_counts_symmetric$naive["Dendritic",])),  -->
<!--       rep("Naive", length(list_counts_symmetric$naive["Dendritic",]))) -->
<!-- colnames(a) <- c("counts", "cell", "group") -->
<!-- b <-  cbind(as.data.frame(list_counts_symmetric$grouped_pr["Dendritic",]),  -->
<!--       row.names(as.data.frame(list_counts_symmetric$grouped_pr["Dendritic",])),  -->
<!--       rep("PR", length(list_counts_symmetric$grouped_pr["Dendritic",]))) -->
<!-- colnames(b) <- c("counts", "cell", "group") -->
<!-- c <-  cbind(as.data.frame(list_counts_symmetric$grouped_pd["Dendritic",]),  -->
<!--       row.names(as.data.frame(list_counts_symmetric$grouped_pd["Dendritic",])),  -->
<!--       rep("PD", length(list_counts_symmetric$grouped_pd["Dendritic",]))) -->
<!-- colnames(c) <- c("counts", "cell", "group") -->
<!-- mat.neo <-  rbind(a,b,c) -->
<!-- rm(a,b,c) -->
<!-- # Plot  -->
<!-- p <-  ggplot(data=mat.neo, aes(x=cell, y=counts, group=group)) + -->
<!--       geom_line(aes(color=group))+ -->
<!--       geom_point(aes(shape=group))+  -->
<!--       theme(axis.text.x = element_text(angle=90,hjust=0.95,vjust=0.05, size=10), axis.text.y = element_text(angle=0)) + -->
<!--       #labs(x = "Giver", y = "Receiver") +  -->
<!--       labs(x = "", y = "") +  -->
<!--       theme(strip.placement = "outside") +  -->
<!--       ggtitle("Number of possible Dendritic cell interactions") -->
<!-- ggsave(filename = "/myVolume/sclung_adeno/interaction_analysis/plot_out/collapsed_annotation/Number_of_Dendritic_interactions_across_groups.pdf", plot = p, width = 10, height = 7) -->
<!-- p -->
<!-- ``` -->