---
title: "Regression of Clinical Outcomes to Sigs"
output: html_notebook
---

```{r}
library(Seurat)
library(DAAG)
library(tidyverse)
library(relaimpo)
library(bootstrap)
```

Read in tumor object
```{r}
# rm(list=ls())
dir <- "/myVolume/scell_lung_adenocarcinoma/"
load(file = paste(dir, "Data_input/objects/NI04_tumor_seurat_object.RData", sep = ""))

#Read in depth of response clinical outcomes
dor_meta <- read.csv(file = paste(dir, "Data_input/csv_files/depthofresponse_tn.csv", sep = ""))
#correct misannoation in dor
dor_meta$sample_name <- gsub(pattern = "LT_S57", replacement = "LT_S51", x = dor_meta$sample_name)
dor_meta$dor <- gsub(pattern = ".12", replacement = ".46", x = dor_meta$dor)
dor_meta$dor_class <- c("low", "low", "low", "low", "low", "high", "high", "high", "high", "high", "high")
dor_meta
```

subset tumor seurat obeject to TN only
```{r}
tn_samples <- filter(tiss_subset_tumor2@meta.data, sample_name == "LT_S34" | sample_name == "LT_S43" | sample_name == "LT_S45" | sample_name == "LT_S49" | sample_name == "LT_S52" | sample_name == "LT_S51" | sample_name == "LT_S56" | sample_name == "LT_S67" | sample_name == "LT_S69" | sample_name == "LT_S74" | sample_name == "LT_S75")

tn_seurat <- SubsetData(tiss_subset_tumor2, cells.use = tn_samples$cell_id)
rownames(tn_seurat@meta.data) <- tn_seurat@meta.data$cell_id
```


```{r}
tn_seurat@meta.data <- merge(dor_meta[,c(2:4)], tn_seurat@meta.data, by = "sample_name")
rownames(tn_seurat@meta.data) <- tn_seurat@meta.data$cell_id
```


Investigate each Signature found from grouped analysis:
1. Alveolar Sig
2. Kynurenine Sig
3. Plasminogen Sig
4. Serpine1
5. Gap Junction Sig

1. Alveolar Sig
```{r}
DOR_Alveolar <- as.data.frame(FetchData(object = tn_seurat, vars.all = c("SFTPC", "SFTPB", "SFTPD", "PGC", "CLDN18", "AQP4", "SCGB3A1", "ABCA3", "GATA6", "NKX2-1", "SFTA3", "IGFBP2", "HOPX", "NAPSA", "FOXA2", "AGER", "LAMP1")))
DOR_Alveolar$cell_id <- rownames(DOR_Alveolar)
DOR_Alveolar <- merge(tn_seurat@meta.data, DOR_Alveolar, by = "cell_id")
rownames(DOR_Alveolar) <- DOR_Alveolar$cell_id
```

2. Kynurenine Sig
```{r}
DOR_Kynurenine <- as.data.frame(FetchData(object = tn_seurat, vars.all = c('IDO1', 'KYNU', 'QPRT')))
DOR_Kynurenine$cell_id <- rownames(DOR_Kynurenine)
DOR_Kynurenine <- merge(tn_seurat@meta.data, DOR_Kynurenine, by = "cell_id")
rownames(DOR_Kynurenine) <- DOR_Kynurenine$cell_id
```

3. Plasminogen Sig
```{r}
DOR_Plasminogen <- as.data.frame(FetchData(object = tn_seurat, vars.all = c('ANXA2', 'PLAT', 'PLAU', 'PLAUR')))
DOR_Plasminogen$cell_id <- rownames(DOR_Plasminogen)
DOR_Plasminogen <- merge(tn_seurat@meta.data, DOR_Plasminogen, by = "cell_id")
rownames(DOR_Plasminogen) <- DOR_Plasminogen$cell_id
```

4. Serpine1
```{r}
DOR_SERPINE1 <- as.data.frame(FetchData(object = tn_seurat, vars.all = c('SERPINE1')))
DOR_SERPINE1$cell_id <- rownames(DOR_SERPINE1)
DOR_SERPINE1 <- merge(tn_seurat@meta.data, DOR_SERPINE1, by = "cell_id")
rownames(DOR_SERPINE1) <- DOR_SERPINE1$cell_id
```

5. Gap Junction Sig
```{r}
DOR_GapJunction <- as.data.frame(FetchData(object = tn_seurat, vars.all = c('GJB3', 'GJB2', 'GJB4','GJB5')))
DOR_GapJunction$cell_id <- rownames(DOR_GapJunction)
DOR_GapJunction <- merge(tn_seurat@meta.data, DOR_GapJunction, by = "cell_id")
rownames(DOR_GapJunction) <- DOR_GapJunction$cell_id
```

fit 1 = Alveolar Sig
```{r}
fit1 <- lm(dor ~ SFTPC +SFTPB + SFTPD + PGC + CLDN18 + AQP4 + SCGB3A1 + ABCA3 + GATA6 + `NKX2-1` + SFTA3 + IGFBP2+ HOPX + NAPSA + FOXA2 + AGER + LAMP1, data=DOR_Alveolar)
summary(fit1) # show results

# diagnostic plots
plot(fit1)

ggplot(DOR_Alveolar, aes(x = `NKX2-1`, y = dor, color = sample_name)) + geom_point()
ggplot(DOR_Alveolar, aes(x = IGFBP2, y = dor, color = sample_name)) + geom_point()
ggplot(DOR_Alveolar, aes(x = HOPX, y = dor, color = sample_name)) + geom_point()
ggplot(DOR_Alveolar, aes(x = NAPSA, y = dor, color = sample_name)) + geom_point()
ggplot(DOR_Alveolar, aes(x = FOXA2, y = dor, color = sample_name)) + geom_point()
```

fit2 = Kynurenine Sig
```{r}
fit2 <- lm(dor ~ IDO1 + KYNU + QPRT, data=DOR_Kynurenine)
summary(fit2) # show results

# diagnostic plots 
plot(fit2)

ggplot(DOR_Kynurenine, aes(x = IDO1, y = dor, color = sample_name)) + geom_point()
ggplot(DOR_Kynurenine, aes(x = KYNU, y = dor, color = sample_name)) + geom_point()
ggplot(DOR_Kynurenine, aes(x = QPRT, y = dor, color = sample_name)) + geom_point()
```

fit3 = Plasminogen Sig
```{r}
fit3 <- lm(dor ~ PLAU + PLAUR + PLAT + ANXA2, data=DOR_Plasminogen)
summary(fit3) # show results

# diagnostic plots 
plot(fit3)

ggplot(DOR_Plasminogen, aes(x = PLAU, y = dor, color = sample_name)) + geom_point()
ggplot(DOR_Plasminogen, aes(x = PLAUR, y = dor, color = sample_name)) + geom_point()
ggplot(DOR_Plasminogen, aes(x = PLAT, y = dor, color = sample_name)) + geom_point()
ggplot(DOR_Plasminogen, aes(x = ANXA2, y = dor, color = sample_name)) + geom_point()
```

fit4 = SERPINE1
```{r}
fit4 <- lm(dor ~ SERPINE1, data=DOR_SERPINE1)
summary(fit4) # show results

# diagnostic plots 
plot(fit4)

ggplot(DOR_SERPINE1, aes(x = SERPINE1, y = dor, color = sample_name)) + geom_point()
```

fit5 = Gap Junction Sig
```{r}
fit5 <- lm(dor ~ GJB3 + GJB2 + GJB4 + GJB5, data=DOR_GapJunction)
summary(fit5) # show results

# diagnostic plots 
plot(fit5)

ggplot(DOR_GapJunction, aes(x = GJB2, y = dor, color = sample_name)) + geom_point()
ggplot(DOR_GapJunction, aes(x = GJB3, y = dor, color = sample_name)) + geom_point()
ggplot(DOR_GapJunction, aes(x = GJB4, y = dor, color = sample_name)) + geom_point()
ggplot(DOR_GapJunction, aes(x = GJB5, y = dor, color = sample_name)) + geom_point()

# # K-fold cross-validation
# cv.lm(data = DOR_GapJunction, form.lm = fit5, m = 10, plotit = FALSE)
# # Assessing R2 shrinkage using 10-Fold Cross-Validation 
# # define functions 
# theta.fit <- function(x,y){lsfit(x,y)}
# theta.predict <- function(fit5,x){cbind(1,x)%*%fit5$coef} 
# 
# # matrix of predictors
# X <- as.matrix(DOR_GapJunction[c("GJB3","GJB2","GJB4","GJB5")])
# # vector of predicted values
# y <- as.matrix(DOR_GapJunction[c("dor")]) 
# 
# results <- crossval(X,y,theta.fit,theta.predict,ngroup=10)
# cor(y, fit5$fitted.values)**2 # raw R2 
# cor(y,results$cv.fit5)**2 # cross-validated R2
# 
# # Calculate Relative Importance for Each Predictor
# calc.relimp(fit5,type = c("lmg","last","first","pratt"), rela=TRUE)
# # Bootstrap Measures of Relative Importance (1000 samples) 
# boot <- boot.relimp(fit5, b = 1000, type = c("lmg", "last", "first", "pratt"), rank = TRUE, diff = TRUE, rela = TRUE)
# booteval.relimp(boot) # print result
# plot(booteval.relimp(boot,sort=TRUE)) # plot result
```

```{r}
table(tn_seurat@meta.data$biopsy_site, tn_seurat@meta.data$dor)
table(tn_seurat@meta.data$sample_name, tn_seurat@meta.data$dor)
table(tn_seurat@meta.data$sample_name)
```

Bulkize the samples
```{r}
tn_seurat <- SetIdent(tn_seurat, ident.use = tn_seurat@meta.data$sample_name)
table(tn_seurat@ident)
sample.averages <- AverageExpression(object = tn_seurat)
```

To find DE genes between bulkized TN samples with low and high DOR, export table with groups
```{r}
# set up table 
sample.averages.t <- as.data.frame(t(sample.averages))
head(sample.averages.t)
sample.averages.t$sample_name <- rownames(sample.averages.t)
sample.averages.t <- left_join(sample.averages.t, dor_meta, by = "sample_name")
rownames(sample.averages.t) <- sample.averages.t$sample_name

length(colnames(sample.averages.t))
DE_avg <- pairwise.wilcox.test(x = sample.averages.t$EGFR, g = sample.averages.t$dor_class)
write.csv(sample.averages.t, file = "/myVolume/TN_bulkized_data.csv")
TN.sample.averages <- sample.averages
head(TN.sample.averages)
```


Bulkize fit analysis Alveolar
```{r}
Alveolar_sig <- c("SFTPC", "SFTPB", "SFTPD", "PGC", "CLDN18", "AQP4", "SCGB3A1", "ABCA3", "GATA6", "NKX2-1", "SFTA3", "IGFBP2", "HOPX", "NAPSA", "FOXA2", "AGER", "LAMP1")
TN_Alveolar <- TN.sample.averages[Alveolar_sig, ]
TN_Alveolar_mean <- as.data.frame(colMeans(TN_Alveolar))
TN_Alveolar_mean$sample_name <- rownames(TN_Alveolar_mean)
TN_Alveolar_mean <- left_join(TN_Alveolar_mean, dor_meta, by = "sample_name")
rownames(TN_Alveolar_mean) <- TN_Alveolar_mean$sample_name

TN_Alveolar_fit <- lm(dor ~ colMeans(TN_Alveolar), data= TN_Alveolar_mean)
summary(TN_Alveolar_fit)
TN_Alveolar_mean$predlm <- predict(TN_Alveolar_fit)

ggp_TN_Alveolar <- ggplot(TN_Alveolar_mean, aes(x = colMeans(TN_Alveolar), y = dor, color = dor_class)) + geom_point()

ggsave(ggp_TN_Alveolar, filename = paste(dir, "plot_out/NI08/TN_Alveolar_bulkized.pdf", sep = ""))
```

Bulkize fit analysis Kynurenine
```{r}
Kynurenine_sig <- c('IDO1', 'KYNU', 'QPRT')
TN_Kynurenine <- TN.sample.averages[Kynurenine_sig, ]
TN_Kynurenine_mean <- as.data.frame(colMeans(TN_Kynurenine))
TN_Kynurenine_mean$sample_name <- rownames(TN_Kynurenine_mean)
TN_Kynurenine_mean <- left_join(TN_Kynurenine_mean, dor_meta, by = "sample_name")
rownames(TN_Kynurenine_mean) <- TN_Kynurenine_mean$sample_name

TN_Kynurenine_fit <- lm(dor ~ colMeans(TN_Kynurenine), data= TN_Kynurenine_mean)
summary(TN_Kynurenine_fit)

ggp_TN_Kynurenine <- ggplot(TN_Kynurenine_mean, aes(x = colMeans(TN_Kynurenine), y = dor)) + geom_point(aes(color=dor_class))
ggsave(ggp_TN_Kynurenine, filename = paste(dir, "plot_out/NI08/TN_Kynurenine_bulkized.pdf", sep = ""))
```

Bulkize fit analysis Plasminogen
```{r}
Plasminogen_sig <- c('ANXA2', 'PLAT', 'PLAU', 'PLAUR')
TN_Plasminogen <- TN.sample.averages[Plasminogen_sig, ]
TN_Plasminogen_mean <- as.data.frame(colMeans(TN_Plasminogen))
TN_Plasminogen_mean$sample_name <- rownames(TN_Plasminogen_mean)
TN_Plasminogen_mean <- left_join(TN_Plasminogen_mean, dor_meta, by = "sample_name")
rownames(TN_Plasminogen_mean) <- TN_Plasminogen_mean$sample_name

TN_Plasminogen_fit <- lm(dor ~ colMeans(TN_Plasminogen), data= TN_Plasminogen_mean)
summary(TN_Plasminogen_fit)

ggp_TN_Plasminogen <- ggplot(TN_Plasminogen_mean, aes(x = colMeans(TN_Plasminogen), y = dor)) + geom_point(aes(color = dor_class))
ggsave(ggp_TN_Plasminogen, filename = paste(dir, "plot_out/NI08/TN_Plasminogen_bulkized.pdf", sep = ""))
```

Bulkize fit analysis of SERPINE1
```{r}
TN_Serpine_sig <-  as.data.frame(t(TN.sample.averages["SERPINE1", ]))
TN_Serpine_sig$sample_name <- rownames(TN_Serpine_sig)
TN_Serpine_sig <- left_join(TN_Serpine_sig, dor_meta, by = "sample_name")
rownames(TN_Serpine_sig) <- TN_Serpine_sig$sample_name

TN_Serpine_fit <- lm(dor ~ SERPINE1, data= TN_Serpine_sig)
summary(TN_Serpine_fit)

ggp_TN_Serpine1 <- ggplot(TN_Serpine_sig, aes(x = SERPINE1, y = dor)) + geom_point(aes(color = dor_class))
ggsave(ggp_TN_Serpine1, filename = paste(dir, "plot_out/NI08/TN_Serpine1_bulkized.pdf", sep = ""))
```

Bulkize fit analysis GapJunction
```{r}
GapJunction_sig <- c('GJB3', 'GJB2', 'GJB4','GJB5')
TN_GapJunction <- TN.sample.averages[GapJunction_sig, ]
TN_GapJunction_mean <- as.data.frame(colMeans(TN_GapJunction))
TN_GapJunction_mean$sample_name <- rownames(TN_GapJunction_mean)
TN_GapJunction_mean <- left_join(TN_GapJunction_mean, dor_meta, by = "sample_name")
rownames(TN_GapJunction_mean) <- TN_GapJunction_mean$sample_name

TN_GapJunction_fit <- lm(dor ~ colMeans(TN_GapJunction), data= TN_GapJunction_mean)
summary(TN_GapJunction_fit)

ggp_TN_GapJunction <- ggplot(TN_GapJunction_mean, aes(x = colMeans(TN_GapJunction), y = dor)) + geom_point(aes(color = dor_class))
ggsave(ggp_TN_GapJunction, filename = paste(dir, "plot_out/NI08/TN_GapJucion_bulkized.pdf", sep = ""))
```


```{r}
bulkized_TN_markers <- read.csv(file = paste(dir, "Data_input/mwu_luad.csv", sep = ""))
bulkized_TN_markers.f <- filter(bulkized_TN_markers, pval_1 <= 0.05)
hist(bulkized_TN_markers.f$stat_1)
length(bulkized_TN_markers.f$pval_1)
bulkized_TN_markers.f <- bulkized_TN_markers.f[order(bulkized_TN_markers.f$stat_1, decreasing = TRUE), ] 
```

```{r}
table(bulkized_TN_markers.f$test)
```

Most compelling high expression corr to low dor
```{r}
ggplot(sample.averages.t, aes(x = ADAR, y = dor)) + geom_point(aes(color = patient_id))
ggplot(sample.averages.t, aes(x = CFL1, y = dor)) + geom_point(aes(color = patient_id))
```

Most compelling high expression corr to high dor
```{r}
ggplot(sample.averages.t, aes(x = TTLL13P, y = dor)) + geom_point(aes(color = dor_class))
ggplot(sample.averages.t, aes(x = ALS2, y = dor)) + geom_point(aes(color = dor_class))
ggplot(sample.averages.t, aes(x = RLN1, y = dor)) + geom_point(aes(color = dor_class))
ggplot(sample.averages.t, aes(x = USP45, y = dor)) + geom_point(aes(color = dor_class))
ggplot(sample.averages.t, aes(x = BDKRB1, y = dor)) + geom_point(aes(color = dor_class))
ggplot(sample.averages.t, aes(x = LINC01061, y = dor)) + geom_point(aes(color = dor_class))
ggplot(sample.averages.t, aes(x = ZNF563, y = dor)) + geom_point(aes(color = dor_class))
ggplot(sample.averages.t, aes(x = WDR19, y = dor)) + geom_point(aes(color = dor_class))
```

