---
title: "02.1_Create_Seurat_object"
output: html_document
---

load libraries
```{r}
require(Seurat)
library(tidyverse)
```

Load RData object 
```{r}
rm(list=ls())
dir <- "/home/ubuntu/scell_lung_adenocarcinoma/"
# dir <- "/myVolume/scell_lung_adenocarcinoma/"
```

load and clean rawdata
```{r}
osi.raw.data <- read.csv(paste(dir,"Data_input/csv_files/neo-osi_rawdata.csv", sep=""), row.names = 1)
colnames(osi.raw.data) <- gsub("_S.*.homo", "", colnames(osi.raw.data))
head(osi.raw.data)
tail(osi.raw.data)

# drop sequencing details from gene count table
row.names(osi.raw.data)[grep("__", row.names(osi.raw.data))]
osi.raw.data <- osi.raw.data[-grep("__", row.names(osi.raw.data)),]
```

Make osi.metadata by cell from osi.metadata by plate
```{r}
osi.metadata <- read.csv(paste(dir, "Data_input/csv_files/neo-osi_metadata.csv", sep = ""))
osi.meta.cell <- as.data.frame(colnames(osi.raw.data))
osi.meta.cell <- data.frame(do.call('rbind', strsplit(as.character(osi.meta.cell$`colnames(osi.raw.data)`),'_',fixed=TRUE)))
rownames(osi.meta.cell) <- paste(osi.meta.cell$X1, osi.meta.cell$X2, sep = "_")
colnames(osi.meta.cell) <- c("well", "plate")
osi.meta.cell$cell_id <- rownames(osi.meta.cell)

osi.metadata <- left_join(osi.meta.cell, osi.metadata, by = "plate")
rownames(osi.metadata) <- osi.metadata$cell_id
head(osi.metadata)

unique(osi.metadata$plate)
```

Find ERCC's, compute the percent ERCC, and drop them from the raw data.
```{r}
erccs <- grep(pattern = "^ERCC-", x = rownames(x = osi.raw.data), value = TRUE)
percent.ercc <- Matrix::colSums(osi.raw.data[erccs, ])/Matrix::colSums(osi.raw.data)
ercc.index <- grep(pattern = "^ERCC-", x = rownames(x = osi.raw.data), value = FALSE)
osi.raw.data <- osi.raw.data[-ercc.index,]
dim(osi.raw.data)
```

Create the Seurat object with all the data (unfiltered)
```{r}
osi_object <- CreateSeuratObject(counts = osi.raw.data, meta.data = osi.metadata)
osi_object <- AddMetaData(object = osi_object, metadata = osi.metadata)
osi_object <- AddMetaData(object = osi_object, percent.ercc, col.name = "percent.ercc")
# Changing nUMI column name to nReads
colnames(osi_object@meta.data)[colnames(osi_object@meta.data) == 'nUMI'] <- 'nReads'
head(osi_object@meta.data)
```

Calculate percent ribosomal genes and add to osi.metadata
```{r}
ribo.genes <- grep(pattern = "^RP[SL][[:digit:]]", x = rownames(x = osi_object@assays$RNA@data), value = TRUE)
percent.ribo <- Matrix::colSums(osi_object@assays$RNA@data[ribo.genes, ])/Matrix::colSums(osi_object@assays$RNA@data)
osi_object <- AddMetaData(object = osi_object, metadata = percent.ribo, col.name = "percent.ribo")
osi_object
```

Save prefiltered Seurat object 
```{r}
save(osi_object, file=paste(dir,"Data_input/objects/S02.1_Main_Seurat_object_prefilter_neo_osi.RData", sep=""))
```

Filter cells so that remaining cells have nGenes >= 500 and nReads >= 50000
```{r}
osi_object_filtered <- subset(x=osi_object, subset = nCount_RNA > 50000 & nFeature_RNA > 500)
osi_object_filtered
osi_object_filtered
```

Save filtered Seurat object
```{r}
save(osi_object_filtered, file=paste(dir,"Data_input/objects/S02.1_Main_Seurat_object_filtered_neo_osi.RData", sep=""))
```
