---
title: "03.1_Subset_and_general_annotations"
output: html_document
---

Libraries
```{r}
library(Seurat)
library(devtools)
library(clustree)
library(tidyverse)
library(gridExtra)
library(ggridges)
library(ggplot2)
library(ggExtra)
library(clustree)
library(DoubletFinder)
```

Clear environment and load filtered Seurat object 
```{r}
rm(list=ls())
# dir <- "/myVolume/scell_lung_adenocarcinoma/"
dir <- "/home/ubuntu/scell_lung_adenocarcinoma/"
load(file=paste(dir,"Data_input/objects/S03_Merged_main_filtered_with_neo_osi.RData", sep=""))
```

Drop any samples with 10 or less cells
```{r}
main_tiss_filtered1@meta.data$sample_name <- as.character(main_tiss_filtered1@meta.data$sample_name)
sample_name <- as.character(main_tiss_filtered1@meta.data$sample_name)
# Make table 
tab.1 <- table(main_tiss_filtered1@meta.data$sample_name) 
# Which samples have less than 10 cells 
samples.keep <- names(which(tab.1 > 10))
metadata_keep <- filter(main_tiss_filtered1@meta.data, sample_name %in% samples.keep)
# Subset Seurat object 
tiss_subset <- subset(main_tiss_filtered1, cells=as.character(metadata_keep$cell_id))
tiss_subset
```

Check sample and patient counts
```{r}
table(tiss_subset@meta.data$sample_name)
table(tiss_subset@meta.data$patient_id)
```

Save Tiss Subset
```{r}
save(tiss_subset, file=paste(dir,"Data_input/objects/S03_subset_preprocessed.RData", sep=""))
# load(file="~/scell_lung_adenocarcinoma/Data_input/objects/S03_subset_preprocessed.RData")
```

Normalize and scale the data
```{r}
tiss_subset <- NormalizeData(object = tiss_subset, scale.factor = 1e6)
tiss_subset <- ScaleData(object = tiss_subset)
```

Find variable genes
```{r}
tiss_subset <- FindVariableFeatures(object = tiss_subset)
```

Perform PCA
```{r}
tiss_subset <- RunPCA(object = tiss_subset, do.print = FALSE)
```

Visualize variance along each component
```{r}
ElbowPlot(tiss_subset)
```

Visualize first two PCs
```{r}
DimPlot(tiss_subset, reduction = 'pca')
```

Visualize top genes and their loadings 
```{r}
VizDimLoadings(tiss_subset, dims = 1:5, reduction = "pca", nfeatures = 10)
```

Visualize top genes in principal components
```{r}
DimHeatmap(tiss_subset, dims = 1:10, cells = 100, balanced = TRUE)
```

Set nPCs from above visualizations
```{r}
n.pcs <- 20
```

Construct Neighbor graph 
```{r}
tiss_subset <- FindNeighbors(object = tiss_subset, dims = 1:20, verbose = T)
```

Check clustering stability at given resolution
```{r}
# Set different resolutions
res.used <- seq(0.1,1,by=0.2)
# Loop over and perform clustering of different resolutions
for(i in res.used){
        tiss_subset <- FindClusters(object = tiss_subset, reduction.type = "pca", dims.use = 1:n.pcs,
        resolution = i, print.output = 0, save.SNN = TRUE, k.param = 30, force.recalc = T)
        }
# rename best response column to best_reaction as to not confuse clustree with res
colnames(tiss_subset@meta.data)
colnames(tiss_subset@meta.data)[colnames(tiss_subset@meta.data) == 'best_response_status'] <- 'best_rxn_status'
# Make plot
clus.tree.out <- clustree(tiss_subset) +
    theme(legend.position = "bottom") +
    scale_color_brewer(palette = "Set1") +
    scale_edge_color_continuous(low = "grey80", high = "red")
# Plot
clus.tree.out
```

Find Clusters 
```{r}
tiss_subset <- FindClusters(object = tiss_subset, verbose = T, resolution = 0.5)
```

Run and project TSNEs
```{r}
tiss_subset <- RunTSNE(tiss_subset, dims = 1:20)
DimPlot(tiss_subset, reduction = "tsne", label = TRUE)
```

Find Doublets, pK Identification (no ground-truth)
```{r}
sweep.res.tiss_subset <- paramSweep_v3(tiss_subset, PCs = 1:20, sct = FALSE)
sweep.stats_tiss_subset <- summarizeSweep(sweep.res.tiss_subset, GT = FALSE)
bcmvn_tiss_subset <- find.pK(sweep.stats_tiss_subset)
```

Homotypic Doublet Proportion Estimate
```{r}
homotypic.prop <- modelHomotypic(tiss_subset$seurat_clusters)
nExp_poi <- round(0.01*length(tiss_subset@meta.data$cell_id))  ## Assuming 1% doublet formation rate for SmartSeq2
nExp_poi.adj <- round(nExp_poi*(1-homotypic.prop))
```

Run DoubletFinder using nExp_poi.adj
```{r}
tiss_subset <- doubletFinder_v3(tiss_subset, PCs = 1:10, pN = 0.25, pK = 0.09, nExp = nExp_poi.adj, sct = FALSE)
```

Check Doublet outputs
```{r}
hist(tiss_subset@meta.data$pANN_0.25_0.09_218)
table(tiss_subset@meta.data$DF.classifications_0.25_0.09_218)
table(tiss_subset@meta.data$DF.classifications_0.25_0.09_218, tiss_subset1@meta.data$immune_annotation)
DimPlot(tiss_subset, reduction = "tsne", group.by = "DF.classifications_0.25_0.09_218")
VlnPlot(tiss_subset, features = "nFeature_RNA", group.by = "DF.classifications_0.25_0.09_218")
```

Remove doublets (estimated at 1%)
```{r}
singlet_cells <- row.names(tiss_subset@meta.data)[which(tiss_subset@meta.data$DF.classifications_0.25_0.09_218=='Singlet')]
length(singlet_cells)
# Subset only the singlet cells
tiss_subset <-subset(tiss_subset, cells = singlet_cells)
```

Construct Neighbor graph 
```{r}
tiss_subset <- FindNeighbors(object = tiss_subset, dims = 1:20, verbose = T)
```

Check clustering stability at given resolution
```{r}
# Set different resolutions
res.used <- seq(0.1,1,by=0.2)
# Loop over and perform clustering of different resolutions
for(i in res.used){
        tiss_subset <- FindClusters(object = tiss_subset, reduction.type = "pca", dims.use = 1:n.pcs,
        resolution = i, print.output = 0, save.SNN = TRUE, k.param = 30, force.recalc = T)
        }
# rename best response column to best_reaction as to not confuse clustree with res
colnames(tiss_subset@meta.data)
colnames(tiss_subset@meta.data)[colnames(tiss_subset@meta.data) == 'best_response_status'] <- 'best_rxn_status'
# Make plot
clus.tree.out <- clustree(tiss_subset) +
    theme(legend.position = "bottom") +
    scale_color_brewer(palette = "Set1") +
    scale_edge_color_continuous(low = "grey80", high = "red")
# Plot
clus.tree.out
```

Find Clusters 
```{r}
tiss_subset <- FindClusters(object = tiss_subset, verbose = T, resolution = 0.5)
```

Visualize TSNE colored by cluster
```{r}
pdf(paste(dir,"plot_out/S03/main_tSNE_nodups.pdf", sep=""),10,10)
DimPlot(tiss_subset, reduction = "tsne", label = T)
DimPlot(tiss_subset, reduction = "tsne", label = T)
dev.off()
```

Plot genes of interest and save 
```{r}
# Specify genes  
genes_to_check = c("PTPRC","CD3G","CD3E", "CD79A", "BLNK", "CD68", "CSF1R", "MARCO", "CD207", "FCGR2B", "EPCAM","MYLK","THY1","CD34","PMEL")
# All on Dotplot 
p <- DotPlot(tiss_subset, features = genes_to_check) + coord_flip()
ggsave(paste(dir,"plot_out/S03/dotplot_of_gene_markers.pdf", sep=""), p, width = 10, height = 10)
p
```
Plot genes of interest on dotplot  
```{r}
# Specify genes  
genes_to_check = c("PTPRC","EPCAM")
# All on Dotplot 
p <- DotPlot(tiss_subset, features = genes_to_check) + coord_flip()
ggsave(paste(dir,"plot_out/S03/dotplot_of_PTPRC_EPCAM.pdf", sep=""), p, width = 10, height = 10)
p
```

Annotate Immune vs Nonimmune clusters
At this point we dont care for a more detailed annotation as we will annotate immune and non-immune separately later
```{r}
#add column 'main_seurat_cluster' to store cluster ids from this step.
tiss_subset@meta.data$main_seurat_cluster <- tiss_subset@meta.data$seurat_clusters
# Change the column of the resolution if you ended up using a different one than 0.5 
cluster.ids <- sort(as.numeric(unique(as.character(tiss_subset@meta.data$RNA_snn_res.0.5))))
# Manually check and ananotate each cluster to immmune and non-immune   
immune_annotation <- c("immune","non-immune","immune","immune","immune","non-immune",
                       "immune","non-immune","non-immune","immune", "non-immune",
                       "non-immune","immune","immune","immune","non-immune",
                       "non-immune","immune","non-immune","non-immune","immune",
                       "immune","non-immune","non-immune","non-immune","immune")
# Add annotation to the Seurat object 
tiss_subset@meta.data$immune_annotation <- tiss_subset@meta.data$seurat_clusters 
tiss_subset@meta.data$immune_annotation <- plyr::mapvalues(x = tiss_subset@meta.data$immune_annotation, from = cluster.ids, to = immune_annotation)
# Make a table 
table(tiss_subset@meta.data$immune_annotation)
table(tiss_subset@meta.data$immune_annotation, tiss_subset@meta.data$main_seurat_cluster)
```

Make and save relevant plots 
```{r}
# TSNE plot 
p <- TSNEPlot(object = tiss_subset, do.label = FALSE, group.by = 'immune_annotation')
ggsave(paste(dir,"plot_out/S03/main_tSNE_immune_annotation.pdf", sep=""), p, width = 10, height = 10)
# Annotation count 
p <- ggplot(tiss_subset@meta.data, aes(immune_annotation)) + geom_bar() + 
  coord_flip() + theme(legend.position = "bottom") + xlab("annotation") +
  ylab("count")
ggsave(paste(dir,"plot_out/S03/annotation_count.pdf", sep=""), p, width = 10, height = 10)
# Reads vs Genes 
p <- ggplot(tiss_subset@meta.data, aes(x = nFeature_RNA, y = nCount_RNA)) + geom_point() + theme_bw() + scale_y_log10()
ggsave(paste(dir,"plot_out/S03/reads_vs_genes.pdf", sep=""), p, width = 10, height = 10)
```

Generate immune and nonimmune cell lists
```{r}
# Immune dataset 
cells.use.immune <- row.names(tiss_subset@meta.data)[which(tiss_subset@meta.data$immune_annotation=='immune')]
length(cells.use.immune)
tiss_immune <- subset(tiss_subset, cells=cells.use.immune)
immune_cells <- rownames(tiss_immune@meta.data)
write.csv(immune_cells, file = paste(dir,"data_out/S03/immune_cells.csv", sep=""))
# Non-immune dataset
cells.use.nonimmune <- row.names(tiss_subset@meta.data)[which(tiss_subset@meta.data$immune_annotation=='non-immune')]
length(cells.use.nonimmune)
tiss_nonimmune <-subset(tiss_subset, cells=cells.use.nonimmune)
nonimmune_cells <- rownames(tiss_nonimmune@meta.data)
write.csv(nonimmune_cells, file = paste(dir,"data_out/S03/nonimmune_cells.csv", sep=""))
```

Save Processed Subset Seurat Object
```{r}
save(tiss_subset, file=paste(dir,"Data_input/objects/S03_Main_Seurat_object_filtered_and_subset.RData", sep=""))
save(tiss_immune, file=paste(dir,"Data_input/objects/S03_Immuune_Seurat_object.RData", sep=""))
save(tiss_nonimmune, file=paste(dir,"Data_input/objects/S03_Nonimmune_Seurat_object.RData", sep=""))
```

