---
title: "03_Subset_and_general_annotations"
output: html_document
---

Libraries
```{r}
library(Seurat)
library(devtools)
library(clustree)
library(tidyverse)
library(gridExtra)
library(ggridges)
library(ggplot2)
```

Clear environment and load filtered Seurat object 
```{r}
# rm(list=ls())
dir <- "/myVolume/scell_lung_adenocarcinoma/"
load(file=paste(dir,"Data_input/02_Main_Seurat_object_filtered.RData", sep=""))
```

Drop any samples with 10 or less cells
```{r}
main_tiss_filtered@meta.data$sample_name <- as.character(main_tiss_filtered@meta.data$sample_name)
# Make table 
tab.1 <- table(main_tiss_filtered@meta.data$sample_name) 
# Which samples have less than 10 cells 
samples.keep <- names(which(tab.1 > 10))
metadata_keep <- filter(main_tiss_filtered@meta.data, sample_name %in% samples.keep)
# Subset Seurat object 
tiss_subset <- SubsetData(main_tiss_filtered, cells.use = as.character(metadata_keep$cell_id))
tiss_subset
```

Save subseted Seurat object
```{r}
save(tiss_subset, file=paste(dir,"Data_input/S03_Main_Seurat_object_filtered_and_subset.RData", sep=""))
```

Normalize and scale the data
```{r}
tiss_subset <- NormalizeData(object = tiss_subset, scale.factor = 1e6)
tiss_subset <- ScaleData(object = tiss_subset)
```

Find variable genes
```{r}
tiss_subset <- FindVariableGenes(object = tiss_subset, do.plot = TRUE, x.high.cutoff = Inf, y.cutoff = 0.5)
```

Perform PCA
```{r}
tiss_subset <- RunPCA(object = tiss_subset, do.print = FALSE)
tiss_subset <- ProjectPCA(object = tiss_subset, do.print = FALSE)
```

Visualize top genes in principal components
```{r}
PCHeatmap(object = tiss_subset, pc.use = 1:15, cells.use = 100, do.balanced = TRUE, label.columns = FALSE, num.genes = 10)
```

Perform correlation of PCs and metadata fields
```{r}
#install.packages("corrplot")
require(corrplot)
pca.obj <- tiss_subset@dr$pca
pc.coords <- pca.obj@cell.embeddings
df1 <- tiss_subset@meta.data[,c("nGene","nReads","percent.ribo")]
df2 <- pc.coords[,c(1:10)]
cordf12 <- cor(df1,df2)
# Make a correlation plot
corrplot(cordf12, method = "number", main="Correlation of PCs and metadata")
```
Also visaulize PC variance
```{r}
#comp.dev <-pca.obj@sdev
PCElbowPlot(object = tiss_subset)
```

Choose the number of principal components to use.

```{r}
n.pcs = 20
```

Check clustering stability at given resolution 
```{r}
# Set different resolutions 
res.used <- seq(0.1,1,by=0.2)
# Loop over and perform clustering of different resolutions 
for(i in res.used){
        tiss_subset <- FindClusters(object = tiss_subset, reduction.type = "pca", dims.use = 1:n.pcs, 
        resolution = i, print.output = 0, save.SNN = TRUE, k.param = 30, force.recalc = T)
        }
# rename best response column to best_reaction as to not confuse clustree with res
colnames(tiss_subset@meta.data)
colnames(tiss_subset@meta.data)[colnames(tiss_subset@meta.data) == 'best_response_status'] <- 'best_rxn_status'
# Make plot 
clus.tree.out <- clustree(tiss_subset) +
    theme(legend.position = "bottom") + 
    scale_color_brewer(palette = "Set1") +
    scale_edge_color_continuous(low = "grey80", high = "red")
# Save pdf 
ggsave(clus.tree.out, filename = paste(dir,"plot_out/S03/Cluster_resolutions_clustree_output_all.pdf", sep=""), width = 15, height = 15)
# Plot 
clus.tree.out
```


Set resolution and perform clustering
```{r}
res.used <- 0.5
tiss_subset <- FindClusters(object = tiss_subset, reduction.type = "pca", dims.use = 1:n.pcs, 
    resolution = res.used, print.output = 0, save.SNN = TRUE, k.param = 30, force.recalc = T)
```

Perform  tSNE
```{r}
tiss_subset <- RunTSNE(object = tiss_subset, dims.use = 1:n.pcs, seed.use = 10, perplexity=30)
```

Visualize TSNE colored by cluster
```{r}
pdf(paste(dir,"plot_out/S03/main_tSNE.pdf", sep=""),10,10)
TSNEPlot(object = tiss_subset, do.label = T)
dev.off()
```

Plot genes of interest 
```{r}
# Specify genes  
genes_to_check = c("PTPRC","CD3G","CD3E", "CD79A", "BLNK", "CD68", "CSF1R", "MARCO", "CD207")
# All on Dotplot 
pdf(paste(dir,"plot_out/S03/dotplot_of_gene_markers.pdf", sep=""),10,10)
DotPlot(tiss_subset, genes_to_check, x.lab.rot = T)
dev.off()
```

Annotate Immune vs Nonimmune clusters
At this point we dont care for a more detailed annotation as we will annotate immune and non-immune separately later
```{r}
#add column 'main_seurat_cluster' to store cluster ids from this step.
tiss_subset@meta.data$main_seurat_cluster <- tiss_subset@meta.data$res.0.5
# Change the column of the resolution if you ended up using a different one than 0.5 
cluster.ids <- sort(unique(as.numeric(tiss_subset@meta.data$main_seurat_cluster)))
# Manually check and ananotate each cluster to immmune and non-immune   
immune_annotation <- c("immune","immune","non-immune", "non-immune", "immune", "non-immune", "non-immune", "immune", "non-immune", "immune", "immune", "non-immune", "immune", "immune", "non-immune", "immune", "immune", "non-immune", "immune", "non-immune", "non-immune", "non-immune","non-immune", "immune", "non-immune", "non-immune")
# Add annotation to the Seurat objedct 
tiss_subset@meta.data[,'immune_annotation'] <- plyr::mapvalues(x = tiss_subset@ident, from = cluster.ids, to = immune_annotation)
# MAke a table 
table(tiss_subset@meta.data$immune_annotation)
```

Generate immune and nonimmune cell lists
```{r}
cells.use.immune <- row.names(tiss_subset@meta.data)[which(tiss_subset@meta.data$immune_annotation=='immune')]
length(cells.use.immune)
immune_subset <- SubsetData(tiss_subset, cells.use = cells.use.immune)
immune_subset
immune_cells <- rownames(immune_subset@meta.data)
write.csv(immune_cells, file = paste(dir,"data_out/S03/immune_cells.csv", sep=""))

cells.use.nonimmune <- row.names(tiss_subset@meta.data)[which(tiss_subset@meta.data$immune_annotation=='non-immune')]
length(cells.use.nonimmune)
nonimmune_subset <- SubsetData(tiss_subset, cells.use = cells.use.nonimmune)
nonimmune_subset
nonimmune_cells <- rownames(nonimmune_subset@meta.data)
head(nonimmune_cells)
write.csv(nonimmune_cells, file = paste(dir,"data_out/S03/nonimmune_cells.csv", sep=""))
```

Create Immune Only Seurat Object
```{r}
tiss_immune <- SubsetData(tiss_subset, cells.use = immune_cells)
```

Create Non-immune Only Seurat Object
```{r}
tiss_nonimmune <- SubsetData(tiss_subset, cells.use = nonimmune_cells)
```

Save Processed Subset Seurat Object
```{r}
save(tiss_subset, file=paste(dir,"Data_input/S03_Main_Seurat_object_filtered_and_subset.RData", sep=""))
save(tiss_immune, file=paste(dir,"Data_input/S03_Immuune_Seurat_object.RData", sep=""))
save(tiss_nonimmune, file=paste(dir,"Data_input/S03_Nonimmune_Seurat_object.RData", sep=""))
```

