---
title: "IM01"
author: "Spyros"
date: "19/9/2018"
output: html_document
---

Clear environment (optional) and load Seurat object containing Immune cells (from script S03)
variable "dir" should be changed to point to the location of the cloned github repo locally
```{r}
rm(list=ls())
# dir <- "/myVolume/scell_lung_adenocarcinoma/"
dir <- "/home/ubuntu/scell_lung_adenocarcinoma/"
load(file=paste(dir,"Data_input/objects/S03_Immune_Seurat_object_nodups.RData", sep=""))
tiss_immune
```

Table of immune/non-immune cells 
```{r}
table(tiss_immune@meta.data$immune_annotation)
```
The 353 non-immune cells will be removed from the analysis
```{r}
tiss_immune <- subset(x = tiss_immune, subset = immune_annotation == "immune")
tiss_immune
```
Table of immune/non-immune cells 
```{r}
table(tiss_immune@meta.data$immune_annotation)
```

Normalize data
```{r}
require(Seurat)
tiss_immune <- NormalizeData(object = tiss_immune)
```


Find variable genes
```{r}
tiss_immune <- FindVariableFeatures(object = tiss_immune)
```

Scale data
```{r}
tiss_immune <- ScaleData(object = tiss_immune, features = rownames(tiss_immune))
```


Perform PCA
```{r}
tiss_immune <- RunPCA(object = tiss_immune, do.print = FALSE)
```
Visualize variance along each component
```{r}
ElbowPlot(tiss_immune)
```

Visualize top genes and their loadings 
```{r}
VizDimLoadings(tiss_immune, dims = 1:5, reduction = "pca", nfeatures = 10)
```

Visualize top genes in principal components
```{r}
DimHeatmap(tiss_immune, dims = 1:10, cells = 100, balanced = TRUE)
```
Construct Neighbor graph 
```{r}
tiss_immune <- FindNeighbors(object = tiss_immune, verbose = T)
```

Find Clusters 
```{r}
tiss_immune <- FindClusters(object = tiss_immune, verbose = T, resolution = 0.7)
```
Run and project TSNEs
```{r}
tiss_immune <- RunTSNE(tiss_immune, dims = 1:20)
DimPlot(tiss_immune, reduction = "tsne", label = T)
```

Visualize first two PCs
```{r}
PCAPlot(object = tiss_immune)
```

Visualize metadata fields on TSNE 
```{r}
TSNEPlot(object = tiss_immune, do.label = F, group.by = "driver_gene")
```

Visualize metadata fields on TSNE 
```{r}
TSNEPlot(object = tiss_immune, do.label = F, group.by = "patient_id")
```


Find markers for each cluster
```{r}
tiss.markers.immune <- FindAllMarkers(object = tiss_immune, only.pos = TRUE, min.pct = 0.25, thresh.use = 0.25, 
                                      do.print=T, max.cells.per.ident = 500)
```

Write differential gene table
```{r}
write.table(tiss.markers.immune, file=paste(dir,"data_out/IM01/Immune_cells_DE_genes_among_Seurat_clusters.csv", sep=""))
#tiss.markers.immune <- read.table(file=paste(dir,"data_out/IM01/Immune_cells_DE_genes_among_Seurat_clusters.csv", sep=""))
```

Display the top markers you computed above.
```{r}
require(tidyverse)
require(dplyr)
tiss.markers.immune %>% group_by(cluster) %>% top_n(10, avg_logFC)
```

Short list of genes (top5) per cluster
```{r}
markers.small  <- tiss.markers.immune %>% group_by(cluster) %>% top_n(5, avg_logFC)
genes_to_check <- unique(markers.small$gene)
```

Create plot pdf bundle
```{r}
pdf(paste(dir,"plot_out/IM01/Immune_cells_first_annotation_plots.pdf", sep=""),10,10)
# Plot TSNEs with different annotations 
DimPlot(tiss_immune, reduction = "tsne", label = F)
DimPlot(tiss_immune, reduction = "tsne", label = T)
DimPlot(tiss_immune, reduction = "tsne", label = F, group.by = "driver_gene")
DimPlot(tiss_immune, reduction = "tsne", label = F, group.by = "patient_id")
# Create Dotplot 
DotPlot(tiss_immune, features = genes_to_check) + coord_flip()
DoHeatmap(tiss_immune, features = genes_to_check, raster = F) + NoLegend()
# Barplot of patients per cluster 
tab1 <- cbind(as.data.frame(tiss_immune@meta.data$patient_id),as.data.frame(tiss_immune@meta.data$RNA_snn_res.0.7))
colnames(tab1) <- c("Patient", "Immune.cluster")
ggplot(tab1) +
  aes(x = Immune.cluster, fill = factor(Patient)) +
  geom_bar(position = "fill")
dev.off()
# 
```

Plot individualy
Dotplot of top N DE expressed genes 
```{r}
Ngenes <- 5
markers.small  <- tiss.markers.immune %>% group_by(cluster) %>% top_n(Ngenes, avg_logFC)
genes_to_check <- unique(markers.small$gene)
# Create Dotplot 
DotPlot(tiss_immune, features = genes_to_check) + coord_flip()
```

Plot individualy
Heatmap of top N DE expressed genes 
```{r}
Ngenes <- 5
markers.small  <- tiss.markers.immune %>% group_by(cluster) %>% top_n(Ngenes, avg_logFC)
genes_to_check <- unique(markers.small$gene)
# Create Heatmap
DoHeatmap(tiss_immune, features = genes_to_check) + NoLegend()
```

Plot individualy
Patients per cluster
```{r}
# Barplot of patients per cluster 
tab1 <- cbind(as.data.frame(tiss_immune@meta.data$patient_id),as.data.frame(tiss_immune@meta.data$RNA_snn_res.0.7))
colnames(tab1) <- c("Patient", "Immune.cluster")
ggplot(tab1) +
  aes(x = Immune.cluster, fill = factor(Patient)) +
  geom_bar(position = "fill") + theme_bw()
```

Calculate and plot average expression of broad cell type specific gene sets 
```{r}
require(ggridges)
require(ggplot2)
# # # 
cell.genes <- read.table(paste(dir,"gene_lists/broad_cell_markers_immune.csv", sep=""), header=T)
cell.types  <- as.character(unique(cell.genes$cell))
tsne.coor <- Embeddings(tiss_immune,reduction = "tsne")
## 
ggplot.list <- list()
ggplot.list.2 <- list()
# 
# rm(temp)
data_temp <- as.data.frame(as.matrix(GetAssayData(object = tiss_immune, slot = "data")))
for(i in 1:length(unique(cell.types))){
genes <- as.character(cell.genes$gene[which(cell.genes$cell==cell.types[i])])
gene.exp <- colMeans(as.matrix(data_temp[genes,]))[row.names(tsne.coor)]
clusters <- tiss_immune@meta.data$RNA_snn_res.0.7
# Make ggplot friendly 
temp <- as.data.frame(cbind(tsne.coor, as.data.frame(gene.exp), as.data.frame(clusters)))
# Plot with ggplot 
ggplot.list[[i]] <- ggplot(temp, aes(tSNE_1, tSNE_2)) + 
      geom_point(aes(colour = gene.exp)) + 
      scale_colour_gradient(low = "grey95", high = "red") + 
      labs(title = cell.types[i], subtitle = paste(genes, collapse = ", "))
# Boxplot per cluster 
ggplot.list.2[[i]] <- ggplot(temp, aes(x = clusters, y = gene.exp)) + 
                      geom_boxplot() + 
                      ggtitle(cell.types[i]) + ylab("Average gene expression (log)")
}
# Plot all 
require(grid)
require(gridExtra)
require(gbm)
n <- length(ggplot.list)
nCol <- floor(sqrt(n))
# Expression on tSNE
pdf(paste(dir,"plot_out/IM01/Immune_cells_TSNE_with_average_expression_of_cell_markers.pdf", sep=""),15,15)
do.call("grid.arrange", c(ggplot.list, ncol=nCol))
dev.off()
# Expression per cluster boxplots 
pdf(paste(dir,"plot_out/IM01/Immune_cells_boxplots_with_average_expression_of_cell_markers.pdf", sep=""),15,15)
do.call("grid.arrange", c(ggplot.list.2, ncol=nCol))
dev.off()
```


Annotate cells
```{r}
tiss.markers.immune %>% group_by(cluster) %>% top_n(5, avg_logFC)
# stash current cluster IDs
tiss_immune[["immune.subcluster.ids"]] <- Idents(object = tiss_immune)
# enumerate current cluster IDs and the labels for them
cluster.ids <- 0:(length(unique(tiss_immune@meta.data$immune.subcluster.ids))-1)
# Annotate each of the clusters 
free_annotation <- c("T-cells","MF-Monocytes", "MF-Monocytes", "B-cells-PB", "MF-Monocytes", "T-cells", "T-cells", "Neutrophils", "Dendritic", "Mast-cells", "MF-Monocytes", "T-cells", "B-cells-M", "Unknown", "T-cells", "pDCs", "B-cells-M", "MF-Monocytes")
# free_annotation <- c("0","1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "17", "18")
# free_annotation <- c("T-cells","B-cells-PB","B-cells-M", "MF-Monocytes", "Neutrophils", "Dendritic", "Mast-cells", "pDCs")
#                       
# Map free annotation to cluster numbers and store as immune_subtype_annotation
tiss_immune@meta.data[,'immune_subtype_annotation'] <- plyr::mapvalues(x = tiss_immune@meta.data$immune.subcluster.ids, from = cluster.ids, to = free_annotation)
# Plot 
pdf(paste(dir,"plot_out/IM01/Immune_cells_free_annotation_on_TSNE.pdf", sep=""),width = 10,height = 10)
DimPlot(tiss_immune, reduction = "tsne", label = F, group.by = 'immune_subtype_annotation')
DimPlot(tiss_immune, reduction = "tsne", label = T, group.by = 'immune_subtype_annotation')
dev.off()
```
# Barplot of all immune cell counts 
```{r}
table.temp <- as.data.frame(table(tiss_immune@meta.data$immune_subtype_annotation))
table.temp$Var1 <- factor(table.temp$Var1,levels = as.character(table.temp$Var1[order(table.temp$Freq,decreasing=F)]))
p <-  ggplot(data=table.temp, aes(x=Var1, y=Freq)) +
      geom_bar(stat="identity") + coord_flip()
ggsave(paste(dir,"plot_out/IM01/Immune_cell_counts.pdf", sep=""), width = 90, height = 90, units = "mm")
p
```

Patient occupancy per cell type 
```{r}
require(reshape)
# Barplot of patients per cluster 
tab1 <- table(tiss_immune@meta.data$patient_id, tiss_immune@meta.data$immune_subtype_annotation)
# 
tab1 <- melt((apply(tab1, MARGIN = 2, max)/colSums(tab1))*100)
tab1$cell.type <- row.names(tab1)
# # Order 
# tab1 <- tab1[order(tab1$value),]
# tab1$cell.type <- factor(tab1$cell.type, levels = tab1$cell.type)
# 
tab1$cell.type <- factor(tab1$cell.type,levels = as.character(table.temp$Var1[order(table.temp$Freq,decreasing=F)]))
p <-  ggplot(data=tab1, aes(x=cell.type, y=value)) +
      geom_bar(stat="identity") + coord_flip() + theme_bw()
ggsave(paste(dir,"plot_out/IM01/Immune_cell_patient_occupancy.pdf", sep=""), width = 90, height = 90, units = "mm")
p
```
Patient occupancy per cluster
```{r}
require(reshape)
# Barplot of patients per cluster 
tab1 <- table(tiss_immune@meta.data$patient_id, tiss_immune@meta.data$RNA_snn_res.0.7)
# 
tab1 <- melt((apply(tab1, MARGIN = 2, max)/colSums(tab1))*100)
tab1$cell.type <- row.names(tab1)
# # Order 
# tab1 <- tab1[order(tab1$value),]
# tab1$cell.type <- factor(tab1$cell.type, levels = tab1$cell.type)
# 
tab1$cell.type <- factor(tab1$cell.type,levels = sort(unique(tiss_immune@meta.data$RNA_snn_res.0.7)))
p <-  ggplot(data=tab1, aes(x=cell.type, y=value)) +
      geom_bar(stat="identity") + coord_flip() + theme_bw()
ggsave(paste(dir,"plot_out/IM01/Immune_cell_patient_occupancy_by_cluster.pdf", sep=""), width = 90, height = 90, units = "mm")
p
```


Change lung to Lung 
```{r}
tiss_immune@meta.data$biopsy_site <- gsub("lung", "Lung", tiss_immune@meta.data$biopsy_site)
table(tiss_immune@meta.data$biopsy_site)
```

Export table of all samples broken down by cell type 
```{r}
write.table(table(tiss_immune@meta.data$sample_name, tiss_immune@meta.data$immune_subtype_annotation), file = paste(dir,"data_out/IM01/Table_of_immune_cell_types_by_sample.csv", sep=""))
```



Save immune cell workspace 
```{r}
save(tiss_immune, file=paste(dir,"Data_input/objects/IM01_Immune_Seurat_object_nodups.RData", sep=""))
```




