---
title: "IM02"
output: html_document
---

Count the fraction of Immune cells across different metadata fields 

Libraries 
```{r}
require(tidyr)
require(reshape)
require(ggthemes)
require(rcompanion)
require(ggpubr)
require(GGally)
```

Load immune workspace
```{r}
# rm(list=ls())
# dir <- "/myVolume/scell_lung_adenocarcinoma/"
dir <- "/home/ubuntu/scell_lung_adenocarcinoma/"
load(file=paste(dir,"Data_input/objects/IM01_Immune_Seurat_object_nodups.RData", sep=""))
```

# Subset metadata 
Remove cells that are not immune or are annotated as treatment status Pending or unknown. Also 
exclude thoracentesis derived immune cells as they are not necessarily proximal to the tumor. Brain will also be removed 
since it only has <10 cells. 

Plot fractional changes of selected cell populations across treatment 
```{r}
library(ggrepel)
require(qdapTools)
require(REdaS)
# 
metadata <- tiss_immune@meta.data
# Keep only cells from tissues that are not brain or pleura 
metadata <- metadata[-which(metadata$biopsy_site=="Brain" | metadata$biopsy_site=="Pleura"),]
# Convert to factor with logical order 
metadata$analysis <- factor(metadata$analysis, levels = c("naive", "grouped_pr", "grouped_pd"))
# Create table and keep selected cell types 
meta.temp <- metadata[,c("immune_subtype_annotation", "analysis")]
# Loop over treatment response categories 
# Create list to store frequency tables 
prop.table.error <- list()
for(i in 1:length(unique(meta.temp$analysis))){
vec.temp <- meta.temp[meta.temp$analysis==unique(meta.temp$analysis)[i],"immune_subtype_annotation"]
# Convert to counts and calculate 95% CI 
# Store in list 
table.temp <- freqCI(vec.temp, level = c(.95))
prop.table.error[[i]] <- print(table.temp, percent = TRUE, digits = 3)
# 
}
# Name list 
names(prop.table.error) <- unique(meta.temp$analysis)
# Convert to data frame 
tab.1 <- as.data.frame.array(do.call(rbind, prop.table.error))
# Add analysis column 
b <- c()
a <- c()
for(i in names(prop.table.error)){
  a <- rep(i,nrow(prop.table.error[[1]]))
  b <- c(b,a)
}
tab.1$analysis <- b
# Add common cell names 
aa <- gsub(x = row.names(tab.1), ".1", "")
aa <- gsub(x = aa, ".2", "")
tab.1$cell <- aa
# 
# Resort factor analysis 
tab.1$analysis <- factor(tab.1$analysis, levels = c("naive", "grouped_pr", "grouped_pd"))
# Rename percentile columns 
colnames(tab.1)[1] <- "lower"
colnames(tab.1)[3] <- "upper"
# 
p<- ggplot(tab.1, aes(x=analysis, y=Estimate, group=cell)) +
    geom_line(aes(color=cell))+
    geom_point(aes(color=cell)) + facet_grid(cols =  vars(cell)) + 
    theme(axis.text.x = element_text(angle = 45, hjust=1, vjust=0.5), legend.position="bottom") + 
    xlab("") + 
    geom_errorbar(aes(ymin=lower, ymax=upper), width=.2,position=position_dodge(0.05))
p1<- ggplot(tab.1, aes(x=analysis, y=Estimate, group=cell)) +
    geom_bar(stat = "identity", aes(fill=cell)) + facet_grid(cols =  vars(cell)) + 
    theme_bw() +  
    theme(axis.text.x = element_text(angle = 45, hjust=1, vjust=0.5), legend.position= "none") + 
    xlab("") + 
    geom_errorbar(aes(ymin=lower, ymax=upper), width=.2,position=position_dodge(0.05))
# Save plot 
ggsave(p1, filename = paste(dir,"plot_out/IM02/All_immune_populations_across_treatment2.pdf", sep=""),width = 11, height = 8)
p1
```


Export table of all samples broken down by cell type 
```{r}
library(tidyr)
tab.S1 <- as.data.frame(table(tiss_immune@meta.data$sample_name, tiss_immune@meta.data$immune_subtype_annotation))
tab.S1 <- spread(tab.S1, Var2, Freq)
# Add Sum column 
tab.S1$"Sum_Immune" <- rowSums(tab.S1[,-1])
# Add a column and annotate samples used in the fractional analysis 
samples <- unique(metadata$sample_name)
tab.S1$"Fractional" <- NA
for(i in 1:nrow(tab.S1)){
  a <- which(samples==as.character(tab.S1$Var1[i]))
  if(length(a) != 0) {tab.S1$Fractional[i] <- 1}
}
write.table(tab.S1, file = paste(dir,"data_out/IM02/Table_of_immune_cell_types_by_sample_IM02.csv", sep=""))
```


```{r}
write.table()
paste(dir,"plot_out/IM02/Table_of_samples_used_in_IM02.csv", sep="")

as.data.frame(table(metadata$sample_name))
```


Significance between fractions 
Chi-square Test of Independence  
```{r}
count.mat <- as.matrix(table(meta.temp$analysis,meta.temp$immune_subtype_annotation))
p.mat <- matrix(nrow = ncol(count.mat), ncol=1)
row.names(p.mat) <- colnames(count.mat)
for(i in 1:ncol(count.mat)){
  test <- chisq.test(count.mat[,i])
  p.mat[i,1] <- test$p.value*ncol(count.mat)
}
0.01- as.data.frame(p.mat)
```

Changes of specific cell populations across clinical fields 
All vs All correlation plots 
```{r}
library(ggrepel)
# Create table and keep selected cell types 
meta.temp <- metadata[,c("immune_subtype_annotation", "analysis")]
# Create table for PD and PR
tab.1 <- as.data.frame.array(prop.table(table(meta.temp$immune_subtype_annotation, meta.temp$analysis), margin = 2))
# Correlation matrix 
cor.v <- as.matrix(cor(tab.1))
# Plot 
require(corrplot)
pdf(paste(dir,"plot_out/IM02/All_immune_population_correlations_across_treatment.pdf", sep=""), width = 5, height = 5)
corrplot(cor.v, method = "number", main="Immune annotation correlations", type="lower", diag=F, mar=c(2,2,2,2))
dev.off()
# 
corrplot(cor.v, method = "number", main="Immune annotation correlations", type="lower", diag=F)
```

Changes of specific cell populations across clinical fields 
All vs All correlation plots 
Plot actual correlations between time points 
```{r}
library(ggrepel)
# metadata <- tiss_subset@meta.data
# metadata <- metadata[which(metadata$immune_annotation=="immune"),]
# # Keep only cells from tissues that are not brain or pleura 
# metadata <- metadata[-which(metadata$biopsy_site=="Brain" | metadata$biopsy_site=="Pleura"),]
# # Remove unknown cells 
# # metadata <- metadata[-which(metadata$immune_subtype_annotation=="Unknown"),]
# # Convert to factor with logical order 
# metadata$analysis <- factor(metadata$analysis, levels = c("naive", "grouped_pd", "grouped_pr"))
# Create table and keep selected cell types 
meta.temp <- metadata[,c("immune_subtype_annotation", "analysis")]
# Create table for PD and PR
tab.1 <- as.data.frame.array(prop.table(table(meta.temp$immune_subtype_annotation, meta.temp$analysis), margin = 2))
tab.1$cell.type <- row.names(tab.1)
# Plot correlations 
# Label limits 
x_limits <- c(0.2, 0.5)
# PD vs PR 
cor.v <- cor(tab.1$grouped_pd, tab.1$grouped_pr)
p.1 <-  ggplot(tab.1, aes(x=grouped_pd, y=grouped_pr, label = cell.type)) +
        geom_point(position = position_jitter()) + 
        geom_label_repel(nudge_y = 0.15,direction = "y",hjust= 1,segment.size = 0.1, 
                         label.size = 0, xlim = x_limits) + 
        geom_abline(intercept = 0, slope = 1,linetype = "dashed", color="gray80") + 
        annotate("text", x = 0.05, y = 0.4, label=paste("cor=",round(cor.v,3))) + 
        xlim(0,0.5) + ylim(0,0.5)
# Naive to PD
cor.v <- cor(tab.1$naive, tab.1$grouped_pd)
p.2 <-  ggplot(tab.1, aes(x=naive, y=grouped_pd, label = cell.type)) +
        geom_point(position = position_jitter()) + 
        geom_label_repel(nudge_y = 0.15,direction = "y",hjust= 1,segment.size = 0.1, 
                         label.size = 0, xlim = x_limits) + 
        geom_abline(intercept = 0, slope = 1,linetype = "dashed", color="gray80") + 
        annotate("text", x = 0.05, y = 0.4, label=paste("cor=",round(cor.v,3))) + 
        xlim(0,0.5) + ylim(0,0.5)
# Naive to PR 
cor.v <- cor(tab.1$naive, tab.1$grouped_pr)
p.3 <-  ggplot(tab.1, aes(x=naive, y=grouped_pr, label = cell.type)) +
        geom_point(position = position_jitter()) + 
        geom_label_repel(nudge_y = 0.15,direction = "y",hjust= 1,segment.size = 0.1,
                         label.size = 0, xlim = x_limits) + 
        geom_abline(intercept = 0, slope = 1,linetype = "dashed", color="gray80") + 
        annotate("text", x = 0.05, y = 0.4, label=paste("cor=",round(cor.v,3))) + 
        xlim(0,0.5) + ylim(0,0.5)
# Plot all together
p.all <- grid.arrange(p.1,p.2,p.3,ncol=2)
# Save 
ggsave(filename = paste(dir,"plot_out/IM02/Immune_cell_population_fractions_pairwise.pdf", sep=""), plot = p.all, width = 12, height = 12)
p.all
```

Save immune cell workspace 
```{r}
save(tiss_immune, file=paste(dir,"Data_input/objects/IM01_Immune_Seurat_object_nodups.RData", sep=""))
```




Correlation of immune cell fractions between different driver genes 
All vs All correlation plots 
```{r}
library(ggrepel)
# Create table and keep selected cell types 
metadata <- tiss_immune@meta.data
meta.temp <- metadata[,c("immune_subtype_annotation", "driver_gene")]
# Create table for PD and PR
tab.1 <- as.data.frame.array(prop.table(table(meta.temp$immune_subtype_annotation, meta.temp$driver_gene), margin = 2))
# Correlation matrix 
cor.v <- as.matrix(cor(tab.1))
# Plot 
require(corrplot)
pdf(paste(dir,"plot_out/IM02/All_immune_population_correlations_across_driver_genes.pdf", sep=""), width = 5, height = 5)
corrplot(cor.v, method = "number", main="Immune annotation correlations", type="lower", diag=F, mar=c(2,2,2,2))
dev.off()
# 
corrplot(cor.v, method = "number", main="Immune annotation correlations", type="lower", diag=F)
```

Table of Biopsy site vs analysis 
```{r}
tab.1 <- table(tiss_immune@meta.data$driver_gene, tiss_immune@meta.data$biopsy_site)
balloonplot(tab.1, main ="Driver gene vs Biopsy site", xlab ="", ylab="",
            label = T, show.margins = F)
```

```{r}
library(ggrepel)
# Create table and keep selected cell types 
metadata <- tiss_immune@meta.data
meta.temp <- metadata[,c("immune_subtype_annotation", "driver_gene")]
# Create table for PD and PR
tab.1 <- as.data.frame.array(prop.table(table(meta.temp$immune_subtype_annotation, meta.temp$driver_gene), margin = 2))
tab.1$cell.type <- row.names(tab.1)
# Plot correlations 
# Label limits 
x_limits <- c(0.2, 0.5)
# ALK vs EGFR 
cor.v <- cor(tab.1$ALK, tab.1$EGFR)
p.1 <-  ggplot(tab.1, aes(x=ALK, y=EGFR, label = cell.type)) +
        geom_point(position = position_jitter()) + 
        geom_label_repel(nudge_y = 0.15,direction = "y",hjust= 1,segment.size = 0.1, 
                         label.size = 0, xlim = x_limits) + 
        geom_abline(intercept = 0, slope = 1,linetype = "dashed", color="gray80") + 
        annotate("text", x = 0.05, y = 0.4, label=paste("cor=",round(cor.v,3))) + 
        xlim(0,0.5) + ylim(0,0.5)
# BRAF vs EGFR 
cor.v <- cor(tab.1$BRAF, tab.1$EGFR)
p.2 <-  ggplot(tab.1, aes(x=BRAF, y=EGFR, label = cell.type)) +
        geom_point(position = position_jitter()) + 
        geom_label_repel(nudge_y = 0.15,direction = "y",hjust= 1,segment.size = 0.1, 
                         label.size = 0, xlim = x_limits) + 
        geom_abline(intercept = 0, slope = 1,linetype = "dashed", color="gray80") + 
        annotate("text", x = 0.05, y = 0.4, label=paste("cor=",round(cor.v,3))) + 
        xlim(0,0.5) + ylim(0,0.5)
# BRAF vs ALK
cor.v <- cor(tab.1$BRAF, tab.1$ALK)
p.3 <-  ggplot(tab.1, aes(x=BRAF, y=ALK, label = cell.type)) +
        geom_point(position = position_jitter()) + 
        geom_label_repel(nudge_y = 0.15,direction = "y",hjust= 1,segment.size = 0.1, 
                         label.size = 0, xlim = x_limits) + 
        geom_abline(intercept = 0, slope = 1,linetype = "dashed", color="gray80") + 
        annotate("text", x = 0.05, y = 0.4, label=paste("cor=",round(cor.v,3))) + 
        xlim(0,0.5) + ylim(0,0.5)
# KRAS vs EGFR 
cor.v <- cor(tab.1$KRAS, tab.1$EGFR)
p.4 <-  ggplot(tab.1, aes(x=KRAS, y=EGFR, label = cell.type)) +
        geom_point(position = position_jitter()) + 
        geom_label_repel(nudge_y = 0.15,direction = "y",hjust= 1,segment.size = 0.1, 
                         label.size = 0, xlim = x_limits) + 
        geom_abline(intercept = 0, slope = 1,linetype = "dashed", color="gray80") + 
        annotate("text", x = 0.05, y = 0.4, label=paste("cor=",round(cor.v,3))) + 
        xlim(0,0.5) + ylim(0,0.5)

# Plot all together
p.all <- grid.arrange(p.1,p.2,p.3,p.4,ncol=2)
# Save 
ggsave(filename = paste(dir,"plot_out/IM02/Immune_cell_population_fractions_pairwise_Driver_genes.pdf", sep=""), plot = p.all, width = 12, height = 12)
p.all
```



Correlation of immune cell fractions between different biopsy sites 
All vs All correlation plots 
```{r}
library(ggrepel)
# Create table and keep selected cell types 
metadata <- tiss_immune@meta.data
meta.temp <- metadata[,c("immune_subtype_annotation", "biopsy_site")]
# Create table for PD and PR
tab.1 <- as.data.frame.array(prop.table(table(meta.temp$immune_subtype_annotation, meta.temp$biopsy_site), margin = 2))
# Correlation matrix 
cor.v <- as.matrix(cor(tab.1))
# Plot 
require(corrplot)
pdf(paste(dir,"plot_out/IM02/All_immune_population_correlations_across_biopsy_sites.pdf", sep=""), width = 5, height = 5)
corrplot(cor.v, method = "number", main="Immune annotation correlations", type="lower", diag=F, mar=c(2,2,2,2))
dev.off()
# 
corrplot(cor.v, method = "number", main="Immune annotation correlations", type="lower", diag=F)
```