---
title: "Untitled"
output: html_document
---

More detailed Immune phenotyping of different immune cell types
T-cells 

Load immune workspace
```{r}
rm(list=ls())
dir <- "/myVolume/scell_lung_adenocarcinoma/"
load(file=paste(dir,"Data_input/Immuune_Seurat_object.RData", sep=""))
```


Subset T-cells
```{r}
t.cells <- row.names(tiss_immune@meta.data)[which(tiss_immune@meta.data$immune_subtype_annotation == "T-cells")]
length(t.cells)
t.cell.tiss <- SubsetData(object = tiss_immune, cells.use = t.cells)
```

Save T-cell workspace 
```{r}
save(t.cell.tiss, file=paste(dir,"Data_input/Tcell_Seurat_object.RData", sep=""))
```

Remove other objects 
```{r}
rm(tiss_immune)
```


Classify all T-cells based on CD4 or CD8 expression

First plot CD4 vs CD8
```{r}
t.cell.data <- as.matrix(t.cell.tiss@data[c("CD4", "CD8A"),])
pdf(paste(dir,"plot_out/IM02/cells_CD4_CD8_scatterplot.pdf", sep=""),width = 7, height = 5)
plot(t.cell.data[1,],t.cell.data[2,], xlab="CD8A", ylab="CD4", pch=19)
dev.off()
# 
plot(t.cell.data[1,],t.cell.data[2,], xlab="CD8A", ylab="CD4", pch=19)
```

Score T-cells based on expression of CD4 or CD8
Expression is absolute currently using a cutoff of 0 for expression. 
```{r}
# Convert expression to boolean
t.cell.data[1,which(t.cell.data[1,] != 0)] <- 1
t.cell.data[2,which(t.cell.data[2,] != 0)] <- 3
# Add column for annotating T-cells on CD4 and CD8 expression
t.cell.tiss@meta.data[,"T.cell.generic"] <- NA
# 
vec.score <- c(0,1,3,4)
vec.names <- c("negative", "CD4pos", "CD8pos", "Doublepos")
for(i in 1:length(vec.score)){
    t.cell.tiss@meta.data[names(which(colSums(t.cell.data)==vec.score[i])),"T.cell.generic"] <-  vec.names[i]
}
table(t.cell.tiss@meta.data$T.cell.generic)
```

Unsupervised clustering of T-cells 

Find variable genes
```{r}
t.cell.tiss <- FindVariableGenes(object = t.cell.tiss, do.plot = TRUE, x.high.cutoff = Inf, y.cutoff = 1, num.bin = 20, 
                                          binning.method = "equal_width", do.recalc = T, x.low.cutoff=1)
```

Unsupervised clustering of T-cells 
# PCA
```{r}
t.cell.tiss <- RunPCA(object = t.cell.tiss, do.print = FALSE, pcs.compute = 20)
t.cell.tiss <- ProjectPCA(object = t.cell.tiss, do.print = FALSE)
```

# visualize PCA heatmaps and PC variance
```{r}
PCHeatmap(object = t.cell.tiss, pc.use = 1:15, cells.use = 100, do.balanced = TRUE, label.columns = FALSE, num.genes = 10)
PCElbowPlot(object = t.cell.tiss)
```

Perform correlation of PCs and metadata fields
```{r}
require(corrplot)
pca.obj <- t.cell.tiss@dr$pca
pc.coords <- pca.obj@cell.embeddings
df1 <- t.cell.tiss@meta.data[,c("nGene","nReads","percent.ribo")]
df2 <- pc.coords[,c(1:10)]
cordf12 <- cor(df1,df2)
# Make a correlation plot
corrplot(cordf12, method = "number", main="Correlation of PCs and metadata")
```

JackStraw of PCs 
```{r}
t.cell.tiss <- JackStraw(t.cell.tiss, num.replicate = 100, display.progress = T, 
                         do.par = T, num.cores = 15, num.pc = 15)
JackStrawPlot(t.cell.tiss, PCs = 1:15)
```


Define components to be used for clustering 
```{r}
n.pcs.min = 1
n.pcs.max = 10
```

pick resolution parameter
```{r}
res.used <- 0.3
t.cell.tiss <- FindClusters(object = t.cell.tiss, reduction.type = "pca", dims.use = n.pcs.min:n.pcs.max, 
    resolution = res.used, print.output = 0, save.SNN = TRUE, k.param = 10, force.recalc = T)
```

# Run TSNE
```{r}
t.cell.tiss <- RunTSNE(object = t.cell.tiss, dims.use = n.pcs.min:n.pcs.max, seed.use = 10, perplexity=30)
```

# Plot TSNE
```{r}
TSNEPlot(object = t.cell.tiss, do.label = T)
```

Find all cluster markers 
```{r}
t.cell.markers <- FindAllMarkers(object = t.cell.tiss, only.pos = TRUE, min.pct = 0.25, thresh.use = 0.25)
```

Write table of top genes 
```{r}
write.table(t.cell.markers, paste(dir,"data_out/IM02/T-cells_DE_genes_between_subclusters.csv", sep=""))
```

Plot top genes 
```{r}
require(tidyverse)
t.cell.markers %>% group_by(cluster) %>% top_n(10, avg_logFC) -> top10
DoHeatmap(t.cell.tiss, genes.use = top10$gene, slim.col.label = TRUE, remove.key = TRUE, cex.row = 5)
```



Calculate and plot average expression of broad cell type specific gene sets 
Import a list of genes specific to different T-cell types (Zheng et al and Guo et al)
```{r}
library(ggridges)
library(ggplot2)
# # # 
cell.genes <- read.csv(paste(dir,"gene_lists/Tcell_subtypes_literature.csv", sep=""), header=T)
# Subset gene list to genes that are part of the dataset 
cell.genes <- cell.genes[cell.genes$gene %in%  row.names(t.cell.tiss@data) ,]
cell.types  <- as.character(unique(cell.genes$cell))
tsne.coor <- slot(t.cell.tiss@dr$tsne, "cell.embeddings")
## 
ggplot.list <- list()
ggplot.list.2 <- list()
# 
rm(temp)
for(i in 1:length(unique(cell.types))){
genes <- as.character(cell.genes$gene[which(cell.genes$cell==cell.types[i])])
gene.exp <- colMeans(as.matrix(t.cell.tiss@data[genes,]))[row.names(tsne.coor)]
clusters <- t.cell.tiss@meta.data$res.0.3
# Make ggplot friendly 
temp <- as.data.frame(cbind(tsne.coor, as.data.frame(gene.exp), as.data.frame(clusters)))
# Plot with ggplot 
ggplot.list[[i]] <- ggplot(temp, aes(tSNE_1, tSNE_2)) + 
      geom_point(aes(colour = gene.exp)) + 
      scale_colour_gradient(low = "grey95", high = "red") + 
      labs(title = cell.types[i], subtitle = paste(genes, collapse = ", "))
# Boxplot per cluster 
ggplot.list.2[[i]] <- ggplot(temp, aes(x = clusters, y = gene.exp)) + 
                      geom_boxplot() + 
                      ggtitle(cell.types[i]) + ylab("Average gene expression (log)")
}
# Plot all 
library(gridExtra)
n <- length(ggplot.list)
nCol <- floor(sqrt(n))
# Exzpression on tSNE
pdf(paste(dir,"plot_out/IM02/T-cells_TSNE_with_average_expression_of_cell_markers.pdf", sep=""),15,15)
do.call("grid.arrange", c(ggplot.list, ncol=nCol))
dev.off()
# Expression per cluster boxplots 
pdf(paste(dir,"plot_out/IM02/T-cells_boxplot_with_average_expression_of_cell_markers.pdf", sep=""),15,15)
do.call("grid.arrange", c(ggplot.list.2, ncol=nCol))
dev.off()
```




Plot all relevant, PCA, tSNE and Clustering plots as pdf 
```{r}
pdf(paste(dir,"plot_out/IM02/T-cells_subclustering_TSNE.pdf", sep=""),10,10)
PCHeatmap(object = t.cell.tiss, pc.use = 1:15, cells.use = 100, do.balanced = TRUE, label.columns = FALSE, num.genes = 10)
PCElbowPlot(object = t.cell.tiss)
JackStrawPlot(t.cell.tiss, PCs = 1:12)
TSNEPlot(object = t.cell.tiss, do.label = T)
DoHeatmap(t.cell.tiss, genes.use = top10$gene, slim.col.label = TRUE, remove.key = TRUE, cex.row = 5, title = "Top 10 DE genes")
DoHeatmap(t.cell.tiss, genes.use = cell.genes$gene, slim.col.label = TRUE, remove.key = TRUE, cex.row = 5, title = "Genes of subtypes (Literature)")
# FeaturePlot(t.cell.tiss, genes_to_check_4, pt.size = 1, nCol = 3, cols.use = c("grey90", "red"))
# FeaturePlot(t.cell.tiss, genes_to_check_4, pt.size = 1, nCol = 3, cols.use = c("grey90", "red"))
TSNEPlot(object = t.cell.tiss, do.label = F, group.by = "T.cell.generic")
TSNEPlot(object = t.cell.tiss, do.label = F, group.by = "patient_id")
dev.off()
```


```{r}
VlnPlot(t.cell.tiss, c("CD8A","CD8B", "CD4", "KLRB1","CD3G","FOXP3","GZMB","GZMK"))
VlnPlot(t.cell.tiss, c("CD3G","CD3E"))
```

Annotate T-cells

CD4 and CD8 assignments based on majority of cells within each cluster 
```{r}
table(t.cell.tiss@meta.data$T.cell.generic, t.cell.tiss@meta.data$res.0.3)
```


```{r}
# stash current cluster IDs
t.cell.tiss <- StashIdent(object = t.cell.tiss, save.name = "T_cell.subcluster.ids")
# enumerate current cluster IDs and the labels for them
cluster.ids <- c(0:9)
free_annotation <- c("CD8.cytotoxic_IFNG","CD4.Th", "CD4.Naive", "CD8.cytotoxic_GZMB", "CD4.Treg", "negative.LQ", "CD8.cytotoxic_GZMK", "mixed.exhausted_PD1", "CD8.cytotoxic_GNLY", "NKT")

t.cell.tiss@meta.data[,'t_cell_subtypes'] <- plyr::mapvalues(x = t.cell.tiss@meta.data$T_cell.subcluster.ids, from = cluster.ids, to = free_annotation)
# Plot 
pdf(paste(dir,"plot_out/IM02/T-cells_free_annotation_on_TSNE.pdf", sep=""),10,10)
TSNEPlot(object = t.cell.tiss, do.label = TRUE, pt.size = 1, group.by='t_cell_subtypes', label.size = 3)
TSNEPlot(object = t.cell.tiss, do.label = FALSE, pt.size = 1, group.by='t_cell_subtypes', label.size = 3)
dev.off()
```


# Barplot of T-cell counts 
```{r}
table.temp <- as.data.frame(table(t.cell.tiss@meta.data$t_cell_subtypes))
p <-  ggplot(data=table.temp, aes(x=Var1, y=Freq)) +
      geom_bar(stat="identity") + coord_flip()
ggsave(paste(dir,"plot_out/IM02/T-cells_subtype_counts.pdf", sep=""), width = 10, height = 7)
```

# Boxplot of Ngenes 
```{r}
temp <- cbind(as.data.frame(t.cell.tiss@meta.data$nGene), as.data.frame(t.cell.tiss@meta.data$t_cell_subtypes))
colnames(temp) <- c("ngenes", "subtype")
p <-  ggplot(temp, aes(x=subtype, y=ngenes)) + 
      geom_jitter(position=position_jitter(0.2), color="grey80") +    
      geom_boxplot(outlier.shape = NA) + 
      labs(title="Ngenes by T-cell subtype",x="T-cell subtype", y = "Ngenes") + 
      theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))
ggsave(paste(dir,"plot_out/IM02/T-cells_subtype_ngenes.pdf", sep=""), width = 10, height = 7)
```


Save T-cell workspace 
```{r}
save(t.cell.tiss, file=paste(dir,"Data_input/Tcell_Seurat_object.RData", sep=""))
```

Write annotations of immune cells to tiss_subset
```{r}
load(file=paste(dir,"Data_input/Immuune_Seurat_object.RData", sep=""))
# Add column to main immune seurat object 
tiss_immune@meta.data[,"T_cell_subtype_annotation"] <- NA
# Add annotations 
for(i in 1:nrow(t.cell.tiss@meta.data)){
  cell <- row.names(t.cell.tiss@meta.data)[i]
  a <- which(row.names(tiss_immune@meta.data)==cell)
  tiss_immune@meta.data[a,"T_cell_subtype_annotation"] <- t.cell.tiss@meta.data$t_cell_subtypes[i]
}
```

Combine immune annotations to one metadata field in the master Seurat object and save it 
```{r}
temp <- paste(tiss_immune@meta.data$immune_annotation ,tiss_immune@meta.data$immune_subtype_annotation, tiss_immune@meta.data$T_cell_subtype_annotation)
# Replace NA with blanks 
temp <- gsub(temp, pattern = "NA", replacement = "")
# REplace double space
temp <- gsub(temp, pattern = "  ", replacement = " ")
# REplace space with _
temp <- gsub(temp, pattern = " ", replacement = "/")
# Replace the last "/"
temp <- sub("/$", "", temp)
# Replace the last "/"
temp <- sub("/$", "", temp)
tiss_immune@meta.data[,"Final_immune_annotation"] <- temp
# Show table 
table(tiss_immune@meta.data[,"Final_immune_annotation"])
```

Save immune cell workspace as well as updated main workspace 
```{r}
save(tiss_immune, file=paste(dir,"Data_input/Immuune_Seurat_object.RData", sep=""))
```




