---
title: "IM03"
output: html_document
---

More detailed Immune phenotyping of different immune cell types
Macrophages and Monocytes of the lung

Load immune workspace
```{r}
rm(list=ls())
dir <- "/myVolume/scell_lung_adenocarcinoma/"
load(file=paste(dir,"Data_input/objects/IM01_Immune_Seurat_object.RData", sep=""))
```

Biopsy site vs analysis all cell types 
```{r}
require(gplots)
tab.1 <- table(tiss_immune@meta.data$biopsy_site, tiss_immune@meta.data$analysis)
balloonplot(tab.1, main ="Response vs Biopsy site for all cells", xlab ="", ylab="",
            label = T, show.margins = F)
```

Table of Biopsy site vs analysis 
```{r}
cells <- row.names(tiss_immune@meta.data)[which(tiss_immune@meta.data$biopsy_site == "Lung")]
tiss.temp <- SubsetData(object = tiss_immune, cells.use = cells)
tab.1 <- table(tiss.temp@meta.data$analysis, tiss.temp@meta.data$immune_subtype_annotation )
balloonplot(tab.1, main ="Cell types vs treatment for Lung", xlab ="", ylab="",
            label = T, show.margins = F)
rm(tiss.temp)
```


Subset Macrophages and Monocytes
```{r}
mf.cells <- row.names(tiss_immune@meta.data)[which(tiss_immune@meta.data$immune_subtype_annotation == "MF-Monocytes")]
length(mf.cells)
mf.cell.tiss <- SubsetData(object = tiss_immune, cells.use = mf.cells)
```


Biopsy site vs analysis 
```{r}
tab.1 <- table(mf.cell.tiss@meta.data$biopsy_site, mf.cell.tiss@meta.data$analysis)
balloonplot(tab.1, main ="Response vs Biopsy site", xlab ="", ylab="",
            label = T, show.margins = F)
```

Subset only cells derived from Lung samples 
```{r}
mf.cells <- row.names(mf.cell.tiss@meta.data)[which(mf.cell.tiss@meta.data$biopsy_site == "Lung")]
length(mf.cells)
mf.cell.tiss <- SubsetData(object = tiss_immune, cells.use = mf.cells)
```

Biopsy site vs analysis 
```{r}
tab.1 <- table(mf.cell.tiss@meta.data$biopsy_site, mf.cell.tiss@meta.data$analysis)
balloonplot(tab.1, main ="Response vs Biopsy site", xlab ="", ylab="",
            label = T, show.margins = F)
```

Unsupervised clustering of Myeloid cells

Find variable genes
```{r}
mf.cell.tiss <- FindVariableGenes(object = mf.cell.tiss, do.plot = TRUE, x.high.cutoff = Inf, y.cutoff = 1, num.bin = 20, 
                                          binning.method = "equal_width", do.recalc = T, x.low.cutoff=1)
length(mf.cell.tiss@var.genes)
```

Unsupervised clustering of Myeloid cells
# PCA
```{r}
mf.cell.tiss <- RunPCA(object = mf.cell.tiss, do.print = FALSE, pcs.compute = )
mf.cell.tiss <- ProjectPCA(object = mf.cell.tiss, do.print = FALSE)
```

# visualize PCA heatmaps and PC variance
```{r}
PCHeatmap(object = mf.cell.tiss, pc.use = 1:15, cells.use = 100, do.balanced = TRUE, label.columns = FALSE, num.genes = 10)
```

```{r}
PCElbowPlot(object = mf.cell.tiss)
```

Perform correlation of PCs and metadata fields
```{r}
require(corrplot)
pca.obj <- mf.cell.tiss@dr$pca
pc.coords <- pca.obj@cell.embeddings
df1 <- mf.cell.tiss@meta.data[,c("nGene","nReads","percent.ribo")]
df2 <- pc.coords[,c(1:10)]
cordf12 <- cor(df1,df2)
# Make a correlation plot
corrplot(cordf12, method = "number", main="Correlation of PCs and metadata")
```

JackStraw of PCs 
```{r}
mf.cell.tiss <- JackStraw(mf.cell.tiss, num.replicate = 100, display.progress = T, 
                         do.par = T, num.cores = 15, num.pc = 15)
JackStrawPlot(mf.cell.tiss, PCs = 1:15)
```


Define components to be used for clustering 
```{r}
n.pcs.min = 1
n.pcs.max = 10
```

pick resolution parameter
```{r}
res.used <- 0.3
mf.cell.tiss <- FindClusters(object = mf.cell.tiss, reduction.type = "pca", dims.use = n.pcs.min:n.pcs.max, 
    resolution = res.used, print.output = 0, save.SNN = TRUE, k.param = 10, force.recalc = T)
```

# Run TSNE
```{r}
mf.cell.tiss <- RunTSNE(object = mf.cell.tiss, dims.use = n.pcs.min:n.pcs.max, seed.use = 10, perplexity=30)
```

# Plot TSNE
```{r}
TSNEPlot(object = mf.cell.tiss, do.label = T)
```

# Plot TSNE and save 
```{r}
pdf(paste(dir, "plot_out/IM03/MF_TSNE_manuscript.pdf",sep=""), 5,5)
TSNEPlot(object = mf.cell.tiss, do.label = F)
dev.off()
```

# Plot TSNE with analysis colors 
```{r}
mf.cell.tiss <- SetIdent(mf.cell.tiss,ident.use = mf.cell.tiss@meta.data$analysis)
TSNEPlot(object = mf.cell.tiss, do.label = T)
mf.cell.tiss <- SetIdent(mf.cell.tiss,ident.use = mf.cell.tiss@meta.data$res.0.3)
```

```{r}
tab.1 <- table(mf.cell.tiss@meta.data$res.0.3, mf.cell.tiss@meta.data$analysis)
balloonplot(tab.1, main ="Response vs T-cell cluster", xlab ="", ylab="",
            label = T, show.margins = F)
```

```{r}
require(reshape)
tab.1 <- prop.table(table(mf.cell.tiss@meta.data$res.0.3, mf.cell.tiss@meta.data$analysis), margin = 1)
tab.1 <- melt(tab.1)
tab.1$Var.1 <- as.factor(tab.1$Var.1)
fraction.plot <- ggplot() + geom_bar(aes(y = value, x = Var.1, fill = Var.2), data = tab.1,
                           stat="identity" , position=position_dodge())
ggsave(filename = paste(dir, "plot_out/IM03/MF_TSNE_clusters_by_treatment_manuscript.pdf",sep=""), plot = fraction.plot, width = 7,height = 5)
fraction.plot
```

Replot barplots using error bars 
```{r}
library(ggrepel)
require(qdapTools)
require(REdaS)
require(plyr)
meta.temp <- mf.cell.tiss@meta.data
meta.temp$res.0.3 <- as.numeric(meta.temp$res.0.3)
# Change res clusters to MF clusters 
meta.temp$cluster <- mapvalues(meta.temp$res.0.3, from=c(0,1,2,3,4), to=c("MF0", "MF1", "MF2","MF3", "MF4"))
# Calculate fractions and error bars 
prop.table.error <- list()
for(i in 1:length(unique(meta.temp$cluster))){
vec.temp <- meta.temp[meta.temp$cluster==unique(meta.temp$cluster)[i],"analysis"]
# Convert to counts and calculate 95% CI 
# Store in list 
table.temp <- freqCI(vec.temp, level = c(.95))
prop.table.error[[i]] <- print(table.temp, percent = TRUE, digits = 3)
# 
}
# Name list 
names(prop.table.error) <- unique(meta.temp$cluster)
# Convert to data frame 
tab.1 <- as.data.frame.array(do.call(rbind, prop.table.error))
# Add analysis column 
b <- c()
a <- c()
for(i in names(prop.table.error)){
  a <- rep(i,length(unique(row.names(tab.1))))
  b <- c(b,a)
}
tab.1$cluster <- b
tab.1$cell <- row.names(tab.1)
# Resort factor analysis 
tab.1$cluster <- factor(tab.1$cluster, levels = c("MF0", "MF1", "MF2", "MF3", "MF4"))
# Rename percentile columns 
colnames(tab.1)[1] <- "lower"
colnames(tab.1)[3] <- "upper"
# 
p<- ggplot(tab.1, aes(x=cluster, y=Estimate, fill=cell)) + 
    geom_bar(position=position_dodge(), stat="identity") +
    geom_errorbar(aes(ymin=lower, ymax=upper), width=.2,position=position_dodge(0.9)) + 
    theme(legend.position="bottom")
# Save plot 
ggsave(filename = paste(dir, "plot_out/IM03/MF_TSNE_clusters_by_treatment_with_error_bars_manuscript.pdf",sep=""), plot = p, width = 7,height = 5)
p
```


```{r}
tab.1 <- table(mf.cell.tiss@meta.data$res.0.3, as.character(mf.cell.tiss@meta.data$patient_id))
balloonplot(tab.1, main ="Patient ID vs MF-cell cluster", xlab ="", ylab="",
            label = T, show.margins = F)
```


```{r}
tab.1 <- table(mf.cell.tiss@meta.data$analysis, as.character(mf.cell.tiss@meta.data$patient_id))
balloonplot(tab.1, main ="Patient ID vs MF-cell cluster", xlab ="", ylab="",
            label = T, show.margins = F)
```
Fraction of PD
```{r}
tab.1 <- prop.table(table(mf.cell.tiss@meta.data$res.0.3, mf.cell.tiss@meta.data$analysis), margin = 1)
tab.1 <- melt(tab.1)
tab.1$Var.1 <- as.factor(tab.1$Var.1)
fraction.plot <- ggplot() + geom_bar(aes(y = value, x = Var.1, fill = Var.2), data = tab.1,
                           stat="identity")
ggsave(filename = paste(dir, "plot_out/IM03/MF_fraction_of_each_response_group_TSNE_clusters.pdf",sep=""), plot = fraction.plot,width = 7,height = 7)
fraction.plot
```

Find all cluster markers 
```{r}
mf.cell.markers <- FindAllMarkers(object = mf.cell.tiss, only.pos = TRUE, min.pct = 0.25, thresh.use = 0.25)
# mf.cell.markers <- read.table(paste(dir, "data_out/IM03/MFs_DE_genes_between_subclusters_Lung.csv",sep=""))
```

Plot top genes 
```{r}
require(tidyverse)
mf.cell.markers %>% group_by(cluster) %>% top_n(10, avg_logFC) -> top10
mf.cell.markers %>% group_by(cluster) %>% top_n(20, avg_logFC) -> top20
pdf(paste(dir, "plot_out/IM03/Heatmap_markers_of_MFcell_clusters.pdf",sep=""), 7,7)
DoHeatmap(mf.cell.tiss, genes.use = top10$gene, slim.col.label = TRUE, remove.key = TRUE, cex.row = 5)
dev.off()
# DoHeatmap(mf.cell.tiss, genes.use = c("CD8A", "CD4", "PDCD1", "CD3E", "TOP2A"), slim.col.label = TRUE, remove.key = TRUE, cex.row = 5, use.scaled = F)
```

Plot top genes 
```{r}
require(tidyverse)
mf.cell.markers %>% group_by(cluster) %>% top_n(50, avg_logFC) -> top50
DoHeatmap(mf.cell.tiss, genes.use = top50$gene, slim.col.label = TRUE, remove.key = TRUE, cex.row = 5, use.scaled = F)
# DoHeatmap(mf.cell.tiss, genes.use = c("CD8A", "CD4", "PDCD1", "CD3E", "TOP2A"), slim.col.label = TRUE, remove.key = TRUE, cex.row = 5, use.scaled = F)
```

Plot top genes annotate by reponse
```{r}
mf.cell.tiss <- SetIdent(mf.cell.tiss,ident.use = mf.cell.tiss@meta.data$analysis)
#t.cell.markers %>% group_by(cluster) %>% top_n(10, avg_logFC) -> top10
DoHeatmap(mf.cell.tiss, genes.use = top10$gene, slim.col.label = TRUE, remove.key = TRUE, cex.row = 5)
mf.cell.tiss <- SetIdent(mf.cell.tiss,ident.use = mf.cell.tiss@meta.data$res.0.3)
```



Write table of top genes 
```{r}
write.table(mf.cell.markers, paste(dir, "data_out/IM03/MFs_DE_genes_between_subclusters_Lung.csv",sep=""))
```


Plot genes of choice
```{r}
# Violin plot 
genes <- c("IDO1","WARS","CXCL10","GBP5", "ANKRD22", "THBS1", "PTX3", "MARCO", "CCL13", "IL1B")
a <- VlnPlot(mf.cell.tiss, features.plot = genes, do.return = T, point.size.use = 0)
ggsave(filename = paste(dir, "plot_out/IM03/Markers_of_PD_MFs.pdf",sep=""),plot = a,width = 10,height = 10)
a
```

Plot top genes 
```{r}
# Violin plot 
a <- VlnPlot(tiss_immune, features.plot = "CXCR3", group.by = "immune_subtype_annotation",do.sort = T, x.lab.rot = T, do.return = T)
ggsave(filename = paste(dir, "plot_out/IM03/CXCR3_expression_all_immune_cells.pdf",sep=""),plot = a,width = 7,height = 5)
```


Plot all relevant, PCA, tSNE and Clustering plots as pdf 
```{r}
pdf(paste(dir, "plot_out/IM03/MF-cells_subclustering_TSNE_LUNG.pdf",sep=""),width = 10,height = 7)
# Tables
# 1
tab.1 <- table(mf.cell.tiss@meta.data$res.0.3, mf.cell.tiss@meta.data$analysis)
balloonplot(tab.1, main ="MF-cell subcluster vs Response group", xlab ="", ylab="",
            label = T, show.margins = F)
# 2
tab.1 <- table(mf.cell.tiss@meta.data$res.0.3, as.character(mf.cell.tiss@meta.data$patient_id))
balloonplot(tab.1, main ="Patient ID vs MF-cell cluster", xlab ="", ylab="",
            label = T, show.margins = F)
# TSNE plots 
TSNEPlot(object = mf.cell.tiss, do.label = T)
TSNEPlot(object = mf.cell.tiss, do.label = T, group.by="analysis")
# Heatmaps
DoHeatmap(mf.cell.tiss, genes.use = top10$gene, slim.col.label = TRUE, remove.key = TRUE, cex.row = 5, title = "Top 10 DE genes")
DoHeatmap(mf.cell.tiss, genes.use = top20$gene, slim.col.label = TRUE, remove.key = TRUE, cex.row = 5, title = "Top 20 DE genes")
DoHeatmap(mf.cell.tiss, genes.use = top50$gene, slim.col.label = TRUE, remove.key = TRUE, cex.row = 5, title = "Top 50 DE genes")
# Violin plot 
mf.cell.tiss <- SetIdent(object = mf.cell.tiss, ident.use = as.character(mf.cell.tiss@meta.data$analysis))
genes <- c("IDO1","CXCL9","CXCL10","CXCL11", "GBP1", "GBP5", "ANKRD22")
VlnPlot(mf.cell.tiss, features.plot = genes)
mf.cell.tiss <- SetIdent(object = mf.cell.tiss, ident.use = mf.cell.tiss@meta.data$res.0.3)
# PCA plots 
PCHeatmap(object = mf.cell.tiss, pc.use = 1:15, cells.use = 100, do.balanced = TRUE, label.columns = FALSE, num.genes = 10)
PCElbowPlot(object = mf.cell.tiss)
#JackStrawPlot(mf.cell.tiss, PCs = 1:12)
# Feature plot
DotPlot(mf.cell.tiss, top10$gene, x.lab.rot = T)
# DotPlot(mf.cell.tiss, top10$gene, x.lab.rot = T, group.by = "analysis")
dev.off()
```

Plot top genes 
```{r}
# Violin 
genes <- c("TGFB1", "IL10", "IL1B", "TNF", "IL6", "IL12A", "IL12B")
a <- VlnPlot(mf.cell.tiss, features.plot = genes, do.return = T, point.size.use = 1)

```


Save immune cell workspace 
```{r}
save(mf.cell.tiss, file=paste(dir,"Data_input/objects/IM03_MFs_Seurat_object.RData", sep=""))
```