---
title: "IM03"
output: html_document
---

More detailed Immune phenotyping of different immune cell types
Macrophages and Monocytes of the lung

Load immune workspace
```{r}
# rm(list=ls())
dir <- "/home/ubuntu/scell_lung_adenocarcinoma/"
# dir <- "/myVolume/scell_lung_adenocarcinoma/"
load(file=paste(dir,"Data_input/objects/IM01_Immune_Seurat_object_nodups.RData", sep=""))
```

Biopsy site vs analysis all cell types 
```{r}
require(gplots)
tab.1 <- table(tiss_immune@meta.data$biopsy_site, tiss_immune@meta.data$analysis)
balloonplot(tab.1, main ="Response vs Biopsy site for all cells", xlab ="", ylab="",
            label = T, show.margins = F)
```

Table of Biopsy site vs analysis 
```{r}
cells <- row.names(tiss_immune@meta.data)[which(tiss_immune@meta.data$biopsy_site == "Lung")]
tiss.temp <- subset(tiss_immune, cells=cells)
tab.1 <- table(tiss.temp@meta.data$analysis, tiss.temp@meta.data$immune_subtype_annotation )
balloonplot(tab.1, main ="Cell types vs treatment for Lung", xlab ="", ylab="",
            label = T, show.margins = F)
rm(tiss.temp)
```

Subset Macrophages and Monocytes From Lung 
```{r}
mf.cells <- tiss_immune@meta.data[which(tiss_immune@meta.data$biopsy_site == "Lung"),]
dim(mf.cells)
mf.cells.2 <- mf.cells[which(mf.cells$immune_subtype_annotation == "MF-Monocytes"),]
dim(mf.cells.2)
mf.cell.tiss <- subset(tiss_immune, cells=row.names(mf.cells.2)  )  
mf.cell.tiss
```

Biopsy site vs analysis sanity check 
```{r}
tab.1 <- table(mf.cell.tiss@meta.data$biopsy_site, mf.cell.tiss@meta.data$analysis)
balloonplot(tab.1, main ="Response vs Biopsy site", xlab ="", ylab="",
            label = T, show.margins = F)
```

Unsupervised clustering of Myeloid cells

Find variable genes, Normalize and scale
```{r}
mf.cell.tiss <- NormalizeData(object = mf.cell.tiss)
mf.cell.tiss <- FindVariableFeatures(object = mf.cell.tiss, num.bin = 20, binning.method = "equal_width")
mf.cell.tiss <- ScaleData(object = mf.cell.tiss, features = rownames(mf.cell.tiss))
```

Unsupervised clustering of Myeloid cells

Perform PCA
```{r}
mf.cell.tiss <- RunPCA(object = mf.cell.tiss, do.print = FALSE)
```

Visualize variance along each component
```{r}
ElbowPlot(mf.cell.tiss)
```

Visualize first two PCs
```{r}
PCAPlot(object = mf.cell.tiss)
```

Visualize top genes and their loadings 
```{r}
VizDimLoadings(mf.cell.tiss, dims = 1:5, reduction = "pca", nfeatures = 10)
```

Visualize top genes in principal components
```{r}
DimHeatmap(mf.cell.tiss, dims = 1:10, cells = 100, balanced = TRUE)
```

Construct Neighbor graph 
```{r}
mf.cell.tiss <- FindNeighbors(object = mf.cell.tiss, verbose = T, dims = 1:10)
```

Find Clusters 
```{r}
mf.cell.tiss <- FindClusters(object = mf.cell.tiss, verbose = T, resolution = 0.3)
```
Run and project TSNEs
```{r}
mf.cell.tiss <- RunTSNE(mf.cell.tiss, dims = 1:10)
DimPlot(mf.cell.tiss, reduction = "tsne")
```

# Plot TSNE and save 
```{r}
pdf(paste(dir, "plot_out/IM03/MF_TSNE_manuscript.pdf",sep=""), 5,5)
DimPlot(mf.cell.tiss, reduction = "tsne")
DimPlot(mf.cell.tiss, reduction = "tsne", label = T)
dev.off()
```

# Plot TSNE with analysis colors 
```{r}
Idents(object = mf.cell.tiss) <- mf.cell.tiss@meta.data$analysis
DimPlot(mf.cell.tiss, reduction = "tsne", label = T)
Idents(object = mf.cell.tiss) <- mf.cell.tiss@meta.data$RNA_snn_res.0.1
# DimPlot(mf.cell.tiss, reduction = "tsne", label = T)
```

```{r}
tab.1 <- table(mf.cell.tiss@meta.data$RNA_snn_res.0.1, mf.cell.tiss@meta.data$analysis)
balloonplot(tab.1, main ="Response vs T-cell cluster", xlab ="", ylab="",
            label = T, show.margins = F)
```

```{r}
require(reshape)
tab.1 <- prop.table(table(mf.cell.tiss@meta.data$RNA_snn_res.0.1, mf.cell.tiss@meta.data$analysis), margin = 1)
tab.1 <- melt(tab.1)
tab.1$Var1 <- as.factor(tab.1$Var1)
fraction.plot <- ggplot() + geom_bar(aes(y = value, x = Var1, fill = Var2), data = tab.1,
                           stat="identity" , position=position_dodge())
ggsave(filename = paste(dir, "plot_out/IM03/MF_TSNE_clusters_by_treatment_manuscript.pdf",sep=""), plot = fraction.plot, width = 7,height = 5)
fraction.plot
```

Replot barplots using error bars 
```{r}
library(ggrepel)
require(qdapTools)
require(REdaS)
require(plyr)
meta.temp <- mf.cell.tiss@meta.data
meta.temp$RNA_snn_res.0.1 <- as.numeric(as.character(meta.temp$RNA_snn_res.0.1))
# Change res clusters to MF clusters 
meta.temp$cluster <- mapvalues(meta.temp$RNA_snn_res.0.1, from=c(0,1,2,3), to=c("MF0", "MF1", "MF2","MF3"))
# Calculate fractions and error bars 
prop.table.error <- list()
for(i in 1:length(unique(meta.temp$cluster))){
vec.temp <- meta.temp[meta.temp$cluster==unique(meta.temp$cluster)[i],"analysis"]
# Convert to counts and calculate 95% CI 
# Store in list 
table.temp <- freqCI(vec.temp, level = c(.95))
prop.table.error[[i]] <- print(table.temp, percent = TRUE, digits = 3)
# 
}
# Name list 
names(prop.table.error) <- unique(meta.temp$cluster)
#
#
# # Custom in case one cluster is completely empty of one or more treatment groups 
# # adding zeros to cluster MF4 
# prop.table.error$MF4
# temp <-  prop.table.error$MF3[c(2,3),]
# temp[1:2,1:3] <- 0
# prop.table.error$MF4 <- rbind(prop.table.error$MF4, temp)
# #
# #
# #
# Convert to data frame 
tab.1 <- as.data.frame.array(do.call(rbind, prop.table.error))
# Add analysis column 
b <- c()
a <- c()
for(i in names(prop.table.error)){
  a <- rep(i,3)
  b <- c(b,a)
}
tab.1$cluster <- b
tab.1$cell <- rep(row.names(tab.1)[1:3], length(unique(tab.1$cluster)))
# Resort factor analysis 
tab.1$cluster <- factor(tab.1$cluster, levels = c("MF0", "MF1", "MF2", "MF3"))
# Rename percentile columns 
colnames(tab.1)[1] <- "lower"
colnames(tab.1)[3] <- "upper"
# 
p <- ggplot(tab.1, aes(x=cluster, y=Estimate, fill=cell)) + 
    geom_bar(position=position_dodge(), stat="identity") +
    geom_errorbar(aes(ymin=lower, ymax=upper), width=.2,position=position_dodge(0.9)) + 
    theme(legend.position="bottom")
# Save plot 
ggsave(filename = paste(dir, "plot_out/IM03/MF_TSNE_clusters_by_treatment_with_error_bars_manuscript.pdf",sep=""), plot = p, width = 7,height = 5)
p
```

Significance between fractions 
Chi-square Test of Independence  
```{r}
count.mat <- as.matrix(table(meta.temp$analysis, meta.temp$cluster))
p.mat <- matrix(nrow = ncol(count.mat), ncol=1)
row.names(p.mat) <- colnames(count.mat)
for(i in 1:ncol(count.mat)){
  test <- chisq.test(count.mat[,i])
  p.mat[i,1] <- test$p.value*ncol(count.mat)
}
0.01-p.mat[,1]
```


```{r}
tab.1 <- table(mf.cell.tiss@meta.data$RNA_snn_res.0.1, as.character(mf.cell.tiss@meta.data$patient_id))
balloonplot(tab.1, main ="Patient ID vs MF-cell cluster", xlab ="", ylab="",
            label = T, show.margins = F)
```


```{r}
tab.1 <- table(mf.cell.tiss@meta.data$analysis, as.character(mf.cell.tiss@meta.data$patient_id))
balloonplot(tab.1, main ="Patient ID vs MF-cell cluster", xlab ="", ylab="",
            label = T, show.margins = F)
```

Fraction of PD
```{r}
tab.1 <- prop.table(table(mf.cell.tiss@meta.data$RNA_snn_res.0.1, mf.cell.tiss@meta.data$analysis), margin = 1)
tab.1 <- melt(tab.1)
tab.1$Var1 <- as.factor(tab.1$Var1)
fraction.plot <- ggplot() + geom_bar(aes(y = value, x = Var1, fill = Var2), data = tab.1,
                           stat="identity")
ggsave(filename = paste(dir, "plot_out/IM03/MF_fraction_of_each_response_group_TSNE_clusters.pdf",sep=""), plot = fraction.plot,width = 7,height = 7)
fraction.plot
```

Find all cluster markers 
```{r}
mf.cell.markers <- FindAllMarkers(object = mf.cell.tiss, only.pos = TRUE, min.pct = 0.25, thresh.use = 0.25)
# mf.cell.markers <- read.table(paste(dir, "data_out/IM03/MFs_DE_genes_between_subclusters_Lung.csv",sep=""))
```

Plot top genes 
```{r}
require(tidyverse)
mf.cell.markers %>% group_by(cluster) %>% top_n(10, avg_logFC) -> top10
mf.cell.markers %>% group_by(cluster) %>% top_n(20, avg_logFC) -> top20
mf.cell.markers %>% group_by(cluster) %>% top_n(50, avg_logFC) -> top50
a <- DoHeatmap(mf.cell.tiss, features = top20$gene, raster = F)
ggsave(filename = paste(dir, "plot_out/IM03/Markers_of_MFcell_clusters_heatmap.pdf",sep=""),plot = a,width = 10,height = 15)
```

Plot top genes 
```{r}
mf.cell.markers %>% group_by(cluster) %>% top_n(10, avg_logFC) -> top10
DoHeatmap(mf.cell.tiss, features = top10$gene)
```

Write table of top genes 
```{r}
write.csv(mf.cell.markers, paste(dir, "data_out/IM03/MFs_DE_genes_between_subclusters_Lung.csv",sep=""), row.names=F)
# mf.cell.markers %>% group_by(cluster) %>% top_n(10, avg_logFC)
```


Plot genes of choice
```{r}
# Violin plot 
genes <- c("IDO1","WARS","CXCL10","GBP5", "ANKRD22", "THBS1", "PTX3", "MARCO", "CCL13", "IL1B")
a <- VlnPlot(mf.cell.tiss, features = genes, pt.size = 0)
ggsave(filename = paste(dir, "plot_out/IM03/Markers_of_PD_MFs.pdf",sep=""),plot = a,width = 10,height = 10)
a
```

Plot top genes 
```{r}
# Violin plot 
a <- VlnPlot(tiss_immune, features= "CXCR3", group.by = "immune_subtype_annotation")
ggsave(filename = paste(dir, "plot_out/IM03/CXCR3_expression_all_immune_cells.pdf",sep=""),plot = a,width = 7,height = 5)
a
```


Plot all relevant, PCA, tSNE and Clustering plots as pdf 
```{r}
pdf(paste(dir, "plot_out/IM03/MF-cells_subclustering_TSNE_LUNG.pdf",sep=""),width = 10,height = 7)
# Tables
# 1
tab.1 <- table(mf.cell.tiss@meta.data$RNA_snn_res.0.1, mf.cell.tiss@meta.data$analysis)
balloonplot(tab.1, main ="MF-cell subcluster vs Response group", xlab ="", ylab="",
            label = T, show.margins = F)
# 2
tab.1 <- table(mf.cell.tiss@meta.data$RNA_snn_res.0.1, as.character(mf.cell.tiss@meta.data$patient_id))
balloonplot(tab.1, main ="Patient ID vs MF-cell cluster", xlab ="", ylab="",
            label = T, show.margins = F)
# TSNE plots 
DimPlot(mf.cell.tiss, reduction = "tsne")
DimPlot(mf.cell.tiss, reduction = "tsne", label = T)
# Heatmaps
DoHeatmap(mf.cell.tiss, features = top10$gene)
DoHeatmap(mf.cell.tiss, features = top20$gene)
# Violin plot 
Idents(object = mf.cell.tiss) <- mf.cell.tiss@meta.data$analysis
genes <- c("IDO1","CXCL9","CXCL10","CXCL11", "GBP1", "GBP5", "ANKRD22")
VlnPlot(mf.cell.tiss, features = genes)
Idents(object = mf.cell.tiss) <- mf.cell.tiss@meta.data$RNA_snn_res.0.1
# Feature plot
DotPlot(mf.cell.tiss, features = top10$gene) + coord_flip()
# DotPlot(mf.cell.tiss, top10$gene, x.lab.rot = T, group.by = "analysis")
dev.off()
```

Plot custom genes 
```{r}
# Violin
genes <- c("CD1A", "CD1C", "TOP2A", "IL1B")
a <- VlnPlot(mf.cell.tiss,features = genes)
```

Save immune cell workspace 
```{r}
save(mf.cell.tiss, file=paste(dir,"Data_input/objects/IM03_MFs_Seurat_object_nodups_new.RData", sep=""))
```

