---
title: "Untitled"
output: html_document
---

Count the fraction of Immune cells across different metadata fields 

Libraries 
```{r}
require(tidyr)
require(ggthemes)
require(reshape)
require(rcompanion)
require(ggpubr)
require(GGally)
```

Load immune workspace
```{r}
rm(list=ls())
dir <- "/myVolume/scell_lung_adenocarcinoma/"
load(file=paste(dir,"Data_input/Immuune_Seurat_object.RData", sep=""))
```

# Subset metadata 
Remove cells that are not immune or are annotated as treatment status Pending or unknown. Also 
exclude thoracentesis derived immune cells as they are not necessarily proximal to the tumor. Brain will also be removed 
since it only has <10 cells. 

Plot fractional changes of selected cell populations across treatment 
```{r}
library(ggrepel)
require(qdapTools)
require(REdaS)
# 
metadata <- tiss_immune@meta.data
# Keep only cells from tissues that are not brain or pleura 
metadata <- metadata[-which(metadata$biopsy_site=="Brain" | metadata$biopsy_site=="Pleura"),]
# Convert to factor with logical order 
metadata$analysis <- factor(metadata$analysis, levels = c("naive", "grouped_pr", "grouped_pd"))
# Create table and keep selected cell types 
meta.temp <- metadata[,c("immune_subtype_annotation", "analysis")]
# Loop over treatment response categories 
# Create list to store frequency tables 
prop.table.error <- list()
for(i in 1:length(unique(meta.temp$analysis))){
vec.temp <- meta.temp[meta.temp$analysis==unique(meta.temp$analysis)[i],"immune_subtype_annotation"]
# Convert to counts and calculate 95% CI 
# Store in list 
table.temp <- ?freqCI(vec.temp, level = c(.95))
prop.table.error[[i]] <- print(table.temp, percent = TRUE, digits = 3)
# 
}
# Name list 
names(prop.table.error) <- unique(meta.temp$analysis)
# Convert to data frame 
tab.1 <- as.data.frame.array(do.call(rbind, prop.table.error))
# Add analysis column 
b <- c()
a <- c()
for(i in names(prop.table.error)){
  a <- rep(i,length(unique(row.names(tab.1))))
  b <- c(b,a)
}
tab.1$analysis <- b
tab.1$cell <- row.names(tab.1)
# Resort factor analysis 
tab.1$analysis <- factor(tab.1$analysis, levels = c("naive", "grouped_pr", "grouped_pd"))
# Rename percentile columns 
colnames(tab.1)[1] <- "lower"
colnames(tab.1)[3] <- "upper"
# 
p<- ggplot(tab.1, aes(x=analysis, y=Estimate, group=cell)) +
    geom_line(aes(color=cell))+
    geom_point(aes(color=cell)) + facet_grid(cols =  vars(cell)) + 
    theme(axis.text.x = element_text(angle = 45, hjust=1, vjust=0.5), legend.position="bottom") + 
    xlab("") + 
    geom_errorbar(aes(ymin=lower, ymax=upper), width=.2,position=position_dodge(0.05))
# Save plot 
ggsave(paste(dir,"plot_out/IM03/All_immune_populations_across_treatment.pdf", sep=""),width = 11, height = 8)
p
```



Changes of specific cell populations across clinical fields 
All vs All correlation plots 
```{r}
library(ggrepel)
# Create table and keep selected cell types 
meta.temp <- metadata[,c("immune_subtype_annotation", "analysis")]
# Create table for PD and PR
tab.1 <- as.data.frame.array(prop.table(table(meta.temp$immune_subtype_annotation, meta.temp$analysis), margin = 2))
# Correlation matrix 
cor.v <- as.matrix(cor(tab.1))
# Plot 
require(corrplot)
pdf(paste(dir,"plot_out/IM03/All_immune_population_correlations_across_treatment.pdf", sep=""), width = 5, height = 5)
corrplot(cor.v, method = "number", main="Immune annotation correlations", type="lower", diag=F, mar=c(2,2,2,2))
dev.off()
# 
corrplot(cor.v, method = "number", main="Immune annotation correlations", type="lower", diag=F)
```

Changes of specific cell populations across clinical fields 
All vs All correlation plots 
Plot actual correlations between time points 
```{r}
library(ggrepel)
# metadata <- tiss_subset@meta.data
# metadata <- metadata[which(metadata$immune_annotation=="immune"),]
# # Keep only cells from tissues that are not brain or pleura 
# metadata <- metadata[-which(metadata$biopsy_site=="Brain" | metadata$biopsy_site=="Pleura"),]
# # Remove unknown cells 
# # metadata <- metadata[-which(metadata$immune_subtype_annotation=="Unknown"),]
# # Convert to factor with logical order 
# metadata$analysis <- factor(metadata$analysis, levels = c("naive", "grouped_pd", "grouped_pr"))
# Create table and keep selected cell types 
meta.temp <- metadata[,c("immune_subtype_annotation", "analysis")]
# Create table for PD and PR
tab.1 <- as.data.frame.array(prop.table(table(meta.temp$immune_subtype_annotation, meta.temp$analysis), margin = 2))
tab.1$cell.type <- row.names(tab.1)
# Plot correlations 
# Label limits 
x_limits <- c(0.2, 0.5)
# PD vs PR 
cor.v <- cor(tab.1$grouped_pd, tab.1$grouped_pr)
p.1 <-  ggplot(tab.1, aes(x=grouped_pd, y=grouped_pr, label = cell.type)) +
        geom_point(position = position_jitter()) + 
        geom_label_repel(nudge_y = 0.15,direction = "y",hjust= 1,segment.size = 0.1, 
                         label.size = 0, xlim = x_limits) + 
        geom_abline(intercept = 0, slope = 1,linetype = "dashed", color="gray80") + 
        annotate("text", x = 0.05, y = 0.4, label=paste("cor=",round(cor.v,3))) + 
        xlim(0,0.5) + ylim(0,0.5)
# Naive to PD
cor.v <- cor(tab.1$naive, tab.1$grouped_pd)
p.2 <-  ggplot(tab.1, aes(x=naive, y=grouped_pd, label = cell.type)) +
        geom_point(position = position_jitter()) + 
        geom_label_repel(nudge_y = 0.15,direction = "y",hjust= 1,segment.size = 0.1, 
                         label.size = 0, xlim = x_limits) + 
        geom_abline(intercept = 0, slope = 1,linetype = "dashed", color="gray80") + 
        annotate("text", x = 0.05, y = 0.4, label=paste("cor=",round(cor.v,3))) + 
        xlim(0,0.5) + ylim(0,0.5)
# Naive to PR 
cor.v <- cor(tab.1$naive, tab.1$grouped_pr)
p.3 <-  ggplot(tab.1, aes(x=naive, y=grouped_pr, label = cell.type)) +
        geom_point(position = position_jitter()) + 
        geom_label_repel(nudge_y = 0.15,direction = "y",hjust= 1,segment.size = 0.1,
                         label.size = 0, xlim = x_limits) + 
        geom_abline(intercept = 0, slope = 1,linetype = "dashed", color="gray80") + 
        annotate("text", x = 0.05, y = 0.4, label=paste("cor=",round(cor.v,3))) + 
        xlim(0,0.5) + ylim(0,0.5)
# Plot all together
p.all <- grid.arrange(p.1,p.2,p.3,ncol=2)
# Save 
ggsave(filename = paste(dir,"plot_out/IM03/Immune_cell_population_fractions_pairwise.pdf", sep=""), plot = p.all, width = 12, height = 12)
p.all
```

<!-- Plot fractional changes of T-cell subsets across treatment  -->
<!-- ```{r} -->
<!-- library(ggrepel) -->
<!-- require(qdapTools) -->
<!-- require(REdaS) -->
<!-- #  -->
<!-- metadata <- tiss_immune@meta.data -->
<!-- # Keep only cells from tissues that are not brain or pleura  -->
<!-- metadata <- metadata[-which(metadata$biopsy_site=="Brain" | metadata$biopsy_site=="Pleura"),] -->
<!-- # Convert to factor with logical order  -->
<!-- metadata$analysis <- factor(metadata$analysis, levels = c("naive", "grouped_pr", "grouped_pd")) -->
<!-- metadata.T <- metadata[which(metadata$immune_subtype_annotation=="T-cells"),] -->
<!-- # REmove low quality T-cells  -->
<!-- metadata.T <- metadata.T[-which(metadata.T$T_cell_subtype_annotation=="negative.LQ"),] -->
<!-- #  -->
<!-- meta.temp <- metadata.T[,c("T_cell_subtype_annotation", "analysis")] -->
<!-- # Keep only common T-cell subtypes  -->
<!-- tab.temp <- table(meta.temp$T_cell_subtype_annotation, meta.temp$analysis) -->
<!-- tab.temp[tab.temp !=0] <- 1 -->
<!-- meta.temp <- meta.temp[meta.temp$T_cell_subtype_annotation %in% names(which(rowSums(tab.temp)==3)),] -->
<!-- # Loop over treatment response categories  -->
<!-- # Create list to store frequency tables  -->
<!-- prop.table.est <- list() -->
<!-- for(i in 1:length(unique(meta.temp$analysis))){ -->
<!-- vec.temp <- meta.temp[meta.temp$analysis==unique(meta.temp$analysis)[i],"T_cell_subtype_annotation"] -->
<!-- # Convert to counts and calculate 95% CI  -->
<!-- # Store in list  -->
<!-- table.temp <- freqCI(vec.temp, level = c(.95)) -->
<!-- prop.table.error[[i]] <- print(table.temp, percent = TRUE, digits = 3) -->
<!-- #  -->
<!-- } -->
<!-- # Name list  -->
<!-- names(prop.table.error) <- unique(meta.temp$analysis) -->
<!-- # Convert to data frame  -->
<!-- tab.1 <- as.data.frame.array(do.call(rbind, prop.table.error)) -->
<!-- # Add analysis column  -->
<!-- b <- c() -->
<!-- a <- c() -->
<!-- for(i in names(prop.table.error)){ -->
<!--   a <- rep(i,length(unique(row.names(tab.1)))) -->
<!--   b <- c(b,a) -->
<!-- } -->
<!-- tab.1$analysis <- b -->
<!-- tab.1$cell <- row.names(tab.1) -->
<!-- # Resort factor analysis  -->
<!-- tab.1$analysis <- factor(tab.1$analysis, levels = c("naive", "grouped_pr", "grouped_pd")) -->
<!-- # Rename percentile columns  -->
<!-- colnames(tab.1)[1] <- "lower" -->
<!-- colnames(tab.1)[3] <- "upper" -->
<!-- #  -->
<!-- p <-ggplot(tab.1, aes(x=analysis, y=Estimate, group=cell)) + -->
<!--     geom_line(aes(color=cell))+ -->
<!--     geom_point(aes(color=cell)) + facet_grid(cols =  vars(cell)) +  -->
<!--     theme(axis.text.x = element_text(angle = 45, hjust=1, vjust=0.5), legend.position="bottom") +  -->
<!--     xlab("") +  -->
<!--     geom_errorbar(aes(ymin=lower, ymax=upper), width=.2,position=position_dodge(0.05)) -->
<!-- # Save plot  -->
<!-- ggsave(paste(dir,"plot_out/IM03/T-cell_populations_across_treatment.pdf", sep=""),width = 11, height = 8) -->
<!-- p -->
<!-- ``` -->


<!-- ```{r} -->
<!-- library(treemap) -->
<!-- #  -->
<!-- tab.1 <- as.data.frame(prop.table(table(meta.temp), margin = 2)*100) -->
<!-- cats <- unique(tab.1$analysis) -->
<!-- pdf(paste(dir,"plot_out/IM03/Treemaps_T-cell_subtypes.pdf", sep=""),width = 7, height = 5) -->
<!-- for(i in 1:length(cats)){ -->
<!--     tab.1.temp <- tab.1[which(tab.1$analysis == cats[i]),] -->
<!--     treemap(tab.1.temp, -->
<!--             index="T_cell_subtype_annotation", -->
<!--             vSize="Freq", -->
<!--             type="index",  -->
<!--             lowerbound.cex.labels = 0,  -->
<!--             title = cats[i] -->
<!--             )   -->
<!-- } -->
<!-- dev.off() -->
<!-- ``` -->

<!-- Plot fractional changes of T-cell subsets across treatment ONLY within LUNG -->
<!-- ```{r} -->
<!-- library(ggrepel) -->
<!-- require(qdapTools) -->
<!-- require(REdaS) -->
<!-- #  -->
<!-- # metadata <- tiss_subset@meta.data -->
<!-- # metadata <- metadata[which(metadata$immune_annotation=="immune"),] -->
<!-- # # Keep only cells from tissues that are not brain or pleura  -->
<!-- metadata.lung <- metadata[which(metadata$biopsy_site=="Lung"),] -->
<!-- # # Remove unknown cells  -->
<!-- # # metadata <- metadata[-which(metadata$immune_subtype_annotation=="Unknown"),] -->
<!-- # # Convert to factor with logical order  -->
<!-- # metadata$analysis <- factor(metadata$analysis, levels = c("naive", "grouped_pd", "grouped_pr")) -->
<!-- # # Keep only T-cells  -->
<!-- metadata.T <- metadata.lung[which(metadata.lung$immune_subtype_annotation=="T-cells"),] -->
<!-- # REmove low quality T-cells  -->
<!-- metadata.T <- metadata.T[-which(metadata.T$T_cell_subtype_annotation=="negative.LQ"),] -->
<!-- # Create table and keep selected cell types  -->
<!-- meta.temp <- metadata.T[,c("T_cell_subtype_annotation", "analysis")] -->
<!-- # Keep only common T-cell subtypes  -->
<!-- tab.temp <- table(meta.temp$T_cell_subtype_annotation, meta.temp$analysis) -->
<!-- tab.temp[tab.temp !=0] <- 1 -->
<!-- meta.temp <- meta.temp[meta.temp$T_cell_subtype_annotation %in% names(which(rowSums(tab.temp)==3)),] -->
<!-- # Loop over treatment response categories  -->
<!-- # Create list to store frequency tables  -->
<!-- prop.table.est <- list() -->
<!-- for(i in 1:length(unique(meta.temp$analysis))){ -->
<!-- vec.temp <- meta.temp[meta.temp$analysis==unique(meta.temp$analysis)[i],"T_cell_subtype_annotation"] -->
<!-- # Convert to counts and calculate 95% CI  -->
<!-- # Store in list  -->
<!-- table.temp <- freqCI(vec.temp, level = c(.95)) -->
<!-- prop.table.error[[i]] <- print(table.temp, percent = TRUE, digits = 3) -->
<!-- #  -->
<!-- } -->
<!-- # Name list  -->
<!-- names(prop.table.error) <- unique(meta.temp$analysis) -->
<!-- # Convert to data frame  -->
<!-- tab.1 <- as.data.frame.array(do.call(rbind, prop.table.error)) -->
<!-- # Add analysis column  -->
<!-- b <- c() -->
<!-- a <- c() -->
<!-- for(i in names(prop.table.error)){ -->
<!--   a <- rep(i,length(unique(row.names(tab.1)))) -->
<!--   b <- c(b,a) -->
<!-- } -->
<!-- tab.1$analysis <- b -->
<!-- tab.1$cell <- row.names(tab.1) -->
<!-- # Resort factor analysis  -->
<!-- tab.1$analysis <- factor(tab.1$analysis, levels = c("naive", "grouped_pr", "grouped_pd")) -->
<!-- # Rename percentile columns  -->
<!-- colnames(tab.1)[1] <- "lower" -->
<!-- colnames(tab.1)[3] <- "upper" -->
<!-- #  -->
<!-- p <-ggplot(tab.1, aes(x=analysis, y=Estimate, group=cell)) + -->
<!--     geom_line(aes(color=cell))+ -->
<!--     geom_point(aes(color=cell)) + facet_grid(cols =  vars(cell)) +  -->
<!--     theme(axis.text.x = element_text(angle = 45, hjust=1, vjust=0.5), legend.position="bottom") +  -->
<!--     xlab("") +  -->
<!--     geom_errorbar(aes(ymin=lower, ymax=upper), width=.2,position=position_dodge(0.05)) -->
<!-- # Save plot  -->
<!-- ggsave(paste(dir,"plot_out/IM03/T-cell_populations_across_treatment_LUNG.pdf", sep=""),width = 11, height = 8) -->
<!-- p -->
<!-- ``` -->

<!-- Plot fractional changes of T-cell subsets across treatment ONLY within LIVER -->
<!-- ```{r} -->
<!-- library(ggrepel) -->
<!-- require(qdapTools) -->
<!-- require(REdaS) -->
<!-- #  -->
<!-- # metadata <- tiss_subset@meta.data -->
<!-- # metadata <- metadata[which(metadata$immune_annotation=="immune"),] -->
<!-- # Keep only cells from tissues that are not brain or pleura  -->
<!-- metadata.liver <- metadata[which(metadata$biopsy_site=="Liver"),] -->
<!-- # Remove unknown cells  -->
<!-- # metadata <- metadata[-which(metadata$immune_subtype_annotation=="Unknown"),] -->
<!-- # Convert to factor with logical order  -->
<!-- # metadata$analysis <- factor(metadata$analysis, levels = c("naive", "grouped_pd", "grouped_pr")) -->
<!-- # Keep only T-cells  -->
<!-- metadata.T <- metadata.liver[which(metadata.liver$immune_subtype_annotation=="T-cells"),] -->
<!-- # REmove low quality T-cells  -->
<!-- metadata.T <- metadata.T[-which(metadata.T$T_cell_subtype_annotation=="negative.LQ"),] -->
<!-- # Create table and keep selected cell types  -->
<!-- meta.temp <- metadata.T[,c("T_cell_subtype_annotation", "analysis")] -->
<!-- # Keep only common T-cell subtypes  -->
<!-- tab.temp <- table(meta.temp$T_cell_subtype_annotation, meta.temp$analysis) -->
<!-- tab.temp[tab.temp !=0] <- 1 -->
<!-- meta.temp <- meta.temp[meta.temp$T_cell_subtype_annotation %in% names(which(rowSums(tab.temp)==3)),] -->
<!-- # Loop over treatment response categories  -->
<!-- # Create list to store frequency tables  -->
<!-- prop.table.est <- list() -->
<!-- for(i in 1:length(unique(meta.temp$analysis))){ -->
<!-- vec.temp <- meta.temp[meta.temp$analysis==unique(meta.temp$analysis)[i],"T_cell_subtype_annotation"] -->
<!-- # Convert to counts and calculate 95% CI  -->
<!-- # Store in list  -->
<!-- table.temp <- freqCI(vec.temp, level = c(.95)) -->
<!-- prop.table.error[[i]] <- print(table.temp, percent = TRUE, digits = 3) -->
<!-- #  -->
<!-- } -->
<!-- # Name list  -->
<!-- names(prop.table.error) <- unique(meta.temp$analysis) -->
<!-- # Convert to data frame  -->
<!-- tab.1 <- as.data.frame.array(do.call(rbind, prop.table.error)) -->
<!-- # Add analysis column  -->
<!-- b <- c() -->
<!-- a <- c() -->
<!-- for(i in names(prop.table.error)){ -->
<!--   a <- rep(i,length(unique(row.names(tab.1)))) -->
<!--   b <- c(b,a) -->
<!-- } -->
<!-- tab.1$analysis <- b -->
<!-- tab.1$cell <- row.names(tab.1) -->
<!-- # Resort factor analysis  -->
<!-- tab.1$analysis <- factor(tab.1$analysis, levels = c("naive", "grouped_pr", "grouped_pd")) -->
<!-- # Rename percentile columns  -->
<!-- colnames(tab.1)[1] <- "lower" -->
<!-- colnames(tab.1)[3] <- "upper" -->
<!-- #  -->
<!-- p <-ggplot(tab.1, aes(x=analysis, y=Estimate, group=cell)) + -->
<!--     geom_line(aes(color=cell))+ -->
<!--     geom_point(aes(color=cell)) + facet_grid(cols =  vars(cell)) +  -->
<!--     theme(axis.text.x = element_text(angle = 45, hjust=1, vjust=0.5), legend.position="bottom") +  -->
<!--     xlab("") +  -->
<!--     geom_errorbar(aes(ymin=lower, ymax=upper), width=.2,position=position_dodge(0.05)) -->
<!-- # Save plot  -->
<!-- ggsave(paste(dir,"plot_out/IM03/T-cell_populations_across_treatment_LIVER.pdf", sep=""),width = 11, height = 8) -->
<!-- p -->
<!-- ``` -->

<!-- Changes of specific cell populations across clinical fields  -->
<!-- Correlation plots among t_cell subsets  -->
<!-- ```{r} -->
<!-- library(ggrepel) -->
<!-- metadata <- tiss_immune@meta.data -->
<!-- # Keep only cells from tissues that are not brain or pleura  -->
<!-- metadata <- metadata[-which(metadata$biopsy_site=="Brain" | metadata$biopsy_site=="Pleura"),] -->
<!-- # Convert to factor with logical order  -->
<!-- metadata$analysis <- factor(metadata$analysis, levels = c("naive", "grouped_pr", "grouped_pd")) -->
<!-- metadata.T <- metadata[which(metadata$immune_subtype_annotation=="T-cells"),] -->
<!-- metadata.T <- metadata.T[-which(metadata.T$T_cell_subtype_annotation=="negative.LQ"),] -->
<!-- meta.temp <- metadata.T[,c("T_cell_subtype_annotation", "analysis")] -->
<!-- # Create table for PD and PR -->
<!-- tab.1 <- as.data.frame.array(prop.table(table(meta.temp$T_cell_subtype_annotation, meta.temp$analysis), margin = 2)) -->
<!-- cor.v <-  as.matrix(cor(tab.1)) -->
<!-- # Plot  -->
<!-- require(corrplot) -->
<!-- pdf(paste(dir,"plot_out/IM03/T-cell_fraction_correlations.pdf", sep=""), width = 5, height = 5) -->
<!-- corrplot(cor.v, method = "number", main="T-cell subsets correlations", type="lower", diag=F, mar=c(2,2,2,2)) -->
<!-- dev.off() -->
<!-- #  -->
<!-- corrplot(cor.v, method = "number", main="T-cell subsets correlations", type="lower", diag=F) -->
<!-- ``` -->

<!-- Changes of specific cell populations across clinical fields  -->
<!-- Correlation plots among t_cell subsets  -->
<!-- Plot actual correlations between time points  -->
<!-- ```{r} -->
<!-- library(ggrepel) -->
<!-- metadata <- tiss_immune@meta.data -->
<!-- # Keep only cells from tissues that are not brain or pleura  -->
<!-- metadata <- metadata[-which(metadata$biopsy_site=="Brain" | metadata$biopsy_site=="Pleura"),] -->
<!-- # Convert to factor with logical order  -->
<!-- metadata$analysis <- factor(metadata$analysis, levels = c("naive", "grouped_pr", "grouped_pd")) -->
<!-- metadata.T <- metadata[which(metadata$immune_subtype_annotation=="T-cells"),] -->
<!-- metadata.T <- metadata.T[-which(metadata.T$T_cell_subtype_annotation=="negative.LQ"),] -->
<!-- meta.temp <- metadata.T[,c("T_cell_subtype_annotation", "analysis")] -->
<!-- # Create table for PD and PR -->
<!-- tab.1 <- as.data.frame.array(prop.table(table(meta.temp$T_cell_subtype_annotation, meta.temp$analysis), margin = 2)) -->
<!-- tab.1$cell.type <- row.names(tab.1) -->
<!-- # Plot correlations  -->
<!-- # Label limits  -->
<!-- x_limits <- c(0.2, 0.5) -->
<!-- # PD vs PR  -->
<!-- cor.v <- cor(tab.1$grouped_pd, tab.1$grouped_pr) -->
<!-- p.1 <-  ggplot(tab.1, aes(x=grouped_pd, y=grouped_pr, label = cell.type)) + -->
<!--         geom_point(position = position_jitter()) +  -->
<!--         geom_label_repel(nudge_y = 0.15,direction = "y",hjust= 1,segment.size = 0.1,  -->
<!--                          label.size = 0, xlim = x_limits) +  -->
<!--         geom_abline(intercept = 0, slope = 1,linetype = "dashed", color="gray80") +  -->
<!--         annotate("text", x = 0.05, y = 0.4, label=paste("cor=",round(cor.v,3))) +  -->
<!--         xlim(0,0.5) + ylim(0,0.5) -->
<!-- # Naive to PD -->
<!-- cor.v <- cor(tab.1$naive, tab.1$grouped_pd) -->
<!-- p.2 <-  ggplot(tab.1, aes(x=naive, y=grouped_pd, label = cell.type)) + -->
<!--         geom_point(position = position_jitter()) +  -->
<!--         geom_label_repel(nudge_y = 0.15,direction = "y",hjust= 1,segment.size = 0.1,  -->
<!--                          label.size = 0, xlim = x_limits) +  -->
<!--         geom_abline(intercept = 0, slope = 1,linetype = "dashed", color="gray80") +  -->
<!--         annotate("text", x = 0.05, y = 0.4, label=paste("cor=",round(cor.v,3))) +  -->
<!--         xlim(0,0.5) + ylim(0,0.5) -->
<!-- # Naive to PR  -->
<!-- cor.v <- cor(tab.1$naive, tab.1$grouped_pr) -->
<!-- p.3 <-  ggplot(tab.1, aes(x=naive, y=grouped_pr, label = cell.type)) + -->
<!--         geom_point(position = position_jitter()) +  -->
<!--         geom_label_repel(nudge_y = 0.15,direction = "y",hjust= 1,segment.size = 0.1, -->
<!--                          label.size = 0, xlim = x_limits) +  -->
<!--         geom_abline(intercept = 0, slope = 1,linetype = "dashed", color="gray80") +  -->
<!--         annotate("text", x = 0.05, y = 0.4, label=paste("cor=",round(cor.v,3))) +  -->
<!--         xlim(0,0.5) + ylim(0,0.5) -->
<!-- p.all <- grid.arrange(p.1,p.2,p.3,ncol=2) -->
<!-- ggsave(filename = paste(dir,"plot_out/IM03/T-cell_population_fractions_pairwise.pdf", sep=""), plot = p.all, width = 12, height = 12) -->
<!-- p.all -->
<!-- ``` -->



<!-- Look at all cells and perform chi.square tests -->
<!-- This plotting is redudant since most things have already been plotted above  -->
<!-- The output here is just a bit more "concentrated" -->
<!-- ```{r} -->
<!-- require(ggthemes) -->
<!-- require(rcompanion) -->
<!-- require(ggpubr) -->
<!-- #  -->
<!-- metadata <- tiss_subset@meta.data -->
<!-- metadata <- metadata[which(metadata$immune_annotation=="immune"),] -->
<!-- # Keep only cells from tissues that are not brain or pleura  -->
<!-- metadata <- metadata[-which(metadata$biopsy_site=="Brain" | metadata$biopsy_site=="Pleura"),] -->
<!-- # Remove unknown cells  -->
<!-- # metadata <- metadata[-which(metadata$immune_subtype_annotation=="Unknown"),] -->
<!-- # Convert to factor with logical order  -->
<!-- metadata$analysis <- factor(metadata$analysis, levels = c("naive", "grouped_pd", "grouped_pr")) -->
<!-- # Create table and keep selected cell types  -->
<!-- meta.temp <- metadata[,c("immune_subtype_annotation", "analysis")] -->
<!-- ###### -->
<!-- # Loop over metadata labels  -->
<!-- for(i in 2:ncol(meta.temp)){ -->
<!-- table.temp <- melt(as.data.frame(meta.temp[c(1,i)])) -->
<!-- colnames(table.temp) <- c("Var1", "Var2") -->
<!-- pal <- tableau_color_pal("Tableau 20") -->
<!-- # Imune cells per category -->
<!-- p <- ggplot(table.temp) + geom_bar(aes(x = Var2,fill = Var1), position = "fill") +  -->
<!--   scale_fill_manual(values = pal(20)) +  -->
<!--   labs(x = colnames(meta.temp)[i], y="Fraction of cells") +  -->
<!--   guides(fill=guide_legend(title="Cell types")) -->
<!-- # Total nu,ber of cells  -->
<!-- q <- ggplot(melt(meta.temp[,i])) + geom_bar(aes(x = value)) + -->
<!--   geom_text(data = as.data.frame(table(meta.temp[,i])),aes(x = Var1, y = Freq, label=Freq), -->
<!--     position = position_dodge(width = 1), -->
<!--     vjust = -0.5, size = 4) + ggtitle("Ncells") -->
<!-- # Perform a chiSquare test  -->
<!-- table.chi <- t(table(meta.temp[c(1,i)])) -->
<!-- table.chi.res <- pairwiseNominalIndependence(table.chi,fisher = FALSE,gtest  = FALSE,chisq  = TRUE,method = "fdr") -->
<!-- temp <- -log10(table.chi.res$p.adj.Chisq) -->
<!-- temp[is.infinite(temp)] <- 0 -->
<!-- temp[is.na(temp)] <- 0 -->
<!-- # Plot  -->
<!-- temp <- cbind(as.data.frame(temp), as.data.frame( table.chi.res$Comparison)) -->
<!-- colnames(temp) <- c("p.value", "group") -->
<!-- r <- ggplot(temp) +geom_point(aes(x = p.value, y = group)) +  -->
<!--   labs(x = "-log10(p.value)", y="Treatment Status group") +  -->
<!--   geom_vline(xintercept = 5) -->
<!-- # Also make a line chart  -->
<!-- tt <- as.data.frame(table(as.data.frame(meta.temp[c(1,i)]))) -->
<!-- colnames(tt) <- c("Var1", "Var2", "Freq") -->
<!-- o <- ggplot(tt, aes(x=Var1, group=Var2, y=Freq)) + -->
<!--   geom_line(aes(color=Var2))+ -->
<!--   geom_point(aes(color=Var2)) +  -->
<!--   theme(axis.text.x = element_text(angle = 60, hjust = 1)) +  -->
<!--   labs(x ="", y="Number of cells") +  -->
<!--   guides(fill=guide_legend(title=colnames(meta.temp)[i])) -->
<!-- # Similar plot with normalized axis  -->
<!-- tt2 <- as.data.frame(prop.table(table(as.data.frame(meta.temp[c(1,i)])), margin = 2)) -->
<!-- colnames(tt2) <- c("Var1", "Var2", "Freq") -->
<!-- o2 <- ggplot(tt2, aes(x=Var1, group=Var2, y=Freq)) + geom_ribbon(data = tt2, aes(ymin=0, ymax=Freq, fill=Var2), alpha=0.5) + -->
<!--   geom_line(aes(color=Var2))+ -->
<!--   theme(axis.text.x = element_text(angle = 60, hjust = 1)) +  -->
<!--   labs(x ="", y="Fraction of cells") +  -->
<!--   guides(fill=guide_legend(title=colnames(meta.temp)[i])) -->

<!-- #Make a correlation panel -->
<!-- tab.2 <- as.data.frame.matrix(prop.table(table(as.data.frame(meta.temp[c(1,i)])))) -->
<!-- tab.2$types <- row.names(tab.2) -->
<!-- # Make and get legend -->
<!-- tab.3 <- as.data.frame(prop.table(table(as.data.frame(meta.temp[c(1,i)])))) -->
<!-- p.dum <- ggplot(tab.3, aes(Freq,Freq,color=immune_subtype_annotation)) + geom_point() + -->
<!--       guides(col = guide_legend(ncol = 3)) + -->
<!--       theme(legend.text=element_text(size=8), legend.title=element_blank()) -->
<!-- ######  -->
<!-- p.dum <- get_legend(p.dum) -->
<!-- p.dum <- as_ggplot(p.dum) -->
<!-- # Create ggpair plot -->
<!-- pm <- ggpairs(tab.2,columns = c(1:3), diag=list("blankDiag"), ggplot2::aes(colour=types), upper = list(continuous = "blank")) #, upper = list(continuous = gglegend("points")) -->
<!-- pm[1,2] <- p.dum -->
<!-- # Combine and plot all  -->
<!-- # pqr <- ggarrange(p,ggarrange(q, r, ncol = 2),nrow = 2)  -->
<!-- opqr <- ggarrange(p,o,o2,q,r,nrow = 2, ncol=3, labels = "AUTO")  -->
<!-- # Save  -->
<!-- ggsave(filename = paste("/myVolume/sclung_adeno/immune_cell_analysis/plot_out/I04/","Immune_cell_population_fractions_by_",colnames(meta.temp)[i], ".pdf", sep="") , plot = opqr, width = 17, height = 10) -->
<!-- } -->
<!-- ``` -->


<!-- Repeat the above analysis for T-cells only  -->
<!-- ```{r} -->
<!-- metadata <- tiss_subset@meta.data -->
<!-- metadata <- metadata[which(metadata$immune_annotation=="immune"),] -->
<!-- # Keep only cells from tissues that are not brain or pleura  -->
<!-- metadata <- metadata[-which(metadata$biopsy_site=="Brain" | metadata$biopsy_site=="Pleura"),] -->
<!-- # Remove unknown cells  -->
<!-- # metadata <- metadata[-which(metadata$immune_subtype_annotation=="Unknown"),] -->
<!-- # Convert to factor with logical order  -->
<!-- metadata$analysis <- factor(metadata$analysis, levels = c("naive", "grouped_pd", "grouped_pr")) -->
<!-- # Keep only T-cells  -->
<!-- metadata <- metadata[which(metadata$immune_subtype_annotation=="T-cells"),] -->
<!-- # Create table and keep selected cell types  -->
<!-- meta.temp <- metadata[,c("T_cell_subtype_annotation", "analysis")] -->
<!-- ###### -->
<!-- # Loop over metadata labels  -->
<!-- for(i in 2:ncol(meta.temp)){ -->
<!-- table.temp <- melt(as.data.frame(meta.temp[c(1,i)])) -->
<!-- colnames(table.temp) <- c("Var1", "Var2") -->
<!-- pal <- tableau_color_pal("Tableau 20") -->
<!-- # Imune cells per category -->
<!-- p <- ggplot(table.temp) + geom_bar(aes(x = Var2,fill = Var1), position = "fill") +  -->
<!--   scale_fill_manual(values = pal(20)) +  -->
<!--   labs(x = colnames(meta.temp)[i], y="Fraction of cells") +  -->
<!--   guides(fill=guide_legend(title="Cell types")) -->
<!-- # Total nu,ber of cells  -->
<!-- q <- ggplot(melt(meta.temp[,i])) + geom_bar(aes(x = value)) + -->
<!--   geom_text(data = as.data.frame(table(meta.temp[,i])),aes(x = Var1, y = Freq, label=Freq), -->
<!--     position = position_dodge(width = 1), -->
<!--     vjust = -0.5, size = 4) + ggtitle("Ncells") -->
<!-- # Perform a chiSquare test  -->
<!-- table.chi <- t(table(meta.temp[c(1,i)])) -->
<!-- table.chi.res <- pairwiseNominalIndependence(table.chi,fisher = FALSE,gtest  = FALSE,chisq  = TRUE,method = "fdr") -->
<!-- temp <- -log10(table.chi.res$p.adj.Chisq) -->
<!-- temp[is.infinite(temp)] <- 0 -->
<!-- temp[is.na(temp)] <- 0 -->
<!-- # Plot  -->
<!-- temp <- cbind(as.data.frame(temp), as.data.frame( table.chi.res$Comparison)) -->
<!-- colnames(temp) <- c("p.value", "group") -->
<!-- r <- ggplot(temp) +geom_point(aes(x = p.value, y = group)) +  -->
<!--   labs(x = "-log10(p.value)", y="Treatment Status group") +  -->
<!--   geom_vline(xintercept = 5) -->
<!-- # Also make a line chart  -->
<!-- tt <- as.data.frame(table(as.data.frame(meta.temp[c(1,i)]))) -->
<!-- colnames(tt) <- c("Var1", "Var2", "Freq") -->
<!-- o <- ggplot(tt, aes(x=Var1, group=Var2, y=Freq)) + -->
<!--   geom_line(aes(color=Var2))+ -->
<!--   geom_point(aes(color=Var2)) +  -->
<!--   theme(axis.text.x = element_text(angle = 60, hjust = 1)) +  -->
<!--   labs(x ="", y="Number of cells") +  -->
<!--   guides(fill=guide_legend(title=colnames(meta.temp)[i])) -->
<!-- # Similar plot with normalized axis  -->
<!-- tt2 <- as.data.frame(prop.table(table(as.data.frame(meta.temp[c(1,i)])), margin = 2)) -->
<!-- colnames(tt2) <- c("Var1", "Var2", "Freq") -->
<!-- o2 <- ggplot(tt2, aes(x=Var1, group=Var2, y=Freq)) + geom_ribbon(data = tt2, aes(ymin=0, ymax=Freq, fill=Var2), alpha=0.5) + -->
<!--   geom_line(aes(color=Var2))+ -->
<!--   theme(axis.text.x = element_text(angle = 60, hjust = 1)) +  -->
<!--   labs(x ="", y="Fraction of cells") +  -->
<!--   guides(fill=guide_legend(title=colnames(meta.temp)[i])) -->

<!-- #Make a correlation panel -->
<!-- tab.2 <- as.data.frame.matrix(prop.table(table(as.data.frame(meta.temp[c(1,i)])))) -->
<!-- tab.2$types <- row.names(tab.2) -->
<!-- # Make and get legend -->
<!-- tab.3 <- as.data.frame(prop.table(table(as.data.frame(meta.temp[c(1,i)])))) -->
<!-- p.dum <- ggplot(tab.3, aes(Freq,Freq,color=T_cell_subtype_annotation)) + geom_point() + -->
<!--       guides(col = guide_legend(ncol = 3)) + -->
<!--       theme(legend.text=element_text(size=8), legend.title=element_blank()) -->
<!-- p.dum <- get_legend(p.dum) -->
<!-- p.dum <- as_ggplot(p.dum) -->
<!-- # Create ggpair plot -->
<!-- pm <- ggpairs(tab.2,columns = c(1:3), diag=list("blankDiag"), ggplot2::aes(colour=types), upper = list(continuous = "blank")) #, upper = list(continuous = gglegend("points")) -->
<!-- pm[1,2] <- p.dum -->
<!-- # Combine and plot all  -->
<!-- opqr <- ggarrange(p,o,o2,q,r,nrow = 2, ncol=3, labels = "AUTO")  -->
<!-- # Save  -->
<!-- ggsave(filename = paste("/myVolume/sclung_adeno/immune_cell_analysis/plot_out/I04/","T_cell_population_fractions_by_",colnames(meta.temp)[i], ".pdf", sep="") , plot = opqr, width = 17, height = 10) -->
<!-- } -->
<!-- ``` -->



<!-- Conclusions hold true even when only conisdering Liver and Lung (which are common across the three fields) -->
<!-- All cells  -->
<!-- ```{r} -->
<!-- library(ggrepel) -->
<!-- require(qdapTools) -->
<!-- require(REdaS) -->
<!-- #  -->
<!-- metadata <- tiss_subset@meta.data -->
<!-- metadata <- metadata[which(metadata$immune_annotation=="immune"),] -->
<!-- # Keep only cells from tissues that are not brain or pleura  -->
<!-- metadata <- metadata[which(metadata$biopsy_site=="Lung" | metadata$biopsy_site=="Liver"),] -->
<!-- # Remove unknown cells  -->
<!-- # metadata <- metadata[-which(metadata$immune_subtype_annotation=="Unknown"),] -->
<!-- # Convert to factor with logical order  -->
<!-- metadata$analysis <- factor(metadata$analysis, levels = c("naive", "grouped_pd", "grouped_pr")) -->
<!-- # Create table and keep selected cell types  -->
<!-- meta.temp <- metadata[,c("immune_subtype_annotation", "analysis")] -->
<!-- # Loop over treatment response categories  -->
<!-- # Create list to store frequency tables  -->
<!-- prop.table.error <- list() -->
<!-- for(i in 1:length(unique(meta.temp$analysis))){ -->
<!-- vec.temp <- meta.temp[meta.temp$analysis==unique(meta.temp$analysis)[i],"immune_subtype_annotation"] -->
<!-- # Convert to counts and calculate 95% CI  -->
<!-- # Store in list  -->
<!-- table.temp <- freqCI(vec.temp, level = c(.95)) -->
<!-- prop.table.error[[i]] <- print(table.temp, percent = TRUE, digits = 3) -->
<!-- #  -->
<!-- } -->
<!-- # Name list  -->
<!-- names(prop.table.error) <- unique(meta.temp$analysis) -->
<!-- # Convert to data frame  -->
<!-- tab.1 <- as.data.frame.array(do.call(rbind, prop.table.error)) -->
<!-- # Add analysis column  -->
<!-- b <- c() -->
<!-- a <- c() -->
<!-- for(i in names(prop.table.error)){ -->
<!--   a <- rep(i,length(unique(row.names(tab.1)))) -->
<!--   b <- c(b,a) -->
<!-- } -->
<!-- tab.1$analysis <- b -->
<!-- tab.1$cell <- row.names(tab.1) -->
<!-- # Resort factor analysis  -->
<!-- tab.1$analysis <- factor(tab.1$analysis, levels = c("naive", "grouped_pd", "grouped_pr")) -->
<!-- # Rename percentile columns  -->
<!-- colnames(tab.1)[1] <- "lower" -->
<!-- colnames(tab.1)[3] <- "upper" -->
<!-- #  -->
<!-- p<- ggplot(tab.1, aes(x=analysis, y=Estimate, group=cell)) + -->
<!--     geom_line(aes(color=cell))+ -->
<!--     geom_point(aes(color=cell)) + facet_grid(cols =  vars(cell)) +  -->
<!--     theme(axis.text.x = element_text(angle = 45, hjust=1, vjust=0.5), legend.position="bottom") +  -->
<!--     xlab("") +  -->
<!--     geom_errorbar(aes(ymin=lower, ymax=upper), width=.2,position=position_dodge(0.05)) -->
<!-- # Save plot  -->
<!-- ggsave("/myVolume/sclung_adeno/immune_cell_analysis/plot_out/I04/All_immune_populations_across_treatment_Lung_Liver.pdf",width = 11, height = 8) -->
<!-- p -->
<!-- ``` -->