---
title: "Untitled"
output: html_document
---

More detailed Immune phenotyping of different immune cell types
Myeloid 

Load immune workspace
```{r}
rm(list=ls())
dir <- "/myVolume/scell_lung_adenocarcinoma/"
load(file=paste(dir,"Data_input/Immuune_Seurat_object.RData", sep=""))
```

Subset Myeloid
```{r}
mf.cells <- row.names(tiss_immune@meta.data)[which(tiss_immune@meta.data$immune_subtype_annotation == "MF-Monocytes")]
length(mf.cells)
mf.cell.tiss <- SubsetData(object = tiss_immune, cells.use = mf.cells)
```

Save Myeloid workspace 
```{r}
save(t.cell.tiss, file = "/myVolume/sclung_adeno/R_objects/04_tiss_subset_190128_Myeloid.RData")
```

Biopsy site vs analysis 
```{r}
tab.1 <- table(t.cell.tiss@meta.data$biopsy_site, t.cell.tiss@meta.data$analysis)
balloonplot(tab.1, main ="Response vs Biopsy site", xlab ="", ylab="",
            label = T, show.margins = F)
```

Subset Myeloid only within Lung 
```{r}
t.cells <- row.names(t.cell.tiss@meta.data)[which(t.cell.tiss@meta.data$biopsy_site == "Lung")]
length(t.cells)
t.cell.tiss <- SubsetData(object = tiss_subset_immune, cells.use = t.cells)
```

Unsupervised clustering of Myeloid cells

Find variable genes
```{r}
t.cell.tiss <- FindVariableGenes(object = t.cell.tiss, do.plot = TRUE, x.high.cutoff = Inf, y.cutoff = 1, num.bin = 20, 
                                          binning.method = "equal_width", do.recalc = T, x.low.cutoff=1)
# # Selction vector 
# sel.vec <- row.names(t.cell.tiss@data) %in% t.cell.tiss@var.genes
# table(sel.vec)
# Create color vector 
# col.vec <- rep("black", nrow(t.cell.tiss@data))
# col.vec[sel.vec] <- "red"
# Plot 
# par(mfcol=c(2,1))
# plot(t.cell.tiss@hvg.info$gene.mean, t.cell.tiss@hvg.info$gene.dispersion.scaled, 
#      pch=19, col=col.vec,cex=0.2)
# plot(t.cell.tiss@hvg.info$gene.mean[sel.vec], t.cell.tiss@hvg.info$gene.dispersion.scaled[sel.vec], 
#      pch=19, col="red",cex=0.2)
```

Unsupervised clustering of Myeloid cells
# PCA
```{r}
t.cell.tiss <- RunPCA(object = t.cell.tiss, do.print = FALSE, pcs.compute = )
t.cell.tiss <- ProjectPCA(object = t.cell.tiss, do.print = FALSE)
```

# visualize PCA heatmaps and PC variance
```{r}
PCHeatmap(object = t.cell.tiss, pc.use = 1:15, cells.use = 100, do.balanced = TRUE, label.columns = FALSE, num.genes = 10)
```

```{r}
PCElbowPlot(object = t.cell.tiss)
```

Perform correlation of PCs and metadata fields
```{r}
require(corrplot)
pca.obj <- t.cell.tiss@dr$pca
pc.coords <- pca.obj@cell.embeddings
df1 <- t.cell.tiss@meta.data[,c("nGene","nReads","percent.ribo")]
df2 <- pc.coords[,c(1:10)]
cordf12 <- cor(df1,df2)
# Make a correlation plot
corrplot(cordf12, method = "number", main="Correlation of PCs and metadata")
```

JackStraw of PCs 
```{r}
t.cell.tiss <- JackStraw(t.cell.tiss, num.replicate = 100, display.progress = T, 
                         do.par = T, num.cores = 15, num.pc = 15)
JackStrawPlot(t.cell.tiss, PCs = 1:15)
```


Define components to be used for clustering 
```{r}
n.pcs.min = 1
n.pcs.max = 10
```

pick resolution parameter
```{r}
res.used <- 0.3
t.cell.tiss <- FindClusters(object = t.cell.tiss, reduction.type = "pca", dims.use = n.pcs.min:n.pcs.max, 
    resolution = res.used, print.output = 0, save.SNN = TRUE, k.param = 10, force.recalc = T)
```

Plot a few of the principal components 
```{r}
require(GGally)
require(reshape)
temp <- t.cell.tiss@dr$pca@cell.embeddings
temp <- as.data.frame(temp)
names <- colnames(temp)
temp <- cbind(temp, t.cell.tiss@meta.data$analysis)
colnames(temp) <- c(names, "cluster")
pca.scatter = ggpairs(data=temp,
             columns=1:10, 
             upper = list(continuous = "points"),
             lower = list(combo = "na"),
             mapping=ggplot2::aes(colour = cluster), legend = 2) + theme(legend.position = "bottom")
ggsave(plot = pca.scatter, filename = "/myVolume/sclung_adeno/immune_cell_analysis/plot_out/I03/Myeloid-cells_PCA_scatterplots_largefile_LUNG.pdf",width = 15, height = 12)
```


# Run TSNE
```{r}
t.cell.tiss <- RunTSNE(object = t.cell.tiss, dims.use = n.pcs.min:n.pcs.max, seed.use = 10, perplexity=30)
```

# Plot TSNE
```{r}
TSNEPlot(object = t.cell.tiss, do.label = T)
```


# Plot TSNE with analysis colors 
```{r}
t.cell.tiss <- SetIdent(t.cell.tiss,ident.use = t.cell.tiss@meta.data$analysis)
TSNEPlot(object = t.cell.tiss, do.label = T)
t.cell.tiss <- SetIdent(t.cell.tiss,ident.use = t.cell.tiss@meta.data$res.0.3)
```

```{r}
tab.1 <- table(t.cell.tiss@meta.data$res.0.3, t.cell.tiss@meta.data$analysis)
balloonplot(tab.1, main ="Response vs Biopsy site", xlab ="", ylab="",
            label = T, show.margins = F)
```

Find all cluster markers 
```{r}
t.cell.markers <- FindAllMarkers(object = t.cell.tiss, only.pos = TRUE, min.pct = 0.25, thresh.use = 0.25)
```

Plot top genes 
```{r}
require(tidyverse)
t.cell.markers %>% group_by(cluster) %>% top_n(10, avg_logFC) -> top10
DoHeatmap(t.cell.tiss, genes.use = top10$gene, slim.col.label = TRUE, remove.key = TRUE, cex.row = 5)
```

Plot top genes annotate by reponse
```{r}
t.cell.tiss <- SetIdent(t.cell.tiss,ident.use = t.cell.tiss@meta.data$analysis)
#t.cell.markers %>% group_by(cluster) %>% top_n(10, avg_logFC) -> top10
DoHeatmap(t.cell.tiss, genes.use = top10$gene, slim.col.label = TRUE, remove.key = TRUE, cex.row = 5)
t.cell.tiss <- SetIdent(t.cell.tiss,ident.use = t.cell.tiss@meta.data$res.0.3)
```



Write table of top genes 
```{r}
write.table(t.cell.markers, "/myVolume/sclung_adeno/immune_cell_analysis/data_out/I03/Myeloid-cells_DE_genes_between_subclusters_Lung.csv")
```



Plot all relevant, PCA, tSNE and Clustering plots as pdf 
```{r}
pdf("/myVolume/sclung_adeno/immune_cell_analysis/plot_out/I03/Myeloid-cells_subclustering_TSNE_LUNG.pdf",10,10)
# Table 
tab.1 <- table(t.cell.tiss@meta.data$res.0.3, t.cell.tiss@meta.data$analysis)
balloonplot(tab.1, main ="Response vs Biopsy site", xlab ="", ylab="",
            label = T, show.margins = F)
# TSNE plots 
TSNEPlot(object = t.cell.tiss, do.label = T)
TSNEPlot(object = t.cell.tiss, do.label = T, group.by="analysis")
# Heatmaps
DoHeatmap(t.cell.tiss, genes.use = top10$gene, slim.col.label = TRUE, remove.key = TRUE, cex.row = 5, title = "Top 10 DE genes")
# PCA plots 
PCHeatmap(object = t.cell.tiss, pc.use = 1:15, cells.use = 100, do.balanced = TRUE, label.columns = FALSE, num.genes = 10)
PCElbowPlot(object = t.cell.tiss)
JackStrawPlot(t.cell.tiss, PCs = 1:12)
# Feature plot
DotPlot(t.cell.tiss, top10$gene, x.lab.rot = T)
DotPlot(t.cell.tiss, top10$gene, x.lab.rot = T, group.by = "analysis")
dev.off()
```

Save Myeloid workspace 
```{r}
save(t.cell.tiss, file = "/myVolume/sclung_adeno/R_objects/04_tiss_subset_190128_Myeloid_LUNG.RData")
```


Import the differential expression results 
Convert to IPA format and export for IPA analysis
```{r}
# Read table generated above 
markers <- read.table("/myVolume/sclung_adeno/immune_cell_analysis/data_out/I03/Myeloid-cells_DE_genes_between_subclusters_Lung.csv")
# Source function 
source("/myVolume/sclung_adeno/immune_cell_analysis/scripts/seurat_to_IPA.R")
# Import table of DE genes 
t.ipa <- seurat.to.ipa(df = markers, score.column = "avg_logFC",divide.by.column = "cluster",
                        gene.column = "gene",divide.append = cell_type)

# # Write table 
write.table(t.ipa, "/myVolume/sclung_adeno/immune_cell_analysis/data_out/I03/Differentially_expressed_genes_Myeloid_clusters_LUNG.txt" , row.names = T, quote=F, sep="\t")
```



Save Myeloid workspace 
```{r}
VlnPlot(t.cell.tiss, c("CTLA4","CD274"))
```
