---
title: "Untitled"
output: html_document
---

Count the fraction of Immune cells across different metadata fields 

Libraries 
```{r}
require(tidyr)
require(ggthemes)
require(reshape)
require(rcompanion)
require(ggpubr)
require(GGally)
library(ggrepel)
require(qdapTools)
require(REdaS)
```

Load immune workspace
```{r}
rm(list=ls())
dir <- "/myVolume/scell_lung_adenocarcinoma/"
load(file=paste(dir,"Data_input/objects/IM01_Immune_Seurat_object.RData", sep=""))
```

```{r}
require(ggthemes)
require(devtools)
require(reshape)
# packageurl <- "https://cran.r-project.org/src/contrib/Archive/DescTools/DescTools_0.99.28.tar.gz"
# install.packages(packageurl, repos = NULL, type = "source")
# install.packages('rcompanion')
require(rcompanion)
require(ggpubr)
require(gplots)
```

# Subset metadata 
Remove cells that are not immune or are annotated as treatment status Pending or unknown. Also 
exclude thoracentesis derived immune cells as they are not necessarily proximal to the tumor. Brain will also be removed 
since it only has <10 cells. 

Count the fraction of Immune cells across patients with multiple biopsies 
```{r}
# Create list to save Myeloid and T-cell counts for every patient with multiple biopsies 
list.sum <- list()
# Subset metadata 
metadata <- tiss_immune@meta.data
# Keep only cells from tissues that are not brain or pleura 
metadata <- metadata[-which(metadata$biopsy_site=="Brain" | metadata$biopsy_site=="Pleura"),]
metadata$biopsy_date_2 <- as.factor(paste(metadata$biopsy_date, metadata$analysis))
tab.1 <- table(metadata$biopsy_date_2,metadata$patient_id)
# Which patients have cells across multiple timepoints ? 
tab.1[tab.1 > 0] <- 1
# patients <- colnames(tab.1)[which(colSums(tab.1) > 1) ]
patients <- c("TH226", "TH266")
# Make a table of patients+biopsy date+biopsy site+ treatment status  
temp.1 <- metadata[metadata$patient_id %in% patients,c("patient_id","biopsy_date", "biopsy_site", "analysis", "biopsy_date_2")]
tab.1 <- table(temp.1$biopsy_date_2, temp.1$patient_id)
# Remove patients with single time points 
tab.1 <- tab.1[,names(which(colSums(tab.1) !=0))]
# Zeros to NAs
tab.1[tab.1 == 0] <- NA
# Save an image with all patients and their time points 
# pdf(paste(dir,"plot_out/IM05/All_immune_population_correlations_across_treatment.pdf", sep=""), width = 5, height = 5)
# pdf("/myVolume/sclung_adeno/immune_cell_analysis/plot_out/I04/Heatmap_of_patient_timepoints.pdf",10,10)
colfunc <- colorRampPalette(c("white", "red"))
heatmap.2(tab.1, Rowv = F, Colv = F, col = colfunc(10), trace="n", key = T,
          colsep = 1:ncol(tab.1), sepcolor = "grey90", margins = c(5,10), rowsep = 1:nrow(tab.1), 
          cellnote=tab.1,
          notecex=1.0,
          notecol="black",
          na.color=par("bg"))
# dev.off()

# Loop over all patients 
patients <- c("TH226", "TH266")
for(i in 1:length(patients)) {
metadata2 <- metadata[which(metadata$patient_id==patients[i]),]
# Custom for TH179
print(dim(metadata2))
# Subset to fields of interest 
meta.temp <- metadata2[,c("immune_subtype_annotation", "biopsy_date", "biopsy_site", "analysis")]
meta.temp$biopsy_date <- as.factor(paste(meta.temp$biopsy_date, meta.temp$analysis))
# Color function
pal <- tableau_color_pal("Tableau 20")
# Imune cells per category
p <- ggplot(meta.temp) + geom_bar(aes(x = biopsy_date,fill = immune_subtype_annotation), position = "fill") + 
  scale_fill_manual(values = pal(20)) + ggtitle(patients[i])
# Total number of cells 
q <- ggplot(melt(meta.temp[,2])) + geom_bar(aes(x = value)) +
  geom_text(data = as.data.frame(table(meta.temp[,2])),aes(x = Var1, y = Freq, label=Freq), 
    position = position_dodge(width = 1),
    vjust = -0.5, size = 4) + ggtitle("Ncells")
# Perform a chiSquare test 
table.chi <- t(table(meta.temp[c(1,2)]))
table.chi.res <- pairwiseNominalIndependence(table.chi,fisher = FALSE,gtest  = FALSE,chisq  = TRUE,method = "fdr")
temp <- -log10(table.chi.res$p.adj.Chisq)
temp[is.infinite(temp)] <- 0
temp[is.na(temp)] <- 0
# Plot 
temp <- cbind(as.data.frame(temp), as.data.frame(table.chi.res$Comparison))
colnames(temp) <- c("p.value", "group")
r <- ggplot(temp) +geom_point(aes(x = p.value, y = group)) + 
  labs(x = "-log10(p.value)", y="Treatment Status group") + 
  geom_vline(xintercept = 5)
# Also make a line chart 
tt <- as.data.frame(table(as.data.frame(meta.temp[c(1,2)])))
colnames(tt) <- c("Var1", "Var2", "Freq")
o <- ggplot(tt, aes(x=Var1, group=Var2, y=Freq)) +
  geom_line(aes(color=Var2))+
  geom_point(aes(color=Var2)) + 
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) + # , colour = col.imm.generic
  labs(x ="", y="Number of cells") 
# Similar plot with normalized axis 
tt2 <- as.data.frame(prop.table(table(as.data.frame(meta.temp[c(1,2)])),margin = 2))
colnames(tt2) <- c("Var1", "Var2", "Freq")
o2 <- ggplot(data=tt2, aes(x=Var1, y=Freq, fill=Var2)) +
geom_bar(stat="identity", position=position_dodge()) + 
theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
  labs(x ="", y="Fraction of cells")
# Combine and plot all 
opqr <- ggarrange(p,o,o2,q,r,nrow = 2, ncol=3) 
# Save 
# ggsave(filename = paste(dir,"plot_out/IM05/Immune_cell_population_changes_multiple_biopsies_",patients[i], ".pdf", sep="") , plot = opqr, width = 17, height = 10)}
# Also export counts for T-cells and myeloid cells to make a "before-after" plot 
list.sum[[i]] <- tt2[which(tt2$Var1=="MFs.monocytes" | tt2$Var1=="T-cells" | tt2$Var1=="DCs" | tt2$Var1=="Neutrophils"),]
names(list.sum)[i] <- patients[i]
}
```


Plot fractional changes of selected cell populations across treatment (Patient TH226)
```{r}
metadata <- tiss_immune@meta.data
# Keep only cells from tissues that are not brain or pleura 
metadata <- metadata[-which(metadata$biopsy_site=="Brain" | metadata$biopsy_site=="Pleura"),]
#Keep only TH226
metadata_TH226 <- filter(metadata, patient_id == "TH226")
#add back rownames
rownames(metadata_TH226) <- metadata_TH226$cell_id
# Convert to factor with logical order 
metadata_TH226$analysis <- factor(metadata_TH226$analysis, levels = c("naive", "grouped_pr", "grouped_pd"))
# Create table and keep selected cell types 
meta.temp <- metadata_TH226[,c("immune_subtype_annotation", "analysis")]

# Loop over treatment response categories 
# Create list to store frequency tables 
prop.table.error <- list()
for(i in 1:length(unique(meta.temp$analysis))){
vec.temp <- meta.temp[meta.temp$analysis==unique(meta.temp$analysis)[i],"immune_subtype_annotation"]
# Convert to counts and calculate 95% CI 
# Store in list 
table.temp <- freqCI(vec.temp, level = c(.95))
prop.table.error[[i]] <- print(table.temp, percent = TRUE, digits = 3)
# 
}
# Name list 
names(prop.table.error) <- unique(meta.temp$analysis)
# Add the analysis labels 
for(i in 1:length(prop.table.error)){
  row.names(prop.table.error[[i]]) <- paste(row.names(prop.table.error[[i]]), names(prop.table.error)[i], sep="__")
}
# Convert to data frame 
tab.1 <- as.data.frame.array(do.call(rbind, prop.table.error))
# Add analysis column
tab.1$analysis <- do.call(rbind, strsplit(row.names(tab.1), "__"))[,2]
# Resort factor analysis 
tab.1$analysis <- factor(tab.1$analysis, levels = c("naive", "grouped_pr", "grouped_pd"))
# Store cell type in different column 
tab.1$cell <- do.call(rbind, strsplit(row.names(tab.1), "__"))[,1]

colnames(tab.1)[1] <- "lower"
colnames(tab.1)[3] <- "upper"

# Plot
p1<- ggplot(tab.1, aes(x=analysis, y=Estimate, group=cell)) +
    geom_bar(stat = "identity", aes(fill=analysis)) + facet_grid(cols =  vars(cell)) + 
    geom_errorbar(aes(ymin=lower, ymax=upper), width=.2,position=position_dodge(0.05)) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust=1, vjust=0.5), legend.position = 'none') + 
    xlab("")

# Save plot 
ggsave(plot = p1, filename = paste(dir,"plot_out/IM02/All_immune_populations_across_treatment_TH226.pdf", sep=""),width = 11, height = 8)
p1
```

Plot fractional changes of selected cell populations across treatment (Patient TH226)
```{r}
metadata_TH266 <- filter(metadata, patient_id == "TH266")
#add back rownames
rownames(metadata_TH266) <- metadata_TH266$cell_id
# Convert to factor with logical order 
metadata_TH266$analysis <- factor(metadata_TH266$analysis, levels = c("naive", "grouped_pr", "grouped_pd"))
# Create table and keep selected cell types 
meta.temp <- metadata_TH266[,c("immune_subtype_annotation", "analysis")]

# Loop over treatment response categories 
# Create list to store frequency tables 
prop.table.error <- list()
for(i in 1:length(unique(meta.temp$analysis))){
vec.temp <- meta.temp[meta.temp$analysis==unique(meta.temp$analysis)[i],"immune_subtype_annotation"]
# Convert to counts and calculate 95% CI 
# Store in list 
table.temp <- freqCI(vec.temp, level = c(.95))
prop.table.error[[i]] <- print(table.temp, percent = TRUE, digits = 3)
# 
}
# Name list 
names(prop.table.error) <- unique(meta.temp$analysis)
# Add the analysis labels 
for(i in 1:length(prop.table.error)){
  row.names(prop.table.error[[i]]) <- paste(row.names(prop.table.error[[i]]), names(prop.table.error)[i], sep="__")
}
# Convert to data frame 
tab.1 <- as.data.frame.array(do.call(rbind, prop.table.error))
# Add analysis column
tab.1$analysis <- do.call(rbind, strsplit(row.names(tab.1), "__"))[,2]
# Resort factor analysis 
tab.1$analysis <- factor(tab.1$analysis, levels = c("naive", "grouped_pr", "grouped_pd"))
# Store cell type in different column 
tab.1$cell <- do.call(rbind, strsplit(row.names(tab.1), "__"))[,1]

colnames(tab.1)[1] <- "lower"
colnames(tab.1)[3] <- "upper"

# Plot
p2 <- ggplot(tab.1, aes(x=analysis, y=Estimate, group=cell)) +
    geom_bar(stat = "identity", aes(fill=analysis)) + facet_grid(cols =  vars(cell)) + 
    geom_errorbar(aes(ymin=lower, ymax=upper), width=.2,position=position_dodge(0.05)) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust=1, vjust=0.5), legend.position = 'none') + 
    xlab("")

# Save plot 
ggsave(plot = p2, filename = paste(dir,"plot_out/IM02/All_immune_populations_across_treatment_TH266.pdf", sep=""),width = 11, height = 8)
p2
```