---
title: "Untitled"
output: html_document
---

Count the fraction of Immune cells across different metadata fields 

Libraries 
```{r}
require(tidyr)
require(ggthemes)
require(reshape)
require(rcompanion)
require(ggpubr)
require(GGally)
```

Load immune workspace
```{r}
rm(list=ls())
dir <- "/myVolume/scell_lung_adenocarcinoma/"
load(file=paste(dir,"Data_input/objects/IM01_Immune_Seurat_object.RData", sep=""))
```

# Subset metadata 
Remove cells that are not immune or are annotated as treatment status Pending or unknown. Also 
exclude thoracentesis derived immune cells as they are not necessarily proximal to the tumor. Brain will also be removed 
since it only has <10 cells. 


Count the fraction of Immune cells across patients with multiple biopsies 
```{r}
require(ggthemes)
require(reshape)
require(rcompanion)
require(ggpubr)
require(gplots)
# Create list to save Myeloid and T-cell counts for every patient with multiple biopsies 
list.sum <- list()
# Subset metadata 
metadata <- tiss_immune@meta.data
# Keep only cells from tissues that are not brain or pleura 
metadata <- metadata[-which(metadata$biopsy_site=="Brain" | metadata$biopsy_site=="Pleura"),]
metadata$biopsy_date_2 <- as.factor(paste(metadata$biopsy_date, metadata$analysis))
tab.1 <- table(metadata$biopsy_date_2,metadata$patient_id)
# Which patients have cells across multiple timepoints ? 
tab.1[tab.1 > 0] <- 1
# patients <- colnames(tab.1)[which(colSums(tab.1) > 1) ]
patients <- c("TH226", "TH266")
# Make a table of patients+biopsy date+biopsy site+ treatment status  
temp.1 <- metadata[metadata$patient_id %in% patients,c("patient_id","biopsy_date", "biopsy_site", "analysis", "biopsy_date_2")]
tab.1 <- table(temp.1$biopsy_date_2, temp.1$patient_id)
# Remove patients with single time points 
tab.1 <- tab.1[,names(which(colSums(tab.1) !=0))]
# Zeros to NAs
tab.1[tab.1 == 0] <- NA
# Save an image with all patients and their time points 
pdf(paste(dir,"plot_out/IM05/All_immune_population_correlations_across_treatment.pdf", sep=""), width = 5, height = 5)
# pdf("/myVolume/sclung_adeno/immune_cell_analysis/plot_out/I04/Heatmap_of_patient_timepoints.pdf",10,10)
colfunc <- colorRampPalette(c("white", "red"))
heatmap.2(tab.1, Rowv = F, Colv = F, col = colfunc(10), trace="n", key = T,
          colsep = 1:ncol(tab.1), sepcolor = "grey90", margins = c(5,10), rowsep = 1:nrow(tab.1), 
          cellnote=tab.1,
          notecex=1.0,
          notecol="black",
          na.color=par("bg"))
dev.off()
# Loop over all patients 
patients <- c("TH226", "TH266")
for(i in 1:length(patients)){
metadata2 <- metadata[which(metadata$patient_id==patients[i]),]
# Custom for TH179
print(dim(metadata2))
if(patients[i]=="TH179"){metadata2 <- metadata2[-which(metadata2$biopsy_site=="LN"),]}
print(dim(metadata2))
if(dim(metadata2)[1] != 0 ) {
# Subset to fields of interest 
meta.temp <- metadata2[,c("immune_subtype_annotation", "biopsy_date", "biopsy_site", "analysis")]
meta.temp$biopsy_date <- as.factor(paste(meta.temp$biopsy_date, meta.temp$analysis))
# Color function
pal <- tableau_color_pal("Tableau 20")
# Imune cells per category
p <- ggplot(meta.temp) + geom_bar(aes(x = biopsy_date,fill = immune_subtype_annotation), position = "fill") + 
  scale_fill_manual(values = pal(20)) + ggtitle(patients[i])
# Total number of cells 
q <- ggplot(melt(meta.temp[,2])) + geom_bar(aes(x = value)) +
  geom_text(data = as.data.frame(table(meta.temp[,2])),aes(x = Var1, y = Freq, label=Freq), 
    position = position_dodge(width = 1),
    vjust = -0.5, size = 4) + ggtitle("Ncells")
# Perform a chiSquare test 
table.chi <- t(table(meta.temp[c(1,2)]))
table.chi.res <- pairwiseNominalIndependence(table.chi,fisher = FALSE,gtest  = FALSE,chisq  = TRUE,method = "fdr")
temp <- -log10(table.chi.res$p.adj.Chisq)
temp[is.infinite(temp)] <- 0
temp[is.na(temp)] <- 0
# Plot 
temp <- cbind(as.data.frame(temp), as.data.frame( table.chi.res$Comparison))
colnames(temp) <- c("p.value", "group")
r <- ggplot(temp) +geom_point(aes(x = p.value, y = group)) + 
  labs(x = "-log10(p.value)", y="Treatment Status group") + 
  geom_vline(xintercept = 5)
# Also make a line chart 
tt <- as.data.frame(table(as.data.frame(meta.temp[c(1,2)])))
colnames(tt) <- c("Var1", "Var2", "Freq")
o <- ggplot(tt, aes(x=Var1, group=Var2, y=Freq)) +
  geom_line(aes(color=Var2))+
  geom_point(aes(color=Var2)) + 
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) + # , colour = col.imm.generic
  labs(x ="", y="Number of cells") 
# Similar plot with normalized axis 
tt2 <- as.data.frame(prop.table(table(as.data.frame(meta.temp[c(1,2)])),margin = 2))
colnames(tt2) <- c("Var1", "Var2", "Freq")
o2 <- ggplot(data=tt2, aes(x=Var1, y=Freq, fill=Var2)) +
geom_bar(stat="identity", position=position_dodge()) + 
theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
  labs(x ="", y="Fraction of cells")
# Combine and plot all 
opqr <- ggarrange(p,o,o2,q,r,nrow = 2, ncol=3) 
# Save 
ggsave(filename = paste(dir,"plot_out/IM05/Immune_cell_population_changes_multiple_biopsies_",patients[i], ".pdf", sep="") , plot = opqr, width = 17, height = 10)}
# Also export counts for T-cells and myeloid cells to make a "before-after" plot 
list.sum[[i]] <- tt2[which(tt2$Var1=="MFs.monocytes" | tt2$Var1=="T-cells" | tt2$Var1=="DCs" | tt2$Var1=="Neutrophils"),]
names(list.sum)[i] <- patients[i]
}
```