---
title: "NI01 Non Immune Subsetting and General Annotation"
output: html_notebook
---

Libraries
```{r}
library(Seurat)
library(devtools)
library(clustree)
library(tidyverse)
library(gridExtra)
library(ggridges)
library(ggplot2)
require(corrplot)
```

Clear environment and load filtered Seurat object 
```{r}
# rm(list=ls())
dir <- "/myVolume/scell_lung_adenocarcinoma/"
load(file=paste(dir,"Data_input/S03_Nonimmune_Seurat_object.RData", sep=""))
```

Normalize and scale the data
```{r}
tiss_nonimmune <- NormalizeData(object = tiss_nonimmune, scale.factor = 1e6)
tiss_nonimmune <- ScaleData(object = tiss_nonimmune)
```

Find variable genes
```{r}
tiss_nonimmune <- FindVariableGenes(object = tiss_nonimmune, do.plot = TRUE, x.high.cutoff = Inf, y.cutoff = 0.5)
```

Perform PCA
```{r}
tiss_nonimmune <- RunPCA(object = tiss_nonimmune, do.print = FALSE)
tiss_nonimmune <- ProjectPCA(object = tiss_nonimmune, do.print = FALSE)
```

Visualize top genes in principal components
```{r}
PCHeatmap(object = tiss_nonimmune, pc.use = 1:15, cells.use = 100, do.balanced = TRUE, label.columns = FALSE, num.genes = 10)
```

Perform correlation of PCs and metadata fields
```{r}
pca.obj <- tiss_nonimmune@dr$pca
pc.coords <- pca.obj@cell.embeddings
df1 <- tiss_nonimmune@meta.data[,c("nGene","nReads","percent.ribo")]
df2 <- pc.coords[,c(1:10)]
cordf12 <- cor(df1,df2)
# Make a correlation plot
corrplot(cordf12, method = "number", main="Correlation of PCs and metadata")
```

Also visaulize PC variance
```{r}
#comp.dev <-pca.obj@sdev
PCElbowPlot(object = tiss_nonimmune)
```

Choose the number of principal components to use.

```{r}
n.pcs = 20
```

Check clustering stability at given resolution 
```{r}
# Set different resolutions 
res.used <- seq(0.1,1,by=0.2)
# Loop over and perform clustering of different resolutions 
for(i in res.used){
        tiss_nonimmune <- FindClusters(object = tiss_nonimmune, reduction.type = "pca", dims.use = 1:n.pcs, 
        resolution = i, print.output = 0, save.SNN = TRUE, k.param = 30, force.recalc = T)
        }
# Make plot 
clus.tree.out <- clustree(tiss_nonimmune) +
    theme(legend.position = "bottom") + 
    scale_color_brewer(palette = "Set1") +
    scale_edge_color_continuous(low = "grey80", high = "red")
# Save pdf 
ggsave(clus.tree.out, filename = paste(dir,"plot_out/NI01/Cluster_resolutions_clustree_output.pdf", sep=""), width = 15, height = 15)
# Plot 
clus.tree.out
```

Set resolution and perform clustering
```{r}
res.used <- 1
tiss_nonimmune <- FindClusters(object = tiss_nonimmune, reduction.type = "pca", dims.use = 1:n.pcs, 
    resolution = res.used, print.output = 0, save.SNN = TRUE, k.param = 30, force.recalc = T)
```

Perform  tSNE
```{r}
tiss_nonimmune <- RunTSNE(object = tiss_nonimmune, dims.use = 1:n.pcs, seed.use = 10, perplexity=30)
```

Visualize TSNE colored by cluster
```{r}
pdf(paste(dir,"plot_out/NI01/nonimmune_all_tSNE.pdf", sep=""),10,10)
TSNEPlot(object = tiss_nonimmune, do.label = T)
dev.off()
```

Plot genes of interest 
```{r}
# Specify genes  
genes_to_check = c("PMEL", "MLANA","PECAM1", "CD34", "VWF", "EPCAM","SFN", "KRT19",
                   "ACTA2", "MCAM", "MYLK", "MYL9", "FAP", "THY1", "ALB")
# All on Dotplot 
pdf(paste(dir,"plot_out/NI01/nonimmune_dotplot_of_gene_markers.pdf", sep=""),10,10)
DotPlot(tiss_nonimmune, genes_to_check, x.lab.rot = T)
dev.off()
```

Annotate General Non-Immune Clusters
```{r}
#add column 'main_seurat_cluster' to store cluster ids from this step. Change the column of the resolution if you ended up using a different one than 1
tiss_nonimmune@meta.data$nonimmune_seurat_cluster <- tiss_nonimmune@meta.data$res.1

# set the cluster ids
cluster.ids <- sort(unique(as.numeric(tiss_nonimmune@meta.data$nonimmune_seurat_cluster)))
# Manually check and ananotate each cluster to immmune and non-immune   
nonimmune_general_annotation <- c("Epithelial","Fibroblast", "Fibroblast", "Epithelial", "Endothelial", "Fibroblast", "Epithelial", "Epithelial", "Epithelial", "Epithelial", "Epithelial", "Fibroblast", "Epithelial", "Unknown", "Epithelial", "Epithelial", "Melanocytes", "Endothelial", "Fibroblast", "Epithelial", "Fibroblast", "Fibroblast","Epithelial", "Hepatocyte", "Epithelial", "Epithelial")
# Add annotation to the Seurat objedct 
tiss_nonimmune@meta.data[,'nonimmune_general_annotation'] <- plyr::mapvalues(x = tiss_nonimmune@ident, from = cluster.ids, to = nonimmune_general_annotation)
# MAke a table 
table(tiss_nonimmune@meta.data$nonimmune_general_annotation)
```

Save Processed Subset Seurat Object
```{r}
save(tiss_nonimmune, file=paste(dir,"Data_input/NI01_Nonimmune_Seurat_object_annotated.RData", sep=""))
```

Save annotatoins to main seurat object
```{r}
load(file=paste(dir,"Data_input/NI01_Nonimmune_Seurat_object_annotated.RData", sep=""))
load(file=paste(dir,"Data_input/S03_Main_Seurat_object_filtered_and_subset.RData", sep=""))
colnames(tiss_nonimmune@meta.data)
colnames(tiss_subset@meta.data)

tiss_subset@meta.data <- left_join(tiss_subset@meta.data, tiss_nonimmune@meta.data[,c(6,60)], by = 'cell_id')
table(tiss_subset@meta.data$nonimmune_general_annotation)
tiss_subset@meta.data$general_annotation <- tiss_subset@meta.data$nonimmune_general_annotation
tiss_subset@meta.data$general_annotation[is.na(tiss_subset@meta.data$general_annotation)] <- "immune"
table(tiss_subset@meta.data$general_annotation)
# replace Endo/Fibro/Hepta/Melano/Ukn without "stroma"
tiss_subset@meta.data$general_annotation <- gsub(pattern = "Endothelial", replacement = "Stroma", x = tiss_subset@meta.data$general_annotation)
tiss_subset@meta.data$general_annotation <- gsub(pattern = "Fibroblast", replacement = "Stroma", x = tiss_subset@meta.data$general_annotation)
tiss_subset@meta.data$general_annotation <- gsub(pattern = "Hepatocyte", replacement = "Stroma", x = tiss_subset@meta.data$general_annotation)
tiss_subset@meta.data$general_annotation <- gsub(pattern = "Melanocytes", replacement = "Stroma", x = tiss_subset@meta.data$general_annotation)
tiss_subset@meta.data$general_annotation <- gsub(pattern = "Unknown", replacement = "Stroma", x = tiss_subset@meta.data$general_annotation)
rownames(tiss_subset@meta.data) <- tiss_subset@meta.data$cell_id
save(tiss_subset, file = paste(dir,"Data_input/S03_Main_Seurat_object_filtered_and_subset_annotated.RData", sep=""))

pdf(file = paste(dir, "plot_out/NI01/NI01_main_tSNE_with_anno.pdf", sep = ""), width = 7, height = 5)
TSNEPlot(tiss_subset, group.by = 'general_annotation', do.label = FALSE, pt.size = 0.5, colors.use = c("orchid3", "palegreen4","sandybrown"))
dev.off()
```
