---
title: "NI01 Non Immune Subsetting and General Annotation"
output: html_notebook
---

Libraries
```{r}
library(Seurat)
library(devtools)
library(clustree)
library(tidyverse)
library(gridExtra)
library(ggridges)
library(ggplot2)
require(corrplot)
library(scales)
```

Clear environment and load filtered Seurat object 
```{r}
rm(list=ls())
# dir <- "/myVolume/scell_lung_adenocarcinoma/"
dir <- "/home/ubuntu/scell_lung_adenocarcinoma/"
load(file=paste(dir,"Data_input/objects/S03_Nonimmune_Seurat_object.RData", sep=""))
```

Normalize and scale the data
```{r}
tiss_nonimmune <- NormalizeData(object = tiss_nonimmune)
```

Find variable genes
```{r}
tiss_nonimmune <- FindVariableFeatures(object = tiss_nonimmune)
```

Scale data
```{r}
tiss_nonimmune <- ScaleData(object = tiss_nonimmune)
```

Perform PCA
```{r}
tiss_nonimmune <- RunPCA(object = tiss_nonimmune, do.print = FALSE)
```

Visualize first two PCs
```{r}
pdf(paste(dir,file = "plot_out/NI01/pca_by_tisssubsetclus.pdf", sep = ""))
DimPlot(tiss_nonimmune, reduction = 'pca')
dev.off()
```

Visualize top genes in principal components
```{r}
DimHeatmap(tiss_nonimmune, dims = 1:10, cells = 100, balanced = TRUE)
```

Perform correlation of PCs and metadata fields
```{r}
pca.obj <- tiss_nonimmune@reductions$pca
pc.coords <- pca.obj@cell.embeddings
df1 <- tiss_nonimmune@meta.data[,c("nFeature_RNA","nCount_RNA","percent.ribo")]
df2 <- pc.coords[,c(1:10)]
cordf12 <- cor(df1,df2)
# Make a correlation plot
corrplot(cordf12, method = "number", main="Correlation of PCs and metadata")
```

Also visaulize PC variance
```{r}
ElbowPlot(object = tiss_nonimmune)
```

Choose the number of principal components to use.

```{r}
n.pcs = 20
```

Construct Neighbor graph 
```{r}
tiss_nonimmune <- FindNeighbors(object = tiss_nonimmune, dims = 1:20, verbose = T)
```

Check clustering stability at given resolution 
```{r}
# Set different resolutions 
res.used <- seq(0.1,1,by=0.2)
# Loop over and perform clustering of different resolutions 
for(i in res.used){
        tiss_nonimmune <- FindClusters(object = tiss_nonimmune, verbose = T, resolution = res.used)
        }
# Make plot 
clus.tree.out <- clustree(tiss_nonimmune) +
    theme(legend.position = "bottom") + 
    scale_color_brewer(palette = "Set1") +
    scale_edge_color_continuous(low = "grey80", high = "red")
# Save pdf 
ggsave(clus.tree.out, filename = paste(dir,"plot_out/NI01/Cluster_resolutions_clustree_output.pdf", sep=""), width = 15, height = 15)
# Plot 
clus.tree.out
```

Set resolution and perform clustering
```{r}
res.used <- 1
tiss_nonimmune <- FindClusters(object = tiss_nonimmune, verbose = T, resolution = res.used)
```

Perform  tSNE
```{r}
tiss_nonimmune <- RunTSNE(tiss_nonimmune, dims = 1:20)
DimPlot(tiss_nonimmune, reduction = "tsne", label = TRUE)
```

Visualize TSNE colored by cluster
```{r}
pdf(paste(dir,"plot_out/NI01/nonimmune_all_tSNE.pdf", sep=""),10,10)
DimPlot(tiss_nonimmune, reduction = "tsne", label = TRUE)
dev.off()
```

Plot genes of interest and save 
```{r}
# Specify genes  
genes_to_check = c("PMEL", "MLANA","PECAM1", "CD34", "VWF", "EPCAM","SFN", "KRT19",
                   "ACTA2", "MCAM", "MYLK", "MYL9", "FAP", "THY1", "ALB")
# All on Dotplot 
p <- DotPlot(tiss_nonimmune, features = genes_to_check) + coord_flip()
ggsave(paste(dir,"plot_out/NI01/nonimmune_dotplot_of_gene_markers.pdf", sep=""), p, width = 10, height = 10)
p

```

Annotate General Non-Immune Clusters
```{r}
#add column 'nonimmune_seurat_cluster' to store cluster ids from this step. 
tiss_nonimmune@meta.data$nonimmune_seurat_cluster <- tiss_nonimmune@meta.data$seurat_clusters

# set the cluster ids
cluster.ids <- sort(unique(tiss_nonimmune@meta.data$seurat_clusters))
# Manually check and ananotate each cluster to immmune and non-immune   
nonimmune_general_annotation <- c("fibroblast","epithelial", "endothelial", "epithelial", "epithelial", "fibroblast", 
                                  "epithelial", "fibroblast", "epithelial", "epithelial", "fibroblast", 
                                  "epithelial", "epithelial", "epithelial", "epithelial", "fibroblast", 
                                  "endothelial", "epithelial", "fibroblast", "epithelial", "epithelial", 
                                  "melanocytes", "endothelial", "hepatocyte", "epithelial", "epithelial",
                                  "hepatocyte")
# Add annotation to the Seurat object
tiss_nonimmune@meta.data[,'nonimmune_general_annotation'] <- plyr::mapvalues(x = tiss_nonimmune@meta.data$seurat_clusters, from = cluster.ids, to = nonimmune_general_annotation)
# Make a table 
table(tiss_nonimmune@meta.data$nonimmune_general_annotation)
table(tiss_nonimmune@meta.data$nonimmune_general_annotation, tiss_nonimmune@meta.data$seurat_clusters)
```

Visualize TSNE colored by cluster
```{r}
pdf(paste(dir,"plot_out/NI01/nonimmune_tSNE_non_immuneanno.pdf", sep=""),10,10)
DimPlot(tiss_nonimmune, reduction = "tsne", group.by = "nonimmune_general_annotation")
dev.off()
```

Save Processed Subset Seurat Object
```{r}
save(tiss_nonimmune, file=paste(dir,"Data_input/objects/NI01_Nonimmune_Seurat_object_annotated.RData", sep=""))
```

Load objects to add metadata and cells
```{r}
# load(file=paste(dir,"Data_input/objects/NI01_Nonimmune_Seurat_object_annotated.RData", sep=""))
load(file=paste(dir,"Data_input/objects/S03_Main_Seurat_object_filtered_and_subset.RData", sep=""))
```

Save annotations to tiss_subset
```{r}
# colnames(tiss_nonimmune@meta.data)
tiss_subset@meta.data <- left_join(tiss_subset@meta.data, tiss_nonimmune@meta.data[,c("cell_id","nonimmune_general_annotation")], by = 'cell_id')
table(tiss_subset@meta.data$nonimmune_general_annotation)

tiss_subset@meta.data$general_annotation <- tiss_subset@meta.data$nonimmune_general_annotation

tiss_subset@meta.data$general_annotation <- as.character(tiss_subset@meta.data$general_annotation)
table(is.na(tiss_subset@meta.data$general_annotation)) # look for NAs

tiss_subset@meta.data$general_annotation[is.na(tiss_subset@meta.data$general_annotation)] <- "immune" #replace NAs with immune
table(tiss_subset@meta.data$general_annotation)
```


Color tSNE by general annotation (Epi/Immune/Stroma)
```{r}
tiss_subset@meta.data$general_annotation1 <- tiss_subset@meta.data$general_annotation
# replace endo/fibro/hepta/melano without "stroma"
tiss_subset@meta.data$general_annotation <- gsub(pattern = "endothelial", replacement = "stroma", x = tiss_subset@meta.data$general_annotation)
tiss_subset@meta.data$general_annotation <- gsub(pattern = "fibroblast", replacement = "stroma", x = tiss_subset@meta.data$general_annotation)
tiss_subset@meta.data$general_annotation <- gsub(pattern = "hepatocyte", replacement = "stroma", x = tiss_subset@meta.data$general_annotation)
tiss_subset@meta.data$general_annotation <- gsub(pattern = "melanocytes", replacement = "stroma", x = tiss_subset@meta.data$general_annotation)
rownames(tiss_subset@meta.data) <- tiss_subset@meta.data$cell_id  # reassign rownames
table(tiss_subset@meta.data$general_annotation) #check
# save
save(tiss_subset, file = paste(dir,"Data_input/objects/S03_Main_Seurat_object_filtered_and_subset_annotated.RData", sep=""))
```

Plot general annotation on tSNE
```{r}

# my_color_palette <- hue_pal()(length(unique(tiss_subset@meta.data$general_annotation)))
my_color_palette <- c("#CC3399", "#009966", "#FF9933")
pdf(file = paste(dir, "plot_out/NI01/NI01_main_tSNE_with_anno.pdf", sep = ""), width = 7, height = 5)
TSNEPlot(tiss_subset, group.by = 'general_annotation', do.label = FALSE, pt.size = 0.5) + scale_color_manual(values = my_color_palette)
dev.off()
```
