---
title: "NI02 Subset Epithelial Cells and Cluster"
output: html_notebook
---

```{r}
library(Seurat)
library(tidyverse)
require(ape)
require(corrplot)
library(clustree)
library(ggplot2)
library(ggridges)
library(ggsignif)
```

Clear environment and load filtered Seurat object 
```{r}
# rm(list=ls())
dir <- "/myVolume/scell_lung_adenocarcinoma/"
load(file=paste(dir,"Data_input/objects/NI01_Nonimmune_Seurat_object_annotated.RData", sep=""))
```

Subset Seurat object to Only Epithelial Cells
```{r}
Epi_cells <- filter(tiss_nonimmune@meta.data, nonimmune_general_annotation == "Epithelial")
cells.use <- Epi_cells$cell_id
length(cells.use)
tiss_nonimmune_epi <- SubsetData(tiss_nonimmune, cells.use = cells.use)
```

Find variable genes
```{r}
tiss_nonimmune_epi <- FindVariableGenes(object = tiss_nonimmune_epi, do.plot = TRUE, x.high.cutoff = Inf, y.cutoff = 0.5)
```

Perform PCA
```{r}
tiss_nonimmune_epi <- RunPCA(object = tiss_nonimmune_epi, do.print = FALSE)
tiss_nonimmune_epi <- ProjectPCA(object = tiss_nonimmune_epi, do.print = FALSE)
```

Visualize top genes in principal components
```{r}
PCHeatmap(object = tiss_nonimmune_epi, pc.use = 1:6, cells.use = 100, do.balanced = TRUE, label.columns = FALSE, num.genes = 10)
```

Perform correlation of PCs and metadata fields
```{r}
head(tiss_nonimmune_epi@meta.data)
pca.obj <- tiss_nonimmune_epi@dr$pca
pc.coords <- pca.obj@cell.embeddings
df1 <- tiss_nonimmune_epi@meta.data[,c("nGene","nReads","percent.ribo")]
df2 <- pc.coords[,c(1:10)]
cordf12 <- cor(df1,df2)
# Make a correlation plot
corrplot(cordf12, method = "number", main="Correlation of PCs and metadata")
```
Also visaulize PC variance
```{r}
PCElbowPlot(object = tiss_nonimmune_epi)
```

Choose the number of principal components to use.
```{r}
n.pcs = 20
```

Check clustering stability at given resolution (Clustree)
```{r}
# Set different resolutions 
res.used <- seq(0.1,1,by=0.2)
# Loop over and perform clustering of different resolutions 
for(i in res.used){
        tiss_nonimmune_epi <- FindClusters(object = tiss_nonimmune_epi, reduction.type = "pca", dims.use = 1:n.pcs, 
        resolution = i, print.output = 0, save.SNN = TRUE, k.param = 10, force.recalc = T)
        }
# Make plot 
clus.tree.out <- clustree(tiss_nonimmune_epi) +
    theme(legend.position = "bottom") + 
    scale_color_brewer(palette = "Set1") +
    scale_edge_color_continuous(low = "grey80", high = "red")
# Save pdf 
ggsave(clus.tree.out, filename = paste(dir,"plot_out/NI02/Cluster_resolutions_clustree_output.pdf", sep=""), width = 15, height = 15)
# Plot 
clus.tree.out
```

Set resolution and perform clustering
```{r}
res.used <- .9
tiss_nonimmune_epi <- FindClusters(object = tiss_nonimmune_epi, reduction.type = "pca", dims.use = 1:n.pcs, resolution = res.used, print.output = 0, save.SNN = TRUE, k.param = 10, force.recalc = T)
```

Perform  tSNE
```{r}
tiss_nonimmune_epi <- RunTSNE(object = tiss_nonimmune_epi, dims.use = 1:n.pcs, seed.use = 10, perplexity=30)
```

Visualize TSNE colroed by cluster
```{r}
pdf(paste(dir,"plot_out/NI02/epi_all_tSNE.pdf", sep=""),10,10)
TSNEPlot(object = tiss_nonimmune_epi, do.label = T)
dev.off()
```

Set Metadata Column for Cluster IDs
```{r}
tiss_nonimmune_epi@meta.data$epi_seurat_cluster <- tiss_nonimmune_epi@meta.data$res.0.9
```


```{r}
save(tiss_nonimmune_epi, file= paste(dir,"/Data_input/objects/NI02_Epi_Seurat_object_clustered.RData", sep=""))
```


