---
title: "NI02 Subset Epithelial Cells and Cluster"
output: html_notebook
---

```{r}
library(Seurat)
library(tidyverse)
require(ape)
require(corrplot)
library(clustree)
library(ggplot2)
library(ggridges)
```

Clear environment and load filtered Seurat object 
```{r}
rm(list=ls())
# dir <- "/myVolume/scell_lung_adenocarcinoma/"
dir <- "/home/ubuntu/scell_lung_adenocarcinoma/"
load(file=paste(dir,"Data_input/objects/NI01_Nonimmune_Seurat_object_annotated.RData", sep=""))
```

Subset Seurat object to Only Epithelial Cells
```{r}
Epi_cells <- filter(tiss_nonimmune@meta.data, nonimmune_general_annotation == "epithelial")
cells.use <- Epi_cells$cell_id
length(cells.use)
tiss_nonimmune_epi <- subset(tiss_nonimmune, cells = cells.use)
```

Normalize data
```{r}
tiss_nonimmune_epi <- NormalizeData(object = tiss_nonimmune_epi)
```

Find variable genes
```{r}
tiss_nonimmune_epi <- FindVariableFeatures(object = tiss_nonimmune_epi)
```

Scale data
```{r}
tiss_nonimmune_epi <- ScaleData(object = tiss_nonimmune_epi)
```

Perform PCA
```{r}
tiss_nonimmune_epi <- RunPCA(object = tiss_nonimmune_epi)
```

PCA plot of 1st two PCs
```{r}
DimPlot(tiss_nonimmune_epi, reduction = 'pca')
```

Visualize top genes in principal components
```{r}
DimHeatmap(tiss_nonimmune_epi, dims = 1:10, cells = 100, balanced = TRUE)
```

Perform correlation of PCs and metadata fields
```{r}
pca.obj <- tiss_nonimmune_epi@reductions$pca
pc.coords <- pca.obj@cell.embeddings
df1 <- tiss_nonimmune_epi@meta.data[,c("nFeature_RNA","nCount_RNA","percent.ribo")]
df2 <- pc.coords[,c(1:10)]
cordf12 <- cor(df1,df2)
# Make a correlation plot
corrplot(cordf12, method = "number", main="Correlation of PCs and metadata")
```

Also visaulize PC variance
```{r}
ElbowPlot(object = tiss_nonimmune_epi, ndims = 40)
```

Choose the number of principal components to use.
```{r}
n.pcs = 30
```

Find Neighbors
```{r}
tiss_nonimmune_epi <- FindNeighbors(object = tiss_nonimmune_epi, dims = 1:n.pcs, verbose = T)
```

Check clustering stability at given resolution (Clustree)
```{r}
# Set different resolutions 
res.used <- seq(0.1,1,by=0.2)
# Loop over and perform clustering of different resolutions 
for(i in res.used){
        tiss_nonimmune_epi <- FindClusters(object = tiss_nonimmune_epi, verbose = T, resolution = res.used)}
# Make plot 
clus.tree.out <- clustree(tiss_nonimmune_epi) +
    theme(legend.position = "bottom") + 
    scale_color_brewer(palette = "Set1") +
    scale_edge_color_continuous(low = "grey80", high = "red")
# Save pdf 
ggsave(clus.tree.out, filename = paste(dir,"plot_out/NI02/Cluster_resolutions_clustree_output.pdf", sep=""), width = 15, height = 15)
# Plot 
clus.tree.out
```

Set resolution and perform clustering
```{r}
res.used <- .7
tiss_nonimmune_epi <- FindClusters(object = tiss_nonimmune_epi, verbose = T, resolution = res.used)
```

Perform  tSNE
```{r}
tiss_nonimmune_epi <- RunTSNE(object = tiss_nonimmune_epi, dims.use = 1:n.pcs, seed.use = 10)
```

Visualize TSNE colroed by cluster
```{r}
pdf(paste(dir,"plot_out/NI02/epi_all_tSNE.pdf", sep=""),10,10)
DimPlot(tiss_nonimmune_epi, reduction = "tsne", label = FALSE, group.by = "seurat_clusters")
dev.off()
```

Set Metadata Column for Cluster IDs
```{r}
tiss_nonimmune_epi@meta.data$epi_seurat_cluster <- tiss_nonimmune_epi@meta.data$seurat_clusters
```


```{r}
save(tiss_nonimmune_epi, file= paste(dir,"/Data_input/objects/NI02_Epi_Seurat_object_clustered.RData", sep=""))
```


