---
title: "NI03 InferCNV Analysis"
output: html_document
---

Install inferCNV. Instructions at https://github.com/broadinstitute/inferCNV/wiki/Installing_inferCNV and load packages
```{r}
# install GMD
# packageurl <- "https://cran.r-project.org/src/contrib/Archive/GMD/GMD_0.3.3.tar.gz"
# install.packages(packageurl, repos=NULL, type="source")

# NGHCM
# devtools::install_github("bmbroom/tsvio")
# devtools::install_github("bmbroom/NGCHMR", ref="stable")

# Install inferCNV from within R using devtools
library(devtools)
# install_github("broadinstitute/inferCNV")
# install.packages("phylogram")
library(phylogram)
library(gridExtra)
library(grid)
require(dendextend)
require(ggthemes)
library(tidyverse)
library(Seurat)
```

```{r}
# rm(list=ls())
dir <- "/myVolume/scell_lung_adenocarcinoma/"
load(file=paste(dir,"Data_input/NI02_Epi_Seurat_object_annotated.RData", sep=""))
load(file=paste(dir,"Data_input/NI01_Nonimmune_Seurat_object_annotated.RData", sep=""))
```

Create and save a Raw Counts Table
```{r}
temp <- as.matrix(tiss_nonimmune@raw.data)
write.table(x = temp, file =  paste(dir, "Data_input/NI03_CNV_data_out_all_cells_raw_counts_largefile.txt", sep = ""), quote = F,sep = '\t')
rm(temp)
```


Create slim cell annotation file (malignant vs non-malignant) from Seurat object 
```{r}
# Epithelial cells 
temp.1 <- tiss_nonimmune_epi@meta.data[tiss_nonimmune_epi@meta.data$nonimmune_general_annotation %in% "Epithelial", c("nonimmune_general_annotation","epi_seurat_cluster")] 
temp.1 <- cbind(as.data.frame(row.names(temp.1)), as.data.frame(do.call("paste",temp.1)))
colnames(temp.1) <- c("V1","V2")
# Endothelial cells and fibroblasts
temp.2 <- tiss_nonimmune@meta.data[tiss_nonimmune@meta.data$nonimmune_general_annotation %in% "Endothelial", c("cell_id","nonimmune_general_annotation")]
colnames(temp.2) <- c("V1","V2")
temp.3 <- tiss_nonimmune@meta.data[tiss_nonimmune@meta.data$nonimmune_general_annotation %in% "Fibroblast", c("cell_id","nonimmune_general_annotation")]
colnames(temp.3) <- c("V1","V2")
# Keep a total of 500 cells from both 
temp.2 <- temp.2[sample(nrow(temp.2), size = 800),]
temp.3<- temp.3[sample(nrow(temp.3), size = 800),]

# Convert some of the fibroblasts and endos to spikeins for the clustering 
temp.2$V2 <- paste(as.character(temp.2$V2), "_normal", sep="")
temp.2$V2[sample(which(temp.2$V2=="Endothelial_normal"),300)] <- "Endothelial"
temp.3$V2 <- paste(as.character(temp.3$V2), "_normal", sep="")
temp.3$V2[sample(which(temp.3$V2=="Fibroblast_normal"),300)] <- "Fibroblast"
# Combine 
inferCNV.annotation <- rbind(temp.1, temp.2, temp.3)
rm("temp.1", "temp.2", "temp.3")
# Write table
write.table(inferCNV.annotation, file = paste(dir,"Data_input/NI03_CNV_cell_metadata_shuffle_largefile.txt", sep=""),row.names = F, col.names = F, quote=F, sep="\t")
```

Import gene location table 
```{r}
inferCNV.genes <- read.table(file = paste(dir,"Data_input/NI03_CNV_hg19_genes_ordered_correct_noXY.txt", sep = ""))
head(inferCNV.genes)
```

Create the infercnv object
```{r}
infercnv_obj = infercnv::CreateInfercnvObject(raw_counts_matrix = paste(dir, "Data_input/NI03_CNV_data_out_all_cells_raw_counts_largefile.txt", sep = ""), annotations_file = paste(dir, "Data_input/NI03_CNV_cell_metadata_shuffle_largefile.txt", sep = ""), delim="\t", gene_order_file = paste(dir, "Data_input/NI03_CNV_hg19_genes_ordered_correct_noXY.txt", sep = ""), ref_group_names = c("Endothelial_normal", "Fibroblast_normal"))
```

Save infercnv Object
```{r}
save(infercnv_obj, file = paste(dir, "Data_input/NI03_infercnv_obj.RData", sep = ""))
```

Perform infercnv operations to reveal cnv signal
```{r}
# Make sure that chrmosomes are ordered correctly 
slot(infercnv_obj, "gene_order")[,"chr"] <- factor(slot(infercnv_obj, "gene_order")[,"chr"], levels = c("chr1", "chr2","chr3","chr4", "chr5", "chr6","chr7", "chr8", "chr9","chr10", "chr11", "chr12","chr13", "chr14", "chr15","chr16", "chr17", "chr18","chr19", "chr20", "chr21","chr22"))
# Run infer CNV
infercnv_all = infercnv::run(infercnv_obj,
                             cutoff=1,  # use 1 for smart-seq, 0.1 for 10x-genomics
                             out_dir="/myVolume/scell_lung_adenocarcinoma/plot_out/NI03/",  # dir is auto-created for storing outputs
                             cluster_by_groups=F,   # cluster
                             include.spike=T, hclust_method="ward.D2", plot_steps=F)
```

Parse inferCNV dendrograms. For that we will be using the inferCNV calculated on all cells and not by group 
```{r}
#  Import inferCNV dendrogram
infercnv.dend <- read.dendrogram(file = paste(dir, "plot_out/NI03/infercnv.observations_dendrogram.txt", sep = ""))

# Cut tree 
infercnv.labels <- cutree(infercnv.dend, k = 3, order_clusters_as_data = FALSE)
# infercnv.labels <- cutree(infercnv.dend,h = 500, order_clusters_as_data = FALSE)
# Color labels
the_bars <- as.data.frame(tableau_color_pal("Tableau 20")(20)[infercnv.labels])
colnames(the_bars) <- "inferCNV_tree"
the_bars$inferCNV_tree <- as.character(the_bars$inferCNV_tree)
# PLot tree
pdf(file = paste(dir, "/plot_out/NI03/NI03_inferCNV_dendrogram_cut.pdf", sep = ""))
infercnv.dend %>% set("labels",rep("", nobs(infercnv.dend)) )  %>% plot(main="inferCNV dendrogram") %>%
colored_bars(colors = as.data.frame(the_bars), dend = infercnv.dend, sort_by_labels_order = FALSE, add = T, y_scale=1000, y_shift = 0)
dev.off()
```

Add CNV dendrogram clusters labels to annoation
```{r}
# Add labels
inferCNV.annotation$inferCNV.class <- NA
for(i in 1:length(infercnv.labels)){
  inferCNV.annotation[inferCNV.annotation$V1 %in%  names(infercnv.labels)[i],"inferCNV.class"] <- infercnv.labels[i]
}
# Remove normal cells 
inferCNV.annotation.malignant <- inferCNV.annotation[-grep("normal", inferCNV.annotation$V2),] 

table(inferCNV.annotation.malignant$V2, inferCNV.annotation.malignant$inferCNV.class)
```

Classify each cell as tumor or nontumor based on CNV dendrogram cluster
```{r}
#replace inferCNV.class 1 as "tumor"
inferCNV.annotation.malignant$inferCNV.class <- gsub(pattern = 1, replacement = "tumor", x = inferCNV.annotation.malignant$inferCNV.class)
#replace inferCNV.class 2 as "nontumor"
inferCNV.annotation.malignant$inferCNV.class <- gsub(pattern = 2, replacement = "nontumor", x = inferCNV.annotation.malignant$inferCNV.class)
#replace inferCNV.class 3 as "tumor"
inferCNV.annotation.malignant$inferCNV.class <- gsub(pattern = 3, replacement = "tumor", x = inferCNV.annotation.malignant$inferCNV.class)
#update colnames of inferCNV.annotation.malignant 
colnames(inferCNV.annotation.malignant) <- c("cell_id", "Epithelial_cluster", "inferCNV_annotation")
table(inferCNV.annotation.malignant$inferCNV_annotation)
# Write updated cell annotation 
write.table(inferCNV.annotation.malignant, paste(dir, "/data_out/NI03/NI03_inferCNV_final_annotation_per_cell.txt", sep = ""), row.names = F, quote = F)
```

Update Seurat objects with tumor annotations
```{r}
# Add metadata inferCNV_annotation by cell_id
tiss_nonimmune_epi@meta.data <- left_join(x = tiss_nonimmune_epi@meta.data, y = inferCNV.annotation.malignant[,c(1,3)], by = "cell_id")
rownames(tiss_nonimmune_epi@meta.data) <- tiss_nonimmune_epi@meta.data$cell_id
#Save Seurat object 
save(tiss_nonimmune_epi, file = paste(dir, "Data_input/NI03_epithelial_annotated_tumor.RData", sep = ""))

tiss_nonimmune@meta.data <- left_join(x = tiss_nonimmune@meta.data, y = inferCNV.annotation.malignant[,c(1,3)], by = "cell_id")
rownames(tiss_nonimmune@meta.data) <- tiss_nonimmune@meta.data$cell_id
#Save Seurat object 
save(tiss_nonimmune, file = paste(dir, "Data_input/NI03_nonimmune_annotated_tumor.RData", sep = ""))
```




