---
title: "Cancer Cell Diff. Expression"
output: html_notebook
---

```{r}
library(ggsignif)
library(corrplot)
library(Seurat)
library(tidyverse)
library(ggplot2)
```

```{r}
dir <- "/myVolume/scell_lung_adenocarcinoma/"
load(file = paste(dir,"Data_input/NI03_epithelial_annotated_tumor.RData", sep=""))
```

Check nGenes and nReads for tumor vs nontumor
```{r}
x1 <- ggplot(data = tiss_nonimmune_epi@meta.data, aes(x = inferCNV_annotation, y = nGene)) + geom_boxplot() + geom_signif(comparisons = list(c("nontumor", "tumor")), map_signif_level=TRUE)
ggsave(plot = x1, paste(dir,"plot_out/NI04/tumor_nontumor_uniquegenes.pdf", sep=""), width = 90, height = 90, units = "mm")

x <- filter(tiss_nonimmune_epi@meta.data, inferCNV_annotation == 'tumor')
mean(x$nGene) # mean genes expressed by tumor 5576 1726195(nReads)
y <- filter(tiss_nonimmune_epi@meta.data, inferCNV_annotation == 'nontumor')
mean(y$nGene) # mean genes expressed by tumor 2588 1395728(nReads)

cor(x = tiss_nonimmune_epi@meta.data$nGene, y = tiss_nonimmune_epi@meta.data$nReads, method = "pearson")
cor(x = tiss_nonimmune_epi@meta.data$nGene, y = tiss_nonimmune_epi@meta.data$nReads, method = "spearman")
```

Subset tumor cells from epi_cells object
```{r}
cells.use <- row.names(tiss_nonimmune_epi@meta.data)[which(tiss_nonimmune_epi@meta.data$inferCNV_annotation=="tumor")]
length(cells.use)
tiss_subset_tumor2 <- SubsetData(tiss_nonimmune_epi, cells.use = cells.use)
```

Normalize and scale the data
```{r}
tiss_subset_tumor2 <- NormalizeData(object = tiss_subset_tumor2)
tiss_subset_tumor2 <- ScaleData(object = tiss_subset_tumor2)
```

Find variable genes
```{r}
tiss_subset_tumor2 <- FindVariableGenes(object = tiss_subset_tumor2, do.plot = TRUE, x.high.cutoff = Inf, y.cutoff = 0.5)
```

Perform PCA
```{r}
tiss_subset_tumor2 <- RunPCA(object = tiss_subset_tumor2, do.print = FALSE)
tiss_subset_tumor2 <- ProjectPCA(object = tiss_subset_tumor2, do.print = FALSE)
```

Visualize top genes in principal components
```{r}
PCHeatmap(object = tiss_subset_tumor2, pc.use = 1:6, cells.use = 100, do.balanced = TRUE, label.columns = FALSE, num.genes = 20)
```

Perform correlation of PCs and metadata fields
```{r}
pca.obj <- tiss_subset_tumor2@dr$pca
pc.coords <- pca.obj@cell.embeddings
df1 <- tiss_subset_tumor2@meta.data[,c("nGene","nReads","percent.ribo")]
df2 <- pc.coords[,c(1:10)]
cordf12 <- cor(df1,df2)
# Make a correlation plot
corrplot(cordf12, method = "number", main="Correlation of PCs and metadata")
```

Also visaulize PC variance
```{r}
PCElbowPlot(object = tiss_subset_tumor2)
```

Choose the number of principal components to use.
```{r}
n.pcs = 20
```

Check clustering stability at given resolution (Clustree)
```{r}
# Set different resolutions 
res.used <- seq(0.1,1,by=0.2)
# Loop over and perform clustering of different resolutions 
for(i in res.used){
tiss_subset_tumor2 <- FindClusters(object = tiss_subset_tumor2, reduction.type = "pca", dims.use = 1:n.pcs, 
    resolution = i, print.output = 0, save.SNN = TRUE, k.param = 10, force.recalc = T)}
# Make Plot
clus.tree.out <- clustree(tiss_subset_tumor2, layout="sugiyama") +
    theme(legend.position = "bottom") + 
  scale_color_brewer(palette = "Set1") +
    scale_edge_color_continuous(low = "grey80", high = "red")

clus.tree.out
```

Set resolution and perform clustering
```{r}
res.used <- 0.9
tiss_subset_tumor2 <- FindClusters(object = tiss_subset_tumor2, reduction.type = "pca", dims.use = 1:n.pcs, resolution = res.used, print.output = 0, save.SNN = TRUE, k.param = 10, force.recalc = T)
```

Perform  tSNE
```{r}
tiss_subset_tumor2 <- RunTSNE(object = tiss_subset_tumor2, dims.use = 1:n.pcs, seed.use = 10, perplexity=30)
```

Visualize TSNE colroed by cluster
```{r}
pdf(file = paste(dir, "plot_out/NI04/NI04_tumor_tsne.pdf", sep = ""))
TSNEPlot(object = tiss_subset_tumor2, do.label = T, group.by = "res.0.9")
TSNEPlot(object = tiss_subset_tumor2, do.label = F, group.by = "analysis")
dev.off()
```

Cluster Occ by patient
```{r}
# Calculate mixing score for each cluster 
tab.1 <- table(tiss_subset_tumor2@meta.data$patient_id, tiss_subset_tumor2@meta.data$res.0.9)
occ_score <- apply(tab.1, 2, max)/colSums(tab.1)
# Plot mixing score
pdf(file = paste(dir, "plot_out/NI04/NI04_tumor_clusocc_bargraph.pdf", sep = ""))
par(las=3);barplot(sort(occ_score), xlab="Cluster", ylab="Patient max Ncells/Total cells", ylim=c(0,1));abline(h=0.7, col="red")
dev.off()
```

```{r}
# set the ident of the object to the "analysis" column
unique(tiss_subset_tumor2@ident) # check current ident
tiss_subset_tumor2 <- SetIdent(tiss_subset_tumor2, ident.use = tiss_subset_tumor2@meta.data$analysis)
unique(tiss_subset_tumor2@ident) # check current ident
```

Calculate the pairwise comparisons between treatment groups of naive vs pr
```{r}
# calculate the pairwise comparision of naive vs pr
naive_v_pr <- FindMarkers(object = tiss_subset_tumor2, ident.1 = "naive", ident.2 = "grouped_pr")

# calculate the pairwise comparision of naive vs pd
naive_v_pd <- FindMarkers(object = tiss_subset_tumor2, ident.1 = "naive", ident.2 = "grouped_pd")

# calculate the pairwise comparision of pr vs pd
pr_v_pd <- FindMarkers(object = tiss_subset_tumor2, ident.1 = "grouped_pr", ident.2 = "grouped_pd")
```

To avoid patient specific effects, filter the DE list to exclude genes explained by a few patients
```{r}
# Group the DE genes and add the number of patients with nonzero expressing cells and the highest contributing patient's occupancy

# naive vs pr
naive_v_pr.1 <- naive_v_pr
groups <- c("naive", "grouped_pr")

for(i in 1:nrow(naive_v_pr.1)){
  # gene <- as.character(naive_v_pr.1$gene)[i]
  gene <- row.names(naive_v_pr.1)[i]
  gene.vec <- tiss_subset_tumor2@data[gene,]
    for(j in 1:length(groups)){
      cells <- row.names(tiss_subset_tumor2@meta.data)[which(tiss_subset_tumor2@meta.data$analysis==groups[j])]
      all.no.zero.cells <- names(which(gene.vec[cells] !=0 )) # Set threshold
      tab.1 <- table(as.character(tiss_subset_tumor2@meta.data[all.no.zero.cells,"patient_id"]))
      high.pat.per <- tab.1[which(tab.1==max(tab.1))[1]]/length(all.no.zero.cells)
      all.pat.length <- length(tab.1)
      naive_v_pr.1[i,paste(groups[j],"pt.occupancy")] <- high.pat.per
      naive_v_pr.1[i,paste(groups[j],"n.nonzero.pts")] <- all.pat.length
    }  
}

# naive vs pd
naive_v_pd.1 <- naive_v_pd
groups <- c("naive", "grouped_pd")

for(i in 1:nrow(naive_v_pd.1)){
  # gene <- as.character(naive_v_pd.1$gene)[i]
  gene <- row.names(naive_v_pd.1)[i]
  gene.vec <- tiss_subset_tumor2@data[gene,]
    for(j in 1:length(groups)){
      cells <- row.names(tiss_subset_tumor2@meta.data)[which(tiss_subset_tumor2@meta.data$analysis==groups[j])]
      all.no.zero.cells <- names(which(gene.vec[cells] !=0 )) # Set threshold
      tab.1 <- table(as.character(tiss_subset_tumor2@meta.data[all.no.zero.cells,"patient_id"]))
      high.pat.per <- tab.1[which(tab.1==max(tab.1))[1]]/length(all.no.zero.cells)
      all.pat.length <- length(tab.1)
      naive_v_pd.1[i,paste(groups[j],"pt.occupancy")] <- high.pat.per
      naive_v_pd.1[i,paste(groups[j],"n.nonzero.pts")] <- all.pat.length
    }  
}

# pr vs pd
pr_v_pd.1 <- pr_v_pd
groups <- c("grouped_pr", "grouped_pd")

for(i in 1:nrow(pr_v_pd.1)){
  # gene <- as.character(pr_v_pd.1$gene)[i]
  gene <- row.names(pr_v_pd.1)[i]
  gene.vec <- tiss_subset_tumor2@data[gene,]
    for(j in 1:length(groups)){
      cells <- row.names(tiss_subset_tumor2@meta.data)[which(tiss_subset_tumor2@meta.data$analysis==groups[j])]
      all.no.zero.cells <- names(which(gene.vec[cells] !=0 )) # Set threshold
      tab.1 <- table(as.character(tiss_subset_tumor2@meta.data[all.no.zero.cells,"patient_id"]))
      high.pat.per <- tab.1[which(tab.1==max(tab.1))[1]]/length(all.no.zero.cells)
      all.pat.length <- length(tab.1)
      pr_v_pd.1[i,paste(groups[j],"pt.occupancy")] <- high.pat.per
      pr_v_pd.1[i,paste(groups[j],"n.nonzero.pts")] <- all.pat.length
    }
}

# save all outputs
write.csv(naive_v_pr.1, file = paste(dir, "data_out/NI04/naive_v_pr1.csv", sep = ""))
write.csv(naive_v_pd.1, file = paste(dir, "data_out/NI04/naive_v_pd1.csv", sep = ""))
write.csv(pr_v_pd.1, file = paste(dir, "data_out/NI04/pr_v_pd.csv", sep = ""))
```

Naive vs PR plotting
```{r}
naive_v_pr.2 <- naive_v_pr.1
naive_v_pr.2$gene <- rownames(naive_v_pr.2)
naive_v_pr.2 <- filter(naive_v_pr.2, avg_logFC <= 0)
rownames(naive_v_pr.2) <- naive_v_pr.2$gene
# change avglogFC to positive number
naive_v_pr.2$avg_logFC <- naive_v_pr.2$avg_logFC * -1 # flip direction of axis (TN on left, PER on right)
hist(naive_v_pr.2$`naive n.nonzero.pts`) # set threshold for 3 or more patients
hist(naive_v_pr.2$`grouped_pr n.nonzero.pts`) # set threshold for 3 or more patients
naive_v_pr.2 <- filter(naive_v_pr.2, naive_v_pr.2$`grouped_pr n.nonzero.pts` > 3)
naive_v_pr.2 <- filter(naive_v_pr.2, naive_v_pr.2$`naive n.nonzero.pts` > 6)
rownames(naive_v_pr.2) <- naive_v_pr.2$gene
#Will have different colors depending on significance
mutateddf <- mutate(naive_v_pr.2, sig = ifelse(naive_v_pr.2$p_val_adj < 0.05, "p_val_adj<0.05", "NS")) 
rownames(mutateddf) <- mutateddf$gene
input_naive_pr <- mutateddf # input_naive_pr is sorted by pval_adjust
input_naive_pr.1 <- input_naive_pr[order(input_naive_pr$avg_logFC, decreasing = TRUE), ] # input_naive_pr.1 is sorted by avg_logFC

# save sorted gene lists
write.csv(x = input_naive_pr.1, file = paste(dir, "data_out/NI04/naive_v_pr1_filtered.csv", sep = ""))

# plot
volc = ggplot(input_naive_pr, aes(avg_logFC, -log10(p_val_adj))) + #volcanoplot with avg_logFC versus p_val_adj
    geom_point(aes(col=sig)) + #add points colored by significance
    scale_color_manual(values=c("black", "red")) + 
    ggtitle("Naive vs PR") 

naive_vs_pr_volc.1 <- volc + geom_text_repel(data=head(input_naive_pr.1, 20), aes(label=gene), point.padding = 1, box.padding = .3) +
  geom_text_repel(data=head(input_naive_pr, 20), aes(label=gene), point.padding = 1, box.padding = .3) +
  labs(y = expression(-log[10]*" "*"adjusted pvalue"), x = "avg log fold change") + 
  theme(legend.title = element_blank(), legend.position = "top") + 
  scale_fill_discrete(labels = c("Not Sig", "adjusted pval < 0.05"))
# save volcano plot
ggsave(naive_vs_pr_volc.1, filename = paste(dir,"plot_out/NI04/naive_vs_pr_volcanoplot.pdf", sep=""), width = 15, height = 15)
```


Naive vs PD plotting
```{r}
naive_v_pd.2 <- naive_v_pd.1
naive_v_pd.2$gene <- rownames(naive_v_pd.2)
naive_v_pd.2 <- filter(naive_v_pd.2, avg_logFC <= 0)
rownames(naive_v_pd.2) <- naive_v_pd.2$gene
# change avglogFC to positive number
naive_v_pd.2$avg_logFC <- naive_v_pd.2$avg_logFC * -1
# filter out any genes that are explained by less than 6 patients contributing
hist(naive_v_pd.2$`grouped_pd n.nonzero.pts`) # set threshold for 6 or more patients
hist(naive_v_pd.2$`naive n.nonzero.pts`) # set threshold for 6 or more patients
# filter for genes explained by few pateints
naive_v_pd.2 <- filter(naive_v_pd.2, naive_v_pd.2$`grouped_pd n.nonzero.pts` > 6)
naive_v_pd.2 <- filter(naive_v_pd.2, naive_v_pd.2$`naive n.nonzero.pts` > 6)
rownames(naive_v_pd.2) <- naive_v_pd.2$gene
#Will have different colors depending on significance
mutateddf <- mutate(naive_v_pd.2, sig = ifelse(naive_v_pd.2$p_val_adj < 0.05, "p_val_adj<0.05", "NS")) 
rownames(mutateddf) <- mutateddf$gene
input_naive_pd <- mutateddf # input_naive_pd is sorted by pval_adjust
input_naive_pd.1 <- input_naive_pd[order(input_naive_pd$avg_logFC, decreasing = TRUE), ] # sorted by avglogFC
# save sorted gene lists
write.csv(x = input_naive_pd.1, file = paste(dir, "data_out/NI04/naive_v_pd1_filtered.csv", sep = ""))

# create volcano plot
volc = ggplot(input_naive_pd, aes(avg_logFC, -log10(p_val_adj))) + #volcanoplot with avg_logFC versus p_val_adj
    geom_point(aes(col=sig)) + #add points colored by significance
    scale_color_manual(values=c("black", "red")) + 
    ggtitle("Naive vs PD") 

naive_vs_pd_volc.1 <- volc + geom_text_repel(data=head(input_naive_pd.1, 40), aes(label=gene), point.padding = 1, box.padding = .3) +
  geom_text_repel(data=head(input_naive_pd, 40), aes(label=gene), point.padding = 1, box.padding = .3)
  labs(y = expression(-log[10]*" "*"adjusted pvalue"), x = "avg log fold change") + 
  theme(legend.title = element_blank(), legend.position = "top") + 
  scale_fill_discrete(labels = c("Not Sig", "adjusted pval < 0.05"))
# save volcano plot
ggsave(naive_vs_pd_volc.1, filename = paste(dir,"plot_out/NI04/naive_vs_pd_volcanoplot.pdf", sep=""), width = 15, height = 15)
```

PER vs PD
```{r}
pr_v_pd.2 <- pr_v_pd.1
pr_v_pd.2$gene <- rownames(pr_v_pd.2)
#split the negative and positive avg_locFC
pr <- filter(pr_v_pd.2, avg_logFC > 0)
pd <- filter(pr_v_pd.2, avg_logFC < 0)
# add rownames back
rownames(pr) <- pr$gene
rownames(pd) <- pd$gene
# check the hist to set threshold for filtering out any genes that are explained by few number of patients
hist(pr$`grouped_pr n.nonzero.pts`) # threshold at > 3 patients
hist(pd$`grouped_pd n.nonzero.pts`) # threshold at > 6 patients
# set thresholds for 
pr <- filter(pr, pr$`grouped_pr n.nonzero.pts` > 3)
rownames(pr) <- pr$gene
pd <- filter(pd, pd$`grouped_pd n.nonzero.pts` > 6)
rownames(pd) <- pd$gene
# save pr and pd sorted by avglogFC
pr.1 <- pr[order(pr$avg_logFC, decreasing = TRUE), ]
pd.1 <- pd[order(pd$avg_logFC, decreasing = FALSE), ]
# rbind back together the pr and pd
pr_v_pd.3 <- rbind(pr, pd)
#Will have different colors depending on significance
mutateddf <- mutate(pr_v_pd.3, sig = ifelse(pr_v_pd.3$p_val_adj < 0.05, "p_val_adj<0.05", "NS")) 
rownames(mutateddf) <- mutateddf$gene
input_pr_pd <- mutateddf # input_pr_pd is sorted by pval_adjust
input_pr_pd.1 <- input_pr_pd[order(input_pr_pd$avg_logFC, decreasing = TRUE), ] # sorted by avglogFC
# save sorted gene lists
write.csv(x = input_pr_pd.1, file = paste(dir, "data_out/NI04/pr_v_pd1_filtered.csv", sep = ""))

# subset the list to plot only pr
input_pr_pd_PR <- filter(input_pr_pd, avg_logFC > 0)
rownames(input_pr_pd_PR) <- input_pr_pd_PR$gene

# subset the list to plot only pr
input_pr_pd_PD <- filter(input_pr_pd, avg_logFC < 0)
rownames(input_pr_pd_PD) <- input_pr_pd_PD$gene
input_pr_pd_PD$avg_logFC <- input_pr_pd_PD$avg_logFC * -1
pd.1$avg_logFC <- pd.1$avg_logFC * -1
pd$avg_logFC <- pd$avg_logFC * -1

# plot PER
PR_only_volc = ggplot(input_pr_pd_PR, aes(avg_logFC, -log10(p_val_adj))) +
    geom_point(aes(col=sig)) + #add points colored by significance
    scale_color_manual(values=c("black", "red")) + 
    ggtitle("PER vs PD") 

PR_only_volc.1 <- PR_only_volc + geom_text_repel(data=head(pr.1, 25), aes(label=gene), point.padding = 1, box.padding = .3) +
  geom_text_repel(data=head(pr, 25), aes(label=gene), point.padding = 1, box.padding = .3) +
  labs(y = expression(-log[10]*" "*"adjusted pvalue"), x = "avg log fold change") + 
  theme(legend.title = element_blank(), legend.position = "top") + 
  scale_fill_discrete(labels = c("Not Sig", "adjusted pval < 0.05"))

# plot PD
PD_only_volc = ggplot(input_pr_pd_PD, aes(avg_logFC, -log10(p_val_adj))) +
    geom_point(aes(col=sig)) + #add points colored by significance
    scale_color_manual(values=c("black", "red")) + 
    ggtitle("PD vs PER") 

PD_only_volc.1 <- PD_only_volc + geom_text_repel(data=head(pd.1, 50), aes(label=gene), point.padding = 1, box.padding = .3) +
  geom_text_repel(data=head(pd, 20), aes(label=gene), point.padding = 1, box.padding = .3) +
  labs(y = expression(-log[10]*" "*"adjusted pvalue"), x = "avg log fold change") + 
  theme(legend.title = element_blank(), legend.position = "top") + 
  scale_fill_discrete(labels = c("Not Sig", "adjusted pval < 0.05"))

# save volcano plots
ggsave(PR_only_volc.1, filename = paste(dir,"plot_out/NI04/pr_vs_pd_pronly_volcanoplot.pdf", sep=""), width = 15, height = 15, units = "in")
ggsave(PD_only_volc.1, filename = paste(dir,"plot_out/NI04/pr_vs_pd_pdonly_volcanoplot.pdf", sep=""), width = 15, height = 15, units = "in")
```




Subset TH226 samples for longitudial analysis
```{r}
# subset out Patient TH226 (samples 52, 57 and 82)
TH226_patient <- filter(tiss_subset_tumor2@meta.data, patient_id == "TH226")
TH226_samples <- SubsetData(tiss_subset_tumor2, cells.use = TH226_patient$cell_id)

table(TH226_samples@meta.data$sample_name, TH226_samples@meta.data$analysis)
TH226_samples <- SetIdent(object = TH226_samples, id = TH226_samples@meta.data$sample_name)
unique(TH226_samples@ident)
```

TH226 TN vs PER
```{r}
# compare naive cells (n = 14) to pr cells (n = 187)
TH226_TNvsPER <- FindMarkers(object = TH226_samples, ident.1 = "LT_S52", ident.2 = "LT_S57")
TH226_TNvsPER$gene <- rownames(TH226_TNvsPER)
TH226_TNvsPER.1 <- TH226_TNvsPER
TH226_TNvsPER.1 <- filter(TH226_TNvsPER.1, avg_logFC < 0)
rownames(TH226_TNvsPER.1) <- TH226_TNvsPER.1$gene
# change avglogFC to positive number
TH226_TNvsPER.1$avg_logFC <- TH226_TNvsPER.1$avg_logFC * -1
mutate_TH226_TNvsPER <- mutate(TH226_TNvsPER.1, sig = ifelse(TH226_TNvsPER.1$p_val_adj < 0.05, "p_val_adj<0.05", "NS")) 
rownames(mutate_TH226_TNvsPER) <- mutate_TH226_TNvsPER$gene
TH226_TNvsPER.1 <- mutate_TH226_TNvsPER # sorted by pval_adjust
TH226_TNvsPER.2 <- TH226_TNvsPER.1[order(TH226_TNvsPER.1$avg_logFC, decreasing = TRUE), ] # sorted by avglogFC

# save sorted gene lists
write.csv(x = TH226_TNvsPER.1, file = paste(dir, "data_out/NI04/TH226_analysis/TH226_tn_v_pr_analysis.csv", sep = ""))

# create volcano plot
TH226volc <- ggplot(TH226_TNvsPER.1, aes(avg_logFC, -log10(p_val_adj))) + #volcanoplot with avg_logFC versus p_val_adj
    geom_point(aes(col=sig)) + #add points colored by significance
    scale_color_manual(values=c("black", "red")) + 
    ggtitle("TH226 TN vs PER") 

TH226_TNvsPER_plot <- TH226volc + geom_text_repel(data=head(TH226_TNvsPER.1, 6), aes(label=gene), point.padding = 1, box.padding = .3) +
  labs(y = expression(-log[10]*" "*"adjusted pvalue"), x = "avg log fold change") + 
  theme(legend.title = element_blank(), legend.position = "top") + 
  scale_fill_discrete(labels = c("Not Sig", "adjusted pval < 0.05"))

ggsave(TH226_TNvsPER_plot, filename = paste(dir, "plot_out/NI04/TH226_analysis/TH226_TNvPER_volcanoplot.pdf", sep = ""))
```

TH226 TN vs PD
```{r}
# compare naive cells (n = 14) to pd cells (n = 13)
TH226_TNvsPD <- FindMarkers(object = TH226_samples, ident.1 = "LT_S52", ident.2 = "LT_S82")
TH226_TNvsPD$gene <- rownames(TH226_TNvsPD)
TH226_TNvsPD.1 <- TH226_TNvsPD
TH226_TNvsPD.1 <- filter(TH226_TNvsPD.1, avg_logFC <= 0)
rownames(TH226_TNvsPD.1) <- TH226_TNvsPD.1$gene
# change avglogFC to positive number
TH226_TNvsPD.1$avg_logFC <- TH226_TNvsPD.1$avg_logFC * -1
mutate_TH226_TNvsPD <- mutate(TH226_TNvsPD.1, sig = ifelse(TH226_TNvsPD.1$p_val_adj < 0.05, "p_val_adj<0.05", "NS")) 
rownames(mutate_TH226_TNvsPD) <- mutate_TH226_TNvsPD$gene
TH226_TNvsPD.1 <- mutate_TH226_TNvsPD # sorted by pval_adjust
TH226_TNvsPD.2 <- TH226_TNvsPD.1[order(TH226_TNvsPD.1$avg_logFC, decreasing = TRUE), ] # sorted by avglogFC
# save sorted gene lists
write.csv(x = TH226_TNvsPD.1, file = paste(dir, "data_out/NI04/TH226_analysis/TH226_tn_v_pd_analysis.csv", sep = ""))

# create volcano plot
TH226volc <- ggplot(TH226_TNvsPD.1, aes(avg_logFC, -log10(p_val_adj))) + #volcanoplot with avg_logFC versus p_val_adj
    geom_point(aes(col=sig)) + #add points colored by significance
    scale_color_manual(values=c("black", "red")) + 
    ggtitle("TH226 TN vs PD") 

TH226_TNvsPD_plot <- TH226volc + geom_text_repel(data=head(TH226_TNvsPD.1, 10), aes(label=gene), point.padding = 1, box.padding = .3) +
  geom_text_repel(data=head(TH226_TNvsPD.2, 10), aes(label=gene), point.padding = 1, box.padding = .3)
  labs(y = expression(-log[10]*" "*"adjusted pvalue"), x = "avg log fold change") + 
  theme(legend.title = element_blank(), legend.position = "top") + 
  scale_fill_discrete(labels = c("Not Sig", "adjusted pval < 0.05"))

ggsave(TH226_TNvsPD_plot, filename = paste(dir, "plot_out/NI04/TH226_analysis/TH226_TNvPD_volcanoplot.pdf", sep = ""))

TH226_PTGES3 <- FetchData(TH226_samples, vars.all = c("PTGES3","sample_name", "analysis"))

TH226_PTGES3_test <- pairwise.wilcox.test(x = TH226_PTGES3$PTGES3, g = TH226_PTGES3$analysis)
TH226_PTGES3_test.1 <- as.data.frame(TH226_PTGES3_test$p.value)

TH226_PTGES3_vln <- ggplot(TH226_PTGES3, aes(x = analysis, y = PTGES3, fill = sample_name)) +
  geom_boxplot() + theme(axis.title.y = element_blank()) + 
  xlab("PTGES3 Gene Expression") + guides(colour = FALSE, fill = FALSE) +
  scale_x_discrete(limits=c("naive", "grouped_pr", "grouped_pd")) + 
  geom_signif(comparisons = list(c("grouped_pd", "grouped_pr")), map_signif_level=TRUE, y_position = 4.5, annotations = '7.45e-04') + 
  geom_signif(comparisons = list(c("grouped_pd", "naive")), map_signif_level=TRUE, y_position = 5.5, annotations = '1.20e-06') + 
  geom_signif(comparisons = list(c("grouped_pr", "naive")), map_signif_level=TRUE, y_position = 3.5, annotations = '0.01')

ggsave(TH226_PTGES3_vln, filename = paste(dir, "plot_out/NI04/TH226_analysis/TH226_PTGES3_boxplot.pdf", sep = ""), height = 10, width = 5)
```


TH226 PER vs PD Plot PR
```{r}
# compare pr cells (n = 187) to pd cells (n = 13)
TH226_PERvsPD <- FindMarkers(object = TH226_samples, ident.1 = "LT_S57", ident.2 = "LT_S82")
TH226_PERvsPD$gene <- rownames(TH226_PERvsPD)
#Will have different colors depending on significance
TH226_PERvsPD.1 <- TH226_PERvsPD
mutate_TH226_PERvsPD <- mutate(TH226_PERvsPD.1, sig = ifelse(TH226_PERvsPD.1$p_val_adj < 0.05, "p_val_adj<0.05", "NS")) 
rownames(mutate_TH226_PERvsPD) <- mutate_TH226_PERvsPD$gene
TH226_PERvsPD.1 <- mutate_TH226_PERvsPD # sorted by pval_adjust

TH226_PERvsPD.1_sig_per <- filter(TH226_PERvsPD.1, avg_logFC > 0 & sig == "p_val_adj<0.05") #60 genes
TH226_PERvsPD.1_sig_pd <- filter(TH226_PERvsPD.1, avg_logFC < 0 & sig == "p_val_adj<0.05") #334 genes

# save sorted gene lists
write.csv(x = TH226_PERvsPD.1, file = paste(dir, "data_out/NI04/TH226_analysis/TH226_per_v_pd.csv", sep = ""))
```

TH226 PER vs PD Plot (PR)
```{r}
# sort PER VS PD list for PER only
TH226_PERvsPD.1_pronly <- filter(TH226_PERvsPD.1, avg_logFC > 0)

TH226_PERvsPD.1_pronly.1 <- TH226_PERvsPD.1_pronly[order(TH226_PERvsPD.1_pronly$avg_logFC, decreasing = TRUE), ] # sorted by avglogFC

# create volcano plot
volc <- ggplot(TH226_PERvsPD.1_pronly, aes(avg_logFC, -log10(p_val_adj))) + #volcanoplot with avg_logFC versus p_val_adj
    geom_point(aes(col=sig)) + #add points colored by significance
    scale_color_manual(values=c("black", "red")) + 
    ggtitle("TH226 PER vs PD (PER)") 

TH226_PERvsPD_plot_per <- volc + geom_text_repel(data=head(TH226_PERvsPD.1_pronly.1, 50), aes(label=gene), point.padding = 1, box.padding = .3) +
  geom_text_repel(data=head(TH226_PERvsPD.1_pronly.1, 20), aes(label=gene), point.padding = 1, box.padding = .3) +
  labs(y = expression(-log[10]*" "*"adjusted pvalue"), x = "avg log fold change") + 
  theme(legend.title = element_blank(), legend.position = "top") + 
  scale_fill_discrete(labels = c("Not Sig", "adjusted pval < 0.05"))
ggsave(TH226_PERvsPD_plot_per, filename = paste(dir, "plot_out/NI04/TH226_analysis/TH226_PERvPD_PERonly_volcanoplot.pdf", sep = ""))
```


TH226 PER vs PD Plot (PD)
```{r}
# sort PER VS PD list for PER only
TH226_PERvsPD.1_pdonly <- filter(TH226_PERvsPD.1, avg_logFC < 0)
TH226_PERvsPD.1_pdonly$avg_logFC <- TH226_PERvsPD.1_pdonly$avg_logFC * -1

TH226_PERvsPD.1_pdonly.1 <- TH226_PERvsPD.1_pdonly[order(TH226_PERvsPD.1_pdonly$avg_logFC, decreasing = TRUE), ] # sorted by avglogFC

# create volcano plot
volc <- ggplot(TH226_PERvsPD.1_pdonly, aes(avg_logFC, -log10(p_val_adj))) + #volcanoplot with avg_logFC versus p_val_adj
    geom_point(aes(col=sig)) + #add points colored by significance
    scale_color_manual(values=c("black", "red")) + 
    ggtitle("TH226 PER vs PD (PD)") 

TH226_PERvsPD_plot_pd <- volc + geom_text_repel(data=head(TH226_PERvsPD.1_pdonly, 50), aes(label=gene), point.padding = 1, box.padding = .3) +
  geom_text_repel(data=head(TH226_PERvsPD.1_pdonly.1, 20), aes(label=gene), point.padding = 1, box.padding = .3) +
  labs(y = expression(-log[10]*" "*"adjusted pvalue"), x = "avg log fold change") + 
  theme(legend.title = element_blank(), legend.position = "top") + 
  scale_fill_discrete(labels = c("Not Sig", "adjusted pval < 0.05"))
ggsave(TH226_PERvsPD_plot_pd, filename = paste(dir, "plot_out/NI04/TH226_analysis/TH226_PERvPD_PDonly_volcanoplot.pdf", sep = ""))
```

Plasminogen Pathway
```{r}
Plasminogen_genes <- c('ANXA2', 'PLAT', 'PLAU', 'PLAUR', 'SERPINE1','SERPINB2', 'IGFBP3')

Plasminogen <- FetchData(TH226_samples, c(Plasminogen_genes, 'nGene','nReads','analysis','patient_id','sample_name','biopsy_site'))

Plasminogen$Plasminogen_activating <- rowMeans(Plasminogen[c("ANXA2", "PLAT", "PLAU", "PLAUR")], na.rm=TRUE)
Plasminogen$Plasminogen_inhibiting <- rowMeans(Plasminogen[c("SERPINE1", "SERPINB2")], na.rm=TRUE)

Plasminogen$cell_name <- rownames(Plasminogen)

Plasminogen_test <- pairwise.wilcox.test(x = Plasminogen$Plasminogen_activating, g = Plasminogen$analysis)
Plasminogen_test <- as.data.frame(Plasminogen_test$p.value)

Plasminogen_test1 <- pairwise.wilcox.test(x = Plasminogen$Plasminogen_inhibiting, g = Plasminogen$analysis)
Plasminogen_test1 <- as.data.frame(Plasminogen_test1$p.value)

DoHeatmap(TH226_samples, genes.use = Plasminogen_genes, slim.col.label = TRUE)

Plasminogen_act_vln <- ggplot(Plasminogen, aes(x = analysis, y = Plasminogen_activating, fill = analysis)) +
  geom_boxplot(outlier.shape = NA) + xlab("Group") + ylab("Plasminogen Activation") + ggtitle("Plasminogen Activation") +
  geom_signif(comparisons = list(c("grouped_pd", "grouped_pr")), map_signif_level=TRUE, y_position = 2.5, annotations = '0.76e-03') +
  geom_signif(comparisons = list(c("grouped_pd", "naive")), map_signif_level=TRUE, y_position = 3, annotations = '0.001') +
  geom_signif(comparisons = list(c("grouped_pr", "naive")), map_signif_level=TRUE, y_position = 2, annotations = '0.042') +
  scale_x_discrete(limits=c("naive", "grouped_pr", "grouped_pd")) + 
  theme(legend.position = "none")

Plasminogen_inhib_vln <- ggplot(Plasminogen, aes(x = analysis, y = Plasminogen_inhibiting, fill = analysis)) +
  geom_boxplot(outlier.shape = NA) + xlab("Group") + ylab("Plasminogen Inhibition") + 
  ggtitle("Plasminogen Inhibition") + 
  geom_signif(comparisons = list(c("grouped_pd", "grouped_pr")), map_signif_level=TRUE, y_position = 1.5, annotations = '1.77e-12') + 
  geom_signif(comparisons = list(c("grouped_pd", "naive")), map_signif_level=TRUE, y_position = 2, annotations = '1.70e-03') +
  geom_signif(comparisons = list(c("grouped_pr", "naive")), map_signif_level=TRUE, y_position = 1, annotations = '0.41') + 
  scale_x_discrete(limits=c("naive", "grouped_pr", "grouped_pd")) + 
  theme(legend.position = "none")

ggsave(Plasminogen_act_vln, filename = paste(dir, "plot_out/NI04/TH226_analysis/TH226_Plasminogen_act_sig.pdf", sep = ""), height = 10, width = 5)
ggsave(Plasminogen_inhib_vln, filename = paste(dir, "plot_out/NI04/TH226_analysis/TH226_Plasminogen_inhib_sig.pdf", sep = ""), height = 10, width = 5)
```

```{r}
# Visualize the AT2 Differentiation Signature (PMCID: PMC2644235)
AT2_genes <- c("SFTPC", "PGC", "SFTPB", "LAMP3", "LPL", "IGF2", "IL1RL1", "NR4A2", "HIF3A", "MAOA", "ADH1B", "SEPP1", "SCNN1A", "CLDN18", "AQP4")

AT2_sig <- FetchData(TH226_samples, c(AT2_genes, 'nGene','nReads','analysis','patient_id','sample_name','biopsy_site'))

AT2_sig$AT2_mean <- rowMeans(AT2_sig[c(AT2_genes)], na.rm=TRUE)

AT2_test <- pairwise.wilcox.test(x = AT2_sig$AT2_mean, g = AT2_sig$analysis)
AT2_test1 <- as.data.frame(AT2_test$p.value)

DoHeatmap(TH226_samples, genes.use = AT2_genes, slim.col.label = TRUE)

AT2_vln <- ggplot(AT2_sig, aes(x = analysis, y = AT2_mean, fill = analysis)) + 
  geom_boxplot(outlier.shape = NA) + guides(colour = FALSE, fill = FALSE) + xlab("Group") + 
  ggtitle("AT2 Differentiation Signature Expression per Group") + 
  geom_signif(comparisons = list(c("grouped_pd", "grouped_pr")), map_signif_level=TRUE, y_position = 2.5, annotations = '1.68e-08') +
  geom_signif(comparisons = list(c("grouped_pd", "naive")), map_signif_level=TRUE, y_position = 3, annotations = '5.42e-05	') + 
  geom_signif(comparisons = list(c("grouped_pr", "naive")), map_signif_level=TRUE, y_position = 2, annotations = '4.94e-01	') +  scale_x_discrete(limits=c("naive", "grouped_pr", "grouped_pd")) + theme(legend.position = "none")

ggsave(AT2_vln, filename = paste(dir, "plot_out/NI04/TH226_analysis/TH226_AT2_sig.pdf", sep = ""), height = 10, width = 5)
```

```{r}
# Visualize the Squamous Gene Expression
squamous_genes <- c("KRT16", "KRT6A", "KRT14", "KRT5", "CLCA2", "PKP1", "TP63", "ANXA8", "DSG3")

squamous_sig <- FetchData(TH226_samples, c(squamous_genes, 'nGene','nReads','analysis','patient_id','sample_name','biopsy_site'))

squamous_sig$squamous_mean <- rowMeans(squamous_sig[c(squamous_genes)], na.rm=TRUE)

squamous_test <- pairwise.wilcox.test(x = squamous_sig$squamous_mean, g = squamous_sig$analysis)
squamous_test1 <- as.data.frame(squamous_test$p.value)


DoHeatmap(TH226_samples, genes.use = squamous_genes, slim.col.label = TRUE)

squamous_vln <- ggplot(squamous_sig, aes(x = analysis, y = squamous_mean, fill = analysis)) + 
  geom_boxplot(outlier.shape = NA) + guides(colour = FALSE, fill = FALSE) + xlab("Group") + 
  ggtitle("Squamous Differentiation Signature Expression per Group") + 
  geom_signif(comparisons = list(c("grouped_pd", "grouped_pr")), map_signif_level=TRUE, y_position = 3.5, annotations = '9.26e-19') + 
  geom_signif(comparisons = list(c("grouped_pd", "naive")), map_signif_level=TRUE, y_position = 4, annotations = '3.48e-05') + 
  geom_signif(comparisons = list(c("grouped_pr", "naive")), map_signif_level=TRUE, y_position = 2, annotations = '0.24') +  scale_x_discrete(limits=c("naive", "grouped_pr", "grouped_pd")) + theme(legend.position = "none")

ggsave(squamous_vln, filename = paste(dir, "plot_out/NI04/TH226_analysis/TH226_squamous_sig.pdf", sep = ""), height = 10, width = 5)
```

```{r}
save(tiss_subset_tumor2, file = paste(dir, "Data_input/objects/NI04_tumor_seurat_object.RData", sep = ""))
```


```{r}
VlnPlot(tiss_subset_tumor2, "SELENBP1")
VlnPlot(tiss_subset_tumor2, "AXIN2")
```

