---
title: "Cancer Cell Diff. Expression"
output: html_notebook
---

```{r}
library(ggsignif)
library(corrplot)
library(Seurat)
library(tidyverse)
library(ggplot2)
```

```{r}
dir <- "/myVolume/scell_lung_adenocarcinoma/"
load(file = paste(dir,"Data_input/objects/NI03_epithelial_annotated_tumor.RData", sep=""))
```

Check nGenes and nReads for tumor vs nontumor
```{r}
x1 <- ggplot(data = tiss_nonimmune_epi@meta.data, aes(x = inferCNV_annotation, y = nGene)) + geom_boxplot() + geom_signif(comparisons = list(c("nontumor", "tumor")), map_signif_level=TRUE)
ggsave(plot = x1, paste(dir,"plot_out/NI04/tumor_nontumor_uniquegenes.pdf", sep=""), width = 90, height = 90, units = "mm")

x <- filter(tiss_nonimmune_epi@meta.data, inferCNV_annotation == 'tumor')
mean(x$nGene) # mean genes expressed by tumor 5576 1726195(nReads)
y <- filter(tiss_nonimmune_epi@meta.data, inferCNV_annotation == 'nontumor')
mean(y$nGene) # mean genes expressed by tumor 2588 1395728(nReads)

cor(x = tiss_nonimmune_epi@meta.data$nGene, y = tiss_nonimmune_epi@meta.data$nReads, method = "pearson")
cor(x = tiss_nonimmune_epi@meta.data$nGene, y = tiss_nonimmune_epi@meta.data$nReads, method = "spearman")
```

Subset tumor cells from epi_cells object
```{r}
cells.use <- row.names(tiss_nonimmune_epi@meta.data)[which(tiss_nonimmune_epi@meta.data$inferCNV_annotation=="tumor")]
length(cells.use)
tiss_subset_tumor2 <- SubsetData(tiss_nonimmune_epi, cells.use = cells.use)
```

Normalize and scale the data
```{r}
tiss_subset_tumor2 <- NormalizeData(object = tiss_subset_tumor2)
tiss_subset_tumor2 <- ScaleData(object = tiss_subset_tumor2)
```

Find variable genes
```{r}
tiss_subset_tumor2 <- FindVariableGenes(object = tiss_subset_tumor2, do.plot = TRUE, x.high.cutoff = Inf, y.cutoff = 0.5)
```

Perform PCA
```{r}
tiss_subset_tumor2 <- RunPCA(object = tiss_subset_tumor2, do.print = FALSE)
tiss_subset_tumor2 <- ProjectPCA(object = tiss_subset_tumor2, do.print = FALSE)
```

Visualize top genes in principal components
```{r}
PCHeatmap(object = tiss_subset_tumor2, pc.use = 1:6, cells.use = 100, do.balanced = TRUE, label.columns = FALSE, num.genes = 20)
```

Perform correlation of PCs and metadata fields
```{r}
pca.obj <- tiss_subset_tumor2@dr$pca
pc.coords <- pca.obj@cell.embeddings
df1 <- tiss_subset_tumor2@meta.data[,c("nGene","nReads","percent.ribo")]
df2 <- pc.coords[,c(1:10)]
cordf12 <- cor(df1,df2)
# Make a correlation plot
corrplot(cordf12, method = "number", main="Correlation of PCs and metadata")
```

Also visaulize PC variance
```{r}
PCElbowPlot(object = tiss_subset_tumor2)
```

Choose the number of principal components to use.
```{r}
n.pcs = 20
```

Check clustering stability at given resolution (Clustree)
```{r}
# Set different resolutions 
res.used <- seq(0.1,1,by=0.2)
# Loop over and perform clustering of different resolutions 
for(i in res.used){
tiss_subset_tumor2 <- FindClusters(object = tiss_subset_tumor2, reduction.type = "pca", dims.use = 1:n.pcs, 
    resolution = i, print.output = 0, save.SNN = TRUE, k.param = 10, force.recalc = T)}
# Make Plot
clus.tree.out <- clustree(tiss_subset_tumor2, layout="sugiyama") +
    theme(legend.position = "bottom") + 
  scale_color_brewer(palette = "Set1") +
    scale_edge_color_continuous(low = "grey80", high = "red")

clus.tree.out
```

Set resolution and perform clustering
```{r}
res.used <- 0.9
tiss_subset_tumor2 <- FindClusters(object = tiss_subset_tumor2, reduction.type = "pca", dims.use = 1:n.pcs, resolution = res.used, print.output = 0, save.SNN = TRUE, k.param = 10, force.recalc = T)
```

Perform  tSNE
```{r}
tiss_subset_tumor2 <- RunTSNE(object = tiss_subset_tumor2, dims.use = 1:n.pcs, seed.use = 10, perplexity=30)
```

Visualize TSNE colroed by cluster
```{r}
pdf(file = paste(dir, "plot_out/NI04/NI04_tumor_tsne.pdf", sep = ""))
TSNEPlot(object = tiss_subset_tumor2, do.label = T, group.by = "res.0.9")
TSNEPlot(object = tiss_subset_tumor2, do.label = F, group.by = "analysis")
dev.off()
```

Cluster Occ by patient
```{r}
# Calculate mixing score for each cluster 
tab.1 <- table(tiss_subset_tumor2@meta.data$patient_id, tiss_subset_tumor2@meta.data$res.0.9)
occ_score <- apply(tab.1, 2, max)/colSums(tab.1)
# Plot mixing score
pdf(file = paste(dir, "plot_out/NI04/NI04_tumor_clusocc_bargraph.pdf", sep = ""))
par(las=3);barplot(sort(occ_score), xlab="Cluster", ylab="Patient max Ncells/Total cells", ylim=c(0,1));abline(h=0.7, col="red")
dev.off()
```

```{r}
# set the ident of the object to the "analysis" column
unique(tiss_subset_tumor2@ident) # check current ident
tiss_subset_tumor2 <- SetIdent(tiss_subset_tumor2, ident.use = tiss_subset_tumor2@meta.data$analysis)
unique(tiss_subset_tumor2@ident) # check current ident
```

Calculate the pairwise comparisons between treatment groups of naive vs pr
```{r}
# calculate the pairwise comparision of naive vs pr
naive_v_pr <- FindMarkers(object = tiss_subset_tumor2, ident.1 = "naive", ident.2 = "grouped_pr")

# calculate the pairwise comparision of naive vs pd
naive_v_pd <- FindMarkers(object = tiss_subset_tumor2, ident.1 = "naive", ident.2 = "grouped_pd")

# calculate the pairwise comparision of pr vs pd
pr_v_pd <- FindMarkers(object = tiss_subset_tumor2, ident.1 = "grouped_pr", ident.2 = "grouped_pd")
```

To avoid patient specific effects, filter the DE list to exclude genes explained by a few patients
```{r}
# Group the DE genes and add the number of patients with nonzero expressing cells and the highest contributing patient's occupancy

# naive vs pr
naive_v_pr.1 <- naive_v_pr
groups <- c("naive", "grouped_pr")

for(i in 1:nrow(naive_v_pr.1)){
  # gene <- as.character(naive_v_pr.1$gene)[i]
  gene <- row.names(naive_v_pr.1)[i]
  gene.vec <- tiss_subset_tumor2@data[gene,]
    for(j in 1:length(groups)){
      cells <- row.names(tiss_subset_tumor2@meta.data)[which(tiss_subset_tumor2@meta.data$analysis==groups[j])]
      all.no.zero.cells <- names(which(gene.vec[cells] !=0 )) # Set threshold
      tab.1 <- table(as.character(tiss_subset_tumor2@meta.data[all.no.zero.cells,"patient_id"]))
      high.pat.per <- tab.1[which(tab.1==max(tab.1))[1]]/length(all.no.zero.cells)
      all.pat.length <- length(tab.1)
      naive_v_pr.1[i,paste(groups[j],"pt.occupancy")] <- high.pat.per
      naive_v_pr.1[i,paste(groups[j],"n.nonzero.pts")] <- all.pat.length
    }  
}

# naive vs pd
naive_v_pd.1 <- naive_v_pd
groups <- c("naive", "grouped_pd")

for(i in 1:nrow(naive_v_pd.1)){
  # gene <- as.character(naive_v_pd.1$gene)[i]
  gene <- row.names(naive_v_pd.1)[i]
  gene.vec <- tiss_subset_tumor2@data[gene,]
    for(j in 1:length(groups)){
      cells <- row.names(tiss_subset_tumor2@meta.data)[which(tiss_subset_tumor2@meta.data$analysis==groups[j])]
      all.no.zero.cells <- names(which(gene.vec[cells] !=0 )) # Set threshold
      tab.1 <- table(as.character(tiss_subset_tumor2@meta.data[all.no.zero.cells,"patient_id"]))
      high.pat.per <- tab.1[which(tab.1==max(tab.1))[1]]/length(all.no.zero.cells)
      all.pat.length <- length(tab.1)
      naive_v_pd.1[i,paste(groups[j],"pt.occupancy")] <- high.pat.per
      naive_v_pd.1[i,paste(groups[j],"n.nonzero.pts")] <- all.pat.length
    }  
}

# pr vs pd
pr_v_pd.1 <- pr_v_pd
groups <- c("grouped_pr", "grouped_pd")

for(i in 1:nrow(pr_v_pd.1)){
  # gene <- as.character(pr_v_pd.1$gene)[i]
  gene <- row.names(pr_v_pd.1)[i]
  gene.vec <- tiss_subset_tumor2@data[gene,]
    for(j in 1:length(groups)){
      cells <- row.names(tiss_subset_tumor2@meta.data)[which(tiss_subset_tumor2@meta.data$analysis==groups[j])]
      all.no.zero.cells <- names(which(gene.vec[cells] !=0 )) # Set threshold
      tab.1 <- table(as.character(tiss_subset_tumor2@meta.data[all.no.zero.cells,"patient_id"]))
      high.pat.per <- tab.1[which(tab.1==max(tab.1))[1]]/length(all.no.zero.cells)
      all.pat.length <- length(tab.1)
      pr_v_pd.1[i,paste(groups[j],"pt.occupancy")] <- high.pat.per
      pr_v_pd.1[i,paste(groups[j],"n.nonzero.pts")] <- all.pat.length
    }
}

# save all outputs
write.csv(naive_v_pr.1, file = paste(dir, "data_out/NI04/naive_v_pr1.csv", sep = ""))
write.csv(naive_v_pd.1, file = paste(dir, "data_out/NI04/naive_v_pd1.csv", sep = ""))
write.csv(pr_v_pd.1, file = paste(dir, "data_out/NI04/pr_v_pd.csv", sep = ""))
```

Naive vs PR plotting
```{r}
naive_v_pr.2 <- naive_v_pr.1
naive_v_pr.2$gene <- rownames(naive_v_pr.2)
naive_v_pr.2 <- filter(naive_v_pr.2, avg_logFC <= 0)
rownames(naive_v_pr.2) <- naive_v_pr.2$gene
# change avglogFC to positive number
naive_v_pr.2$avg_logFC <- naive_v_pr.2$avg_logFC * -1 # flip direction of axis (TN on left, PER on right)
hist(naive_v_pr.2$`naive n.nonzero.pts`) # set threshold for 3 or more patients
hist(naive_v_pr.2$`grouped_pr n.nonzero.pts`) # set threshold for 3 or more patients
naive_v_pr.2 <- filter(naive_v_pr.2, naive_v_pr.2$`grouped_pr n.nonzero.pts` > 3)
naive_v_pr.2 <- filter(naive_v_pr.2, naive_v_pr.2$`naive n.nonzero.pts` > 6)
rownames(naive_v_pr.2) <- naive_v_pr.2$gene
#Will have different colors depending on significance
mutateddf <- mutate(naive_v_pr.2, sig = ifelse(naive_v_pr.2$p_val_adj < 0.05, "p_val_adj<0.05", "NS")) 
rownames(mutateddf) <- mutateddf$gene
input_naive_pr <- mutateddf # input_naive_pr is sorted by pval_adjust
input_naive_pr.1 <- input_naive_pr[order(input_naive_pr$avg_logFC, decreasing = TRUE), ] # input_naive_pr.1 is sorted by avg_logFC

# save sorted gene lists
write.csv(x = input_naive_pr.1, file = paste(dir, "data_out/NI04/naive_v_pr1_filtered.csv", sep = ""))

# plot
volc = ggplot(input_naive_pr, aes(avg_logFC, -log10(p_val_adj))) + #volcanoplot with avg_logFC versus p_val_adj
    geom_point(aes(col=sig)) + #add points colored by significance
    scale_color_manual(values=c("black", "red")) + 
    ggtitle("Naive vs PR") 

naive_vs_pr_volc.1 <- volc + geom_text_repel(data=head(input_naive_pr.1, 20), aes(label=gene), point.padding = 1, box.padding = .3) +
  geom_text_repel(data=head(input_naive_pr, 20), aes(label=gene), point.padding = 1, box.padding = .3) +
  labs(y = expression(-log[10]*" "*"adjusted pvalue"), x = "avg log fold change") + 
  theme(legend.title = element_blank(), legend.position = "top") + 
  scale_fill_discrete(labels = c("Not Sig", "adjusted pval < 0.05"))
# save volcano plot
ggsave(naive_vs_pr_volc.1, filename = paste(dir,"plot_out/NI04/naive_vs_pr_volcanoplot.pdf", sep=""), width = 15, height = 15)

table(input_naive_pr.1$sig) # find number of genes that are sig for PER compared to TN
```


Naive vs PD plotting
```{r}
naive_v_pd.2 <- naive_v_pd.1
naive_v_pd.2$gene <- rownames(naive_v_pd.2)
naive_v_pd.2 <- filter(naive_v_pd.2, avg_logFC <= 0)
rownames(naive_v_pd.2) <- naive_v_pd.2$gene
# change avglogFC to positive number
naive_v_pd.2$avg_logFC <- naive_v_pd.2$avg_logFC * -1
# filter out any genes that are explained by less than 6 patients contributing
hist(naive_v_pd.2$`grouped_pd n.nonzero.pts`) # set threshold for 6 or more patients
hist(naive_v_pd.2$`naive n.nonzero.pts`) # set threshold for 6 or more patients
# filter for genes explained by few pateints
naive_v_pd.2 <- filter(naive_v_pd.2, naive_v_pd.2$`grouped_pd n.nonzero.pts` > 6)
naive_v_pd.2 <- filter(naive_v_pd.2, naive_v_pd.2$`naive n.nonzero.pts` > 6)
rownames(naive_v_pd.2) <- naive_v_pd.2$gene
#Will have different colors depending on significance
mutateddf <- mutate(naive_v_pd.2, sig = ifelse(naive_v_pd.2$p_val_adj < 0.05, "p_val_adj<0.05", "NS")) 
rownames(mutateddf) <- mutateddf$gene
input_naive_pd <- mutateddf # input_naive_pd is sorted by pval_adjust
input_naive_pd.1 <- input_naive_pd[order(input_naive_pd$avg_logFC, decreasing = TRUE), ] # sorted by avglogFC
# save sorted gene lists
write.csv(x = input_naive_pd.1, file = paste(dir, "data_out/NI04/naive_v_pd1_filtered.csv", sep = ""))

# create volcano plot
volc = ggplot(input_naive_pd, aes(avg_logFC, -log10(p_val_adj))) + #volcanoplot with avg_logFC versus p_val_adj
    geom_point(aes(col=sig)) + #add points colored by significance
    scale_color_manual(values=c("black", "red")) + 
    ggtitle("Naive vs PD") 

naive_vs_pd_volc.1 <- volc + geom_text_repel(data=head(input_naive_pd.1, 40), aes(label=gene), point.padding = 1, box.padding = .3) +
  geom_text_repel(data=head(input_naive_pd, 40), aes(label=gene), point.padding = 1, box.padding = .3)
  labs(y = expression(-log[10]*" "*"adjusted pvalue"), x = "avg log fold change") + 
  theme(legend.title = element_blank(), legend.position = "top") + 
  scale_fill_discrete(labels = c("Not Sig", "adjusted pval < 0.05"))
# save volcano plot
ggsave(naive_vs_pd_volc.1, filename = paste(dir,"plot_out/NI04/naive_vs_pd_volcanoplot.pdf", sep=""), width = 15, height = 15)

table(input_naive_pd.1$sig) # find number of genes that are sig for PD compared to TN
```

PER vs PD
```{r}
pr_v_pd.2 <- pr_v_pd.1
pr_v_pd.2$gene <- rownames(pr_v_pd.2)
#split the negative and positive avg_locFC
pr <- filter(pr_v_pd.2, avg_logFC > 0)
pd <- filter(pr_v_pd.2, avg_logFC < 0)
# add rownames back
rownames(pr) <- pr$gene
rownames(pd) <- pd$gene
# check the hist to set threshold for filtering out any genes that are explained by few number of patients
hist(pr$`grouped_pr n.nonzero.pts`) # threshold at > 3 patients
hist(pd$`grouped_pd n.nonzero.pts`) # threshold at > 6 patients
# set thresholds for 
pr <- filter(pr, pr$`grouped_pr n.nonzero.pts` > 3)
rownames(pr) <- pr$gene
pd <- filter(pd, pd$`grouped_pd n.nonzero.pts` > 6)
rownames(pd) <- pd$gene
# save pr and pd sorted by avglogFC
pr.1 <- pr[order(pr$avg_logFC, decreasing = TRUE), ]
pd.1 <- pd[order(pd$avg_logFC, decreasing = FALSE), ]
# rbind back together the pr and pd
pr_v_pd.3 <- rbind(pr, pd)
#Will have different colors depending on significance
mutateddf <- mutate(pr_v_pd.3, sig = ifelse(pr_v_pd.3$p_val_adj < 0.05, "p_val_adj<0.05", "NS")) 
rownames(mutateddf) <- mutateddf$gene
input_pr_pd <- mutateddf # input_pr_pd is sorted by pval_adjust
input_pr_pd.1 <- input_pr_pd[order(input_pr_pd$avg_logFC, decreasing = TRUE), ] # sorted by avglogFC
# save sorted gene lists
write.csv(x = input_pr_pd.1, file = paste(dir, "data_out/NI04/pr_v_pd1_filtered.csv", sep = ""))

# subset the list to plot only pr
input_pr_pd_PR <- filter(input_pr_pd, avg_logFC > 0)
rownames(input_pr_pd_PR) <- input_pr_pd_PR$gene

# subset the list to plot only pr
input_pr_pd_PD <- filter(input_pr_pd, avg_logFC < 0)
rownames(input_pr_pd_PD) <- input_pr_pd_PD$gene
input_pr_pd_PD$avg_logFC <- input_pr_pd_PD$avg_logFC * -1
pd.1$avg_logFC <- pd.1$avg_logFC * -1
pd$avg_logFC <- pd$avg_logFC * -1

# plot PER
PR_only_volc = ggplot(input_pr_pd_PR, aes(avg_logFC, -log10(p_val_adj))) +
    geom_point(aes(col=sig)) + #add points colored by significance
    scale_color_manual(values=c("black", "red")) + 
    ggtitle("PER vs PD") 

PR_only_volc.1 <- PR_only_volc + geom_text_repel(data=head(pr.1, 25), aes(label=gene), point.padding = 1, box.padding = .3) +
  geom_text_repel(data=head(pr, 25), aes(label=gene), point.padding = 1, box.padding = .3) +
  labs(y = expression(-log[10]*" "*"adjusted pvalue"), x = "avg log fold change") + 
  theme(legend.title = element_blank(), legend.position = "top") + 
  scale_fill_discrete(labels = c("Not Sig", "adjusted pval < 0.05"))

# plot PD
PD_only_volc = ggplot(input_pr_pd_PD, aes(avg_logFC, -log10(p_val_adj))) +
    geom_point(aes(col=sig)) + #add points colored by significance
    scale_color_manual(values=c("black", "red")) + 
    ggtitle("PD vs PER") 

PD_only_volc.1 <- PD_only_volc + geom_text_repel(data=head(pd.1, 50), aes(label=gene), point.padding = 1, box.padding = .3) +
  geom_text_repel(data=head(pd, 20), aes(label=gene), point.padding = 1, box.padding = .3) +
  labs(y = expression(-log[10]*" "*"adjusted pvalue"), x = "avg log fold change") + 
  theme(legend.title = element_blank(), legend.position = "top") + 
  scale_fill_discrete(labels = c("Not Sig", "adjusted pval < 0.05"))

# save volcano plots
ggsave(PR_only_volc.1, filename = paste(dir,"plot_out/NI04/pr_vs_pd_pronly_volcanoplot.pdf", sep=""), width = 15, height = 15, units = "in")
ggsave(PD_only_volc.1, filename = paste(dir,"plot_out/NI04/pr_vs_pd_pdonly_volcanoplot.pdf", sep=""), width = 15, height = 15, units = "in")

table(input_pr_pd_PR$sig) # find number of genes that are sig for PER compared to PD
table(input_pr_pd_PD$sig) # find number of genes that are sig for PD compared to PER
```

```{r}
save(tiss_subset_tumor2, file = paste(dir, "Data_input/objects/objects/NI04_tumor_seurat_object.RData", sep = ""))
```







