---
title: "NI05 Annotate Non Tumor Epitheial Clusters"
output: html_notebook
---

```{r}
library(Seurat)
library(ggplot2)
library(tidyverse)
require(corrplot)
library(clustree)
```

```{r}
# rm(list=ls())
dir <- "/myVolume/scell_lung_adenocarcinoma/"
load(file=paste(dir,"Data_input/objects/NI03_epithelial_annotated_tumor.RData", sep=""))
load(file=paste(dir,"Data_input/objects/objects/NI04_tumor_seurat_object.RData", sep=""))
```

Look for clincal mutation found in normal classified cells
```{r}
cell_mutation_tab <- read.csv(file = paste(dir, "Data_input/objects/validationTable_cells.4.19.19.csv", sep = ""))
rownames(cell_mutation_tab) <- cell_mutation_tab$cell
cell_mutation_tab$tumorCell_bool <- NULL

# Subset cell_mutation_tab to only normal cells
normal_cells <- filter(tiss_nonimmune_epi@meta.data, inferCNV_annotation == "nontumor")
normal_cells <- normal_cells$cell_id
length(normal_cells)
normal_cell_mutation_tab <- cell_mutation_tab[normal_cells, ]

sub_normal_cell_mutation_tab <- filter(normal_cell_mutation_tab, clinical_mutation_found_bool == 1)
sub_normal_cell_mutation_tab
# only one cell confirmed with clincial mutation (G22_B003776)
```

Subset the Normal Epithelial cells, recluster and annotate
```{r}
cells.use <- row.names(tiss_nonimmune_epi@meta.data)[which(tiss_nonimmune_epi@meta.data$inferCNV_annotation == "nontumor")]
length(cells.use)
tiss_subset_normalepi <- SubsetData(tiss_nonimmune_epi, cells.use = cells.use)
```

Find variable genes
```{r}
tiss_subset_normalepi <- FindVariableGenes(object = tiss_subset_normalepi, do.plot = TRUE, x.high.cutoff = Inf, y.cutoff = 0.5)
```

Perform PCA
```{r}
tiss_subset_normalepi <- RunPCA(object = tiss_subset_normalepi, do.print = FALSE)
tiss_subset_normalepi <- ProjectPCA(object = tiss_subset_normalepi, do.print = FALSE)
```

Visualize top genes in principal components
```{r}
PCHeatmap(object = tiss_subset_normalepi, pc.use = 1:6, cells.use = 100, do.balanced = TRUE, label.columns = FALSE, num.genes = 20)
```

Perform correlation of PCs and metadata fields
```{r}
pca.obj <- tiss_subset_normalepi@dr$pca
pc.coords <- pca.obj@cell.embeddings
df1 <- tiss_subset_normalepi@meta.data[,c("nGene","nReads","percent.ribo")]
df2 <- pc.coords[,c(1:10)]
cordf12 <- cor(df1,df2)
# Make a correlation plot
corrplot(cordf12, method = "number", main="Correlation of PCs and metadata")
```

Also visaulize PC variance
```{r}
PCElbowPlot(object = tiss_subset_normalepi)
```

Choose the number of principal components to use.
```{r}
n.pcs = 20
```

Check clustering stability at given resolution (Clustree)
```{r}
# Set different resolutions 
res.used <- seq(0.1,1,by=0.2)
# Loop over and perform clustering of different resolutions 
for(i in res.used){
tiss_subset_normalepi <- FindClusters(object = tiss_subset_normalepi, reduction.type = "pca", dims.use = 1:n.pcs, 
    resolution = i, print.output = 0, save.SNN = TRUE, k.param = 10, force.recalc = T)}
# Make Plot
clus.tree.out <- clustree(tiss_subset_normalepi, layout="sugiyama") +
    theme(legend.position = "bottom") + 
  scale_color_brewer(palette = "Set1") +
    scale_edge_color_continuous(low = "grey80", high = "red")
# Save pdf 
ggsave(clus.tree.out, filename = paste(dir,"plot_out/NI05/Cluster_resolutions_clustree_output.pdf", sep=""), width = 15, height = 15)
clus.tree.out
```

Set resolution and perform clustering
```{r}
res.used <- 0.3
tiss_subset_normalepi <- FindClusters(object = tiss_subset_normalepi, reduction.type = "pca", dims.use = 1:n.pcs, resolution = res.used, print.output = 0, save.SNN = TRUE, k.param = 10, force.recalc = T)
```

Perform  tSNE
```{r}
tiss_subset_normalepi <- RunTSNE(object = tiss_subset_normalepi, dims.use = 1:n.pcs, seed.use = 10, perplexity=30)
```

Visualize TSNE colroed by cluster
```{r}
pdf(file = paste(dir, "plot_out/NI05/nontumor_epi_tsne.pdf", sep = ""))
TSNEPlot(object = tiss_subset_normalepi, do.label = T)
dev.off()
```

Find which cluster G22_B003776 is found in
```{r}
grep(x = tiss_subset_normalepi@meta.data$cell_id, pattern = "G22_B003776") #480th row
tiss_subset_normalepi@meta.data[480,] # found in cluster 3
```

Cluster Occ by patient
```{r}
# Calculate mixing score for each cluster 
tab.1 <- table(tiss_subset_normalepi@meta.data$patient_id, tiss_subset_normalepi@meta.data$res.0.3)
occ_score <- apply(tab.1, 2, max)/colSums(tab.1)
# Plot mixing score
pdf(file = paste(dir, "plot_out/NI05/clusocc_bargraph.pdf", sep = ""))
par(las=3);barplot(sort(occ_score), xlab="Cluster", ylab="Patient max Ncells/Total cells", ylim=c(0,1));abline(h=0.7, col="red")
dev.off()
```

Compare cluster occ of normal epi to tumor
```{r}
# noraml
tab.1 <- table(tiss_subset_normalepi@meta.data$patient_id, tiss_subset_normalepi@meta.data$res.0.3)
occ_score <- apply(tab.1, 2, max)/colSums(tab.1)
normal_occ <- as.data.frame(occ_score)
normal_occ$group <- "normal"
colnames(normal_occ) <- c("score", "group")
# tumor
tab.2 <- table(tiss_subset_tumor2@meta.data$patient_id, tiss_subset_tumor@meta.data$res.0.9)
occ_score2 <- apply(tab.2, 2, max)/colSums(tab.2)
tumor_occ <- as.data.frame(occ_score2)
tumor_occ$group <- "tumor"
colnames(tumor_occ) <- c("score", "group")

occ_combo <- rbind(normal_occ, tumor_occ)

occ_changes <- ggplot(occ_combo,aes(x=score)) + 
    # geom_histogram(data=subset(occ_combo, group == 'normal'),fill = "blue", alpha = 0.2, bins = 5) +
    # geom_histogram(data=subset(occ_combo, group == 'tumor'),fill = "red", alpha = 0.2, bins = 5) +
    geom_density(data=subset(occ_combo, group == 'normal'), size = 1.5, colour = "blue") + 
    geom_density(data=subset(occ_combo, group == 'tumor'), size = 1.5, colour = "red")

ggsave(occ_changes, filename = paste(dir, "plot_out/NI05/NI05_occ_changes_tumor_nontumor.pdf", sep = ""), width = 10, height = 10)
```


Create a Dendrogram of all Epitheial Clusters
```{r}
# Export data from Seurat object and normalize
data.raw <- tiss_subset_normalepi@raw.data
dim(data.raw)

#r Export metadata from Seurat object
metadata <- tiss_subset_normalepi@meta.data
dim(metadata)

# Subset data and metadata to contain same cells and in the same order. Normalize data
data.raw <- as.matrix(data.raw[,row.names(metadata)])
# Remove non-expressed genes 
data.raw <- data.raw[names(which(rowSums(data.raw)!=0)),]
# Normalize
data.norm <- apply(X=data.raw, MARGIN=2, function(x) log2((((x/sum(x))*1000000)+1)) )
dim(data.norm)

# Overdispersion
sel.by.cv <- function(counts.nodups) {
  require(statmod)# library(pcaMethods); library(fastICA)
  ed <- counts.nodups*1000000/colSums(counts.nodups) # Second pass, no duplicates
  #ed <- counts.nodups
  means <- rowMeans(ed)
  vars <- apply(ed,1,var)
  cv2 <- vars/means^2
  winsorize <- function (x, fraction=0.05) {
    if(length(fraction) != 1 || fraction < 0 ||
       fraction > 0.5) {
      stop("bad value for 'fraction'")
    }
    lim <- quantile(x, probs=c(fraction, 1-fraction))
    x[ x < lim[1] ] <- lim[1]
    x[ x > lim[2] ] <- lim[2]
    x
  }
  wed <- t(apply(ed, 1, winsorize, fraction=2/ncol(ed))) 
  means = rowMeans(wed); vars = apply(wed,1,var); cv2 <- vars/means^2
  useForFit <- means >= unname( quantile( means[ which( cv2 > .3 ) ], .95 ) ) 
  fit <- glmgam.fit( cbind( a0 = 1, a1tilde = 1/means[useForFit] ),cv2[useForFit] )
  xg <- exp(seq( min(log(means[means>0])), max(log(means), na.rm=T), length.out=1000 ))
  afit <- fit$coef["a1tilde"]/means+fit$coef["a0"]
  vfit <- fit$coef["a1tilde"]/xg+fit$coef["a0"]
  varFitRatio <- vars/(afit*means^2)
  varorder <- order(varFitRatio,decreasing=T)
  return(varorder)
}
# OD analysis
o <- sel.by.cv(data.raw)

# select top OD genes (1000 genes)

data.norm.top <- data.norm[o[1:1000],]
dim(data.norm.top)
# Remove cells with no expression of any of the overdispersed genes 
cells <- names(which(colSums(data.norm.top)!=0))
metadata <- metadata[cells,]
data.raw <- data.raw[,row.names(metadata)]
data.norm <- data.norm[,row.names(metadata)]
data.norm.top <- data.norm.top[,row.names(metadata)]

#Calculate distance
dist.cor <- as.dist(1-abs(cor(data.norm.top)))

# Create a cluster distance matrix

# Rename the res column to cluster
mat_clus_dis <- matrix(nrow=length(unique(metadata$res.0.3)), 
                       ncol=length(unique(metadata$res.0.3)))
colnames(mat_clus_dis) <- paste("Cluster_", 0:(length(unique(metadata$res.0.3))-1), sep="")
row.names(mat_clus_dis) <- paste("Cluster_", 0:(length(unique(metadata$res.0.3))-1), sep="")
# 
diag(mat_clus_dis) <- 0
# 
clusters <- 0:max(as.numeric(metadata$res.0.3))
for(i in 1:nrow(mat_clus_dis)){
  cells <- row.names(metadata)[which(metadata$res.0.3==clusters[i])]
  for(j in 1:ncol(mat_clus_dis)){
  no_cells <- row.names(metadata)[which(metadata$res.0.3==clusters[j])]
  mat.dist.temp <- as.matrix(dist.cor)[cells,no_cells]
  mat_clus_dis[i,j] <-  mean(mat.dist.temp)
  }
}
# Convert to distance object
dist.clus <- as.dist(mat_clus_dis)
```

Plot and save Dendrogram
```{r Hierarchical clusterting}
# Convert to clustering object
tree.clus <- hclust(dist.clus, "ward.D2")
# Plot 
pdf(file = paste(dir, "/plot_out/NI05/NI05_normalepi_dendro.pdf", sep = ""))
plot(tree.clus)
dev.off()
```

Find markers for each cluster
```{r}
unique(tiss_subset_normalepi@ident)
tiss.markers.epi <- FindAllMarkers(object = tiss_subset_normalepi, only.pos = TRUE, min.pct = 0.25, thresh.use = 0.25)
```

Write differential gene table
```{r}
write.csv(tiss.markers.epi, file = paste(dir, "data_out/NI05/NI05_DE_epithelial.csv", sep = ""))
```

Display the top markers you computed above.
```{r}
tiss.markers.epi %>% group_by(cluster) %>% top_n(10, avg_logFC)
```

Create dotplots of the top markers displayed above
```{r}
markers.small  <- tiss.markers.epi %>% group_by(cluster) %>% top_n(5, avg_logFC)
genes_to_check <- markers.small$gene
DotPlot(object = tiss_subset_normalepi, genes.plot = genes_to_check, x.lab.rot = TRUE)
```

ID cell types using cell markers
```{r}
# Cell markers
s.muscle <- c('CNN1','SUSD5','ACTC1','ASB2','KCNA5','LDB3','MYOCD','ELN','ACTG2','ACTA2')
neuro.e <- c('RESP18','NOV','SCG5','NNAT','CALCA','PTPRN','SLC35D3','ASCL1','CHGA')
glial <- c('KCNA1','CDH19','SOX10','GFRA3','PLP1','GPR37L1','ART3','RASGEF1C','KCNA6','GFAP')
club <- c('GABRP','CCKAR','HP','KCNK2','UPK3A','CLDN10','PON1','SCGB1A1','BPIFB1','MUC5B')
ciliated <- c('CDHR3','FOXJ1','RGS22','MAPK15','SPEF2','CCDC153')
at2 <- c('NAPSA','CHIA','SFTPC','SFTPB','MUC1','SFTPA1','SFTPA2')
at1 <- c('IGFBP2','COL4A3','PDPN','AGER','CAV1','CDKN2B','RTKN2')
ionocytes <- c('ATP6V1C2','ATP6V0D2','CFTR','FOXI1','ASCL3')
basal <- c('KRT17','KRT5','SYT8','FHL2','MMP1')
heptaocyte <- c('ALB')
all_epi_markers <- c(s.muscle, neuro.e, glial, club, ciliated, at2, at1, basal, heptaocyte)

DotPlot(object = tiss_subset_normalepi, genes.plot = all_epi_markers, x.lab.rot = T)
DotPlot(object = tiss_subset_normalepi, genes.plot = s.muscle, x.lab.rot = T) # non
DotPlot(object = tiss_subset_normalepi, genes.plot = neuro.e, x.lab.rot = T) # cluster 9 ASCL1
DotPlot(object = tiss_subset_normalepi, genes.plot = glial, x.lab.rot = T) # none
DotPlot(object = tiss_subset_normalepi, genes.plot = club, x.lab.rot = T) # cluster 1
DotPlot(object = tiss_subset_normalepi, genes.plot = ciliated, x.lab.rot = T) # cluster 6 and 16
DotPlot(object = tiss_subset_normalepi, genes.plot = at2, x.lab.rot = T) # cluster 0, 11, 12
DotPlot(object = tiss_subset_normalepi, genes.plot = at1, x.lab.rot = T) # cluster 2
DotPlot(object = tiss_subset_normalepi, genes.plot = ionocytes, x.lab.rot = T) # cluster 13
DotPlot(object = tiss_subset_normalepi, genes.plot = basal, x.lab.rot = T) # cluster 14
DotPlot(object = tiss_subset_normalepi, genes.plot = heptaocyte, x.lab.rot = T) # cluster 7
```

Create table of how many cells belong to each cluster assignment
```{r}
table(tiss_subset_normalepi@meta.data$res.0.3)
```

Set Metadata Column for Cluster IDs
```{r}
tiss_subset_normalepi@meta.data$normalepi_seurat_cluster <- tiss_subset_normalepi@meta.data$res.0.3
```

Annotate the normal epi cells
```{r}
# enumerate current cluster IDs and the labels for them
cluster.ids <- c(0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16)
annotation <- c("alveolar type 2 cell", "club cell", "alveolar type 1 cell", "unknown stroma", "unknown stroma", "unknown stroma", "ciliated cell", "unknown stroma", "hepatocyte", "unknown stroma", "unknown stroma", "alveolar type 2 cell", "alveolar type 2 cell", "ionocyte", "basal cell", "unknown stroma", "ciliated cell")

tiss_subset_normalepi@meta.data[,'norm_epi_annotation'] <- plyr::mapvalues(x = tiss_subset_normalepi@meta.data$res.0.3, from = cluster.ids, to = annotation)

# save annotation column with cell_id
write.csv(tiss_subset_normalepi@meta.data[, c(6, 64)], paste(dir, "data_out/NI05/NI05_norm_epi_annotations.csv", sep = ""))
```

Plot tSNE with annoations
```{r}
pdf(file = paste(dir, "plot_out/NI05/NI05_norm_epi_annotated_tsne.csv", sep = ""))
TSNEPlot(object = tiss_subset_normalepi, group.by='norm_epi_annotation')
dev.off()
TSNEPlot(object = tiss_subset_normalepi, group.by='biopsy_site')
```

Save object
```{r}
save(tiss_subset_normalepi, file = paste(dir, "Data_input/objects/objects/NI05_normalepi_seurat_object_annotated.RData", sep = ""))
# load(file = paste(dir, "Data_input/objects/objects/NI05_normalepi_seurat_object_annotated.RData", sep = ""))
```

save normal epi annotations to all epi seurat object
```{r}
tiss_nonimmune_epi@meta.data <- left_join(tiss_nonimmune_epi@meta.data, tiss_subset_normalepi@meta.data[,c(6,64)])
rownames(tiss_nonimmune_epi@meta.data) <- tiss_nonimmune_epi@meta.data$cell_id
tiss_nonimmune_epi@meta.data$epi_anno_final <- tiss_nonimmune_epi@meta.data$norm_epi_annotation
# replace na with tumor
tiss_nonimmune_epi@meta.data$epi_anno_final[is.na(tiss_nonimmune_epi@meta.data$epi_anno_final)] <- "tumor"
table(tiss_nonimmune_epi@meta.data$epi_anno_final)

save(tiss_nonimmune_epi, file = paste(dir, "Data_input/objects/objects/NI05_all_epithelial_annotated_normal_and_tumor.RData", sep = ""))
# load("/myVolume/scell_lung_adenocarcinoma/Data_input/objects/objects/NI05_all_epithelial_annotated_normal_and_tumor.RData")
```


```{r}
# Barplot of all epi cell counts 
table.temp <- as.data.frame(table(tiss_nonimmune_epi@meta.data$epi_anno_final))
table.temp$Var1 <- factor(table.temp$Var1,levels = as.character(table.temp$Var1[order(table.temp$Freq,decreasing=F)]))
p <-  ggplot(data = table.temp, aes(x = Var1, y = Freq, fill = Var1)) +
      geom_bar(stat ="identity") + coord_flip() + theme(legend.position = "none") 
ggsave(plot = p, paste(dir,"plot_out/NI05/epi_cell_counts.pdf", sep=""), width = 90, height = 90, units = "mm")
```

```{r}
#set levels for plotting
tiss_nonimmune_epi@meta.data$epi_anno_final <- factor(tiss_nonimmune_epi@meta.data$epi_anno_final, levels = c("basal cell", "ionocyte", "hepatocyte", "ciliated cell", "alveolar type 1 cell", "club cell", "alveolar type 2 cell", "unknown stroma", "tumor"))

p1 <- ggplot(tiss_nonimmune_epi@meta.data, aes(x = epi_anno_final, y = nGene)) + geom_boxplot(aes(fill = epi_anno_final)) + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + theme(legend.position = "none") + coord_flip()

ggsave(plot = p1, paste(dir,"plot_out/NI05/epi_cell_nGenes.pdf", sep=""), width = 90, height = 90, units = "mm")
```


