---
title: "NI05 Annotate Non Tumor Epitheial Clusters"
output: html_notebook
---

```{r}
library(Seurat)
library(ggplot2)
library(tidyverse)
require(corrplot)
library(clustree)
```

```{r}
# rm(list=ls())
# dir <- "/myVolume/scell_lung_adenocarcinoma/"
dir <- "/home/ubuntu/scell_lung_adenocarcinoma/"
load(file=paste(dir,"Data_input/objects/NI03_epithelial_annotated_tumor.RData", sep=""))
load(file=paste(dir,"Data_input/objects/NI04_tumor_seurat_object.RData", sep=""))
```

Look for clincal mutation found in normal classified cells
```{r}
cell_mutation_tab <- read.csv(file = paste(dir, "Data_input/objects/validationTable_cells.4.19.19.csv", sep = ""))
rownames(cell_mutation_tab) <- cell_mutation_tab$cell
cell_mutation_tab$tumorCell_bool <- NULL

# Subset cell_mutation_tab to only normal cells
normal_cells <- filter(tiss_nonimmune_epi@meta.data, inferCNV_annotation == "nontumor")
normal_cells <- normal_cells$cell_id
length(normal_cells)
normal_cell_mutation_tab <- cell_mutation_tab[normal_cells, ]

sub_normal_cell_mutation_tab <- filter(normal_cell_mutation_tab, clinical_mutation_found_bool == 1)
sub_normal_cell_mutation_tab
# only one cell confirmed with clincial mutation (G22_B003776)
```

Subset the Normal Epithelial cells, recluster and annotate
```{r}
cells.use <- row.names(tiss_nonimmune_epi@meta.data)[which(tiss_nonimmune_epi@meta.data$inferCNV_annotation == "nontumor")]
length(cells.use)
tiss_subset_normalepi <- subset(tiss_nonimmune_epi, cells = cells.use)
table(tiss_nonimmune_epi@meta.data$inferCNV_annotation) #check
```

Fix biop. site metadata
```{r}
tiss_subset_normalepi@meta.data$biopsy_site <- gsub(pattern = "lung", replacement = "Lung", x = tiss_subset_normalepi@meta.data$biopsy_site)
table(tiss_subset_normalepi@meta.data$biopsy_site)
```

Normalize and scale the data
```{r}
tiss_subset_normalepi <- NormalizeData(object = tiss_subset_normalepi)
```

Find variable genes
```{r}
tiss_subset_normalepi <- FindVariableFeatures(object = tiss_subset_normalepi)
```

Scale data
```{r}
tiss_subset_normalepi <- ScaleData(object = tiss_subset_normalepi, features = rownames(tiss_subset_normalepi))
```

Perform PCA
```{r}
tiss_subset_normalepi <- RunPCA(object = tiss_subset_normalepi)
```

Visualize top genes in principal components
```{r}
DimHeatmap(object = tiss_subset_normalepi, dims = 1:10, cells = 100, balanced = TRUE)
```

Perform correlation of PCs and metadata fields
```{r}
pca.obj <- tiss_subset_normalepi@reductions$pca
pc.coords <- pca.obj@cell.embeddings
df1 <- tiss_subset_normalepi@meta.data[,c("nFeature_RNA","nCount_RNA","percent.ribo")]
df2 <- pc.coords[,c(1:10)]
cordf12 <- cor(df1,df2)
# Make a correlation plot
corrplot(cordf12, method = "number", main="Correlation of PCs and metadata")
```

Also visaulize PC variance
```{r}
ElbowPlot(object = tiss_subset_normalepi, ndims = 30)
```

Choose the number of principal components to use.
```{r}
n.pcs = 20
```

Find Neighbors
```{r}
tiss_subset_normalepi <- FindNeighbors(object = tiss_subset_normalepi, dims = 1:n.pcs, verbose = T, k.param = 20)
```

Check clustering stability at given resolution (Clustree)
```{r}
# Set different resolutions 
res.used <- seq(0.1,1,by=0.2)
# Loop over and perform clustering of different resolutions 
for(i in res.used){
tiss_subset_normalepi <- FindClusters(object = tiss_subset_normalepi, verbose = T, resolution = res.used)}
# Make Plot
clus.tree.out <- clustree(tiss_subset_normalepi, layout="sugiyama") +
    theme(legend.position = "bottom") + 
  scale_color_brewer(palette = "Set1") +
    scale_edge_color_continuous(low = "grey80", high = "red")
ggsave(clus.tree.out, filename = paste(dir, "plot_out/NI05/clustree_out.pdf", sep = ""))
clus.tree.out
```

Set resolution and perform clustering
```{r}
res.used <- 0.5
tiss_subset_normalepi <- FindClusters(object = tiss_subset_normalepi, verbose = T, resolution = res.used)
```

Perform  tSNE
```{r}
tiss_subset_normalepi <- RunTSNE(object = tiss_subset_normalepi, dims.use = 1:n.pcs, seed.use = 10)
```

Visualize TSNE colroed by cluster
```{r}
pdf(file = paste(dir, "plot_out/NI05/nontumor_epi_tsne.pdf", sep = ""))
DimPlot(object = tiss_subset_normalepi, reduction = 'tsne')
dev.off()
```

<!-- Find which cluster G22_B003776 is found in -->
<!-- ```{r} -->
<!-- grep(x = tiss_subset_normalepi@meta.data$cell_id, pattern = "G22_B003776") #480th row -->
<!-- tiss_subset_normalepi@meta.data[480,] # found in cluster 3 -->
<!-- ``` -->

Cluster Occ by patient
```{r}
# Calculate mixing score for each cluster 
tab.1 <- table(tiss_subset_normalepi@meta.data$patient_id, tiss_subset_normalepi@meta.data$seurat_clusters)
occ_score <- apply(tab.1, 2, max)/colSums(tab.1)
# Plot mixing score
pdf(file = paste(dir, "plot_out/NI05/clusocc_bargraph.pdf", sep = ""))
par(las=3);barplot(sort(occ_score), xlab="Cluster", ylab="Patient max Ncells/Total cells", ylim=c(0,1));abline(h=0.7, col="red")
dev.off()
```

Compare cluster occ of normal epi to tumor
```{r}
# noraml
tab.1 <- table(tiss_subset_normalepi@meta.data$patient_id, tiss_subset_normalepi@meta.data$seurat_clusters)
occ_score <- apply(tab.1, 2, max)/colSums(tab.1)
normal_occ <- as.data.frame(occ_score)
normal_occ$group <- "normal"
colnames(normal_occ) <- c("score", "group")

# tumor
tab.2 <- table(tiss_subset_tumor2@meta.data$patient_id, tiss_subset_tumor2@meta.data$seurat_clusters)
occ_score2 <- apply(tab.2, 2, max)/colSums(tab.2)
tumor_occ <- as.data.frame(occ_score2)
tumor_occ$group <- "tumor"
colnames(tumor_occ) <- c("score", "group")

occ_combo <- rbind(normal_occ, tumor_occ)

occ_changes <- ggplot(occ_combo,aes(x=score)) + 
    # geom_histogram(data=subset(occ_combo, group == 'normal'),fill = "blue", alpha = 0.2, bins = 5) +
    # geom_histogram(data=subset(occ_combo, group == 'tumor'),fill = "red", alpha = 0.2, bins = 5) +
    geom_density(data=subset(occ_combo, group == 'normal'), size = 1.5, colour = "blue") + 
    geom_density(data=subset(occ_combo, group == 'tumor'), size = 1.5, colour = "red")

ggsave(occ_changes, filename = paste(dir, "plot_out/NI05/NI05_occ_changes_tumor_nontumor.pdf", sep = ""), width = 10, height = 10)
```

Find markers for each cluster
```{r}
unique(tiss_subset_normalepi@active.ident)
tiss.markers.epi <- FindAllMarkers(object = tiss_subset_normalepi, only.pos = TRUE, min.pct = 0.25, thresh.use = 0.25)
```

Write differential gene table
```{r}
write.csv(tiss.markers.epi, file = paste(dir, "data_out/NI05/NI05_DE_epithelial.csv", sep = ""))
```

Display the top markers you computed above.
```{r}
tiss.markers.epi %>% group_by(cluster) %>% top_n(20, avg_logFC)
#cluster 5 mesenchyme?

```

Create dotplots of the top markers displayed above
```{r}
markers.small  <- tiss.markers.epi %>% group_by(cluster) %>% top_n(5, avg_logFC)
genes_to_check <- markers.small$gene
DotPlot(object = tiss_subset_normalepi, features = genes_to_check) + coord_flip()
```

ID cell types using cell markers
```{r}
# Cell markers
s.muscle <- c('CNN1','SUSD5','ACTC1','ASB2','KCNA5','LDB3','MYOCD','ELN','ACTG2','ACTA2')
neuro.e <- c('RESP18','NOV','SCG5','NNAT','CALCA','PTPRN','SLC35D3','ASCL1','CHGA')
glial <- c('KCNA1','CDH19','SOX10','GFRA3','PLP1','GPR37L1','ART3','RASGEF1C','KCNA6','GFAP')
club <- c('GABRP','CCKAR','HP','KCNK2','UPK3A','CLDN10','PON1','SCGB1A1','BPIFB1','MUC5B')
ciliated <- c('CDHR3','FOXJ1','RGS22','MAPK15','SPEF2','CCDC153')
at2 <- c('NAPSA','CHIA','SFTPC','SFTPB','MUC1','SFTPA1','SFTPA2')
at1 <- c('IGFBP2','COL4A3','PDPN','AGER','CAV1','CDKN2B','RTKN2')
ionocytes <- c('ATP6V1C2','ATP6V0D2','CFTR','FOXI1','ASCL3')
basal <- c('KRT17','KRT5','SYT8','FHL2','MMP1')
heptaocyte <- c('ALB')
all_epi_markers <- c(s.muscle, neuro.e, glial, club, ciliated, at2, at1, basal, heptaocyte)
pdf(file = paste(dir,"plot_out/NI05/dotplotepimarkers.pdf", sep = ""))
DotPlot(object = tiss_subset_normalepi, features = all_epi_markers) + coord_flip()
dev.off()

DotPlot(object = tiss_subset_normalepi, features = s.muscle) + coord_flip() # none
DotPlot(object = tiss_subset_normalepi, features = neuro.e) + coord_flip() # 10
DotPlot(object = tiss_subset_normalepi, features = glial) + coord_flip() # none
DotPlot(object = tiss_subset_normalepi, features = club) + coord_flip() # 4?
DotPlot(object = tiss_subset_normalepi, features = ciliated) + coord_flip() #9
DotPlot(object = tiss_subset_normalepi, features = at2) + coord_flip() # 0, 1, 3, 13
DotPlot(object = tiss_subset_normalepi, features = at1) + coord_flip() #2
DotPlot(object = tiss_subset_normalepi, features = ionocytes) + coord_flip() #12
DotPlot(object = tiss_subset_normalepi, features = basal) + coord_flip() #14
DotPlot(object = tiss_subset_normalepi, features = heptaocyte) + coord_flip() #7
```

Create table of how many cells belong to each cluster assignment
```{r}
table(tiss_subset_normalepi@meta.data$seurat_clusters)
```

Set Metadata Column for Cluster IDs
```{r}
tiss_subset_normalepi@meta.data$normalepi_seurat_cluster <- tiss_subset_normalepi@meta.data$seurat_clusters
```

Annotate the normal epi cells
```{r}
# enumerate current cluster IDs and the labels for them
cluster.ids <- c(0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15)
annotation <- c("alveolar type 2 cell", "alveolar type 2 cell", "alveolar type 1 cell", "alveolar type 2 cell", "club cell", "unknown stroma1", 
                "unknown stroma2", "hepatocyte", "unknown stroma3", "ciliated cell", "neuro.e cell",
                "unknown stroma4", "ionocyte", "alveolar type 2 cell", "basal cell", "unknown stroma5")

tiss_subset_normalepi@meta.data[,'norm_epi_annotation'] <- plyr::mapvalues(x = tiss_subset_normalepi@meta.data$seurat_clusters, from = cluster.ids, to = annotation)

# save annotation column with cell_id
write.csv(tiss_subset_normalepi@meta.data[, c("cell_id", "norm_epi_annotation")], paste(dir, "data_out/NI05/NI05_norm_epi_annotations.csv", sep = ""))
```

Plot tSNE with annoations
```{r}
pdf(file = paste(dir, "plot_out/NI05/NI05_norm_epi_annotated_tsne.csv", sep = ""))
TSNEPlot(object = tiss_subset_normalepi, group.by='norm_epi_annotation')
dev.off()
TSNEPlot(object = tiss_subset_normalepi, group.by='biopsy_site')
```

Save object
```{r}
save(tiss_subset_normalepi, file = paste(dir, "Data_input/objects/NI05_normalepi_seurat_object_annotated.RData", sep = ""))
# load(file = paste(dir, "Data_input/objects/NI03_epithelial_annotated_tumor.RData", sep = ""))
```

save normal epi annotations to all epi seurat object
```{r}
tiss_nonimmune_epi@meta.data <- left_join(tiss_nonimmune_epi@meta.data, tiss_subset_normalepi@meta.data[,c("cell_id", "norm_epi_annotation")])

rownames(tiss_nonimmune_epi@meta.data) <- tiss_nonimmune_epi@meta.data$cell_id

tiss_nonimmune_epi@meta.data$epi_anno_final <- tiss_nonimmune_epi@meta.data$norm_epi_annotation

# replace na with tumor
tiss_nonimmune_epi@meta.data$epi_anno_final <- as.character(tiss_nonimmune_epi@meta.data$epi_anno_final)

table(is.na(tiss_nonimmune_epi@meta.data$epi_anno_final))

tiss_nonimmune_epi@meta.data$epi_anno_final[is.na(tiss_nonimmune_epi@meta.data$epi_anno_final)] <- "tumor"
table(tiss_nonimmune_epi@meta.data$epi_anno_final)

save(tiss_nonimmune_epi, file = paste(dir, "Data_input/objects/NI05_all_epithelial_annotated_normal_and_tumor.RData", sep = ""))
# load(paste(dir,"Data_input/objects/NI05_all_epithelial_annotated_normal_and_tumor.RData", sep = ""))
```


```{r}
# Barplot of all epi cell counts 
table.temp <- as.data.frame(table(tiss_nonimmune_epi@meta.data$epi_anno_final))

table(is.na(tiss_nonimmune_epi@meta.data$epi_anno_final))

table.temp$Var1 <- factor(table.temp$Var1,levels = as.character(table.temp$Var1[order(table.temp$Freq,decreasing=F)]))

p <-  ggplot(data = table.temp, aes(x = Var1, y = Freq, fill = Var1)) + geom_bar(stat ="identity") + coord_flip() + theme(legend.position = "none") 

ggsave(plot = p, paste(dir,"plot_out/NI05/epi_cell_counts.pdf", sep=""), width = 90, height = 90, units = "mm")
```

```{r}
#set levels for plotting
tiss_nonimmune_epi@meta.data$epi_anno_final <- factor(tiss_nonimmune_epi@meta.data$epi_anno_final, levels = c("unknown stroma5", "basal cell", "ionocyte", "unknown stroma4", "neuro.e cell", "ciliated cell", "unknown stroma3", "hepatocyte", "unknown stroma2", "unknown stroma1", "club cell", "alveolar type 1 cell", "alveolar type 2 cell", "tumor"))

table(tiss_nonimmune_epi@meta.data$epi_anno_final)

p1 <- ggplot(tiss_nonimmune_epi@meta.data, aes(x = epi_anno_final, y = nFeature_RNA)) + geom_boxplot(aes(fill = epi_anno_final)) + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + theme(legend.position = "none") + coord_flip()

ggsave(plot = p1, paste(dir,"plot_out/NI05/epi_cell_nGenes.pdf", sep=""), width = 90, height = 90, units = "mm")
```


