---
title: "DE Analysis by Response"
output: html_notebook
---

```{r}
library(Seurat)
library(ggplot2)
library(tidyverse)
library(fgsea)
library(gridExtra)
library(devtools)
library(DT)
require(corrplot)
library(clustree)
library(ggsignif)
library(ggpubr)
library(viridis)
library(plotly)
library(ggridges)
library(reshape)
```

Read in tumor object
```{r}
# rm(list=ls())
dir <- "/myVolume/scell_lung_adenocarcinoma/"
load(file = paste(dir, "Data_input/NI04_tumor_seurat_object.RData", sep = ""))
```

Seurat Function for IPA Analysis
```{r}
seurat.to.ipa <- function(df, score.column, divide.by.column, gene.column, divide.append) {
  # Find appropriate columns in DE output 
  col.1 <- which(colnames(df)==divide.by.column)
  col.2 <- which(colnames(df)==score.column)
  col.3 <- which(colnames(df)==gene.column)
  # Create new table
  tab.temp <- matrix(nrow=length(unique(df[,col.3])), ncol=length(unique(df[,col.1])), 0)
  # Set colnames 
  colnames(tab.temp) <- unique(df[,col.1])
  # Set townames 
  row.names(tab.temp) <- as.character(unique(df[,col.3]))
  # Populate values 
    for(i in 1:nrow(tab.temp)){
      temp <- df[as.character(df[,col.3]) %in% row.names(tab.temp)[i] ,]
        for(j in 1:nrow(temp)){
          col.to <- which(colnames(tab.temp)==as.character(temp[j,col.1]))
          tab.temp[i,col.to] <- temp[j,col.2]
        }
    }
  # Set colnames 
  colnames(tab.temp) <- paste(divide.append, colnames(tab.temp), sep="_")
  return(tab.temp)
}
```

Calculate the DE genes for every tumor cluster
```{r}
de_by_cluster <- FindAllMarkers(tiss_subset_tumor)
write.csv(de_by_cluster, file = paste(dir, "data_out/NI07/NI07_tumor_clusters_DEgenes.csv", sep = ""))
```

Calculate the DE genes between different treatment responses (naive, grouped_pr and grouped_pd)
```{r}
# set the ident of the object to the "analysis" column
unique(tiss_subset_tumor@ident) # check current ident
tiss_subset_tumor <- SetIdent(tiss_subset_tumor, ident.use = tiss_subset_tumor@meta.data$analysis)
unique(tiss_subset_tumor@ident) # check current ident

# find diff. expressed genes with wilcox test
analysis_markers <- FindAllMarkers(tiss_subset_tumor)
write.csv(analysis_markers, file = paste(dir, "data_out/NI07/NI07_response_group_DEgenes.csv", sep = ""))

# Group the DE genes and add the number of patients with nonzero expressing cells and the highest contributing patient's occupancy
groups <- as.character(unique(analysis_markers$cluster))
for(i in 1:nrow(analysis_markers)){
  message(paste(round(i/nrow(analysis_markers),2)*100,"% of genes completed"))
  gene <- as.character(analysis_markers$gene)[i]
  gene.vec <- tiss_subset_tumor@data[gene,]
    for(j in 1:length(groups)){
      cells <- row.names(tiss_subset_tumor@meta.data)[which(tiss_subset_tumor@meta.data$analysis==groups[j])]
      all.no.zero.cells <- names(which(gene.vec[cells] !=0 )) # Set threshold
      tab.1 <- table(as.character(tiss_subset_tumor@meta.data[all.no.zero.cells,"patient_id"]))
      high.pat.per <- tab.1[which(tab.1==max(tab.1))[1]]/length(all.no.zero.cells)
      all.pat.length <- length(tab.1)
      analysis_markers[i,paste(groups[j],"pt.occupancy")] <- high.pat.per
      analysis_markers[i,paste(groups[j],"n.nonzero.pts")] <- all.pat.length
    }
}
write.csv(analysis_markers, file = paste(dir, "data_out/NI07/NI07_response_group_DEgenes_with_pt_occ.csv", sep = ""))

# Look at top 20 mutations for each group
markers.small  <- analysis_markers %>% group_by(cluster) %>% top_n(50, -p_val_adj)
markers.small
```

Break markers.medium into analysis groups
```{r}
markers.small.pd <- filter(markers.small, cluster == "grouped_pd") 
markers.small.pd.genes <- as.character(markers.small.pd$gene)

markers.small.pr <- filter(markers.small, cluster == "grouped_pr") 
markers.small.pr.genes <- as.character(markers.small.pr$gene)

markers.small.naive <- filter(markers.small, cluster == "naive") 
markers.small.naive.genes <- as.character(markers.small.naive$gene)
```


Top PD genes breakdown
```{r}
pd.de.genes <- FetchData(tiss_subset_tumor, c(markers.small.pd.genes, 'nGene','nReads','analysis','patient_id', 'sample_name', 'biopsy_site', 'pfs_over_under'))
colnames(tiss_subset_tumor@meta.data)
pd.de.genes1 <- colnames(pd.de.genes)[c(1:50)]
temp <- pd.de.genes[,c(grep("nGene", colnames(pd.de.genes)):ncol(pd.de.genes))]

# Plot jitter plot of PD vs PR vs naive for top 50 DE genes
pd.plot.lists.box <- list()
for(i in pd.de.genes1){
  a <- as.data.frame(pd.de.genes[,i])
  colnames(a) <- "gene"
  temp.1 <- cbind(a, temp) ; rm(a)
  pd.plot.lists.box[[i]] <- ggplot(temp.1, aes(x = analysis, y = gene, fill = analysis)) + geom_jitter(aes(colour = analysis), alpha = 1/4) + ggtitle(i)
}

# Plot jitter plot/boxplot of PD vs PR vs naive for top 50 DE genes by patient
pd.plot.lists.pt.box <- list()
for(i in pd.de.genes1){
  a <- as.data.frame(pd.de.genes[,i])
  colnames(a) <- "gene"
  temp.2 <- cbind(a, temp) ; rm(a)
  pd.plot.lists.pt.box[[i]] <- ggplot(temp.2, aes(x = analysis, y = gene, color = patient_id, fill = patient_id))  + 
      geom_point(position = position_jitterdodge(dodge.width=0.9)) +
      geom_boxplot(fill = "white", outlier.colour = NA, position = position_dodge(width=0.9)) +
      xlab("Group") +
      ylab(paste(i,"Gene Expression")) +
      guides(colour = FALSE) +
      guides(fill = FALSE) + 
      ggtitle(i)
}

# Plot ridge plot of PD vs PR vs naive for top 50 DE genes
pd.plot.lists.ridge <- list()
for(i in pd.de.genes1){
  a <- as.data.frame(pd.de.genes[,i])
  colnames(a) <- "gene"
  temp.3 <- cbind(a, temp) ; rm(a)
  pd.plot.lists.ridge[[i]] <- ggplot(temp.3, aes(x = gene, y = analysis, fill = analysis)) + geom_density_ridges() + ylab("Group") + xlab(paste(i,"Gene Expression")) + ggtitle(paste(i,"Expression per Group")) + guides(colour = FALSE, fill = FALSE)
}

# Plot ridge plot of PD vs PR vs naive for top 50 DE genes by patient
pd.plot.lists.ridge.pt <- list()
for(i in pd.de.genes1){
  a <- as.data.frame(pd.de.genes[,i])
  colnames(a) <- "gene"
  temp.4 <- cbind(a, temp) ; rm(a)
  pd.plot.lists.ridge.pt[[i]] <- ggplot(temp.4, aes(x = gene, y = analysis, fill = patient_id)) + geom_density_ridges(alpha=1/2) + ylab("Group") + xlab(paste(i,"Gene Expression")) + ggtitle(paste(i,"Expression per Group")) + guides(colour = FALSE, fill = FALSE)
}
pd.plot.lists.ridge.pt[1]
```

Top PR DE Genes breakdown
```{r}
pr.de.genes <- FetchData(tiss_subset_tumor, c(markers.small.pr.genes, 'nGene','nReads','analysis','patient_id', 'sample_name', 'biopsy_site'))

pr.de.genes1 <- colnames(pr.de.genes)[c(1:50)]
temp <- pr.de.genes[,c(grep("nGene", colnames(pr.de.genes)):ncol(pr.de.genes))]


# Plot jitter plot of pr vs PR vs naive for top 50 DE genes
pr.plot.lists.box <- list()
for(i in pr.de.genes1){
  a <- as.data.frame(pr.de.genes[,i])
  colnames(a) <- "gene"
  temp.1 <- cbind(a, temp) ; rm(a)
  pr.plot.lists.box[[i]] <- ggplot(temp.1, aes(x = analysis, y = gene, fill = analysis)) + geom_jitter(aes(colour = analysis), alpha = 1/4) + ggtitle(i)
}

# Plot jitter plot/boxplot of pr vs PR vs naive for top 50 DE genes by patient
pr.plot.lists.pt.box <- list()
for(i in pr.de.genes1){
  a <- as.data.frame(pr.de.genes[,i])
  colnames(a) <- "gene"
  temp.2 <- cbind(a, temp) ; rm(a)
  pr.plot.lists.pt.box[[i]] <- ggplot(temp.2, aes(x = analysis, y = gene, color = patient_id, fill = patient_id))  + 
      geom_point(position = position_jitterdodge(dodge.width=0.9)) +
      geom_boxplot(fill = "white", outlier.colour = NA, position = position_dodge(width=0.9)) +
      xlab("Group") +
      ylab(paste(i,"Gene Expression")) +
      guides(colour = FALSE) +
      guides(fill = FALSE) + 
      ggtitle(i)
}

# Plot ridge plot of pr vs PR vs naive for top 50 DE genes
pr.plot.lists.ridge <- list()
for(i in pr.de.genes1){
  a <- as.data.frame(pr.de.genes[,i])
  colnames(a) <- "gene"
  temp.3 <- cbind(a, temp) ; rm(a)
  pr.plot.lists.ridge[[i]] <- ggplot(temp.3, aes(x = gene, y = analysis, fill = analysis)) + geom_density_ridges() + ylab("Group") + xlab(paste(i,"Gene Expression")) + ggtitle(paste(i,"Expression per Group")) + guides(colour = FALSE, fill = FALSE)
}

# Plot ridge plot of pr vs PR vs naive for top 50 DE genes by patient
pr.plot.lists.ridge.pt <- list()
for(i in pr.de.genes1){
  a <- as.data.frame(pr.de.genes[,i])
  colnames(a) <- "gene"
  temp.4 <- cbind(a, temp) ; rm(a)
  pr.plot.lists.ridge.pt[[i]] <- ggplot(temp.4, aes(x = gene, y = analysis, fill = patient_id)) + geom_density_ridges(alpha=1/2) + ylab("Group") + xlab(paste(i,"Gene Expression")) + ggtitle(paste(i,"Expression per Group")) + guides(colour = FALSE, fill = FALSE)
}

pr.plot.lists.ridge.pt[1]
```

Top Naive DE Genes breakdown
```{r}
naive.de.genes <- FetchData(tiss_subset_tumor, c(markers.small.naive.genes, 'nGene','nReads','analysis','patient_id', 'sample_name', 'biopsy_site'))

naive.de.genes1 <- colnames(naive.de.genes)[c(1:50)]
temp <- naive.de.genes[,c(grep("nGene", colnames(naive.de.genes)):ncol(naive.de.genes))]


# Plot jitter plot of naive vs naive vs naive for top 50 DE genes
naive.plot.lists.box <- list()
for(i in naive.de.genes1){
  a <- as.data.frame(naive.de.genes[,i])
  colnames(a) <- "gene"
  temp.1 <- cbind(a, temp) ; rm(a)
  naive.plot.lists.box[[i]] <- ggplot(temp.1, aes(x = analysis, y = gene, fill = analysis)) + geom_jitter(aes(colour = analysis), alpha = 1/4) + ggtitle(i)
}

# Plot jitter plot/boxplot of naive vs naive vs naive for top 50 DE genes by patient
naive.plot.lists.pt.box <- list()
for(i in naive.de.genes1){
  a <- as.data.frame(naive.de.genes[,i])
  colnames(a) <- "gene"
  temp.2 <- cbind(a, temp) ; rm(a)
  naive.plot.lists.pt.box[[i]] <- ggplot(temp.2, aes(x = analysis, y = gene, color = patient_id, fill = patient_id))  + 
      geom_point(position = position_jitterdodge(dodge.width=0.9)) +
      geom_boxplot(fill = "white", outlier.colour = NA, position = position_dodge(width=0.9)) +
      xlab("Group") +
      ylab(paste(i,"Gene Expression")) +
      guides(colour = FALSE) +
      guides(fill = FALSE) + 
      ggtitle(i)
}

# Plot ridge plot of naive vs naive vs naive for top 50 DE genes
naive.plot.lists.ridge <- list()
for(i in naive.de.genes1){
  a <- as.data.frame(naive.de.genes[,i])
  colnames(a) <- "gene"
  temp.3 <- cbind(a, temp) ; rm(a)
  naive.plot.lists.ridge[[i]] <- ggplot(temp.3, aes(x = gene, y = analysis, fill = analysis)) + geom_density_ridges() + ylab("Group") + xlab(paste(i,"Gene Expression")) + ggtitle(paste(i,"Expression per Group")) + guides(colour = FALSE, fill = FALSE)
}

# Plot ridge plot of naive vs naive vs naive for top 50 DE genes by patient
naive.plot.lists.ridge.pt <- list()
for(i in naive.de.genes1){
  a <- as.data.frame(naive.de.genes[,i])
  colnames(a) <- "gene"
  temp.4 <- cbind(a, temp) ; rm(a)
  naive.plot.lists.ridge.pt[[i]] <- ggplot(temp.4, aes(x = gene, y = analysis, fill = patient_id)) + geom_density_ridges(alpha=1/2) + ylab("Group") + xlab(paste(i,"Gene Expression")) + ggtitle(paste(i,"Expression per Group")) + guides(colour = FALSE, fill = FALSE)
}

naive.plot.lists.ridge.pt[1]

```




library(gridExtra)
pdf("/myVolume/plot_out/test.pdf", onefile = TRUE)
marrangeGrob(grobs=pr.plot.lists.ridge.pt, nrow=2, ncol=2)
dev.off()

marrangeGrob


n <- length(pr.plot.lists.ridge.pt)
nCol <- 5
nRow <- 10
do.call("grid.arrange", c(pr.plot.lists.ridge.pt, ncol=nCol, nrow=nRow))

dev.off()