---
title: "Plotting Gene Signatures and DE Genes"
output: html_notebook
---

```{r}
library(Seurat)
library(ggplot2)
library(tidyverse)
library(gridExtra)
library(devtools)
library(ggsignif)
library(ggpubr)
library(viridis)
library(plotly)
library(ggridges)
library(reshape)
library(gridExtra)
library(ggrepel)
library(ggExtra)
```

Read in tumor object
```{r}
# rm(list=ls())
dir <- "/myVolume/scell_lung_adenocarcinoma/"
load(file = paste(dir, "Data_input/objects/NI04_tumor_seurat_object.RData", sep = ""))
load(file = paste(dir, "Data_input/objects/Immuune_Seurat_object.RData", sep = ""))
load(file = paste(dir, "Data_input/S03_Main_Seurat_object_filtered_and_subset.RData", sep = ""))
load(file = paste(dir, "Data_input/objects/NI05_all_epithelial_annotated_normal_and_tumor.RData"))
```

AT2 Sig Plotting
```{r}
# Visualize the AT2 Differentiation Signature (PMCID: PMC2644235)
AT2_genes <- c("SFTPC", "SFTPB", "SFTPD", "PGC", "CLDN18", "AQP4", "SCGB3A1", "ABCA3", "GATA6", "NKX2-1", "SFTA3", "IGFBP2", "HOPX", "NAPSA", "FOXA2", "AGER", "LAMP1")

# make a heatmap
pdf(file = paste(dir, "plot_out/NI10/AT2_Sig_heatmap.pdf", sep = ""))
DoHeatmap(tiss_subset_tumor2, genes.use = AT2_genes, slim.col.label = TRUE, use.scaled = TRUE, group.order = c("naive","grouped_pr","grouped_pd"))
dev.off()

# Fetch Data for AT2 Sig in Tumor Cells
AT2_diff <- FetchData(tiss_subset_tumor2, c(AT2_genes, 'nGene','nReads','analysis','patient_id','sample_name','biopsy_site', 'cell_id'))
AT2_diff$AT2_diff_mean <- rowMeans(AT2_diff[c(AT2_genes)], na.rm=TRUE)
AT2_diff$cell_name <- rownames(AT2_diff)
AT2_diff$group <- "tumor"
```

```{r}
# Fetch Data for AT2 Sig in Normal AT2 Cells
table(tiss_nonimmune_epi@meta.data$epi_anno_final) #434 AT2 cells
normal_at2 <- filter(tiss_nonimmune_epi@meta.data, epi_anno_final == "alveolar type 2 cell")
normal_at2_sub <- SubsetData(tiss_nonimmune_epi, cells.use = normal_at2$cell_id)
Norm_at2 <- FetchData(normal_at2_sub, c(AT2_genes, 'nGene', 'nReads', 'analysis', 'patient_id', 'sample_name', 'biopsy_site', 'cell_id'))
Norm_at2$cell_name <- rownames(Norm_at2)
Norm_at2$AT2_diff_mean <- rowMeans(Norm_at2[c(AT2_genes)], na.rm=TRUE)
Norm_at2$group <- "normal"
table(Norm_at2$analysis) # PD = 80, PER = 245, TN = 109
```

combine normal and tumor cell tables
```{r}
Norm_at2_1 <- Norm_at2
# replace analysis group with normal at2
Norm_at2_1$analysis <- "Normal AT2"
# combine tables
AT2_combine <- rbind(Norm_at2_1, AT2_diff)
```

Plot AT2 Sig across all comparisions
```{r}
# look for differences in AT2 Sig within tumor among analysis groups (TN, PER, PD) no Normal
AT2_diff_test <- pairwise.wilcox.test(x = AT2_combine$AT2_diff_mean, g = AT2_combine$analysis)
AT2_diff_test <- as.data.frame(AT2_diff_test$p.value)

# plot
AT2_combine_p1 <- ggplot(AT2_combine, aes(x = analysis, y = AT2_diff_mean, fill = analysis)) + geom_boxplot() + guides(colour = FALSE, fill = FALSE) + xlab("Group") + ylab("AT2 Differentiation Signature Expression per Group") + ggtitle("AT2 Differentiation Signature Expression per Group") + geom_signif(comparisons = list(c("grouped_pd", "grouped_pr")), map_signif_level=TRUE, y_position = 5, annotations = '1.40e-235') + geom_signif(comparisons = list(c("grouped_pd", "naive")), map_signif_level=TRUE, y_position = 7, annotations = '1.06e-173') + geom_signif(comparisons = list(c("grouped_pr", "naive")), map_signif_level=TRUE, y_position = 6, annotations = '6.90e-138') + geom_signif(comparisons = list(c("Normal AT2", "grouped_pr")), map_signif_level=TRUE, y_position = 8, annotations = '3.29e-155') + scale_x_discrete(limits=c("Normal AT2", "naive", "grouped_pr", "grouped_pd"))

ggsave(AT2_combine_p1, filename = paste(dir, "plot_out/NI10/AT2_pertumor_v_normal_box.pdf", sep = ""), height = 5, width = 5)
```

```{r}
# Lung Only Tumor Cells no Normal
AT2_lung_only <- filter(AT2_combine, AT2_combine$biopsy_site == 'Lung')
rownames(AT2_lung_only) <- AT2_lung_only$cell_id

AT2_diff_test.1 <- pairwise.wilcox.test(x = AT2_lung_only$AT2_diff_mean, g = AT2_lung_only$analysis)
AT2_diff_test.1 <- as.data.frame(AT2_diff_test.1$p.value)

AT2_combine_p2 <- ggplot(AT2_lung_only, aes(x = analysis, y = AT2_diff_mean, fill = analysis)) + geom_boxplot() + guides(colour = FALSE, fill = FALSE) + xlab("Group") + ylab("AT2 Differentiation Signature Expression per Group") + ggtitle("AT2 Differentiation Signature Expression per Group (Lung)") + geom_signif(comparisons = list(c("grouped_pd", "grouped_pr")), map_signif_level=TRUE, y_position = 5, annotations = '4.84-18') + geom_signif(comparisons = list(c("grouped_pd", "naive")), map_signif_level=TRUE, y_position = 7, annotations = '8.71e-14') + geom_signif(comparisons = list(c("grouped_pr", "naive")), map_signif_level=TRUE, y_position = 6, annotations = '3.43e-109') + geom_signif(comparisons = list(c("Normal AT2", "grouped_pr")), map_signif_level=TRUE, y_position = 8, annotations = '2.96-150') + scale_x_discrete(limits=c("Normal AT2", "naive", "grouped_pr", "grouped_pd"))

ggsave(AT2_combine_p2, filename = paste(dir, "plot_out/NI10/AT2_pertumor_v_normal_box_lungonly.pdf", sep = ""), height = 5, width = 5)
```

```{r}
AT2_combine_seurat <- SubsetData(tiss_nonimmune_epi, cells.use = c(AT2_combine$cell_id))
```

Find DE genes between PER tumor cells and AT2 normal cells
```{r}
# make sure these agree
tumor <- filter(tiss_nonimmune_epi@meta.data, epi_anno_final == "tumor")
setdiff(tumor$cell_id, tiss_subset_tumor2@meta.data$cell_id)

tumor_pr <- filter(tiss_nonimmune_epi@meta.data, epi_anno_final == "tumor", analysis == "grouped_pr")

at2_normal <- filter(tiss_nonimmune_epi@meta.data, epi_anno_final == "alveolar type 2 cell")

at2_normal_and_tumor1 <- SubsetData(tiss_nonimmune_epi, cells.use = c(tumor_pr$cell_id, at2_normal$cell_id))
table(at2_normal_and_tumor1@meta.data$epi_anno_final)
at2_normal_and_tumor1 <- SetAllIdent(at2_normal_and_tumor1, id = "epi_anno_final")
table(at2_normal_and_tumor1@ident)
at2_normal_and_tumor1_DE <- FindAllMarkers(at2_normal_and_tumor1)

write.csv(x = at2_normal_and_tumor1_DE, file = paste(dir, "data_out/NI10/at2_normal_vsPERtumor.csv", sep = ""))

table(at2_normal_and_tumor1_DE$cluster)
at2_list <- filter(at2_normal_and_tumor1_DE, cluster == "alveolar type 2 cell")
at2_list.1 <- at2_list[order(at2_list$avg_logFC, decreasing = TRUE), ]

tumor_list <- filter(at2_normal_and_tumor1_DE, cluster == "tumor")
tumor_list.1 <- tumor_list[order(tumor_list$avg_logFC, decreasing = TRUE), ]

pdf(file = paste(dir, "plot_out/NI10/AT2_topDE_heatmap.pdf", sep = ""))
DoHeatmap(at2_normal_and_tumor1, genes.use = c(at2_list.1$gene[1:25], tumor_list.1$gene[1:25]), slim.col.label = TRUE)
dev.off()

pdf(file = paste(dir, "plot_out/NI10/AT2_topDE_bypval_heatmap.pdf", sep = ""))
DoHeatmap(at2_normal_and_tumor1, genes.use = at2_normal_and_tumor1_DE$gene[1:10], slim.col.label = TRUE)
dev.off()

pdf(file = paste(dir, "plot_out/NI10/AT2_AT2genesig_heatmap.pdf", sep = ""))
DoHeatmap(at2_normal_and_tumor1, genes.use = AT2_genes, slim.col.label = TRUE)
dev.off()
```

AT2 Normal + PER Tumor Cells Clustered Alone
```{r}
# Find variable genes
at2_normal_and_tumor1 <- FindVariableGenes(object = at2_normal_and_tumor1, do.plot = TRUE, x.high.cutoff = Inf, y.cutoff = 0.5)

# Perform PCA
at2_normal_and_tumor1 <- RunPCA(object = at2_normal_and_tumor1, do.print = FALSE)
at2_normal_and_tumor1 <- ProjectPCA(object = at2_normal_and_tumor1, do.print = FALSE)

# Visualize top genes in principal components
PCHeatmap(object = at2_normal_and_tumor1, pc.use = 1:6, cells.use = 100, do.balanced = TRUE, label.columns = FALSE, num.genes = 20)

# Also visaulize PC variance
PCElbowPlot(object = at2_normal_and_tumor1)

# Choose the number of principal components to use.
n.pcs = 15

# Set different resolutions 
res.used <- seq(0.1,1,by=0.2)

# Loop over and perform clustering of different resolutions 
for(i in res.used){
at2_normal_and_tumor1 <- FindClusters(object = at2_normal_and_tumor1, reduction.type = "pca", dims.use = 1:n.pcs, 
    resolution = i, print.output = 0, save.SNN = TRUE, k.param = 10, force.recalc = T)}
# Make Plot
clus.tree.out <- clustree(at2_normal_and_tumor1, layout="sugiyama") +
    theme(legend.position = "bottom") + 
  scale_color_brewer(palette = "Set1") +
    scale_edge_color_continuous(low = "grey80", high = "red")
clus.tree.out

# Set resolution and perform clustering
res.used <- 0.25
at2_normal_and_tumor1 <- FindClusters(object = at2_normal_and_tumor1, reduction.type = "pca", dims.use = 1:n.pcs, resolution = res.used, print.output = 0, save.SNN = TRUE, k.param = 10, force.recalc = T)

# Perform  tSNE
at2_normal_and_tumor1 <- RunTSNE(object = at2_normal_and_tumor1, dims.use = 1:n.pcs, seed.use = 10, perplexity=30)

#Visualize TSNE colroed by cluster
at2_normal_and_tumor1 <- SetAllIdent(at2_normal_and_tumor1, id = "epi_anno_final")
table(at2_normal_and_tumor1@ident)

pdf(file = paste(dir, "plot_out/NI10/at2_normal_and_tumor1.pdf", sep = ""))
TSNEPlot(object = at2_normal_and_tumor1, do.label = F)
dev.off()

pdf(file = paste(dir, "plot_out/NI10/at2_normal_and_tumor.pdf", sep = ""))
TSNEPlot(object = at2_normal_and_tumor1, do.label = T)
dev.off()
```

Plasminogen Pathway
```{r}
Plasminogen_genes <- c('ANXA2', 'PLAT', 'PLAU', 'PLAUR', 'SERPINE1')

Plasminogen <- FetchData(tiss_subset_tumor2, c(Plasminogen_genes, 'nGene','nReads','analysis','patient_id','sample_name','biopsy_site'))

Plasminogen$Plasminogen_activating_mean <- rowMeans(Plasminogen[c("ANXA2", "PLAT", "PLAU", "PLAUR")], na.rm=TRUE)
Plasminogen$cell_name <- rownames(Plasminogen)

Plasminogen_test <- pairwise.wilcox.test(x = Plasminogen$Plasminogen_activating_mean, g = Plasminogen$analysis)
Plasminogen_test <- as.data.frame(Plasminogen_test$p.value)

Plasminogen_test1 <- pairwise.wilcox.test(x = Plasminogen$SERPINE1, g = Plasminogen$analysis)
Plasminogen_test1 <- as.data.frame(Plasminogen_test1$p.value)

pdf(file = paste(dir, "plot_out/NI10/Plasminogen_heatmap.pdf", sep = ""))
DoHeatmap(tiss_subset_tumor2, genes.use = Plasminogen_genes, slim.col.label = TRUE, use.scaled = TRUE, group.order = c('naive','grouped_pr','grouped_pd'))
dev.off()

ggplot(Plasminogen, aes(x = ANXA2, y = analysis, fill = sample_name)) + geom_density_ridges(alpha=1/2) + theme(axis.title.y = element_blank()) + xlab("ANXA2 Expression") + guides(colour = FALSE, fill = FALSE) + scale_y_discrete(labels = c("Progressor", "Presister", "Naive"))

ggplot(Plasminogen, aes(x = PLAT, y = analysis, fill = sample_name)) + geom_density_ridges(alpha=1/2) + theme(axis.title.y = element_blank()) + xlab("PLAT Expression") + guides(colour = FALSE, fill = FALSE) + scale_y_discrete(labels = c("Progressor", "Presister", "Naive"))

ggplot(Plasminogen, aes(x = PLAU, y = analysis, fill = sample_name)) + geom_density_ridges(alpha=1/2) + theme(axis.title.y = element_blank()) + xlab("PLAU Expression") + guides(colour = FALSE, fill = FALSE) + scale_y_discrete(labels = c("Progressor", "Presister", "Naive"))

ggplot(Plasminogen, aes(x = SERPINE1, y = analysis, fill = sample_name)) + geom_density_ridges(alpha=1/2) + theme(axis.title.y = element_blank()) + xlab("SERPINE1 Expression") + guides(colour = FALSE, fill = FALSE) + scale_y_discrete(labels = c("Progressor", "Presister", "Naive"))

Plasminogen_act_vln <- ggplot(Plasminogen, aes(x = analysis, y = Plasminogen_activating_mean, fill = analysis)) + geom_boxplot() + xlab("Group") + ylab("Plasminogen Activation") + ggtitle("Plasminogen Activation") + geom_signif(comparisons = list(c("grouped_pd", "grouped_pr")), map_signif_level=TRUE, y_position = 4.5, annotations = '4.63-232') + geom_signif(comparisons = list(c("grouped_pd", "naive")), map_signif_level=TRUE, y_position = 5, annotations = '2.77e-100') + geom_signif(comparisons = list(c("grouped_pr", "naive")), map_signif_level=TRUE, y_position = 4, annotations = '3.41e-111') +   scale_x_discrete(limits=c("naive", "grouped_pr", "grouped_pd")) + theme(legend.position = "none")

Plasminogen_SERPINE1 <- ggplot(Plasminogen, aes(x = analysis, y = SERPINE1, fill = analysis)) + geom_boxplot() + xlab("Group") + ylab("SERPINE1") + ggtitle("SERPINE1") + geom_signif(comparisons = list(c("grouped_pd", "grouped_pr")), map_signif_level=TRUE, y_position = 5.5, annotations = '2.26e-130') + geom_signif(comparisons = list(c("grouped_pd", "naive")), map_signif_level=TRUE, y_position = 6, annotations = '2.57e-136') + geom_signif(comparisons = list(c("grouped_pr", "naive")), map_signif_level=TRUE, y_position = 5, annotations = '4.38e-19') +   scale_x_discrete(limits=c("naive", "grouped_pr", "grouped_pd")) + theme(legend.position = "none")

ggsave(Plasminogen_act_vln, filename = paste(dir, "plot_out/NI10/Plasminogen_act_vln.pdf", sep = ""), height = 5, width = 5)
ggsave(Plasminogen_SERPINE1, filename = paste(dir, "plot_out/NI10/Plasminogen_SERPINE1.pdf", sep = ""), height = 5, width = 5)
```

Kynurenine Pathway
```{r}
Kynurenine_genes <- c('IDO1', 'KYNU', 'QPRT')

Kynurenine <- FetchData(tiss_subset_tumor2, c(Kynurenine_genes, 'nGene','nReads','analysis','patient_id','sample_name','biopsy_site'))

Kynurenine$Kynurenine_mean <- rowMeans(Kynurenine[c("IDO1", "KYNU", "QPRT")], na.rm=TRUE)

Kynurenine$cell_name <- rownames(Kynurenine)

Kynurenine_test <- pairwise.wilcox.test(x = Kynurenine$Kynurenine_mean, g = Kynurenine$analysis)
Kynurenine_test <- as.data.frame(Kynurenine_test$p.value)

pdf(file = paste(dir, "plot_out/NI10/Kynurenine_heatmap.pdf", sep = ""))
DoHeatmap(tiss_subset_tumor2, genes.use = Kynurenine_genes, slim.col.label = TRUE, group.order = c('naive','grouped_pr','grouped_pd'))
dev.off()

ggplot(Kynurenine, aes(x = IDO1, y = analysis, fill = sample_name)) + geom_density_ridges(alpha=1/2) + theme(axis.title.y = element_blank()) + xlab("IDO1 Expression") + guides(colour = FALSE, fill = FALSE) + scale_y_discrete(labels = c("Progressor", "Presister", "Naive"))

ggplot(Kynurenine, aes(x = KYNU, y = analysis, fill = sample_name)) + geom_density_ridges(alpha=1/2) + theme(axis.title.y = element_blank()) + xlab("KYNU Expression") + guides(colour = FALSE, fill = FALSE) + scale_y_discrete(labels = c("Progressor", "Presister", "Naive"))

ggplot(Kynurenine, aes(x = QPRT, y = analysis, fill = sample_name)) + geom_density_ridges(alpha=1/2) + theme(axis.title.y = element_blank()) + xlab("QPRT Expression") + guides(colour = FALSE, fill = FALSE) + scale_y_discrete(labels = c("Progressor", "Presister", "Naive"))

Kynurenine_act_vln <- ggplot(Kynurenine, aes(x = analysis, y = Kynurenine_mean, fill = analysis)) + geom_boxplot() + xlab("Group") + ylab("Kynurenine Activation") + ggtitle("Kynurenine Activation") + geom_signif(comparisons = list(c("grouped_pd", "grouped_pr")), map_signif_level=TRUE, y_position = 3.5, annotations = '2.05e-128') + geom_signif(comparisons = list(c("grouped_pd", "naive")), map_signif_level=TRUE, y_position = 4, annotations = '0.00') + geom_signif(comparisons = list(c("grouped_pr", "naive")), map_signif_level=TRUE, y_position = 3, annotations = '1.74e-47') +   scale_x_discrete(limits=c("naive", "grouped_pr", "grouped_pd")) + theme(legend.position = "none")

ggsave(Kynurenine_act_vln, filename = paste(dir, "plot_out/NI10/Kynurenine_act_vln.pdf", sep = ""), height = 5, width = 5)
```

Gap Junction Signatures
```{r}
GJBs_genes <- c('GJB3', 'GJB2', 'GJB4','GJB5')

GJBs <- FetchData(tiss_subset_tumor2, c(GJBs_genes, 'nGene','nReads','analysis','patient_id','sample_name','biopsy_site'))

GJBs$GJBs_mean <- rowMeans(GJBs[c('GJB3', 'GJB2', 'GJB4','GJB5')], na.rm=TRUE)

GJBs$cell_name <- rownames(GJBs)

GJBs_test <- pairwise.wilcox.test(x = GJBs$GJBs_mean, g = GJBs$analysis)
GJBs_test <- as.data.frame(GJBs_test$p.value)

pdf(file = paste(dir, "plot_out/NI10/GJBs_heatmap.pdf", sep = ""))
DoHeatmap(tiss_subset_tumor2, genes.use = GJBs_genes, slim.col.label = TRUE, group.order = c('naive','grouped_pr','grouped_pd'))
dev.off()

GJBs_box <- ggplot(GJBs, aes(x = analysis, y = GJBs_mean, fill = analysis)) + geom_boxplot() + xlab("Group") + ylab("GJBs Activation") + ggtitle("GJBs Activation") + geom_signif(comparisons = list(c("grouped_pd", "grouped_pr")), map_signif_level=TRUE, y_position = 2.2, annotations = '1.06e-189') + geom_signif(comparisons = list(c("grouped_pd", "naive")), map_signif_level=TRUE, y_position = 2.7, annotations = '3.42e-212') + geom_signif(comparisons = list(c("grouped_pr", "naive")), map_signif_level=TRUE, y_position = 1.7, annotations = '2.56e-30') +   scale_x_discrete(limits=c("naive", "grouped_pr", "grouped_pd")) + theme(legend.position = "none")

ggsave(GJBs_box, filename = paste(dir, "plot_out/NI10/GJBs_boxplot.pdf", sep = ""), height = 5, width = 5)
```

VlnPlot for CRABP2
```{r}
CRABP2_analysis <- FetchData(tiss_subset_tumor2, c('CRABP2', 'nGene','nReads','analysis','patient_id','sample_name','biopsy_site', 'cell_id'))

CRABP2_test <- pairwise.wilcox.test(x = CRABP2_analysis$CRABP2, g = CRABP2_analysis$analysis)
CRABP2_test.1 <- as.data.frame(CRABP2_test$p.value)

CRABP2_vln <- ggplot(CRABP2_analysis, aes(x = analysis, y = CRABP2, fill = analysis)) + geom_boxplot() + xlab("Group") + ylab("CRABP2 Expression per Group") + ggtitle("CRABP2 Expression per Group") + geom_signif(comparisons = list(c("grouped_pd", "grouped_pr")), map_signif_level=TRUE, y_position = 4.5, annotations = '3.47e-75') + geom_signif(comparisons = list(c("grouped_pd", "naive")), map_signif_level=TRUE, y_position = 5, annotations = '0.00') + geom_signif(comparisons = list(c("grouped_pr", "naive")), map_signif_level=TRUE, y_position = 4, annotations = '1.66e-84') + scale_x_discrete(limits=c("naive", "grouped_pr", "grouped_pd")) + theme(legend.position = "none")

ggsave(CRABP2_vln, filename = paste(dir, "plot_out/NI10/CRABP2_only_vln.pdf", sep = ""), height = 10, width = 5)
```


Look for Co-expression of genes of interest
```{r}
gene_compare <- FetchData(tiss_subset_tumor2, c('PLAT', 'PLAU', 'ANXA2', 'PLAUR', 'SERPINE1', 'IDO1', 'KYNU', 'nGene', 'nReads', 'analysis', 'patient_id', 'sample_name', 'biopsy_site', 'cell_id'))

p1 <- ggplot(gene_compare, aes(x = PLAU, y = PLAUR)) + geom_point(aes(colour = analysis))
m1 <- ggMarginal(p1, groupColour = TRUE, groupFill = TRUE)
p2 <- ggplot(gene_compare, aes(x = PLAT, y = ANXA2)) + geom_point(aes(colour = analysis))
m2 <- ggMarginal(p2, groupColour = TRUE, groupFill = TRUE)
p3 <- ggplot(gene_compare, aes(x = PLAU, y = SERPINE1)) + geom_point(aes(colour = analysis))
m3 <- ggMarginal(p3, groupColour = TRUE, groupFill = TRUE)
p4 <- ggplot(gene_compare, aes(x = IDO1, y = KYNU)) + geom_point(aes(colour = analysis))
m4 <- ggMarginal(p4, groupColour = TRUE, groupFill = TRUE) #can add histogram with type = "histogram"


ggsave(m1, filename = paste(dir,"plot_out/NI10/PLAUvsPLAUR.pdf", sep = ""))
ggsave(m2, filename = paste(dir,"plot_out/NI10/PLATvsANXA2.pdf", sep = ""))
ggsave(m3, filename = paste(dir,"plot_out/NI10/PLAUvsSERPINE1.pdf", sep = ""))
ggsave(m4, filename = paste(dir,"plot_out/NI10/IDO1vsKYNU.pdf", sep = ""))
```

PD patient only gene compare
```{r}
pd_gene_compare <- filter(gene_compare, analysis == "grouped_pd")

p5 <- ggplot(pd_gene_compare, aes(x = PLAU, y = SERPINE1)) + geom_point(aes(colour = sample_name))
m5 <- ggMarginal(p5, groupColour = TRUE, groupFill = TRUE)
p6 <- ggplot(pd_gene_compare, aes(x = IDO1, y = KYNU)) + geom_point(aes(colour = sample_name))
m6 <- ggMarginal(p6, groupColour = TRUE, groupFill = TRUE)

ggsave(m5, filename = paste(dir,"plot_out/NI10/PLAUvsSERPINE1_pdalone.pdf", sep = ""))
ggsave(m6, filename = paste(dir,"plot_out/NI10/IDO1vsKYNU_pdalone.pdf", sep = ""))
```
