---
title: "Endothelial Subset"
output: html_notebook
---

Libraries
```{r}
library(Seurat)
library(devtools)
library(clustree)
library(tidyverse)
library(gridExtra)
library(ggridges)
library(ggplot2)
library(ggExtra)
library(corrplot)
library(reshape)
```

```{r}
dir <- "/myVolume/scell_lung_adenocarcinoma/"
load(file = paste(dir,"Data_input/NI01_Nonimmune_Seurat_object_annotated.RData", sep=""))
```

Subset fibroblasts
```{r}
endo <- filter(tiss_nonimmune@meta.data, nonimmune_general_annotation == "Endothelial")
endo_sub <- SubsetData(tiss_nonimmune, cells.use = endo$cell_id)
table(endo$nonimmune_general_annotation, endo$analysis)
table(endo$sample_name, endo$analysis)
```

Normalize and scale the data
```{r}
endo_sub <- NormalizeData(object = endo_sub,)
endo_sub <- ScaleData(object = endo_sub)
```

Find variable genes
```{r}
endo_sub <- FindVariableGenes(object = endo_sub, do.plot = TRUE, x.high.cutoff = Inf, y.cutoff = 0.5)
```

Perform PCA
```{r}
endo_sub <- RunPCA(object = endo_sub, do.print = FALSE)
endo_sub <- ProjectPCA(object = endo_sub, do.print = FALSE)
```

Visualize top genes in principal components
```{r}
PCHeatmap(object = endo_sub, pc.use = 1:15, cells.use = 100, do.balanced = TRUE, label.columns = FALSE, num.genes = 10)
```

Perform correlation of PCs and metadata fields
```{r}
pca.obj <- endo_sub@dr$pca
pc.coords <- pca.obj@cell.embeddings
df1 <- endo_sub@meta.data[,c("nGene","nReads","percent.ribo")]
df2 <- pc.coords[,c(1:10)]
cordf12 <- cor(df1,df2)
# Make a correlation plot
corrplot(cordf12, method = "number", main="Correlation of PCs and metadata")
```

Also visaulize PC variance
```{r}
#comp.dev <-pca.obj@sdev
PCElbowPlot(object = endo_sub)
```

Choose the number of principal components to use.

```{r}
n.pcs = 15
```

Check clustering stability at given resolution 
```{r}
# Set different resolutions 
res.used <- seq(0.1,1,by=0.2)
# Loop over and perform clustering of different resolutions 
for(i in res.used){
        endo_sub <- FindClusters(object = endo_sub, reduction.type = "pca", dims.use = 1:n.pcs, 
        resolution = i, print.output = 0, save.SNN = TRUE, k.param = 30, force.recalc = T)
        }
# Make plot 
clus.tree.out <- clustree(endo_sub) +
    theme(legend.position = "bottom") + 
    scale_color_brewer(palette = "Set1") +
    scale_edge_color_continuous(low = "grey80", high = "red")

# Plot 
clus.tree.out
```

Set resolution and perform clustering
```{r}
res.used <- 0.1
endo_sub <- FindClusters(object = endo_sub, reduction.type = "pca", dims.use = 1:n.pcs, 
    resolution = res.used, print.output = 0, save.SNN = TRUE, k.param = 30, force.recalc = T)
```

Perform  tSNE
```{r}
endo_sub <- RunTSNE(object = endo_sub, dims.use = 1:n.pcs, seed.use = 10, perplexity=30)
```

Visualize TSNE colored by cluster
```{r}
TSNEPlot(object = endo_sub, do.label = T)
TSNEPlot(object = endo_sub, group.by = "analysis")
TSNEPlot(object = endo_sub, group.by = "biopsy_site")
```

Fraction of PD
```{r}
tab.1 <- prop.table(table(endo_sub@meta.data$res.0.1, endo_sub@meta.data$analysis), margin = 1)
tab.1 <- melt(tab.1)
tab.1$Var.1 <- as.factor(tab.1$Var.1)
fraction.plot <- ggplot() + geom_bar(aes(y = value, x = Var.1, fill = Var.2), data = tab.1,
                           stat="identity", position='dodge') + coord_flip()
fraction.plot

tab.2 <- prop.table(table(endo_sub@meta.data$res.0.1, endo_sub@meta.data$patient_id), margin = 1)
tab.2 <- melt(tab.2)
tab.2$Var.1 <- as.factor(tab.2$Var.1)
fraction.plot1 <- ggplot() + geom_bar(aes(y = value, x = Var.1, fill = Var.2), data = tab.2,
                           stat="identity") + coord_flip()
fraction.plot1
```

Cluster Occ by patient
```{r}
# Calculate mixing score for each cluster 
tab.3 <- table(endo_sub@meta.data$patient_id, endo_sub@meta.data$res.0.1)
occ_score <- apply(tab.3, 2, max)/colSums(tab.3)
# Plot mixing score
par(las=3);barplot(sort(occ_score), xlab="Cluster", ylab="Patient max Ncells/Total cells", ylim=c(0,1));abline(h=0.7, col="red")
```

```{r}
endo_clus_markers <- FindAllMarkers(endo_sub)
endo_top_10 <- endo_clus_markers %>% group_by(cluster) %>% top_n(20, avg_logFC)
DoHeatmap(endo_sub, genes.use = endo_top_10$gene, slim.col.label = TRUE, use.scaled = FALSE)
```

```{r}
endo_markers <- FetchData(endo_sub, vars.all = c("CD34", "PECAM1", "FLT1", "analysis", "biopsy_site", "cell_id", "sample_name", "patient_id", "res.0.1"))
ggplot(endo_markers, aes(x = res.0.1, y = CD34)) + geom_boxplot(aes(fill = analysis))
ggplot(endo_markers, aes(x = res.0.1, y = PECAM1)) + geom_boxplot(aes(fill = analysis))
ggplot(endo_markers, aes(x = res.0.1, y = FLT1)) + geom_boxplot(aes(fill = analysis))
```


```{r}
fibroblast_sub <- SetAllIdent(fibroblast_sub, id = "res.0.3")
VlnPlot(fibroblast_sub, "TGFB1")
VlnPlot(fibroblast_sub, "TNF")
VlnPlot(fibroblast_sub, "IL6")
```


```{r}
VlnPlot(fibroblast_sub, "SERPINE1")
```



