---
title: "Fibroblasts Subset"
output: html_notebook
---

Libraries
```{r}
library(Seurat)
library(devtools)
library(clustree)
library(tidyverse)
library(gridExtra)
library(ggridges)
library(ggplot2)
library(ggExtra)
library(corrplot)
library(reshape)
```

```{r}
dir <- "/myVolume/scell_lung_adenocarcinoma/"
load(file = paste(dir,"Data_input/NI01_Nonimmune_Seurat_object_annotated.RData", sep=""))
```

Subset fibroblasts
```{r}
fibroblasts <- filter(tiss_nonimmune@meta.data, nonimmune_general_annotation == "Fibroblast")
fibroblast_sub <- SubsetData(tiss_nonimmune, cells.use = fibroblasts$cell_id)
```

Normalize and scale the data
```{r}
fibroblast_sub <- NormalizeData(object = fibroblast_sub,)
fibroblast_sub <- ScaleData(object = fibroblast_sub)
```

Find variable genes
```{r}
fibroblast_sub <- FindVariableGenes(object = fibroblast_sub, do.plot = TRUE, x.high.cutoff = Inf, y.cutoff = 0.5)
```

Perform PCA
```{r}
fibroblast_sub <- RunPCA(object = fibroblast_sub, do.print = FALSE)
fibroblast_sub <- ProjectPCA(object = fibroblast_sub, do.print = FALSE)
```

Visualize top genes in principal components
```{r}
PCHeatmap(object = fibroblast_sub, pc.use = 1:15, cells.use = 100, do.balanced = TRUE, label.columns = FALSE, num.genes = 10)
```

Perform correlation of PCs and metadata fields
```{r}
pca.obj <- fibroblast_sub@dr$pca
pc.coords <- pca.obj@cell.embeddings
df1 <- fibroblast_sub@meta.data[,c("nGene","nReads","percent.ribo")]
df2 <- pc.coords[,c(1:10)]
cordf12 <- cor(df1,df2)
# Make a correlation plot
corrplot(cordf12, method = "number", main="Correlation of PCs and metadata")
```

Also visaulize PC variance
```{r}
#comp.dev <-pca.obj@sdev
PCElbowPlot(object = fibroblast_sub)
```

Choose the number of principal components to use.

```{r}
n.pcs = 20
```

Check clustering stability at given resolution 
```{r}
# Set different resolutions 
res.used <- seq(0.1,1,by=0.2)
# Loop over and perform clustering of different resolutions 
for(i in res.used){
        fibroblast_sub <- FindClusters(object = fibroblast_sub, reduction.type = "pca", dims.use = 1:n.pcs, 
        resolution = i, print.output = 0, save.SNN = TRUE, k.param = 30, force.recalc = T)
        }
# Make plot 
clus.tree.out <- clustree(fibroblast_sub) +
    theme(legend.position = "bottom") + 
    scale_color_brewer(palette = "Set1") +
    scale_edge_color_continuous(low = "grey80", high = "red")

# Plot 
clus.tree.out
```

Set resolution and perform clustering
```{r}
res.used <- 0.3
fibroblast_sub <- FindClusters(object = fibroblast_sub, reduction.type = "pca", dims.use = 1:n.pcs, 
    resolution = res.used, print.output = 0, save.SNN = TRUE, k.param = 30, force.recalc = T)
```

Perform  tSNE
```{r}
fibroblast_sub <- RunTSNE(object = fibroblast_sub, dims.use = 1:n.pcs, seed.use = 10, perplexity=30)
```

Visualize TSNE colored by cluster
```{r}
TSNEPlot(object = fibroblast_sub, do.label = T)
TSNEPlot(object = fibroblast_sub, group.by = "analysis")
TSNEPlot(object = fibroblast_sub, group.by = "biopsy_site")
```

Fraction of PD
```{r}
tab.1 <- prop.table(table(fibroblast_sub@meta.data$res.0.3, fibroblast_sub@meta.data$analysis), margin = 1)
tab.1 <- melt(tab.1)
tab.1$Var.1 <- as.factor(tab.1$Var.1)
fraction.plot <- ggplot() + geom_bar(aes(y = value, x = Var.1, fill = Var.2), data = tab.1,
                           stat="identity", position='dodge') + coord_flip()
fraction.plot

tab.2 <- prop.table(table(fibroblast_sub@meta.data$res.0.3, fibroblast_sub@meta.data$patient_id), margin = 1)
tab.2 <- melt(tab.2)
tab.2$Var.1 <- as.factor(tab.2$Var.1)
fraction.plot1 <- ggplot() + geom_bar(aes(y = value, x = Var.1, fill = Var.2), data = tab.2,
                           stat="identity") + coord_flip()
fraction.plot1
```

Cluster Occ by patient
```{r}
# Calculate mixing score for each cluster 
tab.3 <- table(fibroblast_sub@meta.data$patient_id, fibroblast_sub@meta.data$res.0.3)
occ_score <- apply(tab.3, 2, max)/colSums(tab.3)
# Plot mixing score
par(las=3);barplot(sort(occ_score), xlab="Cluster", ylab="Patient max Ncells/Total cells", ylim=c(0,1));abline(h=0.7, col="red")
```

Create a dendrogram of all fibroblast clusters
```{r}
# Export data from Seurat object and normalize
data.raw <- fibroblast_sub@raw.data
dim(data.raw)

#r Export metadata from Seurat object
metadata <- fibroblast_sub@meta.data
dim(metadata)

# Subset data and metadata to contain same cells and in the same order. Normalize data
data.raw <- as.matrix(data.raw[,row.names(metadata)])
# Remove non-expressed genes 
data.raw <- data.raw[names(which(rowSums(data.raw)!=0)),]
# Normalize
data.norm <- apply(X=data.raw, MARGIN=2, function(x) log2((((x/sum(x))*1000000)+1)) )
dim(data.norm)

# Overdispersion
sel.by.cv <- function(counts.nodups) {
  require(statmod)# library(pcaMethods); library(fastICA)
  ed <- counts.nodups*1000000/colSums(counts.nodups) # Second pass, no duplicates
  #ed <- counts.nodups
  means <- rowMeans(ed)
  vars <- apply(ed,1,var)
  cv2 <- vars/means^2
  winsorize <- function (x, fraction=0.05) {
    if(length(fraction) != 1 || fraction < 0 ||
       fraction > 0.5) {
      stop("bad value for 'fraction'")
    }
    lim <- quantile(x, probs=c(fraction, 1-fraction))
    x[ x < lim[1] ] <- lim[1]
    x[ x > lim[2] ] <- lim[2]
    x
  }
  wed <- t(apply(ed, 1, winsorize, fraction=2/ncol(ed))) 
  means = rowMeans(wed); vars = apply(wed,1,var); cv2 <- vars/means^2
  useForFit <- means >= unname( quantile( means[ which( cv2 > .3 ) ], .95 ) ) 
  fit <- glmgam.fit( cbind( a0 = 1, a1tilde = 1/means[useForFit] ),cv2[useForFit] )
  xg <- exp(seq( min(log(means[means>0])), max(log(means), na.rm=T), length.out=1000 ))
  afit <- fit$coef["a1tilde"]/means+fit$coef["a0"]
  vfit <- fit$coef["a1tilde"]/xg+fit$coef["a0"]
  varFitRatio <- vars/(afit*means^2)
  varorder <- order(varFitRatio,decreasing=T)
  return(varorder)
}
# OD analysis
o <- sel.by.cv(data.raw)

# select top OD genes (1000 genes)

data.norm.top <- data.norm[o[1:1000],]
dim(data.norm.top)
# Remove cells with no expression of any of the overdispersed genes 
cells <- names(which(colSums(data.norm.top)!=0))
metadata <- metadata[cells,]
data.raw <- data.raw[,row.names(metadata)]
data.norm <- data.norm[,row.names(metadata)]
data.norm.top <- data.norm.top[,row.names(metadata)]

#Calculate distance
dist.cor <- as.dist(1-abs(cor(data.norm.top)))

# Create a cluster distance matrix

# Rename the res column to cluster
mat_clus_dis <- matrix(nrow=length(unique(metadata$res.0.3)), 
                       ncol=length(unique(metadata$res.0.3)))
colnames(mat_clus_dis) <- paste("Cluster_", 0:(length(unique(metadata$res.0.3))-1), sep="")
row.names(mat_clus_dis) <- paste("Cluster_", 0:(length(unique(metadata$res.0.3))-1), sep="")
# 
diag(mat_clus_dis) <- 0
# 
clusters <- 0:max(as.numeric(metadata$res.0.3))
for(i in 1:nrow(mat_clus_dis)){
  cells <- row.names(metadata)[which(metadata$res.0.3==clusters[i])]
  for(j in 1:ncol(mat_clus_dis)){
  no_cells <- row.names(metadata)[which(metadata$res.0.3==clusters[j])]
  mat.dist.temp <- as.matrix(dist.cor)[cells,no_cells]
  mat_clus_dis[i,j] <-  mean(mat.dist.temp)
  }
}
# Convert to distance object
dist.clus <- as.dist(mat_clus_dis)
```

Plot and save Dendrogram
```{r Hierarchical clusterting}
# Convert to clustering object
tree.clus <- hclust(dist.clus, "ward.D2")
# Plot 
plot(tree.clus)
```

Fibroblast Signatures
```{r}
# Typical CAF markers
DoHeatmap(fibroblast_sub, genes.use = c("PDGFRA", "PDGFRB", "FAP", "ACTA2", "PDPN", "VIM"), slim.col.label = TRUE, use.scaled = TRUE)

# myofibroblasts
myofib <- FetchData(fibroblast_sub, vars.all = c("ACTA2", "MYH11", "TAGLN", "analysis", "biopsy_site", "cell_id", "sample_name", "patient_id", "res.0.3"))
myofib$myofib_mean <- rowMeans(myofib[1:3])
ggplot(myofib, aes(x = res.0.3, y = myofib_mean)) + geom_boxplot(outlier.shape = NA) + 
  geom_jitter(aes(color = analysis), alpha = 1/6) + ggtitle("myofib sig")
```


```{r}
fibro_clus_markers <- FindAllMarkers(fibroblast_sub)
fibro_top_10 <- fibro_clus_markers %>% group_by(cluster) %>% top_n(5, avg_logFC)
DoHeatmap(fibroblast_sub, genes.use = fibro_top_10$gene, slim.col.label = TRUE, use.scaled = FALSE)
```

Cluster 8 of fibroblasts == sinusoidal endothelial cells #PMID: 10910247
```{r}
VlnPlot(fibroblast_sub, "ENG")
VlnPlot(fibroblast_sub, "VWF")
VlnPlot(fibroblast_sub, c("FCN3", "FCN2"))
```

synovial like fibroblasts == cluster 7 (from pleural resection TH205/LT_S34)
```{r}
VlnPlot(fibroblast_sub, "HAS1")
VlnPlot(fibroblast_sub, "PRG4")
VlnPlot(fibroblast_sub, "WNT4") # PMID: 11832423
VlnPlot(fibroblast_sub, c("CFB", "CFI"))
```

matrix fibroblast markers
```{r}
VlnPlot(fibroblast_sub, "COL1A1")
VlnPlot(fibroblast_sub, "COL13A1")
VlnPlot(fibroblast_sub, "COL14A1")
VlnPlot(fibroblast_sub, "ELN")
VlnPlot(fibroblast_sub, "FN1")
VlnPlot(fibroblast_sub, "VCAM1")
VlnPlot(fibroblast_sub, "FGF10")
VlnPlot(fibroblast_sub, "TCF21")
```

lipofibroblasts
```{r}
VlnPlot(fibroblast_sub, "PLIN2")
VlnPlot(fibroblast_sub, "PPARG")
VlnPlot(fibroblast_sub, "FABP1")
VlnPlot(fibroblast_sub, "FABP5")
VlnPlot(fibroblast_sub, "LPL")
VlnPlot(fibroblast_sub, "KRT79")
VlnPlot(fibroblast_sub, "MRC1")
```


Find programs of interest 
```{r}
MMPs <- grep(pattern = "MMP*", x = rownames(fibroblast_sub@raw.data))
MMPs1 <- rownames(fibroblast_sub@raw.data)[MMPs]
MMPs2 <- MMPs1[29:54]
MMPs3 <- FetchData(fibroblast_sub, vars.all = c(MMPs2, "analysis", "biopsy_site", "cell_id", "sample_name", "patient_id", "res.0.3"))
MMPs3$MMP_mean <- rowMeans(MMPs3[1:26])
DoHeatmap(fibroblast_sub, genes.use = MMPs2, slim.col.label = TRUE, use.scaled = FALSE)
ggplot(MMPs3, aes(x = res.0.3, y = MMP_mean)) + geom_boxplot(outlier.shape = NA) +
  geom_jitter(aes(color = analysis), alpha = 1/6)

COLs <- grep(pattern = "COL*", x = rownames(fibroblast_sub@raw.data))
COLs1 <- rownames(fibroblast_sub@raw.data)[COLs]
COLs2 <- COLs1[44:93]
COLs3 <- FetchData(fibroblast_sub, vars.all = c(COLs2, "analysis", "biopsy_site", "cell_id", "sample_name", "patient_id", "res.0.3"))
COLs3$COL_mean <- rowMeans(COLs3[1:50])
DoHeatmap(fibroblast_sub, genes.use = COLs2, slim.col.label = TRUE)
ggplot(COLs3, aes(x = res.0.3, y = COL_mean)) + geom_boxplot(outlier.shape = NA) + 
  geom_jitter(aes(color = analysis), alpha = 1/6)

CXCLS <- grep(pattern = "CXCL*", x = rownames(fibroblast_sub@raw.data))
CXCLS1 <- rownames(fibroblast_sub@raw.data)[CXCLS]
DoHeatmap(fibroblast_sub, genes.use = CXCLS1, slim.col.label = TRUE, use.scaled = FALSE)

Wnts <- grep(pattern = "WNT*", x = rownames(fibroblast_sub@raw.data))
Wnts1 <- rownames(fibroblast_sub@raw.data)[Wnts]
Wnts2 <- Wnts1[5:23]
DoHeatmap(fibroblast_sub, genes.use = Wnts2, slim.col.label = TRUE, use.scaled = TRUE)



# plasminogen pathway genes
DoHeatmap(fibroblast_sub, genes.use = c("PLAT", "PLAU", "ANXA2", "PLAUR", "SERPINE1", "SERPINB1"), slim.col.label = TRUE, use.scaled = FALSE)
VlnPlot(fibroblast_sub, c("SERPINE1", "SERPINB1"))
```

Fibroblast Signatures
```{r}
clus_1 <- FetchData(fibroblast_sub, vars.all = c("CTHRC1", "VCAN", "SULF1", "COL10A1","POSTN", "SFRP4", "HTRA3", "ASPN", "analysis", "biopsy_site", "cell_id", "sample_name", "patient_id", "res.0.3"))
clus_1$clus_1mean <- rowMeans(clus_1[1:8])
DoHeatmap(fibroblast_sub, genes.use = colnames(clus_1[1:8]), slim.col.label = TRUE)
ggplot(clus_1, aes(x = res.0.3, y = clus_1mean)) + geom_boxplot(outlier.shape = NA) + 
  geom_jitter(aes(color = analysis), alpha = 1/6) + ggtitle("clus 1")

clus_2 <- FetchData(fibroblast_sub, vars.all = c("COX4I2", "HIGD1B", "RGS5", "GJA4", "NDUFA4L2", "PDGFRB", "COL4A1", "PTP4A3", "COL4A2", "LHFP", "PPP1R14A", "EGFL6", "NOTCH3", "PTN", "COL18A1", "ACTG2", "analysis", "biopsy_site", "cell_id", "sample_name", "patient_id", "res.0.3"))
clus_2$clus_2mean <- rowMeans(clus_2[1:8])
# DoHeatmap(fibroblast_sub, genes.use = )
ggplot(clus_2, aes(x = res.0.3, y = clus_2mean)) + geom_boxplot(outlier.shape = NA) + 
  geom_jitter(aes(color = analysis), alpha = 1/6) + ggtitle("clus 2")

clus_4 <- FetchData(fibroblast_sub, vars.all = c("PLA2G2A", "SFRP2", "analysis", "biopsy_site", "cell_id", "sample_name", "patient_id", "res.0.3"))
clus_4$clus_4mean <- rowMeans(clus_2[1:2])
ggplot(clus_4, aes(x = res.0.3, y = clus_4mean)) + geom_boxplot(outlier.shape = NA) + 
  geom_jitter(aes(color = analysis), alpha = 1/6) + ggtitle("clus 4")

clus_5 <- FetchData(fibroblast_sub, vars.all = c("MMP3", "SERPINE2", "analysis", "biopsy_site", "cell_id", "sample_name", "patient_id", "res.0.3"))
clus_5$clus_5mean <- rowMeans(clus_2[1:2])
ggplot(clus_5, aes(x = res.0.3, y = clus_5mean)) + geom_boxplot(outlier.shape = NA) + 
  geom_jitter(aes(color = analysis), alpha = 1/6) + ggtitle("clus 5")

clus_6 <- FetchData(fibroblast_sub, vars.all = c("GPC3", "MFAP4", "A2M", "CYR61", "MACF1", "GPX3", "TIMP3", "CFD", "FIGF", "LTBP4", "SEPP1", "ADH1B", "CTGF", "PTGDS", "SCN7A", "PRELP", "MAMDC2", "FHL1", "DST", "AOC3", "INMT", "NPNT", "ELN", "USP53", "G0S2", "FMO2", "analysis", "biopsy_site", "cell_id", "sample_name", "patient_id", "res.0.3"))
clus_6$clus_6mean <- rowMeans(clus_2[1:16])
ggplot(clus_6, aes(x = res.0.3, y = clus_6mean)) + geom_boxplot(outlier.shape = NA) + 
  geom_jitter(aes(color = analysis), alpha = 1/6) + ggtitle("clus 6")

clus_7 <- FetchData(fibroblast_sub, vars.all = c("ALDH1A3", "C3", "CCL2", "SOD2", "TNFRSF12A", "SLC20A1", "NFKBIA", "PTX3", "DKK1", "SERPINB2", "analysis", "biopsy_site", "cell_id", "sample_name", "patient_id", "res.0.3"))
clus_7$clus_7mean <- rowMeans(clus_7[1:10])
ggplot(clus_7, aes(x = res.0.3, y = clus_7mean)) + geom_boxplot(outlier.shape = NA) + 
  geom_jitter(aes(color = analysis), alpha = 1/6) + ggtitle("clus 7")

DoHeatmap(object = fibroblast_sub, genes.use = c("MRC1", "CD164", "IL18", "CD9", "TGM2"), use.scaled = FALSE, slim.col.label = TRUE)
```









