---
title: "EGFR vs ALK"
output: html_notebook
---
```{r}
library(Seurat)
library(ggplot2)
library(tidyverse)
library(gridExtra)
library(devtools)
library(ggsignif)
library(ggpubr)
library(viridis)
library(plotly)
library(ggridges)
library(reshape)
library(gridExtra)
library(ggrepel)
library(ggExtra)
```

Read in tumor object
```{r}
rm(list=ls())
dir <- "/home/ubuntu/scell_lung_adenocarcinoma/"
load(file = paste(dir, "Data_input/objects/NI04_tumor_seurat_object.RData", sep = ""))
```

```{r}
table(tiss_subset_tumor2@meta.data$driver_gene, tiss_subset_tumor2@meta.data$analysis)
```

Subset to EGFR and ALK
```{r}
cells.use <- filter(tiss_subset_tumor2@meta.data, driver_gene == 'ALK' | driver_gene == 'EGFR')
cells.use1 <- filter(cells.use, sample_name != "LT_S41")

EGFR_ALK <- subset(tiss_subset_tumor2, cells = cells.use1$cell_id)

table(EGFR_ALK$driver_gene, EGFR_ALK$analysis)
```

Make sure all data is scaled
```{r}
EGFR_ALK <- ScaleData(object = EGFR_ALK, features = rownames(EGFR_ALK))
```

AT2
```{r}
AT2_genes <- c("SFTPC", "SFTPB", "SFTPD", "PGC", "CLDN18", "AQP4", "SCGB3A1", "ABCA3", "GATA6", "NKX2-1", "SFTA3", "IGFBP2", "HOPX", "NAPSA", "FOXA2", "AGER", "LAMP1")

AT2 <- FetchData(EGFR_ALK, c(AT2_genes, 'nFeature_RNA', 'nCount_RNA', 'analysis', 'patient_id', 'sample_name', 'biopsy_site', 'cell_id', 'driver_gene'))

AT2$AT2_diff_mean <- rowMeans(AT2[c(AT2_genes)], na.rm=TRUE)

# plot
AT2_p <- ggplot(AT2, aes(x = analysis, y = AT2_diff_mean, fill = analysis)) + geom_boxplot() + guides(colour = FALSE, fill = FALSE) + xlab("Group") + ylab("AT2 Differentiation Signature Expression per Group") + ggtitle("AT2 Differentiation Signature Expression per Group") + geom_signif(comparisons = list(c("grouped_pd", "grouped_pr")), map_signif_level=TRUE, y_position = 3.5) + geom_signif(comparisons = list(c("grouped_pd", "naive")), map_signif_level=TRUE, y_position = 4.5) + geom_signif(comparisons = list(c("grouped_pr", "naive")), map_signif_level=TRUE, y_position = 4) + scale_x_discrete(limits=c("naive", "grouped_pr", "grouped_pd")) + facet_grid(~driver_gene) + theme_bw()
AT2_p
```

AT2
```{r}
Plasminogen_genes <- c('ANXA2', 'PLAT', 'PLAU', 'PLAUR', 'SERPINE1')

Plasminogen <- FetchData(EGFR_ALK, c(Plasminogen_genes, 'nFeature_RNA', 'nCount_RNA', 'analysis', 'patient_id', 'sample_name', 'biopsy_site', 'cell_id', 'driver_gene'))

Plasminogen$Plasminogen_activating_mean <- rowMeans(Plasminogen[c("ANXA2", "PLAT", "PLAU", "PLAUR")], na.rm=TRUE)

# plot
Plasminogen_p <- ggplot(Plasminogen, aes(x = analysis, y = Plasminogen_activating_mean, fill = analysis)) + geom_boxplot() + guides(colour = FALSE, fill = FALSE) + xlab("Group") + ylab("Plasminogen Differentiation Signature Expression per Group") + ggtitle("Plasminogen Differentiation Signature Expression per Group") + geom_signif(comparisons = list(c("grouped_pd", "grouped_pr")), map_signif_level=TRUE, y_position = 3.5) + geom_signif(comparisons = list(c("grouped_pd", "naive")), map_signif_level=TRUE, y_position = 4.5) + geom_signif(comparisons = list(c("grouped_pr", "naive")), map_signif_level=TRUE, y_position = 4) + scale_x_discrete(limits=c("naive", "grouped_pr", "grouped_pd")) + facet_grid(~driver_gene)

Plasminogen_p1 <- ggplot(Plasminogen, aes(x = analysis, y = SERPINE1, fill = analysis)) + geom_boxplot() + guides(colour = FALSE, fill = FALSE) + xlab("Group") + ylab("SERPINE1 Expression per Group") + ggtitle("SERPINE1 Expression per Group") + geom_signif(comparisons = list(c("grouped_pd", "grouped_pr")), map_signif_level=TRUE, y_position = 3.5) + geom_signif(comparisons = list(c("grouped_pd", "naive")), map_signif_level=TRUE, y_position = 4.5) + geom_signif(comparisons = list(c("grouped_pr", "naive")), map_signif_level=TRUE, y_position = 4) + scale_x_discrete(limits=c("naive", "grouped_pr", "grouped_pd")) + facet_grid(~driver_gene)
Plasminogen_p 
Plasminogen_p1
```


Kynurenine Pathway
```{r}
Kynurenine_genes <- c('IDO1', 'KYNU')

Kynurenine <- FetchData(EGFR_ALK, c(Kynurenine_genes, 'nFeature_RNA', 'nCount_RNA', 'analysis', 'patient_id', 'sample_name', 'biopsy_site', 'cell_id', 'driver_gene'))

Kynurenine$Kynurenine_diff_mean <- rowMeans(Kynurenine[c(Kynurenine_genes)], na.rm=TRUE)

# plot
Kynurenine_p <- ggplot(Kynurenine, aes(x = analysis, y = Kynurenine_diff_mean, fill = analysis)) + geom_boxplot() + guides(colour = FALSE, fill = FALSE) + xlab("Group") + ylab("Kynurenine Differentiation Signature Expression per Group") + ggtitle("Kynurenine Differentiation Signature Expression per Group") + geom_signif(comparisons = list(c("grouped_pd", "grouped_pr")), map_signif_level=TRUE, y_position = 3.5) + geom_signif(comparisons = list(c("grouped_pd", "naive")), map_signif_level=TRUE, y_position = 4.5) + geom_signif(comparisons = list(c("grouped_pr", "naive")), map_signif_level=TRUE, y_position = 4) + scale_x_discrete(limits=c("naive", "grouped_pr", "grouped_pd")) + facet_grid(~driver_gene)
Kynurenine_p
```

Gap Junction Signatures
```{r}
GJB_genes <- c('GJB3', 'GJB2','GJB5')

GJB <- FetchData(EGFR_ALK, c(GJB_genes, 'nFeature_RNA', 'nCount_RNA', 'analysis', 'patient_id', 'sample_name', 'biopsy_site', 'cell_id', 'driver_gene'))

GJB$GJB_diff_mean <- rowMeans(GJB[c(GJB_genes)], na.rm=TRUE)

# plot
GJB_p <- ggplot(GJB, aes(x = analysis, y = GJB_diff_mean, fill = analysis)) + geom_boxplot() + guides(colour = FALSE, fill = FALSE) + xlab("Group") + ylab("GJB Differentiation Signature Expression per Group") + ggtitle("GJB Differentiation Signature Expression per Group") + geom_signif(comparisons = list(c("grouped_pd", "grouped_pr")), map_signif_level=TRUE, y_position = 3.5) + geom_signif(comparisons = list(c("grouped_pd", "naive")), map_signif_level=TRUE, y_position = 4.5) + geom_signif(comparisons = list(c("grouped_pr", "naive")), map_signif_level=TRUE, y_position = 4) + scale_x_discrete(limits=c("naive", "grouped_pr", "grouped_pd")) + facet_grid(~driver_gene)
GJB_p
```

save all
```{r}
ggsave(AT2_p, filename = paste(dir,"plot_out/NI16/AT2_p.pdf", sep = ""))
ggsave(Plasminogen_p, filename = paste(dir,"plot_out/NI16/Plasminogen_act.pdf", sep = ""))
ggsave(Plasminogen_p1, filename = paste(dir,"plot_out/NI16/SERPINE1.pdf", sep = ""))
ggsave(Kynurenine_p, filename = paste(dir,"plot_out/NI16/Kynurenine_p.pdf", sep = ""))
ggsave(GJB_p, filename = paste(dir,"plot_out/NI16/GJB_p.pdf", sep = ""))
```

ALK ONLY ANALYSIS
```{r}
cells.use <- filter(tiss_subset_tumor2@meta.data, driver_gene == 'ALK')

ALK <- subset(tiss_subset_tumor2, cells = cells.use$cell_id)
```

ALK samples and treatment groups
```{r}
table(ALK$sample_name, ALK$analysis)
table(ALK$patient_id, ALK$analysis)
```

Drop the grouped_pr sample as it is only one sample
```{r}
cells.use <- filter(tiss_subset_tumor2@meta.data, analysis != 'grouped_pr')

ALK <- subset(ALK, cells = cells.use$cell_id)
table(ALK$patient_id, ALK$analysis)
```

Make sure all data is scaled
```{r}
ALK <- ScaleData(object = ALK, features = rownames(ALK))
```

AT2
```{r}
AT2_genes <- c("SFTPC", "SFTPB", "SFTPD", "PGC", "CLDN18", "AQP4", "SCGB3A1", "ABCA3", "GATA6", "NKX2-1", "SFTA3", "IGFBP2", "HOPX", "NAPSA", "FOXA2", "AGER", "LAMP1")

AT2 <- FetchData(ALK, c(AT2_genes, 'nFeature_RNA', 'nCount_RNA', 'analysis', 'patient_id', 'sample_name', 'biopsy_site', 'cell_id', 'driver_gene'))

AT2$AT2_diff_mean <- rowMeans(AT2[c(AT2_genes)], na.rm=TRUE)

# plot
AT2_p <- ggplot(AT2, aes(x = analysis, y = AT2_diff_mean, fill = analysis)) + geom_boxplot() + guides(colour = FALSE, fill = FALSE) + xlab("Group") + ylab("AT2 Differentiation Signature Expression per Group") + ggtitle("AT2 Differentiation Signature Expression per Group") + geom_signif(comparisons = list(c("naive", "grouped_pd")), map_signif_level=TRUE, y_position = 1.5) + scale_x_discrete(limits=c("naive", "grouped_pd"))
AT2_p
```

AT2
```{r}
Plasminogen_genes <- c('ANXA2', 'PLAT', 'PLAU', 'PLAUR', 'SERPINE1')

Plasminogen <- FetchData(ALK, c(Plasminogen_genes, 'nFeature_RNA', 'nCount_RNA', 'analysis', 'patient_id', 'sample_name', 'biopsy_site', 'cell_id', 'driver_gene'))

Plasminogen$Plasminogen_activating_mean <- rowMeans(Plasminogen[c("ANXA2", "PLAT", "PLAU", "PLAUR")], na.rm=TRUE)

# plot
Plasminogen_p <- ggplot(Plasminogen, aes(x = analysis, y = Plasminogen_activating_mean, fill = analysis)) + geom_boxplot() + guides(colour = FALSE, fill = FALSE) + xlab("Group") + ylab("Plasminogen Differentiation Signature Expression per Group") + ggtitle("Plasminogen Differentiation Signature Expression per Group") + geom_signif(comparisons = list(c("naive", "grouped_pd")), map_signif_level=TRUE, y_position = 4) +  scale_x_discrete(limits=c("naive", "grouped_pd"))

Plasminogen_p1 <- ggplot(Plasminogen, aes(x = analysis, y = SERPINE1, fill = analysis)) + geom_boxplot() + guides(colour = FALSE, fill = FALSE) + xlab("Group") + ylab("SERPINE1 Expression per Group") + ggtitle("SERPINE1 Expression per Group") + geom_signif(comparisons = list(c("naive", "grouped_pd")), map_signif_level=TRUE, y_position = 5) + scale_x_discrete(limits=c("naive","grouped_pd"))
Plasminogen_p 
Plasminogen_p1
```


Kynurenine Pathway
```{r}
Kynurenine_genes <- c('IDO1', 'KYNU')

Kynurenine <- FetchData(ALK, c(Kynurenine_genes, 'nFeature_RNA', 'nCount_RNA', 'analysis', 'patient_id', 'sample_name', 'biopsy_site', 'cell_id', 'driver_gene'))

Kynurenine$Kynurenine_diff_mean <- rowMeans(Kynurenine[c(Kynurenine_genes)], na.rm=TRUE)

# plot
Kynurenine_p <- ggplot(Kynurenine, aes(x = analysis, y = Kynurenine_diff_mean, fill = analysis)) + geom_boxplot() + guides(colour = FALSE, fill = FALSE) + xlab("Group") + ylab("Kynurenine Differentiation Signature Expression per Group") + ggtitle("Kynurenine Differentiation Signature Expression per Group") + geom_signif(comparisons = list(c("naive", "grouped_pd")), map_signif_level=TRUE, y_position = 4) + scale_x_discrete(limits=c("naive", "grouped_pd"))
Kynurenine_p
```

Gap Junction Signatures
```{r}
GJB_genes <- c('GJB3', 'GJB2','GJB5')

GJB <- FetchData(ALK, c(GJB_genes, 'nFeature_RNA', 'nCount_RNA', 'analysis', 'patient_id', 'sample_name', 'biopsy_site', 'cell_id', 'driver_gene'))

GJB$GJB_diff_mean <- rowMeans(GJB[c(GJB_genes)], na.rm=TRUE)

# plot
GJB_p <- ggplot(GJB, aes(x = analysis, y = GJB_diff_mean, fill = analysis)) + geom_boxplot() + guides(colour = FALSE, fill = FALSE) + xlab("Group") + ylab("GJB Differentiation Signature Expression per Group") + ggtitle("GJB Differentiation Signature Expression per Group") + geom_signif(comparisons = list(c("naive", "grouped_pd")), map_signif_level=TRUE, y_position = 2.5) + scale_x_discrete(limits=c("naive","grouped_pd"))
GJB_p
```

save all
```{r}
ggsave(AT2_p, filename = paste(dir,"plot_out/NI16/AT2_p_ALK.pdf", sep = ""))
ggsave(Plasminogen_p, filename = paste(dir,"plot_out/NI16/Plasminogen_act_ALK.pdf", sep = ""))
ggsave(Plasminogen_p1, filename = paste(dir,"plot_out/NI16/SERPINE1_ALK.pdf", sep = ""))
ggsave(Kynurenine_p, filename = paste(dir,"plot_out/NI16/Kynurenine_p_ALK.pdf", sep = ""))
ggsave(GJB_p, filename = paste(dir,"plot_out/NI16/GJB_p_ALK.pdf", sep = ""))
```

EGFR ONLY ANALYSIS

```{r}
cells.use <- filter(tiss_subset_tumor2@meta.data, driver_gene == 'EGFR')

EGFR <- subset(tiss_subset_tumor2, cells = cells.use$cell_id)
```

EGFR samples and treatment groups
```{r}
table(EGFR$sample_name, EGFR$analysis)
table(EGFR$patient_id, EGFR$analysis)
```

Make sure all data is scaled
```{r}
EGFR <- ScaleData(object = EGFR, features = rownames(EGFR))
```

AT2
```{r}
AT2_genes <- c("SFTPC", "SFTPB", "SFTPD", "PGC", "CLDN18", "AQP4", "SCGB3A1", "ABCA3", "GATA6", "NKX2-1", "SFTA3", "IGFBP2", "HOPX", "NAPSA", "FOXA2", "AGER", "LAMP1")

AT2 <- FetchData(EGFR, c(AT2_genes, 'nFeature_RNA', 'nCount_RNA', 'analysis', 'patient_id', 'sample_name', 'biopsy_site', 'cell_id', 'driver_gene'))

AT2$AT2_diff_mean <- rowMeans(AT2[c(AT2_genes)], na.rm=TRUE)

# plot
AT2_p <- ggplot(AT2, aes(x = analysis, y = AT2_diff_mean, fill = analysis)) + geom_boxplot() + guides(colour = FALSE, fill = FALSE) + xlab("Group") + ylab("AT2 Differentiation Signature Expression per Group") + ggtitle("AT2 Differentiation Signature Expression per Group") + geom_signif(comparisons = list(c("grouped_pd", "grouped_pr")), map_signif_level=TRUE, y_position = 3.5) + geom_signif(comparisons = list(c("grouped_pd", "naive")), map_signif_level=TRUE, y_position = 4.5) + geom_signif(comparisons = list(c("grouped_pr", "naive")), map_signif_level=TRUE, y_position = 4) + scale_x_discrete(limits=c("naive", "grouped_pr", "grouped_pd"))
AT2_p
```

AT2
```{r}
Plasminogen_genes <- c('ANXA2', 'PLAT', 'PLAU', 'PLAUR', 'SERPINE1')

Plasminogen <- FetchData(EGFR, c(Plasminogen_genes, 'nFeature_RNA', 'nCount_RNA', 'analysis', 'patient_id', 'sample_name', 'biopsy_site', 'cell_id', 'driver_gene'))

Plasminogen$Plasminogen_activating_mean <- rowMeans(Plasminogen[c("ANXA2", "PLAT", "PLAU", "PLAUR")], na.rm=TRUE)

# plot
Plasminogen_p <- ggplot(Plasminogen, aes(x = analysis, y = Plasminogen_activating_mean, fill = analysis)) + geom_boxplot() + guides(colour = FALSE, fill = FALSE) + xlab("Group") + ylab("Plasminogen Differentiation Signature Expression per Group") + ggtitle("Plasminogen Differentiation Signature Expression per Group") + geom_signif(comparisons = list(c("grouped_pd", "grouped_pr")), map_signif_level=TRUE, y_position = 3.5) + geom_signif(comparisons = list(c("grouped_pd", "naive")), map_signif_level=TRUE, y_position = 4.5) + geom_signif(comparisons = list(c("grouped_pr", "naive")), map_signif_level=TRUE, y_position = 4) + scale_x_discrete(limits=c("naive", "grouped_pr", "grouped_pd"))

Plasminogen_p1 <- ggplot(Plasminogen, aes(x = analysis, y = SERPINE1, fill = analysis)) + geom_boxplot() + guides(colour = FALSE, fill = FALSE) + xlab("Group") + ylab("SERPINE1 Expression per Group") + ggtitle("SERPINE1 Expression per Group") + geom_signif(comparisons = list(c("grouped_pd", "grouped_pr")), map_signif_level=TRUE, y_position = 3.5) + geom_signif(comparisons = list(c("grouped_pd", "naive")), map_signif_level=TRUE, y_position = 4.5) + geom_signif(comparisons = list(c("grouped_pr", "naive")), map_signif_level=TRUE, y_position = 4) + scale_x_discrete(limits=c("naive", "grouped_pr", "grouped_pd"))
Plasminogen_p 
Plasminogen_p1
```


Kynurenine Pathway
```{r}
Kynurenine_genes <- c('IDO1', 'KYNU')

Kynurenine <- FetchData(EGFR, c(Kynurenine_genes, 'nFeature_RNA', 'nCount_RNA', 'analysis', 'patient_id', 'sample_name', 'biopsy_site', 'cell_id', 'driver_gene'))

Kynurenine$Kynurenine_diff_mean <- rowMeans(Kynurenine[c(Kynurenine_genes)], na.rm=TRUE)

# plot
Kynurenine_p <- ggplot(Kynurenine, aes(x = analysis, y = Kynurenine_diff_mean, fill = analysis)) + geom_boxplot() + guides(colour = FALSE, fill = FALSE) + xlab("Group") + ylab("Kynurenine Differentiation Signature Expression per Group") + ggtitle("Kynurenine Differentiation Signature Expression per Group") + geom_signif(comparisons = list(c("grouped_pd", "grouped_pr")), map_signif_level=TRUE, y_position = 3.5) + geom_signif(comparisons = list(c("grouped_pd", "naive")), map_signif_level=TRUE, y_position = 4.5) + geom_signif(comparisons = list(c("grouped_pr", "naive")), map_signif_level=TRUE, y_position = 4) + scale_x_discrete(limits=c("naive", "grouped_pr", "grouped_pd")) + facet_grid(~driver_gene)
Kynurenine_p
```

Gap Junction Signatures
```{r}
GJB_genes <- c('GJB3', 'GJB2','GJB5')

GJB <- FetchData(EGFR, c(GJB_genes, 'nFeature_RNA', 'nCount_RNA', 'analysis', 'patient_id', 'sample_name', 'biopsy_site', 'cell_id', 'driver_gene'))

GJB$GJB_diff_mean <- rowMeans(GJB[c(GJB_genes)], na.rm=TRUE)

# plot
GJB_p <- ggplot(GJB, aes(x = analysis, y = GJB_diff_mean, fill = analysis)) + geom_boxplot() + guides(colour = FALSE, fill = FALSE) + xlab("Group") + ylab("GJB Differentiation Signature Expression per Group") + ggtitle("GJB Differentiation Signature Expression per Group") + geom_signif(comparisons = list(c("grouped_pd", "grouped_pr")), map_signif_level=TRUE, y_position = 3.5) + geom_signif(comparisons = list(c("grouped_pd", "naive")), map_signif_level=TRUE, y_position = 4.5) + geom_signif(comparisons = list(c("grouped_pr", "naive")), map_signif_level=TRUE, y_position = 4) + scale_x_discrete(limits=c("naive", "grouped_pr", "grouped_pd")) + facet_grid(~driver_gene)
GJB_p
```

save all
```{r}
ggsave(AT2_p, filename = paste(dir,"plot_out/NI16/AT2_p_EGFR.pdf", sep = ""))
ggsave(Plasminogen_p, filename = paste(dir,"plot_out/NI16/Plasminogen_act_EGFR.pdf", sep = ""))
ggsave(Plasminogen_p1, filename = paste(dir,"plot_out/NI16/SERPINE1_EGFR.pdf", sep = ""))
ggsave(Kynurenine_p, filename = paste(dir,"plot_out/NI16/Kynurenine_p_EGFR.pdf", sep = ""))
ggsave(GJB_p, filename = paste(dir,"plot_out/NI16/GJB_p_EGFR.pdf", sep = ""))
```


**Do ALK and EGFR Differ? Check between TN and PD**

ALK TN vs PD
```{r}
table(ALK@active.ident)
ALK_TNvsPD <- FindAllMarkers(ALK)

write.csv(x = ALK_TNvsPD, file = paste(dir,"data_out/NI16/ALK_TNvs_PD.csv", sep = ""))
```

EGFR TN vs PD
```{r}
table(EGFR@meta.data$patient_id, EGFR@meta.data$analysis)

cells.use1 <- filter(EGFR@meta.data, patient_id != 'TH185') # take out the TH185
cells.use2 <- filter(tiss_subset_tumor2@meta.data, patient_id == 'TH185') # subset TH185 alone
TH185 <- subset(EGFR, cells = cells.use2$cell_id)
TH185_100 <- TH185@meta.data[sample(1:nrow(TH185@meta.data), 100,
   replace=FALSE),] # subset TH185 to 100 cells
EGFR2 <- subset(tiss_subset_tumor2, cells = c(cells.use1$cell_id, TH185_100$cell_id))

table(EGFR2@meta.data$patient_id, EGFR2@meta.data$analysis)
table(EGFR2@active.ident)

EGFR_TNvsPD <- FindMarkers(EGFR2, ident.1 = "naive", ident.2 = "grouped_pd")
EGFR_TNvsPR <- FindMarkers(EGFR2, ident.1 = "naive", ident.2 = "grouped_pr")
EGFR_PRvsPD <- FindMarkers(EGFR2, ident.1 = "grouped_pr", ident.2 = "grouped_pd")

write.csv(x = EGFR_TNvsPD, file = paste(dir,"data_out/NI16/EGFR_TNvsPD.csv", sep = ""))
write.csv(x = EGFR_TNvsPR, file = paste(dir,"data_out/NI16/EGFR_TNvsPR.csv", sep = ""))
write.csv(x = EGFR_PRvsPD, file = paste(dir,"data_out/NI16/EGFR_PRvsPD.csv", sep = ""))
```


